### 2018-07-12 manuscript.rmd
first commit

---
bibliography: manuscript.bib
csl: systematic-biology.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

## References

Siphonophores are... [@Mackie:1987uy].

### 2018-07-12 manuscript.rmd
added goals

@@
 
+0 -- PHYLOGENY
+0.0 ML ribosomal marker phylogeny constrained by transcriptome tree with BS values at the nodes.
+1 -- DESCRIPTIVE MORPHOLOGY AND EVOLUTIONARY HISTORY
+1.0 Table showing for each species the mean, number of individuals measured, and standard error of every character, ordered by cnidomic index / tentillum size, and/or colored by clade.
+1.05 Plate with all the tentillum diversity.
+1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
+1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy.
+1.3 Table/figures showing the reconstructed ancestral values at the internal nodes of the phylogeny of characters with a supported phylogenetic model of evolution.
+1.4 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
+2 -- COMPARATIVE ANALYSES
+2.0 Confusion matrix table showing PIC_correlations and trait correlation R2 and p-values for each pair of continuous characters.
+Confusion matrix for quantitative and categorical characters GLS.
+pGLS estimation of regression parameters in significantly correlated pairs.
+2.1 Table showing the model parameters for each significant regression.
+2.3 Verbally PCA and phylogenetic PCA/PICVarA_PCA of the characters. Phylomorphospace superimposed to the tip coordinates in PC1--PC2.
+2.4 Table showing normalized rates of evolution for each character BAMM.
+3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing
+3.0 Phylogeny with the tips mapped with the literature dietary associations, and internal nodes showing SIMMAP reconstructed states.
+3.1 Table showing quantitative and categorical characters association effect size with each prey type in the diet.
+3.2 Table showing the dAICc of OU model fitting versus white_noise and BM using reconstructed diets as regimes in a 16spp tree. Evaluate model adequacy of OU fits.
+3.3 Interpret qualitatively the kinematic implications (high speed video) of the different regions of the morphospace.
+
+Story: low dimensionality, cost-driven, dynamic specialization
+
 ## References

### 2018-07-16 manuscript.rmd
incorporating data and initial data wrangling chunks

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+	# Load packages
+	## General
+library(knitr)
+library(tidyverse)
+library(reshape2)
+	## Graphics
+library(FactoMineR)
+library(factoextra)
+	## Biological
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(Rphylip)
+library(arbutus)
+
+	# Configure knitr, see http://yihui.name/knitr/options
+	opts_knit$set(
+	  progress=TRUE,
+	  verbose=TRUE)
+	opts_chunk$set(
+	#  include=FALSE,
+	  cache=TRUE,
+	  echo=FALSE,
+	  message=FALSE
+	 )
+	# Set paths to input data
+	setwd("~/tentilla_morph")
+
+	#Load raw data
+  read.csv("byslide.csv") -> numbers
+  categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+  rownames(categorical) = categorical$Species
+
+  #Polish fields
+  castnumbers = numbers
+  castnumbers[castnumbers=="needDIC"] <- NA
+  castnumbers[castnumbers=="needConfocal"] <- NA
+  castnumbers[castnumbers=="needMature"] <- NA
+  castnumbers[castnumbers=="needReslide"] <- NA
+  castnumbers[castnumbers==-1] <- NA
+  castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
+  castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)
+
+  #Define functions to deal with NAs and decimals
+  mean.na <- function(a){mean(a, na.rm = TRUE)}
+  var.na <- function(a){var(a, na.rm = TRUE)}
+  round3 <- function(a){round(a, 3)}
+
+  #Compute morphometric ratios
+  coiledness = castnumbers$Cnidoband.free.length..um./castnumbers$Cnidoband.length..um.
+  heteroneme_elongation = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.width..um.
+  haploneme_elongation = castnumbers$Haploneme.free.length..um./castnumbers$Haploneme.width..um.
+  desmoneme_elongation = castnumbers$Desmoneme.length..um./castnumbers$Desmoneme.width..um.
+  rhopaloneme_elongation = castnumbers$Rhopaloneme.length..um./castnumbers$Rhopaloneme.width..um.
+  heteroneme_shaft_extension = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.shaft.free.length..um.
+  Heteroneme_to_CB = castnumbers$Heteroneme.free.length..um./(castnumbers$Cnidoband.free.length..um.+0.001)
+  total_heteroneme_volume = castnumbers$Heteroneme.volume..um3.*castnumbers$Heteroneme.number
+  total_haploneme_volume = (castnumbers$Cnidoband.free.length..um./castnumbers$Haploneme.width..um.)*((4*pi/3)*0.5*castnumbers$Haploneme.free.length..um.*((0.5*castnumbers$Haploneme.width..um.)^2))
+  cnidomic_index = log(total_heteroneme_volume + total_haploneme_volume)
+  cnidomic_index[which(is.na(cnidomic_index))] <- log(total_haploneme_volume[which(is.na(cnidomic_index))])
+  cnidomic_index[which(is.na(cnidomic_index))] <- log(castnumbers[which(is.na(cnidomic_index)), "Heteroneme.volume..um3."])
+  cnidomic_index[cnidomic_index==-Inf]<-NA
+    morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index)
+  names(morphometrics)[1:2] = c("slide_id"," Species")
+  castnumbers = data.frame(castnumbers,morphometrics[,c(-1,-2)])
+
+  #logtransform variables which are not normal
+  castlogs = castnumbers
+  non_normal = apply(castnumbers[,c(-1,-2,-3)], 2, shapiro.test) %>% lapply(function(x){x$p.value}) %>% unlist() 
+  non_normal = which(as.vector(non_normal) < 0.05)+3
+  castlogs[,non_normal] <- sapply(castnumbers[,non_normal], log)
+  castlogs[castlogs==-Inf]<-NA
+
+  #Means, varinces, standard errors
+  castmeans <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], mean.na, na.action = na.pass)
+  castmean_logs <- aggregate(. ~  Species, data = castlogs[,c(-1,-3)], mean.na, na.action = na.pass)
+  castvariances <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], FUN = var.na, na.action = na.pass) #[,-2]
+  castvariance_logs <- aggregate(. ~  Species, data = castlogs[,c(-1,-3)], FUN = var.na, na.action = na.pass)
+  castvariances[is.na(castvariances)] <- 0
+  castvariance_logs[is.na(castvariance_logs)] <- 0
+  castN <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], length, na.action = na.pass) 
+  castN = data.frame(castN$Species, rowMeans(castN[,-1])) #[,-2]
+  names(castN) = c("Species", "N_specimens")
+  castSE <- cbind(castvariances$Species, sqrt(castvariances[,-1])/sqrt(castN$N_specimens))
+  castSE_logs <- cbind(castvariance_logs$Species, sqrt(castvariance_logs[,-1])/sqrt(castN[,-1]))
+  names(castSE)[1] <- "Species"
+  names(castSE_logs)[1] <- "Species"
 ```

### 2018-07-16 manuscript.rmd
incorporating trees and diet data

@@
 1 -- DESCRIPTIVE MORPHOLOGY AND EVOLUTIONARY HISTORY
+
+```{r load_trees, include=F}
+#Load tree
+rRNA18S = read.nexus('bipartitions_root.boot10')
+transcriptome = read.tree('ultimatephylo2018.tre')
+#plot.phylo(consensus)
+#is.rooted(consensus)
+#nodelabels()
+rRNA18S = reroot(rRNA18S, 76, 0.001)
+rRNA18S$tip.label = str_replace_all(rRNA18S$tip.label,'_',' ')
+rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma cordiforme"] = "Cordagalma ordinatum"
+rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma sp "] = "Cordagalma ordinatum"
+rRNA18S$tip.label[rRNA18S$tip.label=="Clausophyes ovata"] = "Kephyes ovata"
+rRNA18S$tip.label[rRNA18S$tip.label=="Erenna sp"] = "Erenna sirena"
+rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp"] = "Apolemia lanosa"
+rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp "] = "Apolemia rubriversa"
+rRNA18S$tip.label[rRNA18S$tip.label=="Sphaeronectes gracilis"] = "Sphaeronectes koellikeri"
+rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
+rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
+rRNA18S = drop.tip(rRNA18S, 41:42) #drop outgroups
+rRNA18S = drop.tip(rRNA18S, c(16,31,23,24)) #drop Cordagalma, Clausophyid, Nectopyramis, Nectadamas
+#plot(rRNA18S)
+
+transcriptome$tip.label = str_replace_all(transcriptome$tip.label,'_',' ')
+transcriptome$tip.label[transcriptome$tip.label=="Cordagalma sp"] = "Cordagalma ordinatum"
+transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
+transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
+transcriptome = reroot(transcriptome, 22, 0.001)
+transcriptome = drop.tip(transcriptome, 19:26) #drop outgroups
+#plot(transcriptome)
+
+multitree = list(rRNA18S,transcriptome)
+class(multitree)="multiPhylo"
+STree = superTree(multitree, rooted = T, method = "MRP", start = transcriptome)
+consensus = STree[[2]]
+consensus = drop.tip(consensus, "Physonect sp ")
+consensus = drop.tip(consensus, "Erenna sirena")
+consensus$tip.label[consensus$tip.label=="Physophora gilmeri"] = "Physophora h" ### ARTIFIIAL SUBSTITUTION ###
+consensus = drop.tip(consensus, "Physophora hydrostatica")
+consensus$tip.label[consensus$tip.label=="Physophora h"] = "Physophora hydrostatica"
+consensus$tip.label[consensus$tip.label=="Vogtia pentacantha"] = "Vogtia serrata"
+consensus = drop.tip(consensus, "Rosacea flaccida")
+#plot(consensus)
+
+#Prune quant matrix to tree species
+matrix = castnumbers[which(!is.na(castnumbers$Species)),]
+matrix_logs = castlogs[which(!is.na(castlogs$Species)),]
+sharedspp = matrix$Species[which(matrix$Species %in% consensus$tip.label)]
+sharedmatrix = matrix[which(matrix$Species %in% sharedspp),]
+sharedlogs = matrix_logs[which(matrix$Species %in% sharedspp),]
+sharedmeans = castmeans[which(castmeans$Species %in% sharedspp),]
+sharedmean_logs = castmean_logs[which(castmean_logs$Species %in% sharedspp),]
+sharedvars = castvariances[which(castvariances$Species %in% sharedspp),]
+sharedvar_logs = castvariance_logs[which(castvariance_logs$Species %in% sharedspp),]
+#sharedmeans = solidSPPmeans[which(solidSPPmeans$Species %in% sharedspp),]
+#sharedvars = solidSPPvars[which(solidSPPvars$Species %in% sharedspp),]
+
+#Prune categorical matrix to tree species
+cat_rowNAs = apply(categorical[,-1], 1, function(x) sum(is.na(x)))
+catmatrix = categorical[which(cat_rowNAs<1),] %>% .[,-1]
+sharedspp_cat = rownames(catmatrix)[which(rownames(catmatrix) %in% consensus$tip.label)]
+sharedcategorical = catmatrix[which(rownames(catmatrix) %in% sharedspp_cat),]
+
+#Prune tree to quant matrix species
+nodatatipnames = consensus$tip.label[which(!(consensus$tip.label %in% sharedmatrix$Species))]
+nodatatips = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames)]
+prunedtree = drop.tip(consensus, nodatatips)
+prunedtree$tip.label
+plot(prunedtree)
+ultram = chronos(prunedtree)
+plot(ultram)
+
+##Make the pseudoindividuals tree
+newtree = ultram
+sharedmatrix_plied = sharedmatrix
+sharedmatrix_plied$slide_id = paste(sharedmatrix$slide_id, sharedmatrix$Species, sep = "_")
+for (i in 1:nrow(sharedmatrix_plied)) {
+  pos = which(newtree$tip.label == sharedmatrix_plied$Species[i])
+  print(pos)
+  newtree = bind.tip(newtree, sharedmatrix_plied$slide_id[i], where = pos, edge.length = 0.1)
+  print(newtree$tip.label)
+  newtree$tip.label = str_replace_all(newtree$tip.label,'_',' ')
+}
+inditree = drop.tip(newtree, which(!grepl(".[0-9].*", newtree$tip.label)))
+zerotipTree = inditree
+inditree$edge.length[inditree$edge.length==0] <- 0.0000000001
+shavedtree = inditree
+inditree = chronos(inditree)
+plot(inditree)
+sharedmatrix_plied$slide_id = str_replace_all(sharedmatrix_plied$slide_id,'_',' ')
+sharedmatrix = sharedmatrix_plied[match(sharedmatrix_plied$slide_id, inditree$tip.label),]
+rownames(sharedmatrix) <- 1:nrow(sharedmatrix)
+
+#Prune tree to categorical matrix species
+nodatatipnames_cat = consensus$tip.label[which(!(consensus$tip.label %in% sharedspp_cat))]
+nodatatips_cat = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames_cat)]
+cat_tree = drop.tip(consensus, nodatatips_cat)
+cat_tree$tip.label
+plot(cat_tree)
+ultram_cat = chronos(cat_tree)
+plot(ultram_cat)
+sharedcategorical = sharedcategorical[match(ultram_cat$tip.label, rownames(sharedcategorical)),]
+cprunedmatrix = sharedcategorical[which(rownames(sharedcategorical)%in%rownames(sharedmatrix)),] %>% .[which(sapply(.,function(x) length(unique(x)))>1)]
+sharedbinary = sharedcategorical
+sharedbinary$Haploneme.type = as.character(sharedbinary$Haploneme.type)
+sharedbinary[sharedbinary=="Isorhizas"] = 0
+sharedbinary[sharedbinary=="Anisorhizas"] = 1
+sharedbinary$Haploneme.type = as.numeric(sharedbinary$Haploneme.type)
+sharedbinary$Heteroneme.type = as.character(sharedbinary$Heteroneme.type)
+sharedbinary[sharedbinary=="Stenotele"] = 0
+sharedbinary[sharedbinary=="Microbasic mastigophore"] = 1
+sharedbinary[sharedbinary=="Eurytele"] = NA
+sharedbinary$Heteroneme.type = as.numeric(sharedbinary$Heteroneme.type)
+
+#purely numerics
+Q_sharedmatrix = sharedmatrix[,c(-1,-2,-3)]
+rownames(sharedmeans) = sharedmeans$Species
+Q_sharedmeans = sharedmeans[,-1]
+rownames(sharedvars) = sharedvars$Species
+Q_sharedvars = sharedvars[,-1]
+Q_sharedmean_logs = sharedmean_logs[,-1]
+rownames(Q_sharedmean_logs) = sharedmean_logs$Species
+
+```
+
 1.0 Table showing for each species the mean, number of individuals measured, and standard error of every character, ordered by cnidomic index / tentillum size, and/or colored by clade.
+
+```{r export_table_morph, include=FALSE}
+morphdata = cbind(castN, castmeans[,-1], castSE[,-1])
+morphdata = monrphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
+names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
+write.csv(morphdata, "characterdata.csv")
+```
+
 1.05 Plate with all the tentillum diversity.
@@
 3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing
+
+```{r diet_data, include=F}
+#Retrieve diet info from literature BINARY
+GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5)] %>% .[which(grepl("diet",.$character) & .$state==1),]
+GC$character = factor(GC$character, levels=unique(GC$character))
+GC = GC[which(GC$species %in% sharedmeans$Species),]
+GC = split(GC,GC$character)
+nrowGC = purrr::map(GC,nrow) %>% as.numeric()
+GC = GC[which(nrowGC>2)]
+GC = purrr::map(GC,unique)
+diet= matrix(ncol=length(GC),nrow=length(unique(sharedmeans$Species))) %>% as.data.frame()
+names(diet) = names(GC)
+rownames(diet) = unique(sharedmeans$Species)
+for(E in GC){
+  print(E$species)
+  for(S in E$species){
+    diet[which(rownames(diet) == S),as.character(unique(E$character))] = 1
+  }
+}
+diet[is.na(diet)] <- 0
+diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
+#diet = rbind(diet, c(0,1,0,0,0,0,0,0))
+#rownames(diet)[12] = 'Erenna richardi'
+dprunedmatrix = sharedmeans[which(sharedmeans$Species%in%rownames(diet)),]
+dprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(diet)),]
+dprunedTree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(diet))))
+plot(dprunedTree)
+
+#Retrieve diet info from literature PROPORTION RELATIVE
+quantDiet = read.csv("Qmerged.csv", header = T, sep=',')[,c(2,4,6)]
+PP = quantDiet[which(grepl("Relative",quantDiet$character)),]
+PP$character = factor(PP$character, levels=unique(PP$character))
+PP = PP[which(PP$species %in% sharedmeans$Species),]
+PP = dcast(PP, species~character, value.var = "state", mean)
+PP[is.na(PP)]<-0
+rownames(PP) = PP$species
+PP=PP[,-1]
+#PP = rbind(PP, c(0,100,0,0,0,0,0,0))
+#rownames(PP)[10] = "Erenna richardi"
+Pprunedmatrix=sharedmeans[which(sharedmeans$Species%in%rownames(PP)),]
+Pprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(PP)),]
+Pprunedtree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(PP))))
+plot(Pprunedtree)
+
+#Retrieve copepod prey length from literature
+preylength = quantDiet[which(grepl("prey",quantDiet$character)),] %>% .[,c(1,3)]
+names(preylength) = c("Species","Copepod prey length (mm)")
+PL_pruned_matrix = sharedmeans[which(sharedmeans$Species %in% preylength$Species),] %>% data.frame(preylength[which(preylength$Species %in% sharedmeans$Species),2])
+names(PL_pruned_matrix)[ncol(PL_pruned_matrix)] <- "Copepod prey length (mm)"
+```
+
 3.0 Phylogeny with the tips mapped with the literature dietary associations, and internal nodes showing SIMMAP reconstructed states.

### 2018-07-16 manuscript.rmd
incorporating physignals, AICc, model adequacy, Rphylip

@@
 library(factoextra)
+library(corrplot)
 	## Biological
@@
 1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
+```{r phylosignals}
+phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
+names(phylosignals) = c("K", "P", "Ntaxa")
+for(i in 2:ncol(sharedmean_logs)){
+  CH_I=as.numeric(sharedmean_logs[,i])
+  names(CH_I) = rownames(sharedmean_logs)
+  SE_I = as.numeric(castSE[,i])
+  names(SE_I) = castSE$Species
+  CH_I= CH_I[!is.na(CH_I)]
+  SE_I= SE_I[!is.na(SE_I)]
+  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
+  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
+  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
+  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
+  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
+  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
+  phylosignals[i-1,1] <- PSIG$K
+  phylosignals[i-1,2] <- PSIG$P
+  phylosignals[i-1,3] <- length(CH_I)
+}
+write.csv(phylosignals, "PhylosignalsWSE_log.csv")
+```
+
 1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy.
-1.3 Table/figures showing the reconstructed ancestral values at the internal nodes of the phylogeny of characters with a supported phylogenetic model of evolution.
-1.4 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
+
+```{r fitContinuous}
+#Model support
+  Q_sharedmean_logs$Heteroneme_to_CB[which(Q_sharedmean_logs$Heteroneme_to_CB > 9)] <- NA
+  AICdf = as.data.frame(matrix(ncol=6,nrow=ncol(Q_sharedmean_logs)))
+  colnames(AICdf) = c("Variable", "white_noise", "starBM", "BM", "EB", "OU")
+  for(c in 1:ncol(Q_sharedmean_logs)){
+    startree <- rescale(ultram, "lambda", 0)
+    C = Q_sharedmean_logs[,c]
+    names(C) = rownames(Q_sharedmean_logs)
+    C = C[!is.na(C)]
+    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
+    startree = drop.tip(startree, which(!(startree$tip.label %in% names(C))))
+    Cse = castSE[,c+1]
+    names(Cse) = castSE$Species
+    Cse = Cse[which(names(Cse) %in% names(C))]
+    model_matrix = matrix("NA", nrow = 5, ncol = 3)
+    colnames(model_matrix) = c("aicc","aicc_best","dAICc")
+    row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
+    for(j in 1:dim(model_matrix)[1]){
+      if(j==2){
+        temp_model = fitContinuous(startree, C, model="BM", SE = Cse)$opt
+      }
+      else{
+        temp_model = fitContinuous(Ctree, C, model=row.names(model_matrix)[j], SE = Cse)$opt
+      }
+      model_matrix = apply(model_matrix,2, as.numeric)
+      row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
+      model_matrix[j, "aicc"] <- temp_model$aicc
+    }
+    model_matrix[,"aicc_best"] <- min(model_matrix[,"aicc"])
+    model_matrix[,"dAICc"] <- model_matrix[, "aicc"] - model_matrix[j, "aicc_best"]
+    print(names(Q_sharedmean_logs)[c])
+    string_c <- c(names(Q_sharedmean_logs)[c], model_matrix[,3])
+    names(string_c) = colnames(AICdf)
+    AICdf[c,] <- string_c
+  }
+  AICdf[,2:6] = apply(AICdf[,2:6], 2, as.numeric) %>% apply(2, round3)
+  write.csv(AICdf, "log_model_support.csv")
+
+#Model adequacy
+  worthy_models = AICdf[which(AICdf$white_noise != 0 & AICdf$starBM != 0),]
+  MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
+  names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
+  rownames(MAD) = worthy_models$Variable
+  for(m in 1:nrow(worthy_models)){
+    C = Q_sharedmean_logs[,which(names(Q_sharedmean_logs) == worthy_models$Variable[m])]
+    names(C) = rownames(Q_sharedmean_logs)
+    C = C[!is.na(C)]
+    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
+    C = C[match(Ctree$tip.label, names(C))]
+    class(Ctree)="phylo"
+    FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
+    UTC <- make_unit_tree(FC)
+    picstat_data <- calculate_pic_stat(UTC)
+    sim <- simulate_char_unit(UTC)
+    picstat_sim <- calculate_pic_stat(sim)
+    compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
+  }
+  phy_models = data.frame(worthy_models,MAD)
+  phy_models[,8:13] = apply(phy_models[,8:13], 2,round3)
+```
+1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
+
 2 -- COMPARATIVE ANALYSES
@@
 pGLS estimation of regression parameters in significantly correlated pairs.
+```{r character_correlations, include=FALSE}
+C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
+Cspecies = C$Species %>% as.character()
+C = as.matrix(C[,-1])
+rownames(C) = Cspecies
+Ctree = drop.tip(ultram,which(!(ultram$tip.label %in% rownames(C))))
+class(Ctree) = "phylo"
+PICi = Rcontrast(Ctree, C, path="phylip-3.695/exe")
+
+```
+
 2.1 Table showing the model parameters for each significant regression.

### 2018-07-16 manuscript.rmd
incorporating diet-character phylogenetic tests, PCAs, and ppcas

@@
 ## Introduction
+
+## Methods
+
+## Results
 
@@
 2.0 Confusion matrix table showing PIC_correlations and trait correlation R2 and p-values for each pair of continuous characters.
-Confusion matrix for quantitative and categorical characters GLS.
-pGLS estimation of regression parameters in significantly correlated pairs.
+
 ```{r character_correlations, include=FALSE}
-C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
+#PIC correlations with Rphylip
+C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
 Cspecies = C$Species %>% as.character()
@@
 class(Ctree) = "phylo"
-PICi = Rcontrast(Ctree, C, path="phylip-3.695/exe")
+PICi = Rcontrast(tree=Ctree, X=C, path="phylip-3.695/exe", cleanup=TRUE)
+
+#Correlation visualizations R2
+phy_corr = PICi$VarA.Correlations
+intra_corr = PICi$VarE.Correlations
+phy_corr[upper.tri(phy_corr)] <- NA
+combicorr = phy_corr
+combicorr[upper.tri(combicorr)] = intra_corr[upper.tri(intra_corr)]
+rownames(combicorr) = colnames(C)
+colnames(combicorr) = colnames(C)
+corrplot(combicorr, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs intraspecific correlations
+PICOLS = combicorr
+PICOLS[upper.tri(PICOLS)]=cor(C)[upper.tri(cor(C))]
+corrplot(PICOLS, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs regular correlations
 
@@
 2.1 Table showing the model parameters for each significant regression.
+
 2.3 Verbally PCA and phylogenetic PCA/PICVarA_PCA of the characters. Phylomorphospace superimposed to the tip coordinates in PC1--PC2.
+```{r PCA}
+par(mar=rep(3,4), mfrow=c(1,1))
+raw_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(1:2,4:20,30)]
+compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:29)]
+raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
+compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))
+
+#Regular PCA on means log
+  ##Raw characters
+PCA(raw_matrix) -> Pca_raw
+Pca_raw %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
+Pca_raw %>% fviz_contrib(choice="var", axes=2, sort.val="desc")
+Pca_raw %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)
+Pca_raw %>% fviz_pca_biplot(axes=c(3,4), col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)
+phylomorphospace(tree=raw_tree, Pca_raw$ind$coord[,1:2], label = "horizontal", xlab = "PC1", ylab = "PC2")
+phylomorphospace(tree=raw_tree, Pca_raw$ind$coord[,3:4], label = "horizontal", xlab = "PC3", ylab = "PC4")
+physignal(Pca_raw$ind$coord, raw_tree)
+  ##Morphometric characters
+PCA(compound_matrix) -> Pca_compound
+Pca_compound %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
+Pca_compound %>% fviz_contrib(choice="var", axes=2, sort.val="desc")
+Pca_compound %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)
+Pca_compound %>% fviz_pca_biplot(axes=c(3,4), col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)
+phylomorphospace(tree=compound_tree, Pca_compound$ind$coord[,1:2], label = "horizontal", xlab = "PC1", ylab = "PC2")
+phylomorphospace(tree=compound_tree, Pca_compound$ind$coord[,3:4], label = "horizontal", xlab = "PC3", ylab = "PC4")
+physignal(Pca_compound$ind$coord, compound_tree)
+
+#PhyloPCA on means
+PPCA_raw = phyl.pca(raw_tree, raw_matrix)
+PPCA_compound = phyl.pca(compound_tree, compound_matrix)
+PPCA %>% biplot(main=paste(signif(summary(PPCA)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA)$importance[2,2]*100,3),"%"), cex = .6, expand =1)
+
+```
+
 2.4 Table showing normalized rates of evolution for each character BAMM.
@@
 3.0 Phylogeny with the tips mapped with the literature dietary associations, and internal nodes showing SIMMAP reconstructed states.
+
+```{r diet_regime_tree}
+regimetree = dprunedTree
+hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed", "Crustacean", "Crustacean", "Ostracod", "Fish", "Fish", "Crustacean", "Mixed", "Mixed", "Copepod")
+names(hypdiet) = regimetree$tip.label
+DietAnc = ace(hypdiet, regimetree, type = "discrete")$lik.anc
+HypDietAnc = 1:nrow(DietAnc)
+for(row in 1:nrow(DietAnc)){
+  SCR = scale(DietAnc[row,])
+  print(SCR)
+  HypDietAnc[row] <- rownames(SCR)[which(SCR[,1] == max(SCR[,1]))] %>% print()
+}
+regimetree$node.label = as.factor(HypDietAnc)
+plotTree(regimetree)
+nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
+```
+
 3.1 Table showing quantitative and categorical characters association effect size with each prey type in the diet.
+
+```{r prey-character-assoc}
+#Phylogenetic ANOVAS with prey type presence
+pANOVAs_diet = as.data.frame(matrix(ncol=ncol(dprunedmatrix_logs[,-1]), nrow=ncol(diet)))
+rownames(pANOVAs_diet) = names(diet)
+colnames(pANOVAs_diet) = names(dprunedmatrix_logs[,-1])
+for(prey in 1:ncol(diet)){
+  CH_J=diet[,prey]
+  names(CH_J) = rownames(diet)
+  for(char in 1:ncol(dprunedmatrix_logs[,-1])){
+    CH_I = dprunedmatrix_logs[,char+1]
+    names(CH_I) = dprunedmatrix_logs$Species
+    CH_I = CH_I[!is.na(CH_I)]
+    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_I))))
+    if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
+    phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
+  }
+  }}
+pANOVAs_diet = pANOVAs_diet[,-1]
+write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")
+
+#PGLS with proportions in Diet
+pGLSp_diet = as.data.frame(matrix(nrow=ncol(Pprunedmatrix_logs[,-1]), ncol=ncol(PP)))
+colnames(pGLSp_diet) = names(PP)
+row.names(pGLSp_diet) = names(Pprunedmatrix_logs[,-1])
+pGLS_sign = pGLSp_diet
+for(i in 1:ncol(Pprunedmatrix_logs[,-1])){
+  CH_I=as.numeric(Pprunedmatrix_logs[,i+1])
+  names(CH_I) = Pprunedmatrix_logs$Species
+  for(j in 1:ncol(PP)){
+    CH_J=as.numeric(PP[,j])
+    names(CH_J) = rownames(PP)
+    pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
+    TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = Pprunedtree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
+    TTABLE %>% .$p %>% .[2] -> pGLSp_diet[i,j]
+    if(pGLSp_diet[i,j]<0.05){
+      print(paste(rownames(pGLSp_diet)[i],colnames(pGLSp_diet)[j],pGLSp_diet[(i),(j)],sep=" "))
+      ValueIJ = TTABLE %>% .$Value %>% .[2]
+      if(ValueIJ>0){pGLS_sign[i,j] = "+"}
+      else pGLS_sign[i,j] = "-"
+    }}}
+write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
+write.csv(pGLSp_sign, "PGLS_SIGN_DietPP.csv")
+
+```
+
 3.2 Table showing the dAICc of OU model fitting versus white_noise and BM using reconstructed diets as regimes in a 16spp tree. Evaluate model adequacy of OU fits.
+
+```{r OUwie}
+OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=nrow(dprunedmatrix_logs)))
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+library(magrittr)
+for(c in 2:ncol(dprunedmatrix_logs)){  #1:ncol(sharedmeans)
+  Cdata = data.frame(dprunedmatrix_logs$Species,hypdiet,dprunedmatrix_logs[,c])
+  names(Cdata) = c("species", "regime", "trait")
+  Cdata$trait[which(Cdata$trait == "NaN")] <- NA
+  Cdata = Cdata[!is.na(Cdata$trait),]
+  Cdata$trait = as.numeric(Cdata$trait)
+  Cdata$species = as.character(Cdata$species)
+  Cdata$regime = as.character(Cdata$regime)
+  Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
+  BM <- OUwie(Ctree, Cdata, model="BM1")
+  OU <- OUwie(Ctree, Cdata, model="OU1")
+  OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
+  OUwie_matrix[c-1,2] = nrow(Cdata)
+  print("BM")
+  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU$AICc))
+  print("OU")
+  OUwie_matrix[c-1,4] = OU$AICc - min(c(BM$AICc, OU$AICc))
+}
+OUwie_matrix[,3:4] <- apply(OUwie_matrix[,3:4], 2, round3)
+#write.csv(OUwie_matrix, "OU_diet_test.csv")
+```
+
 3.3 Interpret qualitatively the kinematic implications (high speed video) of the different regions of the morphospace.
@@
 
+## Discussion
+
+## Acknowledgements
+
 ## References

### 2018-07-16 manuscript.rmd
added writing backbone

@@
 library(tidyverse)
+library(stringr)
 library(reshape2)
-	## Graphics
-library(FactoMineR)
-library(factoextra)
-library(corrplot)
 	## Biological
+library(OUwie)
+library(Rphylip)
+library(arbutus)
 library(vegan)
@@
 library(phytools)
-library(OUwie)
 library(picante)
@@
 library(phylopath)
-library(Rphylip)
-library(arbutus)
+	## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
 
@@
 
-## Introduction
+# The evolution of siphonophore tentilla reveals association with diet {-}
 
-## Methods
+Alejandro Damian-Serrano^1^,^‡, Steven H.D. Haddock^2^, Casey W. Dunn^1^
 
-## Results
+^1^ Department of Ecology and Evolutionary Biology, Yale University, New Haven, CT 06520, USA
+
+^2^ Monterey Bay Aquarium Research Institute, Moss Landing, CA 95039, USA
+
+\‡ Corresponding author, catriona_munro@brown.edu
+
+## Abstract {-}
+
+Siphonophores have the most complex nematocyst batteries of all Cnidaria.
+These structures are held on the tentacles’ side branches called tentilla.
+Tentilla serve as the principal organs for prey capture, making siphonophores an ideal system for the study of trophic specialization from an evolutionary approach.
+Modern comparative methods have been applied to study the evolution of siphonophore zooid types, but not yet to the unique morphological diversity of siphonophore tentilla.
+The primary objectives of this work are to describe the morphology and morphometrics of siphonophore tentilla and nematocysts, and identify patterns in the evolutionary history of siphonophore cnidoband and nematocyst morphologies.
+A phylogeny with XX species was reconstructed using 18S and 16S gene markers, constraining the topology with a transcriptome-based backbone.
+Morphological characters were measured from DIC and confocal microscopy images of fixed tentacle specimens.
+Diet data was extracted from published sources.
+The functional implications of the different morphologies during prey capture were recorded using high speed video on live specimens under a stereoscopic microscope.
+Evolutionary transitions in siphonophore tentilla present a very low dimensionality with a single principal component.
+This main axis of variation aligns with total nematocyst volume per tentillum.
+Most nematocyst complement (cnidome) traits appear to have evolved under simple Brownian Motion (BM) and Early Burst (EB) processes, while tentillum shape and size evolution is better represented by Ohrnstein-Uhlenbeck (OU) models.
+Many tentillum and cnidome traits show stronger supports towards OU models when diet is reconstructed on the tree as selective regimes.
+Using phylogenetic GLS we identified traits with correlated evolutionary histories, some of which are functionally coupled during prey capture.
+Size and abundance of nematocysts were phylogenetic correlated with prey type ratios in the diet.
+These patterns could represent macroevolutionary adaptive responses to prey availability leading to predatory specialization.
+Understanding the evolution of the prey capture apparatus of siphonophores can help us test hypotheses about the evolution of their predatory habits.
+
+## 1. Introduction {-}
+
+Siphonophores bear the most complex nematocyst batteries of all cnidarians, with up to 4 types of regionally differentiated nematocysts and a spring-release mechanism for fast discharge of the structure onto the prey.
+Not all siphonophores bear tentilla on their tentacles, exceptions include Apolemia spp.
+and Bathyphysa conifera.
+While Physalia physalis has been considered to have simple tentacles, it is likely that their button-like structures are homologous to reduced tentilla (Munro et al.
+2018).
+Each gastrozooid bears a single tentacle.
+Each tentacle serially buds tentilla from the basal region (basigaster), which develop as they are displaced further with tentacle growth.
+During development, tentilla grow and change shape into their final configuration while mature nematocysts formed in the basigaster migrate through the tentacle epidermis into the tentillum.
+Nematocysts arriving into the developing tentillum then rearrange into their final position (Skaer 1991).
+Tentilla are a single-use ensnaring weapon which is ingested and digested together with the prey it attached to.
+The cnidoband and terminal filament bear all the active nematocysts.
+Cnidobands range in size from 40 microns to 8 cm, they can be coiled or straight, free hanging or enclosed in an involucrum (Mapstone 2014).
+
+## 2. Methods {-}
+
+### 3.1 Phylogeny{-}
+
+Markers accessions
+
+### 3.2 Microscopy{-}
+
+All specimens are accessioned in the Yale Peabody Museum Invertebrate Zoology Collection.
+Accession numbers and collection data for the specimens are available in Supplementary Table XXX.
+All specimens were preserved in ~4% buffered formalin in seawater.
+
+A total of 39 siphonophore species were selected based on availability and phylogenetic representativity criteria to capture intraspecific variation.
+Three to five specimens from each selected species were measured in order to account for intraspecific variation.
+
+Diet data from Purcell 1981, Purcell 1984.
+
+Microscopy ...
+
+### 3.3 Phylogenetic Comparative Methods{-}
+
+Phylogenetic signal (Blomberg 2003)
+fitContinuous (geiger), BM, EB, OU.
+Adams geomorph
+phytools ppca, pgls, phyl.anova
+
+### 3.4 High-Speed Video
+
+## 3. Results {-}
 
@@
 morphdata = cbind(castN, castmeans[,-1], castSE[,-1])
-morphdata = monrphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
+morphdata = morphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
 names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
@@
   treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
+  class(treeI) = "phylo"
   #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
@@
 
-## Discussion
+## 4. Discussion
+
+## 5. Conclusions
 
 ## Acknowledgements
+
+Fulbright Spain. NSF Waterman Award. NSF siphweb project. Yale Institute of Biospehric Studies. Crew of R/V Western Flyer.
 

### 2018-07-16 manuscript.rmd
preliminary writing

@@
 
+Tentacles from the studied specimens were dissected, dehydrated in a series of ethanol dilutions (25% in PBS, 50% in PBS, 75% in water, 100%), cleared in methyl salicylate or d-limonene, and mounted in plastic slides (Canada balsam, Cytoseal, or Permount).
+Slides were imaged using laser scanning confocal microscopy and differential interference contrast (DIC) microscopy.
+Images were measured using Fiji-ImageJ.
+
+The characters measured for this study are described in Supplementary Table SXX.
+Homology assumptions for nematocyst supertypes (heteroneme, haploneme, rhopaloneme, and desmoneme) and tentillum structures (involucrum, elastic strand, pedicle, cnidoband) were informed by positional, developmental, and morphological criteria.
+
 Diet data from Purcell 1981, Purcell 1984.
@@
 
-Phylogenetic signal (Blomberg 2003)
+All phylogenetic statistical analyses were carried out in the programming environment R (cite).
+Phylogenetic signal in each of the measured characters was calculated using Blomberg’s K (Blomberg 2003).
+
 fitContinuous (geiger), BM, EB, OU.
@@
 ### 3.4 High-Speed Video
+
+High speed footage (1000-3000 fps) of tentillum and nematocyst discharge was recorded on live siphonophore specimens using a Phantom Miro 320S camera mounted on a stereoscopic microscope.
+Specimens were collected by SCUBA divers and the remotely operated underwater vehicle Doc Ricketts during expeditions onboard the R/V Western Flyer.
+Tentillum and nematocyst discharge were elicited mechanically using a fine metallic pin.
+Video footage was analyzed using Phantom PCC software.
 
@@
 
-Fulbright Spain. NSF Waterman Award. NSF siphweb project. Yale Institute of Biospehric Studies. Crew of R/V Western Flyer.
+This work was funded by the Society of Systematic Biologists Graduate Student Award, the NSF Waterman Award, and the Yale Institute of Biospheric Studies Doctoral Pilot Grant.
+ADS was supported by a Fulbright Spain scholarship.
+We thank Philip R.
+Pugh for his assistance in the identification of specimens.
+We also wish to thank the crew of the R/V Western Flyer.
 
 ## References
-
-Siphonophores are... [@Mackie:1987uy].

### 2018-07-30 manuscript.rmd
ran physigs, model fitting w/ new phylo

@@
 
-```{r load_trees, include=F}
+```{r load_tree, include=F}
 #Load tree
-rRNA18S = read.nexus('bipartitions_root.boot10')
-transcriptome = read.tree('ultimatephylo2018.tre')
-#plot.phylo(consensus)
-#is.rooted(consensus)
-#nodelabels()
-rRNA18S = reroot(rRNA18S, 76, 0.001)
-rRNA18S$tip.label = str_replace_all(rRNA18S$tip.label,'_',' ')
-rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma cordiforme"] = "Cordagalma ordinatum"
-rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma sp "] = "Cordagalma ordinatum"
-rRNA18S$tip.label[rRNA18S$tip.label=="Clausophyes ovata"] = "Kephyes ovata"
-rRNA18S$tip.label[rRNA18S$tip.label=="Erenna sp"] = "Erenna sirena"
-rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp"] = "Apolemia lanosa"
-rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp "] = "Apolemia rubriversa"
-rRNA18S$tip.label[rRNA18S$tip.label=="Sphaeronectes gracilis"] = "Sphaeronectes koellikeri"
-rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
-rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
-rRNA18S = drop.tip(rRNA18S, 41:42) #drop outgroups
-rRNA18S = drop.tip(rRNA18S, c(16,31,23,24)) #drop Cordagalma, Clausophyid, Nectopyramis, Nectadamas
-#plot(rRNA18S)
-
-transcriptome$tip.label = str_replace_all(transcriptome$tip.label,'_',' ')
-transcriptome$tip.label[transcriptome$tip.label=="Cordagalma sp"] = "Cordagalma ordinatum"
-transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
-transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
-transcriptome = reroot(transcriptome, 22, 0.001)
-transcriptome = drop.tip(transcriptome, 19:26) #drop outgroups
-#plot(transcriptome)
-
-multitree = list(rRNA18S,transcriptome)
-class(multitree)="multiPhylo"
-STree = superTree(multitree, rooted = T, method = "MRP", start = transcriptome)
-consensus = STree[[2]]
-consensus = drop.tip(consensus, "Physonect sp ")
-consensus = drop.tip(consensus, "Erenna sirena")
-consensus$tip.label[consensus$tip.label=="Physophora gilmeri"] = "Physophora h" ### ARTIFIIAL SUBSTITUTION ###
-consensus = drop.tip(consensus, "Physophora hydrostatica")
-consensus$tip.label[consensus$tip.label=="Physophora h"] = "Physophora hydrostatica"
-consensus$tip.label[consensus$tip.label=="Vogtia pentacantha"] = "Vogtia serrata"
-consensus = drop.tip(consensus, "Rosacea flaccida")
-#plot(consensus)
+consensus = ape::read.tree("concatenate.fasta.treefile")
+consensus = reroot(consensus,99)
+consensus = drop.tip(consensus, c(56:61))
+consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
 
@@
   CH_I=as.numeric(sharedmean_logs[,i])
-  names(CH_I) = rownames(sharedmean_logs)
+  names(CH_I) = sharedmean_logs$Species
   SE_I = as.numeric(castSE[,i])
@@
   phylosignals[i-1,3] <- length(CH_I)
+  phylosignals$K = round(phylosignals$K,3)
 }
@@
   phy_models = data.frame(worthy_models,MAD)
-  phy_models[,8:13] = apply(phy_models[,8:13], 2,round3)
+  phy_models[,7:12] = apply(phy_models[,7:12], 2,round3)
 ```

### 2018-07-30 manuscript.rmd
rerun diet associations and OUwie w/ new phylo

@@
 PPCA_compound = phyl.pca(compound_tree, compound_matrix)
-PPCA %>% biplot(main=paste(signif(summary(PPCA)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA)$importance[2,2]*100,3),"%"), cex = .6, expand =1)
+PPCA_raw %>% biplot(main=paste(signif(summary(PPCA_raw)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_raw)$importance[2,2]*100,3),"%"), cex = .6, expand =1)
+PPCA_compound %>% biplot(main=paste(signif(summary(PPCA_compound)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_compound)$importance[2,2]*100,3),"%"), cex = .6, expand =0.4)
 
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed", "Crustacean", "Crustacean", "Ostracod", "Fish", "Fish", "Crustacean", "Mixed", "Mixed", "Copepod")
+hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed",  "Fish", "Fish", "Ostracod", "Copepod", "Copepod", "Mixed", "Copepod")
 names(hypdiet) = regimetree$tip.label

### 2018-07-31 manuscript.rmd
log CastSE for phylosignals

@@
   rownames(categorical) = categorical$Species
+
+  #Correct species spellings
+  numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+  numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+  numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
 
@@
 
-\‡ Corresponding author, catriona_munro@brown.edu
+\‡ Corresponding author, alejandro.damianserrano@yale.edu
 
@@
 Markers accessions
+
+ML phylogeny was reconstructed from 16S and 18S ribosomal rRNA genes using iqtree(). 1000 bootstraps. 
+A minimal set of nodes were constrained to be consistent with the (Munro etal 2018) transcriptome phylogeny strict consensus tree.
 
@@
 #Load tree
-consensus = ape::read.tree("concatenate.fasta.treefile")
-consensus = reroot(consensus,99)
-consensus = drop.tip(consensus, c(56:61))
+consensus = ape::read.tree("concatenate.fasta.contree")
+consensus = reroot(consensus,103)
+consensus = drop.tip(consensus, c(28,29,30,59:61))
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
@@
 
+Novel phylogenetic relationships:
+-Erenna spp closely related to Stephanomia
+
 1.0 Table showing for each species the mean, number of individuals measured, and standard error of every character, ordered by cnidomic index / tentillum size, and/or colored by clade.
@@
 phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
+#phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmeans[,-1])))
 names(phylosignals) = c("K", "P", "Ntaxa")
@@
   CH_I=as.numeric(sharedmean_logs[,i])
+  #CH_I=as.numeric(sharedmeans[,i])
   names(CH_I) = sharedmean_logs$Species
-  SE_I = as.numeric(castSE[,i])
+  #names(CH_I) = sharedmeans$Species
+  SE_I = as.numeric(castSE[,i]) %>% log()
+  SE_I[which(SE_I==-Inf)] = 0
   names(SE_I) = castSE$Species
@@
 #PIC correlations with Rphylip
-C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
+#C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
+C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
 Cspecies = C$Species %>% as.character()
@@
 par(mar=rep(3,4), mfrow=c(1,1))
-raw_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(1:2,4:20,30)]
-compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:29)]
+raw_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(1:2,4:20)]
+compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:30)]
 raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
@@
 physignal(Pca_raw$ind$coord, raw_tree)
+multiPhylosignal(Pca_raw$ind$coord, raw_tree)
   ##Morphometric characters
@@
 physignal(Pca_compound$ind$coord, compound_tree)
+multiPhylosignal(Pca_compound$ind$coord, compound_tree)
 
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed",  "Fish", "Fish", "Ostracod", "Copepod", "Copepod", "Mixed", "Copepod")
+hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed",  "Fish", "Fish", "Ostracod", "Copepod", "Copepod", "Mixed", "Crustacean")
 names(hypdiet) = regimetree$tip.label
@@
 for(c in 2:ncol(dprunedmatrix_logs)){  #1:ncol(sharedmeans)
-  Cdata = data.frame(dprunedmatrix_logs$Species,hypdiet,dprunedmatrix_logs[,c])
+  #Cdata = data.frame(dprunedmatrix_logs$Species,hypdiet,dprunedmatrix_logs[,c])
+  Cdata = data.frame(dprunedmatrix$Species,hypdiet,dprunedmatrix[,c])
   names(Cdata) = c("species", "regime", "trait")

### 2018-07-31 manuscript.rmd
added model adequacy csv, merged Nanomia spp in morphdata

@@
   numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+  #Merge Nanomias
+  numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+  numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
 
@@
 names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
-write.csv(morphdata, "characterdata.csv")
+#write.csv(morphdata, "characterdata.csv")
 ```
@@
 }
-write.csv(phylosignals, "PhylosignalsWSE_log.csv")
+#write.csv(phylosignals, "PhylosignalsWSE_log.csv")
 ```
@@
     startree = drop.tip(startree, which(!(startree$tip.label %in% names(C))))
-    Cse = castSE[,c+1]
+    Cse = castSE[,c+1] %>% log() %>% abs()
+    Cse[which(Cse == Inf)] <- 0
     names(Cse) = castSE$Species
@@
   AICdf[,2:6] = apply(AICdf[,2:6], 2, as.numeric) %>% apply(2, round3)
-  write.csv(AICdf, "log_model_support.csv")
+  #write.csv(AICdf, "log_model_support.csv")
 
@@
   phy_models[,7:12] = apply(phy_models[,7:12], 2,round3)
+  #write.csv(phy_models, "model_adequacy.csv")
 ```

### 2018-07-31 manuscript.rmd
merged Nanomia sp in tree for analyses

@@
 plot(prunedtree)
+
+#Switch nanomia_bijuga for sp
+prunedtree$tip.label[which(prunedtree$tip.label == "Nanomia bijuga")] <- "Nanomia sp"
+
 ultram = chronos(prunedtree)

### 2018-08-07 manuscript.rmd
switched to bayesian tree

@@
 #Load tree
-consensus = ape::read.tree("concatenate.fasta.contree")
-consensus = reroot(consensus,103)
-consensus = drop.tip(consensus, c(28,29,30,59:61))
+#consensus = ape::read.tree("concatenate.fasta.contree")
+consensus = read.nexus("gene_map_ct.tre")
+read.tree("gene_ct.trees") %>% consensus() -> daconsensus
+plot(daconsensus)
+#consensus = reroot(consensus,103)
+consensus = reroot(consensus,97)
+#consensus = drop.tip(consensus, c(28,29,30,59:61))
+consensus = drop.tip(consensus, c(56:61))
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
+ultra_consensus = chronos(consensus,100)
+
+#PLOT tree figure
+plot(ultra_consensus)
 
@@
 1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
+
+```{r simmaps, include=F}
+par(ask=F)
+tentilla = sharedcategorical$Tentilla
+names(tentilla) = rownames(sharedcategorical)
+prox_het = sharedcategorical$Proximal.heteronemes
+names(prox_het) = rownames(sharedcategorical)
+desmo = sharedcategorical$Desmonemes
+names(desmo) = rownames(sharedcategorical)
+rhopalo = sharedcategorical$Rhopalonemes
+names(rhopalo) = rownames(sharedcategorical)
+dyn_cnido = sharedcategorical$Dynamic.cnidoband
+names(dyn_cnido) = rownames(sharedcategorical)
+elastic = sharedcategorical$Elastic.strand
+names(elastic) = rownames(sharedcategorical)
+distal_desmo = sharedcategorical$Distal.cnidoband.desmonemes
+names(distal_desmo) = rownames(sharedcategorical)
+coiled = sharedcategorical$Coiled.tentilla
+names(coiled) = rownames(sharedcategorical)
+heterotype = sharedcategorical$Heteroneme.type
+heterotype=as.character(heterotype)
+names(heterotype) = rownames(sharedcategorical)
+haplotype = sharedcategorical$Haploneme.type
+haplotype=as.character(haplotype)
+names(haplotype) = rownames(sharedcategorical)
+
+Simmap_list = list()
+###SIMMAP Tentilla:
+make.simmap(ultram_cat, tentilla, nsim = 100) -> tentilla_sim
+Simmap_list[[1]] <- tentilla_sim
+plotTree(ultram_cat, lwd = 4)
+tentilla_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Present", "Absent")
+nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(tentilla_sim)
+
+###SIMMAP Proximal Heteronemes:
+make.simmap(ultram_cat, prox_het, nsim = 100) -> prox_het_sim
+Simmap_list[[2]] <- prox_het_sim
+plotTree(ultram_cat, lwd = 4)
+prox_het_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Present", "Absent")
+nodelabels(pie=(describe.simmap(prox_het_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(prox_het_sim)
+
+###SIMMAP Desmonemes:
+make.simmap(ultram_cat, desmo, nsim = 100) -> desmo_sim
+Simmap_list[[3]] <- desmo_sim
+plotTree(ultram_cat, lwd = 4)
+desmo_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(desmo_sim)
+
+###SIMMAP Rhopalonemes:
+make.simmap(ultram_cat, rhopalo, nsim = 100) -> rhopalo_sim
+Simmap_list[[4]] <- rhopalo_sim
+plotTree(ultram_cat, lwd = 4)
+rhopalo_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(rhopalo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(rhopalo_sim)
+
+###SIMMAP Dynamic Cnidoband:
+make.simmap(ultram_cat, dyn_cnido, nsim = 100) -> dyn_cnido_sim
+Simmap_list[[5]] <- dyn_cnido_sim
+plotTree(ultram_cat, lwd = 4)
+dyn_cnido_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(dyn_cnido_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(dyn_cnido_sim)
+
+###SIMMAP Elastic Strand:
+make.simmap(ultram_cat, elastic, nsim = 100) -> elastic_sim
+Simmap_list[[6]] <- elastic_sim
+plotTree(ultram_cat, lwd = 4)
+elastic_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(elastic_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(elastic_sim)
+
+###SIMMAP Distal CB Desmonemes:
+make.simmap(ultram_cat, distal_desmo, nsim = 100) -> distal_desmo_sim
+Simmap_list[[7]] <- distal_desmo_sim
+plotTree(ultram_cat, lwd = 4)
+distal_desmo_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(distal_desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(distal_desmo_sim)
+
+###SIMMAP Tentilla Coiledness:
+make.simmap(ultram_cat, coiled, nsim = 100) -> coiled_sim
+Simmap_list[[8]] <- coiled_sim
+plotTree(ultram_cat, lwd = 4)
+coiled_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Absent", "Present")
+nodelabels(pie=(describe.simmap(coiled_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(coiled_sim)
+
+###SIMMAP Heteroneme type:
+heterotype = heterotype[heterotype!=""]
+HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(heterotype))))
+make.simmap(HTtree, heterotype, nsim = 100) -> heterotype_sim
+Simmap_list[[9]] <- heterotype_sim
+plotTree(HTtree, lwd = 4)
+heterotype_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red", "green")
+names(colors) = c("Eurytele", "Microbasic mastigophore", "Stenotele")
+nodelabels(pie=(describe.simmap(heterotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+
+###SIMMAP Haploneme type:
+haplotype = haplotype[haplotype!=""]
+HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(haplotype))))
+make.simmap(HTtree, haplotype, nsim = 100) -> haplotype_sim
+Simmap_list[[10]] <- haplotype_sim
+plotTree(HTtree, lwd = 4)
+haplotype_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c("black", "red")
+names(colors) = c("Isorhizas", "Anisorhizas")
+nodelabels(pie=(describe.simmap(haplotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+densityMap(haplotype_sim)
+
+```
 

### 2018-08-08 manuscript.rmd
included BAMMtools chunk, incorporates constrained timetree

@@
 library(corrplot)
+library(BAMMtools)
 
@@
 #consensus = ape::read.tree("concatenate.fasta.contree")
-consensus = read.nexus("gene_map_ct.tre")
-read.tree("gene_ct.trees") %>% consensus() -> daconsensus
-plot(daconsensus)
+#consensus = read.nexus("gene_map_ct.tre")
+#read.tree("gene_ct.trees") %>% consensus() -> daconsensus
+#plot(daconsensus)
+consensus = read.nexus("TimeTreeCT.tre") %>% drop.tip(53:58)
 #consensus = reroot(consensus,103)
-consensus = reroot(consensus,97)
+#consensus = reroot(consensus,97)
 #consensus = drop.tip(consensus, c(28,29,30,59:61))
-consensus = drop.tip(consensus, c(56:61))
+#consensus = drop.tip(consensus, c(56:61))
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
-ultra_consensus = chronos(consensus,100)
-
-#PLOT tree figure
-plot(ultra_consensus)
+#ultra_consensus = chronos(consensus,100)
 
@@
 
-ultram = chronos(prunedtree)
+#ultram = chronos(prunedtree)
+ultram = prunedtree
 plot(ultram)
@@
 2.4 Table showing normalized rates of evolution for each character BAMM.
+
+```{r BAMM}
+
+```
+
 3 -- RELATIONSHIPS WITH DIET / FUNCTION / Hypothesis testing

### 2018-08-08 manuscript.rmd
reran deliversbale tables with timetree

@@
 shavedtree = inditree
-inditree = chronos(inditree)
+#inditree = chronos(inditree)
 plot(inditree)
@@
 plot(cat_tree)
-ultram_cat = chronos(cat_tree)
+#ultram_cat = chronos(cat_tree)
+ultram_cat = cat_tree
 plot(ultram_cat)
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed",  "Fish", "Fish", "Ostracod", "Copepod", "Copepod", "Mixed", "Crustacean")
+hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Ostracod",  "Mixed", "Mixed", "Mixed", "Copepod", "Fish", "Fish")
 names(hypdiet) = regimetree$tip.label

### 2018-08-10 manuscript.rmd
using latest backbone constrained ultrametric-estimated bayesian timetree, BAMM analyses

@@
 #consensus = read.nexus("gene_map_ct.tre")
-#read.tree("gene_ct.trees") %>% consensus() -> daconsensus
-#plot(daconsensus)
-consensus = read.nexus("TimeTreeCT.tre") %>% drop.tip(53:58)
+consensus = read.nexus("TimeTree_CT_perfect.tre") %>% drop.tip(56:61)
 #consensus = reroot(consensus,103)
@@
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
-#ultra_consensus = chronos(consensus,100)
 
@@
 PPCA_compound %>% biplot(main=paste(signif(summary(PPCA_compound)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_compound)$importance[2,2]*100,3),"%"), cex = .6, expand =0.4)
-
+phylomorphospace(raw_tree, PPCA_raw$S)
 ```
@@
 ```{r BAMM}
+traitlist = list()
+for(i in 2:ncol(sharedmean_logs)){
+  traitlist[[i]] <- sharedmean_logs[,c(1,i)]
+  names(traitlist)[i] = names(sharedmean_logs)[i]
+}
+
+traitlist <- lapply(traitlist, function(x){x<-x[which(!is.nan(x[,2])),]})
+
+for(i in 2:length(traitlist)){
+  treei = drop.tip(ultram, which(!(ultram$tip.label %in% traitlist[[i]]$Species)))
+  treei$tip.label = str_replace_all(treei$tip.label, " ", "_")
+  write.tree(treei, file = paste("BAMM/",names(traitlist[[i]])[2], "_tree.tre", sep=""))
+}
+
+for(i in 2:length(traitlist)){
+  traitlist[[i]]$Species = str_replace_all(traitlist[[i]]$Species, " ", "_")
+  write.table(traitlist[[i]],file = paste("BAMM/",names(traitlist[[i]])[2], ".txt", sep=""), sep="\t", col.names = F, row.names = F, quote = F)
+}
 
@@
 pGLSp_diet = as.data.frame(matrix(nrow=ncol(Pprunedmatrix_logs[,-1]), ncol=ncol(PP)))
+pGLS_sign = pGLSp_diet
 colnames(pGLSp_diet) = names(PP)
@@
   names(CH_I) = Pprunedmatrix_logs$Species
+  CH_I = CH_I[!is.na(CH_I)]
   for(j in 1:ncol(PP)){
@@
     names(CH_J) = rownames(PP)
+    CH_J = CH_J[!is.na(CH_J)]
+    CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
+    CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
+    pgls_tree = drop.tip(Pprunedtree, which(!(Pprunedtree$tip.label %in% names(CH_I))))
     pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
-    TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = Pprunedtree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
+    TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
     TTABLE %>% .$p %>% .[2] -> pGLSp_diet[i,j]
@@
 write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
-write.csv(pGLSp_sign, "PGLS_SIGN_DietPP.csv")
+pGLS_sign <- pGLS_sign[which(rowSums(is.na(pGLS_sign))!=ncol(pGLS_sign)),which(colSums(is.na(pGLS_sign))!=nrow(pGLS_sign))]
+write.csv(pGLS_sign, "PGLS_SIGN_DietPP.csv")
 

### 2018-08-10 BAMM/BAMMplots.R

@@ -1,0 +1,37 @@
+# load libraries
+library(BAMMtools)
+library(geiger)
+library(coda)
+setwd("~/tentilla_morph/BAMM")
+# load tree
+tree <- read.tree("Elastic.strand.width..um._tree.tre")
+
+# ESS after 20% burnin
+mcmcout <- read.csv("mcmc_out.txt")
+burnstart <- floor(0.2*nrow(mcmcout))
+postburn <- mcmcout[burnstart:nrow(mcmcout), ]
+effectiveSize(postburn$N_shifts)
+effectiveSize(postburn$logLik)
+
+# load BAMM main output
+edata <- getEventData(tree, eventdata = "event_data.txt", burnin=0.2, type="trait")
+summary(edata)
+
+# the 6 most likely scenario's within the 95% credible scenarios
+# F value is the relative probability, F values from all scenarios add up to F=1
+pdf("BAMM_css.pdf", width=7, height=10)
+css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
+BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T)
+dev.off()
+
+# net diversification graph
+pdf("BAMM_netdiv.pdf", width=7, height=5)
+starttime <- max(branching.times(tree))
+plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
+dev.off()
+
+pdf("_ratesplot.pdf",width=16,height=16)
+plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
+dev.off()
+
+#q()

### 2018-08-10 BAMM/BAMMsetpriors.R

@@ -1,0 +1,14 @@
+library(BAMMtools)
+library(stringr)
+library(readr)
+setwd("~/tentilla_morph/BAMM")
+tree <- read.tree("Elastic.strand.width..um..tre")
+traits <- read.csv("Elastic.strand.width..um..txt", sep="\t", header = F)
+rownames(traits) = traits[,1]
+traits <- traits[tree$tip.label,]
+write_tsv(traits, "Elastic.strand.width..um..txt", col_names = FALSE)
+is.ultrametric(tree) # check for ultrametric
+is.binary.tree(tree) # check if there are no polytomies
+min(tree$edge.length) # check all branch lengths are > 0
+setBAMMpriors(phy = tree, traits = "Elastic.strand.width..um..txt")
+#q()

### 2018-08-11 manuscript.rmd
diet reananlysis with clade B clamped as fish specialists, more BAMMs

@@
 ##Make the pseudoindividuals tree
-newtree = ultram
-sharedmatrix_plied = sharedmatrix
-sharedmatrix_plied$slide_id = paste(sharedmatrix$slide_id, sharedmatrix$Species, sep = "_")
-for (i in 1:nrow(sharedmatrix_plied)) {
-  pos = which(newtree$tip.label == sharedmatrix_plied$Species[i])
-  print(pos)
-  newtree = bind.tip(newtree, sharedmatrix_plied$slide_id[i], where = pos, edge.length = 0.1)
-  print(newtree$tip.label)
-  newtree$tip.label = str_replace_all(newtree$tip.label,'_',' ')
-}
-inditree = drop.tip(newtree, which(!grepl(".[0-9].*", newtree$tip.label)))
-zerotipTree = inditree
-inditree$edge.length[inditree$edge.length==0] <- 0.0000000001
-shavedtree = inditree
-#inditree = chronos(inditree)
-plot(inditree)
-sharedmatrix_plied$slide_id = str_replace_all(sharedmatrix_plied$slide_id,'_',' ')
-sharedmatrix = sharedmatrix_plied[match(sharedmatrix_plied$slide_id, inditree$tip.label),]
-rownames(sharedmatrix) <- 1:nrow(sharedmatrix)
+# newtree = ultram
+# sharedmatrix_plied = sharedmatrix
+# sharedmatrix_plied$slide_id = paste(sharedmatrix$slide_id, sharedmatrix$Species, sep = "_")
+# for (i in 1:nrow(sharedmatrix_plied)) {
+#   pos = which(newtree$tip.label == sharedmatrix_plied$Species[i])
+#   print(pos)
+#   newtree = bind.tip(newtree, sharedmatrix_plied$slide_id[i], where = pos, edge.length = 0.1)
+#   print(newtree$tip.label)
+#   newtree$tip.label = str_replace_all(newtree$tip.label,'_',' ')
+# }
+# inditree = drop.tip(newtree, which(!grepl(".[0-9].*", newtree$tip.label)))
+# zerotipTree = inditree
+# inditree$edge.length[inditree$edge.length==0] <- 0.0000000001
+# shavedtree = inditree
+# #inditree = chronos(inditree)
+# plot(inditree)
+# sharedmatrix_plied$slide_id = str_replace_all(sharedmatrix_plied$slide_id,'_',' ')
+# sharedmatrix = sharedmatrix_plied[match(sharedmatrix_plied$slide_id, inditree$tip.label),]
+# rownames(sharedmatrix) <- 1:nrow(sharedmatrix)
 
@@
 diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
-#diet = rbind(diet, c(0,1,0,0,0,0,0,0))
+cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0),4),nrow=9, ncol = 4) %>% t() %>% as.data.frame()
+names(cladeB) = names(diet)
+rownames(cladeB) = c("Erenna richardi", "Erenna laciniata", "Erenna sirena", "Stephanomia amphytridis")
+diet = rbind(diet, cladeB)
 #rownames(diet)[12] = 'Erenna richardi'
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Ostracod",  "Mixed", "Mixed", "Mixed", "Copepod", "Fish", "Fish")
+hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Ostracod",  "Mixed", "Mixed", "Mixed", "Copepod", "Fish", "Fish", "Fish", "Fish", "Fish", "Fish")
 names(hypdiet) = regimetree$tip.label
@@
 pANOVAs_diet = pANOVAs_diet[,-1]
+pANOVAs_diet[pANOVAs_diet>0.05] <- NA
 write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")
@@
 library(magrittr)
-for(c in 2:ncol(dprunedmatrix_logs)){  #1:ncol(sharedmeans)
-  #Cdata = data.frame(dprunedmatrix_logs$Species,hypdiet,dprunedmatrix_logs[,c])
-  Cdata = data.frame(dprunedmatrix$Species,hypdiet,dprunedmatrix[,c])
+for(c in 2:ncol(dprunedmatrix_logs)){
+  Cdata = data.frame(dprunedmatrix$Species,hypdiet,dprunedmatrix_logs[,c])
   names(Cdata) = c("species", "regime", "trait")
@@
   OUwie_matrix[c-1,2] = nrow(Cdata)
-  print("BM")
   OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU$AICc))
-  print("OU")
   OUwie_matrix[c-1,4] = OU$AICc - min(c(BM$AICc, OU$AICc))

### 2018-08-11 BAMM/BAMMplots.R

@@ -4,7 +4,7 @@ library(geiger)
 library(coda)
 setwd("~/tentilla_morph/BAMM")
 # load tree
-tree <- read.tree("Elastic.strand.width..um._tree.tre")
+tree <- read.tree("Desmoneme.length..um._tree.tre")
 
 # ESS after 20% burnin
 mcmcout <- read.csv("mcmc_out.txt")

### 2018-08-11 BAMM/BAMMsetpriors.R

@@ -2,13 +2,13 @@ library(BAMMtools)
 library(stringr)
 library(readr)
 setwd("~/tentilla_morph/BAMM")
-tree <- read.tree("Elastic.strand.width..um..tre")
-traits <- read.csv("Elastic.strand.width..um..txt", sep="\t", header = F)
+tree <- read.tree("Desmoneme.length..um._tree.tre")
+traits <- read.csv("Desmoneme.length..um..txt", sep="\t", header = F)
 rownames(traits) = traits[,1]
 traits <- traits[tree$tip.label,]
-write_tsv(traits, "Elastic.strand.width..um..txt", col_names = FALSE)
+write_tsv(traits, "Desmoneme.length..um..txt", col_names = FALSE)
 is.ultrametric(tree) # check for ultrametric
 is.binary.tree(tree) # check if there are no polytomies
 min(tree$edge.length) # check all branch lengths are > 0
-setBAMMpriors(phy = tree, traits = "Elastic.strand.width..um..txt")
+setBAMMpriors(phy = tree, traits = "Desmoneme.length..um..txt")
 #q()

### 2018-10-22 manuscript.rmd
manuscript writing, redone timetree with correct rho parameter

@@
   read.csv("byslide.csv") -> numbers
+  numbers$Species = as.character(numbers$Species)
   categorical <- read.csv("Homolog_Categorical.csv")[,-2]
@@
 The primary objectives of this work are to describe the morphology and morphometrics of siphonophore tentilla and nematocysts, and identify patterns in the evolutionary history of siphonophore cnidoband and nematocyst morphologies.
-A phylogeny with XX species was reconstructed using 18S and 16S gene markers, constraining the topology with a transcriptome-based backbone.
+A phylogeny with 55 species was reconstructed using 18S and 16S gene markers, constraining the topology to be congruent with a transcriptome-based tree.
 Morphological characters were measured from DIC and confocal microscopy images of fixed tentacle specimens.
@@
 
-Siphonophores bear the most complex nematocyst batteries of all cnidarians, with up to 4 types of regionally differentiated nematocysts and a spring-release mechanism for fast discharge of the structure onto the prey.
-Not all siphonophores bear tentilla on their tentacles, exceptions include Apolemia spp.
-and Bathyphysa conifera.
-While Physalia physalis has been considered to have simple tentacles, it is likely that their button-like structures are homologous to reduced tentilla (Munro et al.
-2018).
+Siphonophores are colonial planktonic predators present in all oceans of the world.
+
+Siphonophores bear the most complex nematocyst batteries of all cnidarians, with up to 4 types of positionally and morphologically differentiated nematocysts, combined with a spring-release mechanism for fast discharge of the structure onto the prey.
+Not all siphonophores bear tentilla on their tentacles, exceptions include *Apolemia* spp.
+and *Bathyphysa conifera*.
+While *Physalia physalis* has been considered to have simple tentacles, it is likely that their button-like structures are homologous to reduced tentilla [@munro2018improved].
+All tentilla are unilateral side branches of the tentacle, with epidermis, mesoglea, gastrodermis, and gastrovascular cavity.
 Each gastrozooid bears a single tentacle.
@@
 During development, tentilla grow and change shape into their final configuration while mature nematocysts formed in the basigaster migrate through the tentacle epidermis into the tentillum.
-Nematocysts arriving into the developing tentillum then rearrange into their final position (Skaer 1991).
+Nematocysts arriving into the developing tentillum then rearrange into their final position [@skaer1991remodelling].
 Tentilla are a single-use ensnaring weapon which is ingested and digested together with the prey it attached to.
 The cnidoband and terminal filament bear all the active nematocysts.
-Cnidobands range in size from 40 microns to 8 cm, they can be coiled or straight, free hanging or enclosed in an involucrum (Mapstone 2014).
+Cnidobands range in size from 40 microns to 8 cm, they can be coiled or straight, free hanging or enclosed in an involucrum [@mapstone2014global].
+Most tentilla bear a pair of elastic strands (Totton cite) derived from the wall of the gastrovascular cavity.
+
+While zooid type evolution has been addressed in a phylogenetic framework, tentillum and nematocyst morphology has not.
+Since tentilla are used exclusively for prey capture, we expect their morphological diversity to have evolved in adaptive response to the evolution of different diets and prey type specializations.
+Earlier work by Purcell @[purcell1984functions] has shown clear associations between nematocyst morphology, size, and number with prey type and copepod prey length.
+However, this pioneer study did not take phylogenetic relationships into account beyond grouping species by taxonomic suborder, and eas limited to a few epipelagic species.
 
@@
 
-Markers accessions
+For this phylogenetic analysis we included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
+The gene sequences used in this study are available online (accession numbers in Supp.
+Table XX).
+Some of these sequences were used in @[dunn2005molecular], others were sequenced by XYZ.
+Sequences were aligned using MAFFT.
 
-ML phylogeny was reconstructed from 16S and 18S ribosomal rRNA genes using iqtree(). 1000 bootstraps. 
-A minimal set of nodes were constrained to be consistent with the (Munro etal 2018) transcriptome phylogeny strict consensus tree.
+A Maximum Likelihood (ML) phylogeny (Figure XX) was reconstructed from 16S and 18S ribosomal rRNA genes using IQTree (Nguyen et al., 2015) with 1000 bootstraps.
+We used ModelFinder (Kalyaanamoorthy et al., 2017) implemented in IQTree v1.5.5.
+to assess relative model fit.
+ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
+A minimal set of 5 nodes were constrained to be consistent with the [@munro2018improved] transcriptome phylogeny strict consensus tree.
+In addition to the ML tree, we reconstructed a Bayesian tree with each marker as an independent partition in RevBayes.
+The same node constraints were applied, and the tree topology recovered was identical to the ML tree.
+To obtain ultrametric branch lengths for this topology, a Bayesian strict molecular clock time-tree was constructed in Rev Bayes, using a birth-death process constrained to be fully congruent with the topology recovered in the abovementioned analyses.
+Scripts availabe in Suppl.
+Mat.
+XX.
 
 ### 3.2 Microscopy{-}
+
+Speciemns from the Monterey Bay and Gulf of California were collected by remotely operated underwater vehicles (ROV) or by blue-water SCUBA divers.
 
@@
 Three to five specimens from each selected species were measured in order to account for intraspecific variation.
+Adittionally, 30 species with only a single specimen were also measured and reported in this work, but their data will not be used in the statistical analyses downstream.
 
@@
 
-Diet data from Purcell 1981, Purcell 1984.
-
-Microscopy ...
+Diet data for epipelagic siphonophroes was compiled from published studies on visual gut content recognition @[purcell1981dietary], @[purcell1984functions].
+Presence of taxonomic groups in the diet as well as percent individual composition was retrieved from these sources.
+For deep dwelling species, MBARI VARS observations were used to score presence of prey taxonomic groups in annotated predation events with different siphonophore species.
 
@@
 
-All phylogenetic statistical analyses were carried out in the programming environment R (cite).
+All phylogenetic statistical analyses were carried out in the programming environment R (cite), using the species tree, and incorporating intraspecific variation estimated from the specimen data.
 Phylogenetic signal in each of the measured characters was calculated using Blomberg’s K (Blomberg 2003).
+The phylogenetic signal of multivariate character sets was calculated using the package geomorph (Adams cite).
 
-fitContinuous (geiger), BM, EB, OU.
-Adams geomorph
-phytools ppca, pgls, phyl.anova
+Ancestral states were reconstructed using ML for continuous characters (anc.ML phytools), and stochastic character mapping (make.simmap) for categorical characters.
+
+Different models generating the observed data distribution given the phylogeny were fitted for each continuous character using the function fitContinuous (package geiger cite).
+The models compared were the white noise (WN) (non-phylogenetic), the Brownian Motion (BM) model of neutral divergent evolution (cite), the Early Burst (EB) model of decreasing rate of evolutionary change (cite), and the Ohnstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state (cite).
+Models were ranked in order of increasing parametric complexity (WN,BM,EB,OU).
+Corrected Akaika Information Criterion support scores (AICc, cite) were compared to the lowest (best) score, and a cutoff of 2 units was used to determine significantly better support.
+If the best fitting model is not significantly better than a less complex alternative, the least complex model is selected.
+The models selected for each character were evaluated in terms of model adequacy using the package arbutus (cite).
+Multivariate BM and OU models were also evaluated using the package mvSLOUCH (cite).
+
+In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analyses (PCA) and phylogenetic PCA (phytools ppca cite).
+In addition, we obtained the correlations between the phylogenetic independent contratsts (Felsenstein cite) using the package rphylip (cite).
+We modeled the relationship between correlated characters using phylogenetic leats squares regression (PGLS) in the package phytools (Revell..cite).
+Evolutionary relationships between continuous and categorical characters were assessed using phylogenetic ANOVAs (phyl.anova phytools) and phylogenetic generalized linear mixed models (PGLMM).
 
@@
 
+Total cnidoband discharge time (ms), average cnidoband discharge speed (mm/s), maximum cnidoband discharge speed (mm/s), heteroneme discharge speed (mm/s), haploneme discharge speed (mm/s), heteroneme shaft discharge speed (mm/s), and heteroneme filament length (microns) were measured when possible for 10 species.
+
 ## 3. Results {-}
@@
 0.0 ML ribosomal marker phylogeny constrained by transcriptome tree with BS values at the nodes.
+
+The topology of this tree is congruent with the results from @[dunn2005molecular]. In addition, we found *Erenna* and *Stephanomia* as sister genera in a monophyletic group.
+
 1 -- DESCRIPTIVE MORPHOLOGY AND EVOLUTIONARY HISTORY
+
+1.05 Plate with all the tentillum diversity.
+
+1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
+
+Principal component analyses were carried out separately on raw log-transformed measurements and compound morphometric characters (such as volumes and ratios).
+PC1 (aligned with tentillum size and nematocyst shape) explains ~64% of the variation in the tentillum morphospace, whereas PC2 (aligned with nematocyst size characters) explained ~18%.
+
+Controlling for phylogenetic expected covariance, ~88% of the evolutionary variation is explained by shifts in size, exhibiting a low effective dimensionality.
+
+The calycophoran morphospace is quite distinct from that of other siphonophores.
+A non-calycophoran (Frillagalma vityazi), has secondarily “invaded” this morphospace, which could indicate a case of convergence.
+Most characters present a moderate yet significant phylogenetic signal, and predominantly support BM models, indicating a history of neutral constant divergence.
+Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
+These characters may be useful for taxonomic purposes.
+Bayesian Analysis of Macroevolutionary Mixtures [] identified evolutionary rate regime shifts in the branches leading to the euphysonects, to clade B, and to Cordagalma for several characters.
+These shifts could be associated with adaptive responses to dietary change.
 
@@
 #consensus = read.nexus("gene_map_ct.tre")
-consensus = read.nexus("TimeTree_CT_perfect.tre") %>% drop.tip(56:61)
+consensus = read.nexus("TimeTree_CT_truerho.tre") %>% drop.tip(56:61)
 #consensus = reroot(consensus,103)
@@
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
+#Switch nanomia_bijuga for sp
+consensus$tip.label[which(consensus$tip.label == "Nanomia bijuga")] <- "Nanomia sp"
 
@@
 plot(prunedtree)
-
-#Switch nanomia_bijuga for sp
-prunedtree$tip.label[which(prunedtree$tip.label == "Nanomia bijuga")] <- "Nanomia sp"
 
@@
 
-1.05 Plate with all the tentillum diversity.
-1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
 ```{r phylosignals}
@@
 
+#Change directionalities
+changes = matrix(ncol=ncol(sharedmean_logs)-1, nrow=nrow(ultram$edge))
+for(ch in 2:ncol(sharedmean_logs)){
+  X=as.numeric(sharedmean_logs[,ch])
+  names(X) = sharedmean_logs$Species
+  X=X[!is.na(X)]
+  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(X))))
+  class(treeI) = "phylo"
+  #changes = c()
+  tips = X
+  names(tips)=match(names(X), treeI$tip.label)
+  faX = c(anc.ML(treeI,X)$ace,tips)
+  edges = treeI$edge
+  for(i in 1:nrow(edges)){
+    node_old = edges[i,1]
+    node_new = edges[i,2]
+    (faX[which(names(faX) == node_new)] - faX[which(names(faX) == node_old)])-> changes[i,ch-1]
+  }
+  #hist(changes)
+  #abline(v=0,col="red")
+}
+
 ```
@@
 2.3 Verbally PCA and phylogenetic PCA/PICVarA_PCA of the characters. Phylomorphospace superimposed to the tip coordinates in PC1--PC2.
+
 ```{r PCA}
 par(mar=rep(3,4), mfrow=c(1,1))
-raw_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(1:2,4:20)]
+raw_matrix = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[which(!is.na(rowSums(.))),]
+raw_matrix_notf = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[,c(1:7,12:17)] %>% .[which(!is.na(rowSums(.))),]
+
 compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:30)]
 raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
+#raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
 compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))
@@
   ##Raw characters
-PCA(raw_matrix) -> Pca_raw
+#PCA(raw_matrix) -> Pca_raw
+PCA(raw_matrix_notf) -> Pca_raw
 Pca_raw %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
@@
 phylomorphospace(raw_tree, PPCA_raw$S)
+
+#Plot mirror trees QUANT
+X = sharedmean_logs$coiledness
+names(X) = sharedmean_logs$Species
+X = X[!is.nan(X)]
+Y = sharedmean_logs$Involucrum.length..um.
+names(Y) = sharedmean_logs$Species
+Y = Y[!is.nan(Y)]
+Y = Y[which(names(Y) %in% names(X))]
+X = X[which(names(X) %in% names(Y))]
+XYtree = drop.tip(ultram, which(!(ultram$tip.label %in% names(X))))
+class(XYtree) = "phylo"
+layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
+par(cex=0.5)
+#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
+OX = contMap(XYtree,X,sig=1,legend=1, plot = F, outline = F)
+OX$cols[1:length(OX$cols)] = colorRampPalette(c("yellow","purple"), space="Lab")(length(OX$cols))
+plot(OX,ftype="off")
+ylim<-c(1-0.12*(length(XYtree$tip.label)-1),length(XYtree$tip.label))
+plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
+text(rep(0,length(XYtree$tip.label)), 1:length(XYtree$tip.label),XYtree$tip.label)
+OY = contMap(XYtree,Y, sig=1,legend=1, plot = F,  outline = F)
+OY$cols[1:length(OY$cols)] = colorRampPalette(c("green","red"), space="Lab")(length(OY$cols))
+plot(OY, direction="leftwards", ftype = "off")
+
 ```
 
-2.4 Table showing normalized rates of evolution for each character BAMM.
+2.4 Table showing BAMM-analyzed number of regime shifts in the rates of evolution of each character.
 
@@
 
+#PGLS with other data
+BAMMtree <- read.tree("BAMM/Cnidoband.free.length..um._tree.tre")
+# ESS after 20% burnin
+mcmcout <- read.csv("BAMM/Cnidoband_free_length/mcmc_out.txt")
+burnstart <- floor(0.2*nrow(mcmcout))
+postburn <- mcmcout[burnstart:nrow(mcmcout), ]
+effectiveSize(postburn$N_shifts)
+effectiveSize(postburn$logLik)
+
+# load BAMM main output
+edata <- getEventData(BAMMtree, eventdata = "BAMM/Cnidoband_free_length/event_data.txt", burnin=0.2, type="trait")
+summary(edata)
+
+regimes = edata$tipStates[[3]] %>% .[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)]
+names(regimes) = edata$tip.label[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)] %>% str_replace_all("_", " ")
+for(prey in 1:ncol(diet)){
+  print(names(diet)[prey])
+  food=diet[,prey]
+  names(food) = rownames(diet)
+  food = food[which(names(food)%in%names(regimes))]
+  food = food[match(names(regimes), names(food))]
+  if(length(unique(food))>1){
+    pgls.SEy(food~regimes,data=data.frame(food,regimes), tree=dprunedTree, se= rep(0, length(food)))
+  }}
+
 ```
+
+Out of 29 characters, 11 did  not significantly (delta AICc > 2) support a phylogenetic model.
+From the remaining 18, Brownian Motion was supported for 17 of them.
+Only haploneme nematocyst length had uniequivocal support for Early Burst.
 
@@
 GC$character = factor(GC$character, levels=unique(GC$character))
+GC$species = as.character(GC$species)
+GC$species[which(GC$species == "Nanomia bijuga")] <- "Nanomia sp"
 GC = GC[which(GC$species %in% sharedmeans$Species),]
@@
 rownames(cladeB) = c("Erenna richardi", "Erenna laciniata", "Erenna sirena", "Stephanomia amphytridis")
-diet = rbind(diet, cladeB)
+krilleaters = matrix(rep(c(0,0,0,0,0,1,1,0,0),2),nrow=9, ncol = 2) %>% t() %>% as.data.frame()
+names(krilleaters) = names(diet)
+rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala")
+diet = rbind(diet, cladeB, krilleaters)
 #rownames(diet)[12] = 'Erenna richardi'
@@
 PP$character = factor(PP$character, levels=unique(PP$character))
+PP$species = as.character(PP$species)
+PP$species[which(PP$species == "Nanomia bijuga")] <- "Nanomia sp"
 PP = PP[which(PP$species %in% sharedmeans$Species),]
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Ostracod",  "Mixed", "Mixed", "Mixed", "Copepod", "Fish", "Fish", "Fish", "Fish", "Fish", "Fish")
+hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Crustacean", "Crustacean", "Mixed", "Mixed", "Crustacean", "Mixed", "Copepod", "Crustacean", "Fish", "Fish", "Fish", "Fish", "Fish", "Fish")
 names(hypdiet) = regimetree$tip.label
@@
 3.1 Table showing quantitative and categorical characters association effect size with each prey type in the diet.
+
+Nematocyst morphology appears to be associated to prey type presence in diet.
+Phylogenetic regression with frequencies of prey types (in 8 species) revealed that decapod larvae consumption is associated to many traits, while fish larvae specialization is only associated to more rounded nematocyst shapes with stubbier shafts, and copepod specialization is mainly associated to fewer nematocyst and thinner tentacles.
+Transitions to fish and copepod specialization correlate with regime shifts in the rates for those characters (detected with BAMM).
 
@@
     if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
-    phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
+    #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
+       #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
+    gls(CH_I ~ CH_J, correlation =  corBrownian(phy = treeIJ), data = as.data.frame(cbind(CH_I,CH_J)), method = "ML") %>% summary() %>% .$tTable %>% as.data.frame() %>% .$p %>% .[2] -> pANOVAs_diet[prey,char]
   }
@@
 pGLS_sign = pGLSp_diet
-for(i in 1:ncol(Pprunedmatrix_logs[,-1])){
-  CH_I=as.numeric(Pprunedmatrix_logs[,i+1])
+for(i in 2:ncol(Pprunedmatrix_logs)){
+  CH_I=as.numeric(Pprunedmatrix_logs[,i])
   names(CH_I) = Pprunedmatrix_logs$Species
@@
     CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
+    SE_I = castSE_logs[which(castSE$Species %in% names(CH_I)),i]
+    names(SE_I) = castSE_logs[which(castSE$Species %in% names(CH_I)),1]
+    SE_I = SE_I[match(names(CH_I), names(SE_I))]
     pgls_tree = drop.tip(Pprunedtree, which(!(Pprunedtree$tip.label %in% names(CH_I))))
     pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
-    TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
-    TTABLE %>% .$p %>% .[2] -> pGLSp_diet[i,j]
-    if(pGLSp_diet[i,j]<0.05){
-      print(paste(rownames(pGLSp_diet)[i],colnames(pGLSp_diet)[j],pGLSp_diet[(i),(j)],sep=" "))
-      ValueIJ = TTABLE %>% .$Value %>% .[2]
-      if(ValueIJ>0){pGLS_sign[i,j] = "+"}
+    pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
+    pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
+    #TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
+    LikRat <- 2*(TTABLE$logLik[1] - TTABLE_null$logLik[1])
+    pchisq(LikRat, df=1, lower.tail = F) -> pGLSp_diet[i-1,j]
+    if(pGLSp_diet[i-1,j]<0.05){
+     print(paste(rownames(pGLSp_diet)[i-1],colnames(pGLSp_diet)[j],pGLSp_diet[(i-1),(j)],sep=" "))
+     ValueIJ = TTABLE %>% .$coefficients %>% .[2]
+     if(ValueIJ>0){pGLS_sign[i-1,j] = "+"}
       else pGLS_sign[i,j] = "-"
-    }}}
-write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
+   }
+  }
+}
+#write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
 pGLS_sign <- pGLS_sign[which(rowSums(is.na(pGLS_sign))!=ncol(pGLS_sign)),which(colSums(is.na(pGLS_sign))!=nrow(pGLS_sign))]
@@
 
+dprunedmatrix[,c(2:3,5:21)] -> dprunedraw
+rownames(dprunedraw) = dprunedmatrix$Species
+dprunedraw %>% .[which(!is.na(rowSums(.))),] %>% PCA() -> dprunedPCA
+CH_I = dprunedPCA$ind$coord[,1]
+for(prey in 1:ncol(diet)){
+  CH_J=diet[,prey]
+  names(CH_J) = rownames(diet)
+  CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+  treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_I))))
+  if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
+    print(names(diet)[prey])
+    #phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf -> pANOVAs_diet[prey,char]
+    phylANOVA(treeIJ,x=CH_J,y=CH_I) %>% .$Pf %>% print()
+  #gls(CH_I ~ CH_J, correlation =  corBrownian(phy = treeIJ), data = as.data.frame(cbind(CH_I,CH_J)), method = "ML") %>% summary() %>% .$tTable %>% as.data.frame() %>% .$p %>% .[2]  %>% print()
+  }
+  }
+
+#Plot mirror trees QUANT
+X = dprunedmatrix_logs$Haploneme.free.length..um.
+names(X) = dprunedmatrix_logs$Species
+Y = diet$`Decapod diet`
+names(Y) = rownames(diet)
+Y = Y[which(names(Y) %in% names(X))]
+treeXY = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(X))))
+layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
+par(cex=0.5)
+#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
+OX = contMap(treeXY,X,sig=1,legend=1, plot = F, outline = F)
+OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
+plot(OX,ftype="off")
+ylim<-c(1-0.12*(length(treeXY$tip.label)-1),length(treeXY$tip.label))
+plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
+text(rep(0,length(treeXY$tip.label)), 1:length(treeXY$tip.label),treeXY$tip.label)
+OY = contMap(treeXY,Y, sig=1,legend=1, plot = F,  outline = F)
+OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
+plot(OY, direction="leftwards", ftype = "off")
+
+X = Pprunedmatrix_logs$Heteroneme.volume..um3.
+names(X) = Pprunedmatrix_logs$Species
+Y = PP$`Relative decapod consumption`
+names(Y) = rownames(PP)
+layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
+par(cex=0.5)
+#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
+OX = contMap(Pprunedtree,X,sig=1,legend=1, plot = F, outline = F)
+OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
+plot(OX,ftype="off")
+ylim<-c(1-0.12*(length(Pprunedtree$tip.label)-1),length(Pprunedtree$tip.label))
+plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
+text(rep(0,length(Pprunedtree$tip.label)), 1:length(Pprunedtree$tip.label),Pprunedtree$tip.label)
+OY = contMap(Pprunedtree,Y, sig=1,legend=1, plot = F,  outline = F)
+OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
+plot(OY, direction="leftwards", ftype = "off")
+
 ```
 
-3.2 Table showing the dAICc of OU model fitting versus white_noise and BM using reconstructed diets as regimes in a 16spp tree. Evaluate model adequacy of OU fits.
+3.2 Table showing the dAICc of OU model fitting versus white_noise and BM using reconstructed diets as regimes in a 16 spp tree. Evaluate model adequacy of OU fits.
+
+When I mapped trait evolution onto a diet SIMMAP regime tree, OU models using the reconstructed states as regimes fitted significantly better (dAICc>2) than BM (null models) for cnidoband coiledness, heteroneme shaft shape, haploneme length, haploneme row number, desmoneme length, and desmoneme width.
 
@@
 OUwie_matrix[,3:4] <- apply(OUwie_matrix[,3:4], 2, round3)
-#write.csv(OUwie_matrix, "OU_diet_test.csv")
+write.csv(OUwie_matrix, "OU_diet_test.csv")
+
 ```
@@
 
-Story: low dimensionality, cost-driven, dynamic specialization
+High-speed video of cnidoband and nematocyst discharge revealed the roles of the different tentillum substructures in the mechanics of discharge.
+Moreover, it shows important differences int he discharge dynamics of species with different tentillum morphologies.
+
+Videos have shown the double role of the elastic strands in initiating and controlling cnidoband discharge.
+A few milliseconds before cnidoband discharge, the distal attachment of the cnidoband (at the base of the terminal filament) appears to unwind to the point of a tension-release threshold.
+This observation indicates there might be spring mechanism driving the discharge process.
+
+Euphysonect tentilla discharge considerably faster than Calycophoran tentilla.
+Larger heteronemes discharge faster than small ones, giving Euphysonects a faster heteroneme discharge speed than most calycophorans.
+On the contrary, Calycophoran haploneme tubules fire faster than those of Euphysonects.
+
+The more extreme the coiledness index, the more unpredictable the trajectory of the cnidoband during discharge.
+
+Story: low dimensionality, cost-reward-driven, dynamic specialization.
 
@@
 
+A particularly interesting case is that of *Cordagalma ordinatum*, a specialized copepod eater @[purcell1981dietary], which is sister to the generalist genus *Forskalia*.
+Cordagalma’s tentilla strongly resemble the larval (protozooid exclusive) tentilla of Forskalia spp.
+This could indicate a case of paedomorphosis as a pathway to predatory specialization.
+
+The calycophoran morphospace is quite distinct from that of other siphonophores, revealing a potential reaction line in the 2 PCs (Figure XX).
+A non-calycophoran (*Frillagalma vityazi*), has secondarily occupied this morphospace, which could indicate a case of convergence.
+
+The new phylogeny delivered by this chapter will become a fundamental resource for subsequent studies of siphonophore evolution.
+In addition, a broad and detailed characterization of tentilla morphology and its phylogenetic distribution provide complementary tools for taxonomy, identification, and morphological delimitation.
+
 ## 5. Conclusions
+
+The genera *Erenna* and *Stephanomia* form a monophyletic clade characterized by bearing extremely large tentilla.
 
@@
 
-This work was funded by the Society of Systematic Biologists Graduate Student Award, the NSF Waterman Award, and the Yale Institute of Biospheric Studies Doctoral Pilot Grant.
+This work was funded by the Society of Systematic Biologists Graduate Student Award, the NSF Waterman Award,  the Yale Institute of Biospheric Studies Doctoral Pilot Grant, and the NSF Collaborative Research project SiphWeb.
 ADS was supported by a Fulbright Spain scholarship.
-We thank Philip R.
+We thank Dr.
+Philip R.
 Pugh for his assistance in the identification of specimens.

### 2018-10-29 manuscript.rmd
knitting tests

@@
 Cnidobands range in size from 40 microns to 8 cm, they can be coiled or straight, free hanging or enclosed in an involucrum [@mapstone2014global].
-Most tentilla bear a pair of elastic strands (Totton cite) derived from the wall of the gastrovascular cavity.
+Cnidobands always carry haploneme nematocysts, which can be isorhizas or anisorhizas.
+In additon, many species' cnidoband can carry a row of heteroneme nematocysts along each side.
+These heteroneme nematocyst can be stenoteles, microbasic mastigophores, euryteles, or birhopaloids.
+In codonophorans, tentilla bear a pair of elastic strands [@totton1965synopsis] derived from the wall of the gastrovascular cavity.
 
@@
 Since tentilla are used exclusively for prey capture, we expect their morphological diversity to have evolved in adaptive response to the evolution of different diets and prey type specializations.
-Earlier work by Purcell @[purcell1984functions] has shown clear associations between nematocyst morphology, size, and number with prey type and copepod prey length.
+Earlier work by Purcell [@purcell1984functions] has shown clear associations between nematocyst morphology, size, and number with prey type and copepod prey length.
 However, this pioneer study did not take phylogenetic relationships into account beyond grouping species by taxonomic suborder, and eas limited to a few epipelagic species.
@@
 Table XX).
-Some of these sequences were used in @[dunn2005molecular], others were sequenced by XYZ.
+Some of these sequences were used in [@dunn2005molecular], others were sequenced by XYZ.
 Sequences were aligned using MAFFT.
@@
 
-Speciemns from the Monterey Bay and Gulf of California were collected by remotely operated underwater vehicles (ROV) or by blue-water SCUBA divers.
+Speciemns from the Monterey Bay and Gulf of California were collected by remotely operated underwater vehicles (ROV) or by blue-water SCUBA divers, following the protocols established in [@haddock2005scientific].
 
@@
 Slides were imaged using laser scanning confocal microscopy and differential interference contrast (DIC) microscopy.
-Images were measured using Fiji-ImageJ.
+Images were measured using Fiji-ImageJ [@schindelin2012fiji].
 
@@
 
-Diet data for epipelagic siphonophroes was compiled from published studies on visual gut content recognition @[purcell1981dietary], @[purcell1984functions].
+Diet data for epipelagic siphonophroes was compiled from published studies on visual gut content recognition [@purcell1981dietary], [@purcell1984functions].
 Presence of taxonomic groups in the diet as well as percent individual composition was retrieved from these sources.
-For deep dwelling species, MBARI VARS observations were used to score presence of prey taxonomic groups in annotated predation events with different siphonophore species.
+For deep dwelling species, MBARI VARS [@schlining2006mbari] observations were used to score presence of prey taxonomic groups in annotated predation events with different siphonophore species.
 
@@
 
-All phylogenetic statistical analyses were carried out in the programming environment R (cite), using the species tree, and incorporating intraspecific variation estimated from the specimen data.
-Phylogenetic signal in each of the measured characters was calculated using Blomberg’s K (Blomberg 2003).
-The phylogenetic signal of multivariate character sets was calculated using the package geomorph (Adams cite).
-
-Ancestral states were reconstructed using ML for continuous characters (anc.ML phytools), and stochastic character mapping (make.simmap) for categorical characters.
-
-Different models generating the observed data distribution given the phylogeny were fitted for each continuous character using the function fitContinuous (package geiger cite).
-The models compared were the white noise (WN) (non-phylogenetic), the Brownian Motion (BM) model of neutral divergent evolution (cite), the Early Burst (EB) model of decreasing rate of evolutionary change (cite), and the Ohnstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state (cite).
+All phylogenetic statistical analyses were carried out in the programming environment R [@team2017r], using the species tree, and incorporating intraspecific variation estimated from the specimen data.
+Phylogenetic signal in each of the measured characters was calculated using Blomberg’s K [@blomberg2003testing].
+The phylogenetic signal of multivariate character sets was calculated using the package geomorph [@adams2016geomorph].
+
+Ancestral states were reconstructed using ML for continuous characters (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
+
+Different models generating the observed data distribution given the phylogeny were fitted for each continuous character using the function fitContinuous [@harmon2007geiger].
+The models compared were the white noise (WN) (non-phylogenetic), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ohnstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory],[@butler2004phylogenetic].
 Models were ranked in order of increasing parametric complexity (WN,BM,EB,OU).
-Corrected Akaika Information Criterion support scores (AICc, cite) were compared to the lowest (best) score, and a cutoff of 2 units was used to determine significantly better support.
+Corrected Akaika Information Criterion support scores [@sugiura1978further] were compared to the lowest (best) score, and a cutoff of 2 units was used to determine significantly better support.
 If the best fitting model is not significantly better than a less complex alternative, the least complex model is selected.
-The models selected for each character were evaluated in terms of model adequacy using the package arbutus (cite).
-Multivariate BM and OU models were also evaluated using the package mvSLOUCH (cite).
-
-In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analyses (PCA) and phylogenetic PCA (phytools ppca cite).
-In addition, we obtained the correlations between the phylogenetic independent contratsts (Felsenstein cite) using the package rphylip (cite).
+The models selected for each character were evaluated in terms of model adequacy using the package arbutus [@pennell2015model].
+Multivariate BM and OU models were also evaluated using the package mvSLOUCH [@bartoszek2012phylogenetic].
+
+In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analyses (PCA) and phylogenetic PCA [@revell2012phytools].
+In addition, we obtained the correlations between the phylogenetic independent contratsts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
 We modeled the relationship between correlated characters using phylogenetic leats squares regression (PGLS) in the package phytools (Revell..cite).
@@
 
-The topology of this tree is congruent with the results from @[dunn2005molecular]. In addition, we found *Erenna* and *Stephanomia* as sister genera in a monophyletic group.
+The topology of this tree is congruent with the results from [@dunn2005molecular]. In addition, we found *Erenna* and *Stephanomia* as sister genera in a monophyletic group.
 
@@
 
-1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
+1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of specimens included.
 
@@
 The calycophoran morphospace is quite distinct from that of other siphonophores.
-A non-calycophoran (Frillagalma vityazi), has secondarily “invaded” this morphospace, which could indicate a case of convergence.
+A non-calycophoran (*Frillagalma vityazi*), has secondarily “invaded” this morphospace, which could indicate a case of convergence.
+
 Most characters present a moderate yet significant phylogenetic signal, and predominantly support BM models, indicating a history of neutral constant divergence.
@@
 These characters may be useful for taxonomic purposes.
-Bayesian Analysis of Macroevolutionary Mixtures [] identified evolutionary rate regime shifts in the branches leading to the euphysonects, to clade B, and to Cordagalma for several characters.
+Bayesian Analysis of Macroevolutionary Mixtures [@rabosky2014bamm] identified evolutionary rate regime shifts in the branches leading to the euphysonects, to clade B, and to Cordagalma for several characters.
 These shifts could be associated with adaptive responses to dietary change.
@@
 compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:30)]
-raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
-#raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
+#raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
+raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
 compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))
@@
 #PhyloPCA on means
+raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
 PPCA_raw = phyl.pca(raw_tree, raw_matrix)
@@
 postburn <- mcmcout[burnstart:nrow(mcmcout), ]
-effectiveSize(postburn$N_shifts)
-effectiveSize(postburn$logLik)
-
-# load BAMM main output
-edata <- getEventData(BAMMtree, eventdata = "BAMM/Cnidoband_free_length/event_data.txt", burnin=0.2, type="trait")
-summary(edata)
-
-regimes = edata$tipStates[[3]] %>% .[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)]
-names(regimes) = edata$tip.label[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)] %>% str_replace_all("_", " ")
-for(prey in 1:ncol(diet)){
-  print(names(diet)[prey])
-  food=diet[,prey]
-  names(food) = rownames(diet)
-  food = food[which(names(food)%in%names(regimes))]
-  food = food[match(names(regimes), names(food))]
-  if(length(unique(food))>1){
-    pgls.SEy(food~regimes,data=data.frame(food,regimes), tree=dprunedTree, se= rep(0, length(food)))
-  }}
+#effectiveSize(postburn$N_shifts)
+#effectiveSize(postburn$logLik)
 
@@
 ```
+```{r, BAMM_output, echo=F}
+# load BAMM main output
+edata <- getEventData(BAMMtree, eventdata = "BAMM/Cnidoband_free_length/event_data.txt", burnin=0.2, type="trait")
+summary(edata)
+
+regimes = edata$tipStates[[3]] %>% .[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)]
+names(regimes) = edata$tip.label[which(str_replace_all(BAMMtree$tip.label,"_", " ") %in% dprunedTree$tip.label)] %>% str_replace_all("_", " ")
+for(prey in 1:ncol(diet)){
+  print(names(diet)[prey])
+  food=diet[,prey]
+  names(food) = rownames(diet)
+  food = food[which(names(food)%in%names(regimes))]
+  food = food[match(names(regimes), names(food))]
+  if(length(unique(food))>1){
+    pgls.SEy(food~regimes,data=data.frame(food,regimes), tree=dprunedTree)
+  }}
+```
 
@@
 High-speed video of cnidoband and nematocyst discharge revealed the roles of the different tentillum substructures in the mechanics of discharge.
-Moreover, it shows important differences int he discharge dynamics of species with different tentillum morphologies.
+Moreover, it shows important differences in the discharge dynamics of species with different tentillum morphologies.
 
@@
 
-A particularly interesting case is that of *Cordagalma ordinatum*, a specialized copepod eater @[purcell1981dietary], which is sister to the generalist genus *Forskalia*.
-Cordagalma’s tentilla strongly resemble the larval (protozooid exclusive) tentilla of Forskalia spp.
+A particularly interesting case is that of *Cordagalma ordinatum*, a specialized copepod eater [@purcell1981dietary], which is sister to the generalist genus *Forskalia*.
+*Cordagalma*’s tentilla strongly resemble the larval (protozooid exclusive) tentilla of *Forskalia* spp.
 This could indicate a case of paedomorphosis as a pathway to predatory specialization.

### 2018-10-29 manuscript_knitest.rmd
knitting tests

--- 2018-10-22 manuscript.rmd
@@
 Cnidobands range in size from 40 microns to 8 cm, they can be coiled or straight, free hanging or enclosed in an involucrum [@mapstone2014global].
-Most tentilla bear a pair of elastic strands (Totton cite) derived from the wall of the gastrovascular cavity.
+Cnidobands always carry haploneme nematocysts, which can be isorhizas or anisorhizas.
+In additon, many species' cnidoband can carry a row of heteroneme nematocysts along each side.
+These heteroneme nematocyst can be stenoteles, microbasic mastigophores, euryteles, or birhopaloids.
+In codonophorans, tentilla bear a pair of elastic strands (Totton cite) derived from the wall of the gastrovascular cavity.
 
@@
 
-```{r fitContinuous}
+```{r fitContinuous, echo=F, warning=F}
 #Model support
@@
 ```
+
 1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
@@
 densityMap(haplotype_sim)
-
 ```
@@
 2.4 Table showing BAMM-analyzed number of regime shifts in the rates of evolution of each character.
-
 ```{r BAMM}
@@
 
-```{r diet_regime_tree}
+```{r diet_regime_tree, echo=F}
 regimetree = dprunedTree
@@
 
-```{r prey-character-assoc}
+```{r prey-character-assoc, echo=F, warning=F}
 #Phylogenetic ANOVAS with prey type presence

### 2018-11-26 manuscript.rmd
reknit, table tryouts

@@
 library(BAMMtools)
+library(gridExtra)
+library(xtable)
 
@@
 
-```{r export_table_morph, include=FALSE}
+```{r export_table_morph, include=TRUE}
 morphdata = cbind(castN, castmeans[,-1], castSE[,-1])
@@
 #write.csv(morphdata, "characterdata.csv")
+grid.newpage()
+grid.table(morphdata, base_size=6)
 ```
@@
 
-1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy.
-
-```{r fitContinuous}
+1.2 Table showing the best AICc supported model generating the data for each character and its AICc score. Model adequacy. Phylogenetic signals.
+
+```{r fitContinuous, include=F}
 #Model support

### 2019-01-29 manuscript.rmd
Vars data, soft-hard logistic regressions

@@
 	## Biological
-library(OUwie)
 library(Rphylip)
@@
 library(phytools)
+library(OUwie)
 library(picante)
@@
 library(phylopath)
+library(phylolm)
 	## Graphics
@@
 
-Speciemns from the Monterey Bay and Gulf of California were collected by remotely operated underwater vehicles (ROV) or by blue-water SCUBA divers, following the protocols established in [@haddock2005scientific].
+Specimens from the Monterey Bay and Gulf of California were collected by remotely operated underwater vehicles (ROV) or by blue-water SCUBA divers, following the protocols established in [@haddock2005scientific].
 
@@
 ```{r export_table_morph, include=TRUE}
-morphdata = cbind(castN, castmeans[,-1], castSE[,-1])
+Ses = castSE[,-1]
+Ses[Ses == 0] = NA
+morphdata = cbind(castN, castmeans[,-1], Ses)
 morphdata = morphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
 names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
+
 #write.csv(morphdata, "characterdata.csv")
 grid.newpage()
-grid.table(morphdata, base_size=6)
+grid.table(morphdata)
+
+#Make a heatmap
+heatdata = as.matrix(castmean_logs[,-1])
+rownames(heatdata) = castmean_logs$Species
+heatmap(heatdata, scale = "column", cexCol = 0.5, col=terrain.colors(20))
 ```
@@
 ```
+
+Testing nematocyst shape evolution questions:
+```{r elongation}
+het_el = sharedmean_logs$heteroneme_elongation
+names(het_el) = sharedmean_logs$Species
+hap_el = sharedmean_logs$haploneme_elongation
+names(hap_el) = sharedmean_logs$Species
+het_el = het_el[which(!is.na(het_el))]
+hap_el = hap_el[which(!is.na(hap_el))]
+het_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(het_el))))
+hap_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(hap_el))))
+phenogram(het_tree, het_el)
+phenogram(hap_tree, hap_el)
+
+hap_el = hap_el[which(names(hap_el) %in% names(het_el))]
+het_el = het_el[which(names(het_el) %in% names(hap_el))]
+elon_data = cbind(het_el, hap_el) %>% as.data.frame()
+names(elon_data) = c("Heteroneme elongation (log um)", "Haploneme elongation (log um)")
+elon_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(hap_el))))
+phylomorphospace(elon_tree, elon_data, label="horizontal")
+
+```
+
 1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
@@
 names(PL_pruned_matrix)[ncol(PL_pruned_matrix)] <- "Copepod prey length (mm)"
+
+#Retrieve VARS data from Choy et al 2017
+VARS <- read.csv("Choy2017.tsv", sep="\t")
+VARS_curated = VARS[which(VARS$Pred_lowest_tax %in% ultram$tip.label | VARS$Pred_lowest_tax=="Nanomia bijuga"),]
+VARS_cast = acast(VARS_curated, Pred_lowest_tax~Prey_order, fun.aggregate = length)
+
+#Combination of VARS and GC sources
+diet_VARS = rbind(diet, c(0,0,0,0,0,1,1,0,0))
+diet_VARS = cbind(diet_VARS, rep(0,nrow(diet_VARS)))
+rownames(diet_VARS)[nrow(diet_VARS)] <- "Lychnagalma utricularia"
+names(diet_VARS)[ncol(diet_VARS)] <- "Gelatinous diet"
+diet_VARS["Nanomia sp",] = c(1,0,0,0,0,1,1,1,0,1)
+diet_VARS["Praya dubia",] = c(1,0,0,0,0,1,1,0,0,1)
+
+#Soft vs Hard
+soft_hard = cbind((diet$`Copepod diet`+diet$`Amphipod diet`+diet$`Crustacean diet` + diet$`Decapod diet` + diet$`Ostracod diet`), (diet$`Fish diet`+diet$`Polychaete diet`+diet$`Chaetognath diet`+diet$`Mollusc diet`))
+colnames(soft_hard) = c("Hard", "Soft")
+rownames(soft_hard) = rownames(diet)
+soft_hard <- as.data.frame(soft_hard)
+soft_hard[soft_hard>0]<-1
+softORhard = as.data.frame(soft_hard$Hard+soft_hard$Soft)
+rownames(softORhard)=rownames(soft_hard)
+names(softORhard) = "Type"
+softORhard[softORhard==2]<-"Both"
+softORhard[which(soft_hard$Hard==1 & soft_hard$Soft==0),]<-"Hard"
+softORhard[which(soft_hard$Hard==0 & soft_hard$Soft==1),]<-"Soft"
+
 ```
@@
 nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
+
+#SOft/Hard regime tree
+SHtree = dprunedTree
+hypSH = softORhard$Type[match(SHtree$tip.label,row.names(softORhard))]
+names(hypSH) = SHtree$tip.label
+SHAnc = ace(hypSH, SHtree, type = "discrete")$lik.anc
+HypSHAnc = 1:nrow(SHAnc)
+for(row in 1:nrow(SHAnc)){
+  SCR = scale(SHAnc[row,])
+  print(SCR)
+  HypSHAnc[row] <- rownames(SCR)[which(SCR[,1] == max(SCR[,1]))] %>% print()
+}
+SHtree$node.label = as.factor(HypSHAnc)
+plotTree(SHtree)
+nodelabels(text=SHtree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypSH, frame="none", cex=0.6, adj=c(0,2))
 ```
@@
 
+#using PCs instead of characters
 dprunedmatrix[,c(2:3,5:21)] -> dprunedraw
@@
   }
+
+#LOGISTIC REGRESSION
+copepod = diet$`Copepod diet`
+names(copepod) = rownames(diet)
+heteroneme_elongation = dprunedmatrix_logs$heteroneme_elongation
+names(heteroneme_elongation) = dprunedmatrix_logs$Species
+copepod = copepod[match(dprunedTree$tip.label, names(copepod))]
+heteroneme_elongation = heteroneme_elongation[match(dprunedTree$tip.label, names(heteroneme_elongation))]
+dat = data.frame(heteroneme_elongation, copepod)
+dat = dat[which(!is.nan(dat$heteroneme_elongation)),]
+null = dat
+null$heteroneme_elongation = rep(1, nrow(dat))
+xtree = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% rownames(dat))))
+logit = phyloglm(copepod~heteroneme_elongation,phy=xtree,data=dat,boot=100)
+logit = phyloglm(copepod~,phy=xtree,data=null,boot=100)
+summary(logit)
+coef(logit)
+vcov(logit)
+nlogit = glm(copepod~heteroneme_elongation,data=dat, family="binomial")
+
+logits = data.frame(matrix(ncol = 9, nrow = 0))
+names(logits) = c("Prey type", "Character", "Ntaxa", "phyloglmAIC", "phyloglmP","phyloglm_b","glmAIC", "glmP", "glm_b")
+logit_diet = diet[,-7]
+logits[1,] = rep(1,9)
+for(prey in 1:ncol(logit_diet)){
+  for(char in 2:ncol(dprunedmatrix_logs)){
+    CH_J=logit_diet[,prey]
+    names(CH_J) = rownames(logit_diet)
+    CH_I = dprunedmatrix_logs[,char]
+    names(CH_I) = dprunedmatrix_logs$Species
+    CH_I = CH_I[!is.na(CH_I)]
+    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+    treeIJ = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(CH_J))))
+    CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+    CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+    datIJ = data.frame(preytype = CH_J, character = CH_I)
+      if(length(unique(CH_I))>1 & length(unique(CH_J))>1){
+      logit = glm(preytype~character,data=datIJ, family="binomial")
+      print(logit)
+      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=100)
+      print(phylogit)
+      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
+      } else{
+      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], NA, NA, NA, NA, NA, NA, NA)
+      }
+    print(rowIJ)
+    logits = rbind(logits, rowIJ)
+  }
+}
+logits = logits[-1,]
+logits[,4:9] = sapply(logits[,4:9], as.numeric)
+logits[,4:9] = sapply(logits[,4:9], function(x){round(x,3)})
+write.csv(logits, "logits.csv", row.names = F)
+
+#Soft-Hard logistic regression
+logits = data.frame(matrix(ncol = 9, nrow = 0))
+names(logits) = c("Prey type", "Character", "Ntaxa", "phyloglmAIC", "phyloglmP","phyloglm_b","glmAIC", "glmP", "glm_b")
+logit_diet = soft_hard
+logits[1,] = rep(1,9)
+for(prey in 1:ncol(logit_diet)){
+  for(char in 2:ncol(dprunedmatrix_logs)){
+    CH_J=logit_diet[,prey]
+    names(CH_J) = rownames(logit_diet)
+    CH_I = dprunedmatrix_logs[,char]
+    names(CH_I) = dprunedmatrix_logs$Species
+    CH_I = CH_I[!is.na(CH_I)]
+    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+    treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+    CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+    CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+    datIJ = data.frame(preytype = CH_J, character = CH_I)
+    print(length(unique(CH_J)))
+    print(cbind(CH_I, CH_J))
+      if(length(unique(CH_J))>1){
+      logit = glm(preytype~character,data=datIJ, family="binomial")
+      #print(logit)
+      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=20)
+      #print(phylogit)
+      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
+      print(rowIJ)
+      } else{
+      rowIJ = c(names(logit_diet)[prey], names(dprunedmatrix_logs)[char], phylogit$n, NA, NA, NA, NA, NA, NA)
+      }
+    print(rowIJ)
+    logits = rbind(logits, rowIJ)
+  }
+}
+logits = logits[-1,]
+logits[,4:9] = sapply(logits[,4:9], as.numeric)
+logits[,4:9] = sapply(logits[,4:9], function(x){round(x,3)})
+write.csv(logits, "logits_softhard.csv", row.names = F)
+
+datcombo = dprunedmatrix_logs[,c(1,2,5,7,9)]
+rownames(datcombo) = datcombo[,1]
+datcombo = datcombo[,-1]
+datcombo = datcombo[which(!is.na(rowSums(datcombo))),]
+names(datcombo) = c("heteroneme_length","heteroneme_shaft_length","heteroneme_number", "haploneme_width")
+cop = diet$`Copepod diet`
+names(cop) = rownames(diet)
+cop = cop[which(names(cop) %in% rownames(datcombo))]
+coptree = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(cop))))
+datcombo = datcombo[match(coptree$tip.label, rownames(datcombo)),]
+cop = cop[match(coptree$tip.label, names(cop))]
+combo_phylogit = phyloglm(cop~heteroneme_length+heteroneme_shaft_length+heteroneme_number+haploneme_width,phy=coptree,data=datcombo,boot=10, btol=100)
+coef(summary(combo_phylogit))
 
@@
 ```{r OUwie}
-OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=nrow(dprunedmatrix_logs)))
-names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+OUwie_matrix = as.data.frame(matrix(ncol=5, nrow=nrow(dprunedmatrix_logs)))
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUm")
 library(magrittr)
@@
   BM <- OUwie(Ctree, Cdata, model="BM1")
-  OU <- OUwie(Ctree, Cdata, model="OU1")
+  OU1 <- OUwie(Ctree, Cdata, model="OU1")
+  OUm <- OUwie(Ctree, Cdata, model="OUMV")
   OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
   OUwie_matrix[c-1,2] = nrow(Cdata)
-  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU$AICc))
-  OUwie_matrix[c-1,4] = OU$AICc - min(c(BM$AICc, OU$AICc))
-}
-OUwie_matrix[,3:4] <- apply(OUwie_matrix[,3:4], 2, round3)
+  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+}
+OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
 write.csv(OUwie_matrix, "OU_diet_test.csv")
 
-```
+#SOFT-HARD OUWIE
+
+SH_matrix = as.data.frame(matrix(ncol=5, nrow=nrow(dprunedmatrix_logs)))
+names(SH_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUm")
+for(c in 2:ncol(dprunedmatrix_logs)){
+  Cdata = data.frame(dprunedmatrix$Species,hypSH,dprunedmatrix_logs[,c])
+  names(Cdata) = c("species", "regime", "trait")
+  Cdata$trait[which(Cdata$trait == "NaN")] <- NA
+  Cdata = Cdata[!is.na(Cdata$trait),]
+  Cdata$trait = as.numeric(Cdata$trait)
+  Cdata$species = as.character(Cdata$species)
+  Cdata$regime = as.character(Cdata$regime)
+  Ctree = drop.tip(SHtree,which(!(SHtree$tip.label %in% Cdata$species)))
+  BM <- OUwie(Ctree, Cdata, model="BM1")
+  OU1 <- OUwie(Ctree, Cdata, model="OU1")
+  OUm <- OUwie(Ctree, Cdata, model="OUMV")
+  SH_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
+  SH_matrix[c-1,2] = nrow(Cdata)
+  SH_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  SH_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  SH_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+}
+SH_matrix[,3:5] <- apply(SH_matrix[,3:5], 2, round3)
+write.csv(SH_matrix, "OU_SH_test.csv")
+
+#Using raw morphospace
+rawcoords = Pca_raw$ind$coord[,1:2]
+rawcoords = rawcoords[which(rownames(rawcoords) %in% names(hypdiet)),]
+OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+library(magrittr)
+for(c in 1:ncol(rawcoords)){
+  Cdata = data.frame(rownames(rawcoords),hypdiet[which(names(hypdiet) %in% rownames(rawcoords))],rawcoords[,c])
+  names(Cdata) = c("species", "regime", "trait")
+  Cdata$trait[which(Cdata$trait == "NaN")] <- NA
+  Cdata = Cdata[!is.na(Cdata$trait),]
+  Cdata$trait = as.numeric(Cdata$trait)
+  Cdata$species = as.character(Cdata$species)
+  Cdata$regime = as.character(Cdata$regime)
+  Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
+  BM <- OUwie(Ctree, Cdata, model="BM1")
+  OU1 <- OUwie(Ctree, Cdata, model="OU1")
+  OUm <- OUwie(Ctree, Cdata, model="OUMV")
+  OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
+  OUwie_matrix[c-1,2] = nrow(Cdata)
+  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+}
+OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
+#write.csv(OUwie_matrix, "OU_raw_test.csv")
+
+#Using compound mosphospace
+compcoords = Pca_compound$ind$coord[,1:2]
+compcoords = compcoords[which(rownames(compcoords) %in% names(hypdiet)),]
+OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+library(magrittr)
+for(c in 1:ncol(compcoords)){
+  Cdata = data.frame(rownames(compcoords),hypdiet[which(names(hypdiet) %in% rownames(compcoords))],compcoords[,c])
+  names(Cdata) = c("species", "regime", "trait")
+  Cdata$trait[which(Cdata$trait == "NaN")] <- NA
+  Cdata = Cdata[!is.na(Cdata$trait),]
+  Cdata$trait = as.numeric(Cdata$trait)
+  Cdata$species = as.character(Cdata$species)
+  Cdata$regime = as.character(Cdata$regime)
+  Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
+  BM <- OUwie(Ctree, Cdata, model="BM1")
+  OU1 <- OUwie(Ctree, Cdata, model="OU1")
+  OUm <- OUwie(Ctree, Cdata, model="OUMV")
+  OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
+  OUwie_matrix[c-1,2] = nrow(Cdata)
+  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+}
+OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
+#write.csv(OUwie_matrix, "OU_compound_test.csv")
+```
+
 ```{r, BAMM_output, echo=F}
@@
 Euphysonect tentilla discharge considerably faster than Calycophoran tentilla.
-Larger heteronemes discharge faster than small ones, giving Euphysonects a faster heteroneme discharge speed than most calycophorans.
+Larger heteronemes discharge faster than small ones, giving Euphysonects a faster heteroneme discharge speed than most Calycophorans.
 On the contrary, Calycophoran haploneme tubules fire faster than those of Euphysonects.

### 2019-02-12 manuscript.rmd
added screenshots, added final hypotheses testing analyses

@@
 
+#Categorical-Continuous correlations
+catlogits = data.frame(matrix(ncol = 6, nrow = 0))
+names(catlogits) = c("Character binary", "Character continuous", "Ntaxa", "phyloglmAIC", "phyloglmP","phyloglm_b")
+catlogits[1,]=rep(1,6)
+binary=categorical[,2:9]
+for(cat in 1:ncol(binary)){
+  for(char in 2:ncol(sharedmean_logs)){
+    CH_J=binary[,cat]
+    names(CH_J) = rownames(binary)
+    CH_J = CH_J[!is.na(CH_J)]
+    CH_I = sharedmean_logs[,char]
+    names(CH_I) = sharedmean_logs$Species
+    CH_I = CH_I[!is.na(CH_I)]
+    CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+    CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
+    treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+    CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+    CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+    datIJ = data.frame(char_cat = CH_J, char_con = CH_I)
+    if(length(unique(CH_J))>1){
+      phylogit = phyloglm(char_cat~char_con,phy=treeIJ,data=datIJ,boot=10, btol=20)
+      print(phylogit)
+      rowIJ = c(names(binary)[cat], names(sharedmean_logs)[char], phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1])
+      } else{
+      rowIJ = c(names(binary)[cat], names(sharedmean_logs)[char], phylogit$n, NA, NA, NA)
+      }
+    #print(rowIJ)
+    catlogits = rbind(catlogits, rowIJ)
+    print(catlogits[nrow(catlogits),])
+  }
+}
+catlogits = catlogits[-1,]
+catlogits[,4:6] = sapply(catlogits[,4:6], as.numeric)
+catlogits[,4:6] = sapply(catlogits[,4:6], function(x){round(x,3)})
+write.csv(catlogits, "catlogits.csv", row.names = F)
+
 ```
@@
 #Retrieve diet info from literature BINARY
-GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5)] %>% .[which(grepl("diet",.$character) & .$state==1),]
+GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5,6)] %>% .[which(grepl("diet",.$character) & .$state==1),]
 GC$character = factor(GC$character, levels=unique(GC$character))
@@
 GC$species[which(GC$species == "Nanomia bijuga")] <- "Nanomia sp"
-GC = GC[which(GC$species %in% sharedmeans$Species),]
+GC$species[which(GC$species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
+GC$species[which(GC$species == "Agalma okeni")] <- "Agalma okenii"
+GC = GC[which(GC$species %in% ultram$tip.label),]
 GC = split(GC,GC$character)
@@
 diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
-cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0),4),nrow=9, ncol = 4) %>% t() %>% as.data.frame()
-names(cladeB) = names(diet)
-rownames(cladeB) = c("Erenna richardi", "Erenna laciniata", "Erenna sirena", "Stephanomia amphytridis")
-krilleaters = matrix(rep(c(0,0,0,0,0,1,1,0,0),2),nrow=9, ncol = 2) %>% t() %>% as.data.frame()
-names(krilleaters) = names(diet)
-rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala")
-diet = rbind(diet, cladeB, krilleaters)
+#Add hypothesized diet from personal observations of the authors
+cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0),3),nrow=10, ncol = 3) %>% t() %>% as.data.frame()
+rownames(cladeB) = c("Erenna richardi", "Erenna sirena", "Stephanomia amphytridis")
+krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0),4),nrow=10, ncol = 4) %>% t() %>% as.data.frame()
+rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala", "Lychnagalma utricularia", "Bargmannia amoena")
+Gelatinous_diet = rep(0,nrow(diet))
+diet = cbind(diet, Gelatinous_diet)
+names(diet)[ncol(diet)] = "Gelatinous diet"
+gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1),1),nrow=10, ncol = 1) %>% t() %>% as.data.frame()
+names(gelateaters) = names(diet)
+rownames(gelateaters) = c("Apolemia rubriversa")
+names(gelateaters)=names(diet)
+names(krilleaters)=names(diet)
+names(cladeB)=names(diet)
+diet = rbind(diet, cladeB, krilleaters, gelateaters)
 #rownames(diet)[12] = 'Erenna richardi'
@@
 PP$species[which(PP$species == "Nanomia bijuga")] <- "Nanomia sp"
+PP$species[which(PP$species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
+PP$species[which(PP$species == "Agalma okeni")] <- "Agalma okenii"
 PP = PP[which(PP$species %in% sharedmeans$Species),]
@@
 names(preylength) = c("Species","Copepod prey length (mm)")
-PL_pruned_matrix = sharedmeans[which(sharedmeans$Species %in% preylength$Species),] %>% data.frame(preylength[which(preylength$Species %in% sharedmeans$Species),2])
+PL_pruned_matrix = sharedmean_logs[which(sharedmean_logs$Species %in% preylength$Species),] %>% data.frame(preylength[which(preylength$Species %in% sharedmean_logs$Species),2])
+PL_pruned_SEs = sharedvar_logs[which(sharedvar_logs$Species %in% preylength$Species),] %>% data.frame(preylength[which(preylength$Species %in% sharedmean_logs$Species),2])
 names(PL_pruned_matrix)[ncol(PL_pruned_matrix)] <- "Copepod prey length (mm)"
+names(PL_pruned_SEs)[ncol(PL_pruned_matrix)] <- "Copepod prey length (mm)"
+
+pGLSp_preylength = as.data.frame(matrix(nrow=ncol(PL_pruned_matrix[,-1]), ncol=1))
+colnames(pGLSp_preylength) = "Copepod prey length"
+row.names(pGLSp_preylength) = names(PL_pruned_matrix[,-1])
+pGLS_PL_sign = pGLSp_preylength
+pGLS_sign = pGLSp_preylength
+for(i in 2:(ncol(PL_pruned_matrix)-1)){
+  CH_I=as.numeric(PL_pruned_matrix[,i])
+  names(CH_I) = PL_pruned_matrix$Species
+  CH_I = CH_I[!is.na(CH_I)]
+  CH_J=PL_pruned_matrix[,ncol(PL_pruned_matrix)]
+  names(CH_J) = PL_pruned_matrix$Species
+  CH_I = CH_I[!is.na(CH_I)]
+  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
+  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
+  SE_I = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),i]
+  names(SE_I) = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),1]
+  SE_I = SE_I[match(names(CH_I), names(SE_I))]
+  pgls_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_I))))
+  pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
+  pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
+  pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
+  TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
+  TTABLE$`p-value`[2] -> pGLSp_preylength[i-1,1]
+  if(pGLSp_preylength[i-1,1]<0.05){
+     print(paste(rownames(pGLSp_preylength)[i-1],"Copepod prey length",pGLSp_preylength[(i-1),1],sep=" "))
+     ValueIJ = TTABLE %>% .$Value %>% .[2]
+     if(ValueIJ>0){pGLS_PL_sign[i-1,1] = "+"}
+      else pGLS_PL_sign[i,1] = "-"
+  }
+}
+write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
+pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
+write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")
+for(i in 2:ncol(PL_pruned_matrix)){
+  plot(PL_pruned_matrix[,i], PL_pruned_matrix$`Copepod prey length (mm)`)
+}
 
@@
 #Soft vs Hard
-soft_hard = cbind((diet$`Copepod diet`+diet$`Amphipod diet`+diet$`Crustacean diet` + diet$`Decapod diet` + diet$`Ostracod diet`), (diet$`Fish diet`+diet$`Polychaete diet`+diet$`Chaetognath diet`+diet$`Mollusc diet`))
+soft_hard = cbind((diet$`Copepod diet`+diet$`Crustacean diet` + diet$`Decapod diet`+ diet$`Amphipod diet` + diet$`Ostracod diet`), (diet$`Fish diet`+diet$`Chaetognath diet`+diet$`Gelatinous diet`+diet$`Mollusc diet`+diet$`Polychaete diet`))
 colnames(soft_hard) = c("Hard", "Soft")
@@
 
+#Nematocyst type number
+nematocyst_number=as.numeric(categorical$Heteroneme.type!="")[which(!is.na(categorical$Desmonemes))]+as.numeric(categorical$Haploneme.type!="")[which(!is.na(categorical$Desmonemes))]+as.numeric(categorical$Rhopalonemes!="0")[which(!is.na(categorical$Desmonemes))]+as.numeric(categorical$Desmonemes!="0")[which(!is.na(categorical$Desmonemes))]
+names(nematocyst_number)=categorical$Species[which(!is.na(categorical$Desmonemes))]
+CH_J=softORhard[,1]
+names(CH_J) = rownames(softORhard)
+CH_J[CH_J!="Soft"]<-0
+CH_J[CH_J=="Soft"]<-1
+CH_I = nematocyst_number
+CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
+treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+datIJ = data.frame(preytype = CH_J, character = CH_I)
+datIJ$preytype = as.numeric(as.character(datIJ$preytype))
+logit = glm(preytype~character,data=datIJ, family="binomial")
+    print(logit)
+phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=10)
+    print(phylogit)
+c("Soft specilization", "Number of nematocyst types", phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
+
+#Desmoneme/Rhopaloneme vs crustacean
+dprunedCat = binary[which(rownames(binary)%in% rownames(diet)),]
+CH_I = dprunedCat$Rhopalonemes
+names(CH_I) = rownames(dprunedCat)
+CH_J = diet$`Crustacean diet`
+names(CH_J) = rownames(diet)
+CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
+treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+fitPagel(treeIJ, CH_I, CH_J)
+
+#Differentiated cnidobands with heteronemes
+CH_I = dprunedCat$Proximal.heteronemes
+names(CH_I) = rownames(dprunedCat)
+CH_J = diet$`Crustacean diet`
+names(CH_J) = rownames(diet)
+CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
+treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+fitPagel(treeIJ, CH_I, CH_J) %>% .$P
+
 ```
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Copepod", "Crustacean", "Copepod", "Crustacean", "Crustacean", "Mixed", "Mixed", "Crustacean", "Mixed", "Copepod", "Crustacean", "Fish", "Fish", "Fish", "Fish", "Fish", "Fish")
+hypdiet = c("Mixed", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
 names(hypdiet) = regimetree$tip.label
@@
 nodelabels(text=SHtree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypSH, frame="none", cex=0.6, adj=c(0,2))
+
+#Stenoteles vs large crustaceans
+stenoteles = categorical$Heteroneme.type %>% as.character()
+categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+categorical$Species<-as.character(categorical$Species)
+categorical$Species[which(categorical$Species == "Agalma okeni")] <- "Agalma okenii"
+categorical$Species[which(categorical$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+categorical$Species[which(categorical$Species == "Nanomia bijuga")] <- "Nanomia sp"
+names(stenoteles)=categorical$Species
+stenoteles[stenoteles!="Stenotele"]<-0
+stenoteles[stenoteles=="Stenotele"]<-1
+shrimp = hypdiet
+shrimp[shrimp!="Large crustacean" & shrimp!= "Mixed"]<-0
+shrimp[shrimp=="Large crustacean" | shrimp== "Mixed"]<-1
+stenoteles = stenoteles[which(names(stenoteles) %in% names(shrimp))]
+stenoteles = stenoteles[match(names(shrimp), names(stenoteles))]
+fitPagel(dprunedTree, stenoteles, shrimp) %>% .$P
+
 ```
@@
       print(logit)
-      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=100)
+      phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=30)
       print(phylogit)
@@
 names(X) = dprunedmatrix_logs$Species
+X=X[!(is.na(X))]
 Y = diet$`Decapod diet`
 names(Y) = rownames(diet)
+
+X = nematocyst_number
+Y = soft_hard$Soft
+Y=softORhard[,1]
+names(Y) = rownames(softORhard)
+Y[Y!="Soft"]<-0
+Y[Y=="Soft"]<-1
+
 Y = Y[which(names(Y) %in% names(X))]
+X = X[which(names(X) %in% names(Y))]
 treeXY = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(X))))
@@
 rawcoords = rawcoords[which(rownames(rawcoords) %in% names(hypdiet)),]
-OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
-names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+OUwie_matrix = as.data.frame(matrix(ncol=5, nrow=2))
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
 library(magrittr)
@@
   OUm <- OUwie(Ctree, Cdata, model="OUMV")
-  OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
-  OUwie_matrix[c-1,2] = nrow(Cdata)
-  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,1] = c("PC1","PC2")[c]
+  OUwie_matrix[c,2] = nrow(Cdata)
+  OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
 }
 OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
-#write.csv(OUwie_matrix, "OU_raw_test.csv")
+write.csv(OUwie_matrix, "OU_raw_test.csv")
 
@@
 OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
-names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU")
+names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
 library(magrittr)
@@
   OUm <- OUwie(Ctree, Cdata, model="OUMV")
-  OUwie_matrix[c-1,1] = names(dprunedmatrix_logs)[c]
-  OUwie_matrix[c-1,2] = nrow(Cdata)
-  OUwie_matrix[c-1,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c-1,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c-1,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,1] = c("PC1","PC2")[c]
+  OUwie_matrix[c,2] = nrow(Cdata)
+  OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+  OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
 }
 OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
-#write.csv(OUwie_matrix, "OU_compound_test.csv")
+write.csv(OUwie_matrix, "OU_compound_test.csv")
 ```

### 2019-03-08 manuscript.rmd
added some final figures

@@
 library(xtable)
+library(colorRamps)
 
@@
   names(castSE_logs)[1] <- "Species"
+
+#Define fx Phenogram
+Phenogram <- function(a,b,c){
+  contTrait <- a
+  names(contTrait) = rownames(b)
+  contTrait = contTrait[!is.na(contTrait)]
+  treeI = drop.tip(c,which(!(c$tip.label %in% names(contTrait))))
+  A<-fastAnc(treeI,contTrait,CI=TRUE)
+  paintree<-paintSubTree(treeI,node=length(c$tip)+1,"1")
+  trans<-as.character(floor(0:50/2))
+  trans[as.numeric(trans)<10]<- paste("0", trans[as.numeric(trans)<10],sep="")
+  for(i in 0:50){
+    p<-i/length(trans)
+    phenogram(treeI,c(contTrait,(1-p)*A$CI95[,1]+p*A$ace), colors=setNames(paste("#0000ff",trans[i+1],sep=""),1), add=i>0)
+    phenogram(treeI,c(contTrait,(1-p)*A$CI95[,2]+p*A$ace), colors=setNames(paste("#0000ff",trans[i+1],sep=""),1), add=TRUE)
+  }
+  phenogram(treeI,c(contTrait,A$ace),add=TRUE, colors=setNames("black",1))
+}
 ```
@@
 
-#write.csv(morphdata, "characterdata.csv")
-grid.newpage()
-grid.table(morphdata)
+write.csv(morphdata, "characterdata.csv")
 
@@
 rownames(heatdata) = castmean_logs$Species
-heatmap(heatdata, scale = "column", cexCol = 0.5, col=terrain.colors(20))
+heatdata[is.nan(heatdata)]<- -1
+hcolors = white2blue(19)
+hcolors<-c(rep("#000000FF",10), hcolors)
+heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)
+
 ```
@@
 }
-#write.csv(phylosignals, "PhylosignalsWSE_log.csv")
+write.csv(phylosignals, "PhylosignalsWSE_log.csv")
 ```
@@
 names(hap_el) = sharedmean_logs$Species
+
+###
+cysthets = c(0,0,0)
+names(cysthets) = c("Physalia physalis", "Rhizophysa eysenhardtii", "Rhizophysa filiformis")
+het_el = c(het_el, cysthets)
+###
 het_el = het_el[which(!is.na(het_el))]
@@
 hap_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(hap_el))))
-phenogram(het_tree, het_el)
-phenogram(hap_tree, hap_el)
+Phenogram(het_tree, het_el)
+Phenogram(hap_el, as.data.frame(hap_el), hap_tree)
 
@@
 het_el = het_el[which(names(het_el) %in% names(hap_el))]
+het_el = het_el[match(names(hap_el), names(het_el))]
 elon_data = cbind(het_el, hap_el) %>% as.data.frame()
@@
 
+cbind(as.vector(phy_corr), as.vector(cor(C))) %>% as.data.frame()->phyreg
+names(phyreg)<-c("Phylo", "Reg")
+ggplot(phyreg, aes(x=Reg, y=Phylo, color=(Phylo+Reg)/2)) + geom_point() + geom_hline(yintercept = 0)  + geom_vline(xintercept = 0) + theme_bw()
+abline(h=0)
+abline(v=0)
+
 #Change directionalities
@@
   }
-  #hist(changes)
-  #abline(v=0,col="red")
+  hist(changes)
+  abline(v=0,col="red")
 }
@@
 phylomorphospace(tree=raw_tree, Pca_raw$ind$coord[,3:4], label = "horizontal", xlab = "PC3", ylab = "PC4")
-physignal(Pca_raw$ind$coord, raw_tree)
+physignal(Pca_raw$ind$coord[,2], raw_tree)
 multiPhylosignal(Pca_raw$ind$coord, raw_tree)
+phylosignal(Pca_raw$ind$coord[,1], raw_tree)
   ##Morphometric characters
@@
 }
-#write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
+write.csv(pGLSp_diet, "PGLS_Pval_DietPP.csv")
 pGLS_sign <- pGLS_sign[which(rowSums(is.na(pGLS_sign))!=ncol(pGLS_sign)),which(colSums(is.na(pGLS_sign))!=nrow(pGLS_sign))]
@@
 logits[,4:9] = sapply(logits[,4:9], function(x){round(x,3)})
-write.csv(logits, "logits.csv", row.names = F)
+write.csv(logits, "diet_morph_logits.csv", row.names = F)
 
@@
 #Using compound mosphospace
-compcoords = Pca_compound$ind$coord[,1:2]
-compcoords = compcoords[which(rownames(compcoords) %in% names(hypdiet)),]
-OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
-names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
-library(magrittr)
-for(c in 1:ncol(compcoords)){
-  Cdata = data.frame(rownames(compcoords),hypdiet[which(names(hypdiet) %in% rownames(compcoords))],compcoords[,c])
-  names(Cdata) = c("species", "regime", "trait")
-  Cdata$trait[which(Cdata$trait == "NaN")] <- NA
-  Cdata = Cdata[!is.na(Cdata$trait),]
-  Cdata$trait = as.numeric(Cdata$trait)
-  Cdata$species = as.character(Cdata$species)
-  Cdata$regime = as.character(Cdata$regime)
-  Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
-  BM <- OUwie(Ctree, Cdata, model="BM1")
-  OU1 <- OUwie(Ctree, Cdata, model="OU1")
-  OUm <- OUwie(Ctree, Cdata, model="OUMV")
-  OUwie_matrix[c,1] = c("PC1","PC2")[c]
-  OUwie_matrix[c,2] = nrow(Cdata)
-  OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-  OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
-}
-OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
-write.csv(OUwie_matrix, "OU_compound_test.csv")
+# compcoords = Pca_compound$ind$coord[,1:2]
+# compcoords = compcoords[which(rownames(compcoords) %in% names(hypdiet)),]
+# OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
+# names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
+# library(magrittr)
+# for(c in 1:ncol(compcoords)){
+#   Cdata = data.frame(rownames(compcoords),hypdiet[which(names(hypdiet) %in% rownames(compcoords))],compcoords[,c])
+#   names(Cdata) = c("species", "regime", "trait")
+#   Cdata$trait[which(Cdata$trait == "NaN")] <- NA
+#   Cdata = Cdata[!is.na(Cdata$trait),]
+#   Cdata$trait = as.numeric(Cdata$trait)
+#   Cdata$species = as.character(Cdata$species)
+#   Cdata$regime = as.character(Cdata$regime)
+#   Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
+#   BM <- OUwie(Ctree, Cdata, model="BM1")
+#   OU1 <- OUwie(Ctree, Cdata, model="OU1")
+#   OUm <- OUwie(Ctree, Cdata, model="OUMV")
+#   OUwie_matrix[c,1] = c("PC1","PC2")[c]
+#   OUwie_matrix[c,2] = nrow(Cdata)
+#   OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+#   OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+#   OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
+# }
+# OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
+# write.csv(OUwie_matrix, "OU_compound_test.csv")
 ```
@@
 
+``` {r kine}
+kine = read.csv("Kinematics.tsv", sep='\t', header=T) #%>% .[which(apply(., 1, function(x) sum(is.na(x)))<ncol(.)-2),-2]
+kineWNA = kine[which(kine$Species %in% ultram$tip.label),]
+rownames(kineWNA)=kineWNA$Specimen
+rownames(kine)=kine$Specimen
+#kineWNA = kineWNA[,-1]
+#kine=kine[,-1]
+kinetree = drop.tip(ultram, which(!(ultram$tip.label %in% kine$Species)))
+kinetree$edge.length = 200*kinetree$edge.length
+#kine_clean = kineWNA[,which(colSums(kineWNA)>1)]
+#names(kine) = c("ADS", "MDS", "HeDS","HeMDS", "HSDS", "HFL", "HaDS")
+kine_byspp = aggregate(. ~ kine$Species, data = kine[,c(-1,-2)], mean.na, na.action = na.pass)
+names(kine_byspp)[1] <- "Species"
+kinemorph <- castmeans[which(castmeans$Species %in% kine_byspp$Species),] %>% cbind(kine_byspp[which(kine_byspp$Species %in% castmeans$Species),])
+plot(kinemorph$Cnidoband.free.length..um., kinemorph$Average.CB.discharge.speed..mm.s.)
+calys = kinemorph$Species[c(5,9,12,15,16,17,18)]
+euphys = kinemorph$Species[which(!(kinemorph$Species %in% calys))]
+relspeed = data.frame(kinemorph$Species, c(kinemorph$Average.CB.discharge.speed..mm.s./kinemorph$Cnidoband.free.length..um.))
+names(relspeed) = c("Species", "Speed/Length")
+relspeed <- relspeed[which(!(is.na(relspeed$`Speed/Length`))),]
+t.test(relspeed[which(relspeed$Species %in% calys),2], relspeed[which(relspeed$Species %in% euphys),2])
+t.test(kine$Average.CB.discharge.speed..mm.s.[which(kine$Species %in% calys)], kine$Average.CB.discharge.speed..mm.s.[which(kine$Species %in% euphys)])
+t.test(castnumbers$Cnidoband.free.length..um.[which(castnumbers$Species %in% calys)], castnumbers$Cnidoband.free.length..um.[which(castnumbers$Species %in% euphys)])
+lm(kinemorph$Average.CB.discharge.speed..mm.s.~ kinemorph$Cnidoband.free.length..um.) %>% summary()
+lm(kinemorph$Heteroneme.discharge.speed.MAX..mm.s.~ kinemorph$Heteroneme.volume..um3.) %>% summary()
+t.test(kine$Heteroneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% calys)], kine$Heteroneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% euphys)])
+t.test(kine$Haploneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% calys)], kine$Haploneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% euphys)])
+t.test(kine$Haploneme.discharge.speed.AVG..mm.s., kine$Heteroneme.discharge.speed.AVG..mm.s.)
+cor(kinemorph[,c(-1,-32)], use="pairwise.complete.obs") %>% .[c(1:30),c(31:41)] %>% corrplot(diag=F, tl.cex = 0.4, tl.col="black")
+
+```
+
 High-speed video of cnidoband and nematocyst discharge revealed the roles of the different tentillum substructures in the mechanics of discharge.

### 2019-03-12 manuscript.rmd
polished some tables, changed Apolemia cnidoband sizes from 0 to NA

@@
 pANOVAs_diet[pANOVAs_diet>0.05] <- NA
-write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")
+#write.csv(pANOVAs_diet, "pANOVAS_Diet.csv")
 
@@
 #LOGISTIC REGRESSION
-copepod = diet$`Copepod diet`
-names(copepod) = rownames(diet)
-heteroneme_elongation = dprunedmatrix_logs$heteroneme_elongation
-names(heteroneme_elongation) = dprunedmatrix_logs$Species
-copepod = copepod[match(dprunedTree$tip.label, names(copepod))]
-heteroneme_elongation = heteroneme_elongation[match(dprunedTree$tip.label, names(heteroneme_elongation))]
-dat = data.frame(heteroneme_elongation, copepod)
-dat = dat[which(!is.nan(dat$heteroneme_elongation)),]
-null = dat
-null$heteroneme_elongation = rep(1, nrow(dat))
-xtree = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% rownames(dat))))
-logit = phyloglm(copepod~heteroneme_elongation,phy=xtree,data=dat,boot=100)
-logit = phyloglm(copepod~,phy=xtree,data=null,boot=100)
-summary(logit)
-coef(logit)
-vcov(logit)
-nlogit = glm(copepod~heteroneme_elongation,data=dat, family="binomial")
-
 logits = data.frame(matrix(ncol = 9, nrow = 0))

### 2019-03-12 manuscript.rmd
polished some tables, changed Sulculeolaria to small crustacean specialist

@@
 #Model support
-  Q_sharedmean_logs$Heteroneme_to_CB[which(Q_sharedmean_logs$Heteroneme_to_CB > 9)] <- NA
   AICdf = as.data.frame(matrix(ncol=6,nrow=ncol(Q_sharedmean_logs)))
@@
 PP=PP[,-1]
-#PP = rbind(PP, c(0,100,0,0,0,0,0,0))
-#rownames(PP)[10] = "Erenna richardi"
 Pprunedmatrix=sharedmeans[which(sharedmeans$Species%in%rownames(PP)),]
@@
 plot(Pprunedtree)
+
+selectivity = read.csv("PurcellSiphonophoresDiet.csv", header=T, sep=",")[,c(1,31:39)]
+selectivity$Species <- as.character(selectivity$Species)
+selectivity$Species[which(selectivity$Species == "Nanomia bijuga")] <- "Nanomia sp"
+selectivity$Species[which(selectivity$Species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
+selectivity = aggregate(. ~ Species, data=selectivity, FUN=mean)
+rownames(selectivity) = selectivity$Species
+selectivity=selectivity[,-1]
+Sprunedmatrix = sharedmeans[which(sharedmeans$Species%in%rownames(selectivity)),]
+Sprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(selectivity)),]
+selectivity = selectivity[which(rownames(selectivity) %in% sharedmeans$Species),]
+Sprunedtree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(selectivity))))
+plot(Sprunedtree)
 
@@
 regimetree = dprunedTree
-hypdiet = c("Mixed", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
+hypdiet = c("Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
 names(hypdiet) = regimetree$tip.label
@@
 fitPagel(dprunedTree, stenoteles, shrimp) %>% .$P
+
+#Diet heatmap next to regime tree
+RTorder = regimetree$tip.label
+diet[match(RTorder, rownames(diet)),] %>% as.matrix() %>% heatmap(Rowv=NA, Colv=NA, col=c("grey", "black"))
 
@@
 pGLS_sign <- pGLS_sign[which(rowSums(is.na(pGLS_sign))!=ncol(pGLS_sign)),which(colSums(is.na(pGLS_sign))!=nrow(pGLS_sign))]
-write.csv(pGLS_sign, "PGLS_SIGN_DietPP.csv")
+#write.csv(pGLS_sign, "PGLS_SIGN_DietPP.csv")
+
+#PGLS with Purcell Selectivity
+pGLSp_sel = as.data.frame(matrix(nrow=ncol(Sprunedmatrix_logs[,-1]), ncol=ncol(selectivity)))
+pGLS__sel_sign = pGLSp_sel
+colnames(pGLSp_sel) = names(selectivity)
+row.names(pGLSp_sel) = names(Sprunedmatrix_logs[,-1])
+pGLS_sel_sign = pGLSp_sel
+for(i in 2:ncol(Sprunedmatrix_logs)){
+  CH_I=as.numeric(Sprunedmatrix_logs[,i])
+  names(CH_I) = Sprunedmatrix_logs$Species
+  CH_I = CH_I[!is.na(CH_I)]
+  for(j in 1:ncol(selectivity)){
+    CH_J=as.numeric(selectivity[,j])
+    names(CH_J) = rownames(selectivity)
+    CH_J = CH_J[!is.na(CH_J)]
+    CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
+    CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
+    SE_I = castSE_logs[which(castSE$Species %in% names(CH_I)),i]
+    names(SE_I) = castSE_logs[which(castSE$Species %in% names(CH_I)),1]
+    SE_I = SE_I[match(names(CH_I), names(SE_I))]
+    pgls_tree = drop.tip(Sprunedtree, which(!(Sprunedtree$tip.label %in% names(CH_I))))
+    pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
+    if(length(unique(CH_J))>1){
+          pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
+          pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
+          LikRat <- 2*(TTABLE$logLik[1] - TTABLE_null$logLik[1])
+          pchisq(LikRat, df=1, lower.tail = F) -> pGLSp_sel[i-1,j]
+          if(pGLSp_sel[i-1,j]<0.05){
+          print(paste(rownames(pGLSp_sel)[i-1],colnames(pGLSp_sel)[j],pGLSp_sel[(i-1),(j)],TTABLE$coefficients[2], sep=" "))
+          ValueIJ = TTABLE %>% .$coefficients %>% .[2]
+          if(ValueIJ>0){pGLS_sel_sign[i-1,j] = "+"}
+          else pGLS_sel_sign[i,j] = "-"
+         }
+       }
+    else TTABLE<-NA; TTABLE_null<-NA; LikRat<-NA; pGLSp_sel[i-1,j]<-NA
+  }
+}
+write.csv(pGLSp_sel, "PGLS_Pval_Selectivity.csv")
+pGLS_sel_sign <- pGLS_sel_sign[which(rowSums(is.na(pGLSp_sel))!=ncol(pGLS_sel_sign)),which(colSums(is.na(pGLS_sel_sign))!=nrow(pGLS_sel_sign))]
+write.csv(pGLS_sel_sign, "PGLS_SIGN_Selectivity.csv")
 

### 2019-03-13 BAMM/BAMMsetpriors.R
figure improvement, BAMM redo

@@ -2,7 +2,7 @@ library(BAMMtools)
 library(stringr)
 library(readr)
 setwd("~/tentilla_morph/BAMM")
-tree <- read.tree("Desmoneme.length..um._tree.tre")
+tree <- read.tree("haploneme_elongation_tree.tre")
 traits <- read.csv("Desmoneme.length..um..txt", sep="\t", header = F)
 rownames(traits) = traits[,1]
 traits <- traits[tree$tip.label,]
@@ -11,4 +11,5 @@ is.ultrametric(tree) # check for ultrametric
 is.binary.tree(tree) # check if there are no polytomies
 min(tree$edge.length) # check all branch lengths are > 0
 setBAMMpriors(phy = tree, traits = "Desmoneme.length..um..txt")
+setwd("~/tentilla_morph/")
 #q()

### 2019-03-13 BAMM/BAMMplots.R
finished BAMM analyses of nematcosyt shape

@@ -4,7 +4,7 @@ library(geiger)
 library(coda)
 setwd("~/tentilla_morph/BAMM")
 # load tree
-tree <- read.tree("Desmoneme.length..um._tree.tre")
+tree <- read.tree("heteroneme_elongation_tree.tre")
 
 # ESS after 20% burnin
 mcmcout <- read.csv("mcmc_out.txt")
@@ -19,18 +19,18 @@ summary(edata)
 
 # the 6 most likely scenario's within the 95% credible scenarios
 # F value is the relative probability, F values from all scenarios add up to F=1
-pdf("BAMM_css.pdf", width=7, height=10)
+pdf("BAMM_heteroneme_elongation_css.pdf", width=7, height=10)
 css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
-BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T)
+BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T, use.plot.bammdata = T)
 dev.off()
 
 # net diversification graph
-pdf("BAMM_netdiv.pdf", width=7, height=5)
+pdf("BAMM_heteroneme_elongation_netdiv.pdf", width=7, height=5)
 starttime <- max(branching.times(tree))
 plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
 dev.off()
 
-pdf("_ratesplot.pdf",width=16,height=16)
+pdf("heteroneme_elongation_ratesplot.pdf",width=16,height=16)
 plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
 dev.off()
 

### 2019-03-13 BAMM/BAMMsetpriors.R

@@ -2,14 +2,14 @@ library(BAMMtools)
 library(stringr)
 library(readr)
 setwd("~/tentilla_morph/BAMM")
-tree <- read.tree("haploneme_elongation_tree.tre")
-traits <- read.csv("Desmoneme.length..um..txt", sep="\t", header = F)
+tree <- read.tree("heteroneme_elongation_tree.tre")
+traits <- read.csv("heteroneme_elongation.txt", sep="\t", header = F)
 rownames(traits) = traits[,1]
 traits <- traits[tree$tip.label,]
-write_tsv(traits, "Desmoneme.length..um..txt", col_names = FALSE)
+write_tsv(traits, "heteroneme_elongation.txt", col_names = FALSE)
 is.ultrametric(tree) # check for ultrametric
 is.binary.tree(tree) # check if there are no polytomies
 min(tree$edge.length) # check all branch lengths are > 0
-setBAMMpriors(phy = tree, traits = "Desmoneme.length..um..txt")
+setBAMMpriors(phy = tree, traits = "heteroneme_elongation.txt")
 setwd("~/tentilla_morph/")
 #q()

### 2019-03-14 BAMM/BAMMplots.R
added intro anatomy figure

@@ -4,7 +4,7 @@ library(geiger)
 library(coda)
 setwd("~/tentilla_morph/BAMM")
 # load tree
-tree <- read.tree("heteroneme_elongation_tree.tre")
+tree <- read.tree("desmoneme_elongation_tree.tre")
 
 # ESS after 20% burnin
 mcmcout <- read.csv("mcmc_out.txt")
@@ -19,18 +19,18 @@ summary(edata)
 
 # the 6 most likely scenario's within the 95% credible scenarios
 # F value is the relative probability, F values from all scenarios add up to F=1
-pdf("BAMM_heteroneme_elongation_css.pdf", width=7, height=10)
+pdf("BAMM_desmoneme_elongation_css.pdf", width=7, height=10)
 css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
 BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T, use.plot.bammdata = T)
 dev.off()
 
 # net diversification graph
-pdf("BAMM_heteroneme_elongation_netdiv.pdf", width=7, height=5)
+pdf("BAMM_desmoneme_elongation_netdiv.pdf", width=7, height=5)
 starttime <- max(branching.times(tree))
 plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
 dev.off()
 
-pdf("heteroneme_elongation_ratesplot.pdf",width=16,height=16)
+pdf("desmoneme_elongation_ratesplot.pdf",width=16,height=16)
 plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
 dev.off()
 

### 2019-03-14 BAMM/BAMMsetpriors.R

@@ -2,14 +2,14 @@ library(BAMMtools)
 library(stringr)
 library(readr)
 setwd("~/tentilla_morph/BAMM")
-tree <- read.tree("heteroneme_elongation_tree.tre")
-traits <- read.csv("heteroneme_elongation.txt", sep="\t", header = F)
+tree <- read.tree("desmoneme_elongation_tree.tre")
+traits <- read.csv("desmoneme_elongation.txt", sep="\t", header = F)
 rownames(traits) = traits[,1]
 traits <- traits[tree$tip.label,]
-write_tsv(traits, "heteroneme_elongation.txt", col_names = FALSE)
+write_tsv(traits, "desmoneme_elongation.txt", col_names = FALSE)
 is.ultrametric(tree) # check for ultrametric
 is.binary.tree(tree) # check if there are no polytomies
 min(tree$edge.length) # check all branch lengths are > 0
-setBAMMpriors(phy = tree, traits = "heteroneme_elongation.txt")
+setBAMMpriors(phy = tree, traits = "desmoneme_elongation.txt")
 setwd("~/tentilla_morph/")
 #q()

### 2019-03-15 manuscript.rmd
added phylogeny inference folder

@@
 
+#Cnidoband size evolution
+cnisize = sharedmean_logs$cnidomic_index
+names(cnisize) = sharedmean_logs$Species
+treei = drop.tip(ultram, which(!(ultram$tip.label %in% names(cnisize))))
+Phenogram(cnisize, as.data.frame(cnisize), treei)
+
 ```
@@
 #PIC correlations with Rphylip
-#C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
+#C = sharedlogs[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),] ##Doesn't work
 C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
@@
 PICi = Rcontrast(tree=Ctree, X=C, path="phylip-3.695/exe", cleanup=TRUE)
+
+#PIC correlations by character, to get significance
+PICp = as.data.frame(matrix(nrow=ncol(C), ncol=ncol(C)))
+colnames(PICp) = colnames(C)
+rownames(PICp) = colnames(C)
+for(i in 2:ncol(sharedmean_logs)){
+  Ci = sharedmean_logs[,i]
+  names(Ci) = sharedmean_logs$Species
+  Ci = Ci[!is.na(Ci)]
+  for(j in 2:ncol(sharedmean_logs)){
+    Cj = sharedmean_logs[,j]
+    names(Cj) = sharedmean_logs$Species
+    Cj = Cj[!is.na(Cj)]
+    Cj = Cj[which(names(Cj) %in% names(Ci))]
+    Ci = Ci[which(names(Ci) %in% names(Cj))]
+    if(i!=j){
+      ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(Cj))))
+      class(ctree)<-"phylo"
+      pic_i = pic(Ci, ctree)
+      pic_j = pic(Cj, ctree)
+      cor.test(pic_i, pic_j)$p.value %>% round3() -> PICp[i-1,j-1]
+    }
+    else PICp[i-1,j-1]<-NA
+  }
+}
+write.csv(PICp, "PICcorrelations_pvalues.csv")
 
@@
 write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
-pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
+#pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
 write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")

### 2019-03-15 Phylogeny_inference/agalma_16S18S_extraction.py

@@ -1,0 +1,32 @@
+import sqlite3
+
+conn = sqlite3.connect('agalma-siphonophora-20180401_reduced.sqlite')
+c = conn.cursor()
+
+species16S = [ "Lilyopsis fluoracantha", "Rudjakovia sp", "Bargmannia lata", "Physonect sp", "Erenna richardi", "Resomia ornicephala", "Physophora gilmeri" ]
+species18S = [ "Lychnagalma ultricularia", "Frillagalma vityazi", "Rudjakovia sp", "Bargmannia lata", "Apolemia rubriversa", "Erenna richardi", "Resomia ornicephala", "Physophora gilmeri", "Thermopalia taraxaca", "Marrus claudanielis" ]
+
+print "\n 16S"
+for species in species16S:
+	export16S = open("%s_16S.fasta" % species.replace(" ", "_"), "w")
+	c.execute("select c.species, m.genome_type, m.molecule_type, s.* from agalma_sequences as s join agalma_models as m on s.model_id=m.id join catalog as c on c.id=m.catalog_id where m.molecule_type='S' and m.genome_type='M' and c.species='%s';" % species)
+	out16S = c.fetchall()
+	print species
+	print len(out16S)
+	export16S.writelines([">{0}\n".format(item) for item in out16S])
+	export16S.close()
+
+c = conn.cursor()
+
+print "\n 18S"
+for species in species18S:
+	export18S = open("%s_18S.fasta" % species.replace(" ", "_"), "w")
+	c.execute("select c.species, m.genome_type, m.molecule_type, s.* from agalma_sequences as s join agalma_models as m on s.model_id=m.id join catalog as c on c.id=m.catalog_id where m.molecule_type='S' and m.genome_type='N' and c.species='%s';" % species)
+	out18S = c.fetchall()
+	print species
+	print len(out18S)
+	export18S.writelines([">{0}\n".format(item) for item in out18S])
+	export18S.close()
+
+conn.commit()
+conn.close()

### 2019-04-22 manuscript.rmd
added DAPC and predictions of diet, started updating .bib

@@
   cnidomic_index[cnidomic_index==-Inf]<-NA
-    morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index)
+  surface_ellipsoid <- function(L, W){
+  a <- L/2
+  b <- W/2
+  c = b
+  S <- 4*pi*((((a*b)^1.6)+((a*c)^1.6)+((c*b)^1.6))/3)^(1/1.6)
+  return(S)
+}
+volume_ellipsoid <- function(L, W){
+  a <- L/2
+  b <- W/2
+  c = b
+  V <- (4/3)*pi*a*b*c
+  return(V)
+}
+SAV_haploneme = surface_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)/volume_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)
+names(SAV_haploneme) = castnumbers$Species
+SAV_heteroneme = surface_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)/volume_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)
+names(SAV_heteroneme) = sharedmeans$Species
+morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index, SAV_haploneme)
   names(morphometrics)[1:2] = c("slide_id"," Species")
@@
 heatdata[is.nan(heatdata)]<- -1
-hcolors = white2blue(19)
+hcolors = grDevices::terrain.colors(20)
 hcolors<-c(rep("#000000FF",10), hcolors)
@@
 
+#SURFACE AREA : VOLUME
+SAV_haploneme = surface_ellipsoid(sharedmeans$Haploneme.free.length..um., sharedmeans$Haploneme.width..um.)/volume_ellipsoid(sharedmeans$Haploneme.free.length..um., sharedmeans$Haploneme.width..um.)
+names(SAV_haploneme) = sharedmeans$Species
+SAV_heteroneme = surface_ellipsoid(sharedmeans$Heteroneme.free.length..um., sharedmeans$Heteroneme.width..um.)/volume_ellipsoid(sharedmeans$Heteroneme.free.length..um., sharedmeans$Heteroneme.width..um.)
+names(SAV_heteroneme) = sharedmeans$Species
+SAV_haploneme = SAV_haploneme[which(!is.nan(SAV_haploneme))]
+SAV_heteroneme = SAV_heteroneme[which(!is.nan(SAV_heteroneme))]
+SAVhet_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(SAV_heteroneme))))
+Phenogram(SAV_heteroneme, as.data.frame(SAV_heteroneme), SAVhet_tree)
+Phenogram(SAV_haploneme, as.data.frame(SAV_haploneme), hap_tree)
+
 ```
@@
 
-compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:30)]
+compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
 #raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
@@
 }
-write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
+#write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
 #pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
@@
 
+#SA/V Haplonemes
+CH_J=softORhard[,1]
+names(CH_J) = rownames(softORhard)
+CH_J[CH_J!="Soft"]<-0
+CH_J[CH_J=="Soft"]<-1
+CH_I = SAV_haploneme
+CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
+CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
+treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
+CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
+CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
+datIJ = data.frame(preytype = CH_J, character = CH_I)
+datIJ$preytype = as.numeric(as.character(datIJ$preytype))
+logit = glm(preytype~character,data=datIJ, family="binomial")
+    print(logit)
+phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=10)
+    print(phylogit)
+c("Soft specilization", "Haploneme SA:V", phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
 ```
@@
 
+#Haploneme SA/V to diet
+CH_I=SAV_haploneme
+CH_I = CH_I[!is.na(CH_I)]
+for(j in 1:ncol(selectivity)){
+  CH_J=as.numeric(selectivity[,j])
+  names(CH_J) = rownames(selectivity)
+  CH_J = CH_J[!is.na(CH_J)]
+  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
+  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
+  SE_I = castSE_logs[which(castSE$Species %in% names(CH_I)),i]
+    names(SE_I) = castSE_logs[which(castSE$Species %in% names(CH_I)),1]
+    SE_I = SE_I[match(names(CH_I), names(SE_I))]
+    pgls_tree = drop.tip(Sprunedtree, which(!(Sprunedtree$tip.label %in% names(CH_I))))
+    pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
+    if(length(unique(CH_J))>1){
+          pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
+          pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
+          LikRat <- 2*(TTABLE$logLik[1] - TTABLE_null$logLik[1])
+          pchisq(LikRat, df=1, lower.tail = F) -> pGLSp_sel[i-1,j]
+          if(pGLSp_sel[i-1,j]<0.05){
+          print(paste(rownames(pGLSp_sel)[i-1],colnames(pGLSp_sel)[j],pGLSp_sel[(i-1),(j)],TTABLE$coefficients[2], sep=" "))
+          ValueIJ = TTABLE %>% .$coefficients %>% .[2]
+          if(ValueIJ>0){pGLS_sel_sign[i-1,j] = "+"}
+          else pGLS_sel_sign[i,j] = "-"
+         }
+       }
+    else TTABLE<-NA; TTABLE_null<-NA; LikRat<-NA; pGLSp_sel[i-1,j]<-NA
+  }
+
 #using PCs instead of characters
@@
 #Plot mirror trees QUANT
-X = dprunedmatrix_logs$Haploneme.free.length..um.
+X = dprunedmatrix_logs$Haploneme.row.number
 names(X) = dprunedmatrix_logs$Species
@@
 
-X = nematocyst_number
-Y = soft_hard$Soft
-Y=softORhard[,1]
-names(Y) = rownames(softORhard)
-Y[Y!="Soft"]<-0
-Y[Y=="Soft"]<-1
-
+X = dprunedmatrix_logs$coiledness
+names(X) = dprunedmatrix_logs$Species
+X<-X[!(is.nan(X))]
+Y = diet$`Decapod diet`
+#Y=softORhard[,1]
+names(Y) = rownames(diet)
+#Y[Y!="Soft"]<-0
+#Y[Y=="Soft"]<-1
 Y = Y[which(names(Y) %in% names(X))]
@@
 
-X = Pprunedmatrix_logs$Heteroneme.volume..um3.
-names(X) = Pprunedmatrix_logs$Species
-Y = PP$`Relative decapod consumption`
-names(Y) = rownames(PP)
+X = Sprunedmatrix_logs$Haploneme.row.number..um.
+names(X) = Sprunedmatrix_logs$Species
+Y = selectivity$Selectivity.Decapod.larvae #PP$`Relative decapod consumption`
+names(Y) = rownames(selectivity)
 layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
@@
 #pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
-OX = contMap(Pprunedtree,X,sig=1,legend=1, plot = F, outline = F)
+OX = contMap(Sprunedtree,X,sig=1,legend=1, plot = F, outline = F)
 OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
 plot(OX,ftype="off")
-ylim<-c(1-0.12*(length(Pprunedtree$tip.label)-1),length(Pprunedtree$tip.label))
+ylim<-c(1-0.12*(length(Sprunedtree$tip.label)-1),length(Sprunedtree$tip.label))
 plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
-text(rep(0,length(Pprunedtree$tip.label)), 1:length(Pprunedtree$tip.label),Pprunedtree$tip.label)
-OY = contMap(Pprunedtree,Y, sig=1,legend=1, plot = F,  outline = F)
+text(rep(0,length(Sprunedtree$tip.label)), 1:length(Sprunedtree$tip.label),Sprunedtree$tip.label)
+OY = contMap(Sprunedtree,Y, sig=1,legend=1, plot = F,  outline = F)
 OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
@@
 # write.csv(OUwie_matrix, "OU_compound_test.csv")
+
+#DAPC diet??
+library(adegenet)
+rowNAs = c(0,apply(sharedmean_logs[,-1], 1, function(x) sum(is.nan(x))))
+colNAs = c(0,apply(sharedmean_logs[,-1], 2, function(x) sum(is.nan(x))))
+ldamtrix = sharedmean_logs[,which(colNAs<6)]
+#ldamtrix = sharedmean_logs[which(rowNAs<20),]
+ldamtrix = ldamtrix[which(!is.nan(rowSums(ldamtrix[,-1]))),]
+#ldamtrix = ldamtrix[,which(!is.nan(colSums(ldamtrix[,-1])))]
+#rowNAs = apply(ldamtrix[,-1], 1, function(x) sum(is.na(x)))
+#colNAs = apply(ldamtrix[,-1], 2, function(x) sum(is.nan(x)))
+ldamtrix = ldamtrix[which(rowNAs<1),]
+#ldamtrix = ldamtrix[,which(colNAs<1)]
+ldamtrix$Species = as.character(ldamtrix$Species)
+ldamtrix = ldamtrix[which(ldamtrix$Species %in% names(hypdiet)),]
+#ldamtrix = ldamtrix[which(ldamtrix$Species %in% rownames(diet)),]
+LDAtree = drop.tip(ultram, which(!(ultram$tip.label %in% ldamtrix$Species)))
+ldamtrix = ldamtrix[match(LDAtree$tip.label, ldamtrix$Species),]
+baselda=ldamtrix
+
+#Feeding guild
+prunediets = hypdiet[which(names(hypdiet) %in% ldamtrix$Species)]
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, names(prunediets))])
+names(ldamtrix)[ncol(ldamtrix)]<-"Diet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$Diet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$Diet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+
+prunediets = diet[which(rownames(diet) %in% ldamtrix$Species),]
+#Copepods
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), "Copepod diet"])
+names(ldamtrix)[ncol(ldamtrix)]<-"CopepodDiet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$CopepodDiet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$CopepodDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+summary.dapc(DAPClogs)
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+copselmatrix = cbind(Sprunedmatrix, selectivity$Selectivity.Copepods)
+copselmatrix = copselmatrix[which(copselmatrix$Species %in% LDAtree$tip.label),]
+copselmatrix = copselmatrix[match(LDAtree$tip.label, copselmatrix$Species),]
+CopepodGLM <- glm(CopepodDiet~Tentacle.width..um.+Haploneme.row.number..um., data = ldamtrix)
+summary(CopepodGLM)
+1-(CopepodGLM$deviance/CopepodGLM$null.deviance) #76.2
+CopepodSelGLM <- glm(selectivity$Selectivity.Copepods~Tentacle.width..um.+Haploneme.row.number..um.+total_haploneme_volume, data = copselmatrix)
+summary(CopepodSelGLM)
+1-(CopepodSelGLM$deviance/CopepodSelGLM$null.deviance) #76.6%
+rownames(ldamtrix) = ldamtrix$Species
+CopepodPGLM <- phyloglm(CopepodDiet~Tentacle.width..um.+Haploneme.row.number..um., data = ldamtrix, phy = LDAtree, btol=100)
+summary(CopepodPGLM)
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+
+#Fish
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), "Fish diet"])
+names(ldamtrix)[ncol(ldamtrix)]<-"FishDiet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$FishDiet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$FishDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+summary.dapc(DAPClogs)
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+FishGLM <- glm(FishDiet~Heteroneme.volume..um3.+total_haploneme_volume+Pedicle.width..um., data = ldamtrix)
+summary(FishGLM)
+1-(FishGLM$deviance/FishGLM$null.deviance)
+fishselmatrix = cbind(Sprunedmatrix, selectivity$Selectivity.Fish)
+fishselmatrix = fishselmatrix[which(fishselmatrix$Species %in% ldamtrix$Species),]
+fishselmatrix = fishselmatrix[match(LDAtree$tip.label, fishselmatrix$Species),]
+FishSelGLM <- glm(selectivity$Selectivity.Fish~Pedicle.width..um., data = fishselmatrix)
+summary(FishSelGLM)
+1-(FishSelGLM$deviance/FishSelGLM$null.deviance) #97.5%
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+
+#Decapods
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), "Decapod diet"])
+names(ldamtrix)[ncol(ldamtrix)]<-"DecapodDiet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$DecapodDiet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$DecapodDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+summary.dapc(DAPClogs)
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+DecapodGLM <- glm(DecapodDiet~Heteroneme.volume..um3.+coiledness+Cnidoband.length..um.+haploneme_elongation+heteroneme_elongation, data = ldamtrix)
+summary(DecapodGLM)
+1-(DecapodGLM$deviance/DecapodGLM$null.deviance)
+decselmatrix = cbind(Sprunedmatrix, selectivity$Selectivity.Decapod.larvae)
+decselmatrix = decselmatrix[which(decselmatrix$Species %in% ldamtrix$Species),]
+decselmatrix = decselmatrix[match(LDAtree$tip.label,decselmatrix$Species),]
+DecapodSelGLM <- glm(selectivity$Selectivity.Decapod.larvae~Heteroneme.volume..um3.+coiledness+Cnidoband.length..um.+haploneme_elongation+heteroneme_elongation, data = decselmatrix)
+summary(DecapodSelGLM)
+1-(DecapodSelGLM$deviance/DecapodSelGLM$null.deviance) #89.1%
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+
+#SoftHard
+prunediets = softORhard
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), 1])
+names(ldamtrix)[ncol(ldamtrix)]<-"SoftHard"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$SoftHard, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$SoftHard, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+summary.dapc(DAPClogs)
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.9, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+
+#Predicitions on uncharacterized taxa transforming NAs to zeroes
+ldamtrix = sharedmean_logs
+ldamtrix[is.na(ldamtrix)]<-0
+ldamtrix$Species = as.character(ldamtrix$Species)
+ldamtrix = ldamtrix[which(ldamtrix$Species %in% names(hypdiet)),]
+prunediets = hypdiet[which(names(hypdiet) %in% ldamtrix$Species)]
+#prunediets["Hippopodius hippopus"]<-"Ostracod"
+ldamtrix = cbind(ldamtrix, prunediets[match(ldamtrix$Species, names(prunediets))])
+names(ldamtrix)[ncol(ldamtrix)]<-"Diet"
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$Diet, n.pca.max = 300, training.set = 1,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$Diet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+
+prunediets = diet[which(rownames(diet) %in% ldamtrix$Species),]
+#Fish
+ldamtrix = sharedmean_logs
+ldamtrix[is.na(ldamtrix)]<-0
+ldamtrix$Species = as.character(ldamtrix$Species)
+ldamtrix = ldamtrix[which(ldamtrix$Species %in% rownames(diet)),]
+ldamtrix = cbind(ldamtrix, prunediets[match(ldamtrix$Species, rownames(prunediets)), "Fish diet"])
+names(ldamtrix)[ncol(ldamtrix)]<-"FishDiet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$FishDiet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$FishDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
+summary.dapc(DAPClogs)
+contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
+scatter(DAPClogs, clabel = 0.5)
+assignplot(DAPClogs)
+compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+
 ```
@@
 
+#Ecology prediciton?
+kinediet = diet[which(rownames(diet) %in% kine$Species),]
+kinesel = selectivity[which(rownames(selectivity) %in% kine$Species),]
+kinehypdiet = hypdiet[which(names(hypdiet) %in% kine$Species)]
+
 ```

### 2019-05-07 manuscript.rmd
minor fixes

@@
 The models selected for each character were evaluated in terms of model adequacy using the package arbutus [@pennell2015model].
-Multivariate BM and OU models were also evaluated using the package mvSLOUCH [@bartoszek2012phylogenetic].
 
@@
 #Combination of VARS and GC sources
-diet_VARS = rbind(diet, c(0,0,0,0,0,1,1,0,0))
-diet_VARS = cbind(diet_VARS, rep(0,nrow(diet_VARS)))
-rownames(diet_VARS)[nrow(diet_VARS)] <- "Lychnagalma utricularia"
-names(diet_VARS)[ncol(diet_VARS)] <- "Gelatinous diet"
-diet_VARS["Nanomia sp",] = c(1,0,0,0,0,1,1,1,0,1)
-diet_VARS["Praya dubia",] = c(1,0,0,0,0,1,1,0,0,1)
+# diet_VARS = rbind(diet, c(0,0,0,0,0,1,1,0,0))
+# diet_VARS = cbind(diet_VARS, rep(0,nrow(diet_VARS)))
+# rownames(diet_VARS)[nrow(diet_VARS)] <- "Lychnagalma utricularia"
+# names(diet_VARS)[ncol(diet_VARS)] <- "Gelatinous diet"
+# diet_VARS["Nanomia sp",] = c(1,0,0,0,0,1,1,1,0,1)
+# diet_VARS["Praya dubia",] = c(1,0,0,0,0,1,1,0,0,1)
 
@@
 dprunedCat = binary[which(rownames(binary)%in% rownames(diet)),]
-CH_I = dprunedCat$Rhopalonemes
+CH_I = dprunedCat$Rhopalonemes #same result with desmonemes
 names(CH_I) = rownames(dprunedCat)
@@
 
+```{r rphylopars_and_varpart}
+library(Rphylopars)
+combinedata = data.frame(sharedmean_logs,diet[match(sharedmean_logs$Species, rownames(diet)),])
+names(combinedata)[1]<-"species"
+is.nan.data.frame <- function(x)
+do.call(cbind, lapply(x, is.nan))
+combinedata[is.nan.data.frame(combinedata)] <- NA
+#PhyloParsALL = phylopars(combinedata[,c(1,2,4:22,24,27:42)], ultram, pheno_error = F, pheno_correlated = T)
+#PhyloParsALL = phylopars(combinedata[,c(1,32:42)], ultram, pheno_error = F, pheno_correlated = T)
+
+#How to make combined imputations
+
+###PCOA variance partitionaing method
+phylomatrix = pcoa(cophenetic(dprunedTree))$vectors
+phylomatrix = phylomatrix[match(rownames(diet), rownames(phylomatrix)),]
+nastozeroes = dprunedmatrix_logs
+nastozeroes[is.nan(dprunedmatrix_logs)]<-0
+nastozeroes = nastozeroes[,match(rownames(diet), nastozeroes$Species)]
+dietdist <- vegdist(diet, "bray") %>% as.matrix()
+varpart(nastozeroes[,-1], phylomatrix[,1:3], diet)
+glmatrix_1 = cbind(nastozeroes, phylomatrix)
+glmatrix_2 = cbind(nastozeroes, diet)
+glmatrix_3 = cbind(nastozeroes, diet, phylomatrix)
+glm(Cnidoband.length..um.~Axis.1+Axis.2+Axis.3+Axis.4+Axis.6+Axis.8+Axis.9+Axis.11+Axis.14, data=glmatrix_1[-1,]) -> GLM_1
+1-(GLM_1$deviance/GLM_1$null.deviance)
+predict.glm(GLM_1, newdata = as.data.frame(glmatrix_1[1,]), se.fit = T)
+glm(Cnidoband.length..um.~`Copepod diet`+`Fish diet`+`Amphipod diet`+`Decapod diet`+`Polychaete diet`+`Mollusc diet`+`Crustacean diet`+`Chaetognath diet`+`Ostracod diet`+`Gelatinous diet`, data=glmatrix_2[-1,]) -> GLM_2
+1-(GLM_2$deviance/GLM_2$null.deviance)
+predict.glm(GLM_2, newdata = as.data.frame(glmatrix_2[1,]), se.fit = T)
+glm(Cnidoband.length..um.~Axis.1+Axis.2+Axis.3+Axis.4+Axis.6+Axis.8+Axis.9+Axis.11+Axis.14+`Copepod diet`+`Fish diet`+`Amphipod diet`+`Decapod diet`+`Polychaete diet`+`Mollusc diet`+`Crustacean diet`+`Chaetognath diet`+`Ostracod diet`+`Gelatinous diet`, data=glmatrix_3[-1,]) -> GLM_3
+1-(GLM_2$deviance/GLM_2$null.deviance)
+predict.glm(GLM_3, newdata = as.data.frame(glmatrix_3[1,]), se.fit = T)
+
+varpart(nastozeroes$coiledness, phylomatrix[,c(1:4,6,8,9,11,14)], diet)
+rda(nastozeroes$coiledness, phylomatrix[,c(1:4,6,8,9,11,14)]) %>% summary()
+
+###Phylopars methods
+pparsmatrix = cbind(nastozeroes$Species, nastozeroes$Cnidoband.length..um., diet)
+names(pparsmatrix)[1]<-"species"
+pparsmatrix$`nastozeroes$Cnidoband.length..um.` [1]<-NA
+PhyloParsALL = phylopars(pparsmatrix, dprunedTree, pheno_error = F, pheno_correlated = T)
+PhyloParsALL$anc_recon["Agalma elegans",]
+pparscontrol = pparsmatrix[,1:2]
+PhyloPars_control = phylopars(pparscontrol, dprunedTree, pheno_error = F, pheno_correlated = T)
+PhyloPars_control$anc_recon["Agalma elegans",]
+
+###PGLS predictions do not take into account the phylogenetic position of the new taxon###
+pglsmatrix = glmatrix_2
+names(pglsmatrix) = str_replace_all(names(pglsmatrix)," ", "_")
+rownames(pglsmatrix) = pglsmatrix$Species
+pglm_1 = gls(Cnidoband.length..um.
+~ Copepod_diet+Fish_diet+Amphipod_diet+Decapod_diet+Polychaete_diet+Mollusc_diet+Crustacean_diet+Chaetognath_diet+Ostracod_diet+Gelatinous_diet, data=pglsmatrix[,-1], correlation = corBrownian(phy=dprunedTree))
+pglm_control = gls(Cnidoband.length..um.
+~ Copepod_diet+Fish_diet+Amphipod_diet+Decapod_diet+Polychaete_diet+Mollusc_diet+Crustacean_diet+Chaetognath_diet+Ostracod_diet+Gelatinous_diet, data=pglsmatrix[,-1], correlation = corBrownian(phy=rtree(length(dprunedTree$tip.label))))
+predict(pglm_1, newdata = pglsmatrix[1,])
+predict(pglm_control, newdata = pglsmatrix[1,])
+```
+
 ## 4. Discussion

### 2019-05-09 manuscrip_clean.Rmd
preparing for submission, clean manuscript, clean code

---
bibliography: manuscript.bib
csl: systematic-biology.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
---

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(stringr)
library(reshape2)
	## Biological
library(Rphylip)
library(arbutus)
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(OUwie)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
library(phylolm)
	## Graphics
library(FactoMineR)
library(factoextra)
library(corrplot)
library(BAMMtools)
library(gridExtra)
library(xtable)
library(colorRamps)

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set(
	  progress=TRUE,
	  verbose=TRUE)
	opts_chunk$set(
	#  include=FALSE,
	  cache=TRUE,
	  echo=FALSE,
	  message=FALSE
	 )
knitr::opts_chunk$set(echo = TRUE)

```

# The Evolution of Siphonophore Tentilla as Specialized Tools for Prey Capture {-}

Alejandro Damian-Serrano^1^^,‡^, Steven H.D. Haddock^2^, Elizabeth D. Hetherington^3^, C. Anela Choy^3^, Casey W. Dunn^1^

^1^ Osborn Memorial Laboratories, 165 Prospect St., New Haven, CT 06520, USA

^2^ Monterey Bay Aquarium Research Institute, 7700 Sandholdt Rd., Moss Landing, CA 95039, USA

^3^ Scripps Institution of Oceanography, 9500 Gilman Dr., La Jolla, CA 92093, USA

\‡ Corresponding author: Alejandro Damian-Serrano, email: alejandro.damianserrano@yale.edu

## Abstract {-}

Predators have evolved dedicated body parts to capture and subdue prey. As different lineages specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms. Studying this process requires a predator clade with structures used exclusively for prey capture that present significant morphological variation. Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well, capturing prey with their tentilla (tentacle side branches). Earlier work has shown that extant siphonophore diets correlate with the different morphologies and sizes of their tentilla and nematocysts. We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters. To test this hypothesis, we: (1) measured extensive morphological traits from fixed siphonophore specimens using microscopy and high speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) characterized the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature. Our results show that siphonophore tentilla structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey type specializations are linked to shifts in tentillum and nematocyst size and shape. In addition, we found that these morphological characters are useful for predicting siphonophore diets.  Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution. This study contributes to understanding how morphological evolution has shaped the structure of present-day oceanic food-webs.

## Keywords {-}

Siphonophores, tentilla, nematocysts, predation, specialization, character evolution

##   {-}

  Most animal predators have characteristic biological tools that they use to capture and subdue prey. Raptor birds have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles. The functional morphology of these structures tend to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator]. Long-term adaptive evolution in response to the defense mechanisms (e.g. avoidance, escape, protective barriers) of the prey leads to modifications that can tackle those defenses. The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey. Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.

  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture and present a significant morphological variation across species, which makes it ideal to study the relationships between functional traits and prey specialization. A siphonophore is a colony bearing many feeding polyps (Fig. \@ref(figure1)), each with a single tentacle, which branches into several tentilla bearing the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules). Tentilla function exclusively for prey capture and present a broad diversity of morphologies and sizes [@mapstone2014global]. Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation], built into their tentilla. While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism upon encounter with prey. Tentilla undergo an extremely fast conformational change that wraps around the prey, maximizing the surface area of contact for nematocysts to fire on it [@Mackie:1987uy]. In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent].

  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor (~3000-11000m). This habitat has fairly homogeneous abiotic conditions and stable temporal patterns in the abundance of zooplanktonic animals [@robison2004deep]. With a somewhat predictable prey availability, ecological theory would expect evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox]. If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of specialization on a variety of prey types.

  The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores. Thus, the morphological diversity of tentilla has been only characterized for a few taxa, and their evolutionary history remains largely unexplored. Contemporary underwater sampling technology provides an unprecedented opportunity to explore the trophic ecology [@choy2017deep] and functional morphology [@costello2015multi] of siphonophores. In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved]. These methodological advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.

  The few studies have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification. [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores. These correlations, while found in a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores. We hypothesize that these relationships may reflect correlated evolution between prey selection and tentillum (and nematocyst) traits. Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate predictions about the diets of understudied siphonophore species.
In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures. We aim to assess the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentilla morphologies on cnidoband discharge.

  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.

![\label{figure1} Siphonophore anatomy. A - Nanomia sp. siphonophore colony (photo by Catriona Munro). B,C - Illustration of a Nanomia colony, gastrozooid, and tentacle (by Freya Goetz). D - *Nanomia* sp. Tentillum illustration and main parts. E - Transmission micrograph of the tentillum illustrated in D. F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum. Undischarged to the left, discharged to the right.](Figures_final/figure1.jpg)

![\label{figure2} Tentillum diversity plate. The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow). Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species. A - *Erenna laciniata*, slide E11, 10x. B - *Lychnagalma utricularia*, slide D7, 10x. C - *Agalma elegans*, slide J6, 10x. D - *Resomia ornicephala*, slide X11, 10x. E - *Frillagalma vityazi*, slide H1, 20x. F - *Bargmannia amoena*, slide L8, 10x. G - *Cordagalma* sp., reproduced from Carré 1968. H - *Lilyopsis fluoracantha*, slide J10, 20x. I - *Abylopsis tetragona*, slide U6, 20x.](Figures_final/figure2.jpg)

## Methods {-}

*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in SM1). These specimens were collected intact across many years of fieldwork expeditions, by the means of Blue Water Diving [@haddock2005scientific], Remotely Operated Vehicles (ROVs), and human operated submersibles. Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media. The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues. 30 characters (defined in SM2) were measured using Fiji in ImageJ [@collins2007imagej;@schindelin2012fiji]. We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to capture meaningful measurements.

We measured at least one specimen for 96 different species (SM3). Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade. Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation. In order to observe the discharge behavior of different tentilla, we recorded high speed footage (1000-3000 fps) of tentillum and nematocyst discharge by live siphonophore specimens (26 species) using a Phantom Miro 320S camera mounted on a stereoscopic microscope. We mechanically elicited tentillum and nematocyst discharge using a fine metallic pin. We used the Phantom PCC software to analyze the footage. For the 10 species recorded, we measured total cnidoband discharge time (ms), average cnidoband discharge speed (mm/s), maximum cnidoband discharge speed (mm/s), heteroneme discharge speed (mm/s), haploneme discharge speed (mm/s), heteroneme shaft discharge speed (mm/s), and heteroneme filament length (microns) when possible (SM4). Morphological and kinematic data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])

*Siphonophore phylogeny* – The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*). The gene sequences used in this study are available online (accession numbers in SM5). Some of these sequences we used were accessioned in [@dunn2005molecular], others we extracted from the transcriptomes in [@munro2018improved]. Two new 16S sequences for *Frillagalma vityazi* (accession####) and *Thermopalia* sp. (accession####) analyzed by Lynne Christianson were included and accessioned to NCBI. We aligned these sequences using MAFFT [@katoh2002mafft]. We inferred a Maximum Likelihood (ML) phylogeny (SM6) was reconstructed from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates. We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5. to assess relative model fit. ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score. Additionally, we inferred an unconstrained Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM7), which was topologically congruent with the ML tree. The *alpha* priors were selected to minimize prior load in site variation. This tree was then used to inform a Bayesian strict molecular clock time-tree in RevBayes, using a birth-death process (*rho* parameter calculated from the known number of described siphonophore species) generating an ultrametric tree (SM8). Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved]. Scripts available in https://github.com/dunnlab/tentilla_morph/.

*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources (SM 13), including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic], and ROV observation data [@choy2017deep;@hissmann2005situ]. Since the sampling biases of ROV and gut content based methods are very different, the data was only combined to assign feeding guilds. The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without a heavy load on any one prey group). We removed the gelatinous prey observations for *Praya dubia* and *Nanomia sp.* , since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey. Personal observations on feeding (from SHDH, CAC, and Philip Pugh)  were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*. We extracted copepod prey length data from [@purcell1984functions]. To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species.

*Statistical analyses* – For subsequent comparative analyses, we use the constrained Bayesian ultrametric tree. We removed species present in the tree but not the morphology data, and vice versa. While we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in  some of the species-level identifications, and some specimens were missing diagnostic zooids. Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.). All *Nanomia* sp. Observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.  We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the bayesian ultrametric species tree (Fig. \@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error. For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included. We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.

We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous [@harmon2007geiger]. The models compared were the white noise (WN) (non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic]. We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support. When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model. We calculated model adequacy scores using the R package arbutus [@pennell2015model], which are reported in SMXX. We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing], and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].

In order to study the evolution of predatory specialization, we reconstructed components of the diet and prey selectivity on the phylogeny using ML (R phytools::anc.ML). To identify evolutionary associations of diet with tentillum and nematocyst characters, we compared the performance of a neutral evolution model to that of a diet-driven directional selection model. First, we collapsed the diet data into five feeding guilds (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently. We reconstructed the feeding guild ancestral states using the maximum likelihood function ace (package ape [@paradis2019package]), removing tips with no feeding data. Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model. Finally, we compared their AICc support values to select the best fitting model.

To assess the predictive power of individual tentillum and nematocyst characters on the evolution of the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm). In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature. To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting]. To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic]. To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls).

To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant] in a set of 11 species. This set of taxa was selected to maximize the amount of morphological and dietary data represented without missing values. We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet. For these specific groups, we then generated and compared generalized linear models (GLMs) with multiple predictors. We chose predictors among the characters with significant loading contributions in each specific DAPC. We then selected the best GLM for each prey type based on the lowest AIC scores.

  In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character data contains many gaps due to missing characters, we carried out these analyses on a the subset of species and characters that allowed the largest data volume. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].

  To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different nematocyst types, and identified the branches with the greatest shifts. We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters. In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on these characters to estimate the number and phylogenetic mapping of trait evolution rate regimes.

## Results {-}

![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in SM0). Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells. Values scaled by character. Green indicates relatively small values, pink indicates relatively large values.](Figures_final/figure3.jpg)

![\label{figure4} Bayesian time-tree built from 18S + 16S concatenate. Branch lengths estimated using strict molecular clock. Species names in red indicate replicated representation in the morphology data. Species marked with an asterisk were recorded using high speed video. Nodes labeled with bayesian posteriors (BP). Green circles indicate BP = 1. Blue circles indicate nodes constrained to be congruent with (Munro *et al.* 2018). Tips with black squares indicate the species with transcriptomes used in  (Munro *et al.* 2018). Tips with translucent squares indicate genus-level correspondence to taxa included in  (Munro *et al.* 2018). The main clades are labeled: in black for described taxonomic units, and in grey for operation phylogenetic designations.](Figures_final/figure4.jpg)

*Phylogeny* – Only 5 nodes in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree. The topology of the constrained tree presented here (Fig. \@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].

  We define two new clades within Codonophora (Fig. \@ref(figure4)): Eucladophora as the clade containing *Agalma elegans* and all taxa that are more closely related to it than to *Apolemia lanosa*, and Tendiculophora as the clade containing *Agalma elegans* and all taxa more closely related to it than to *Bargmannia elongata*. Eucladophora is characterized by bearing spatially differentiated tentilla with proximal heteronemes and a narrower terminal filament region. The etymology derives from the Greek for “true branch bearers”. Tendiculophora are characterized by bearing rhopalonemes and desmonemes in the terminal filament, having a pair of elastic strands, and developing proximally detachable cnidobands. The etymology of this clade is derived from the Latin tendicula for “snare or noose”.

![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the OUwie analyses. Right - Grid showing the prey items consumed from which the feeding guild categories were derived. Diet data was obtained from the literature review in SMx.](Figures_final/figure5.jpg)

*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guild show that generalism was not likely ancestral, and it appears to have evolved at least 2 times independently (Fig. \@ref(figure5)). Individual prey type presence reconstructions show that copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once. The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SMx). These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number. Most of these characters are found exclusively in Tendiculophora, thus this is reflecting processes that could be unique to this subtree. Five characters including cnidoband length, cnidoband shape, and haploneme length show maximal support for a diet-driven single-optimum OU model. The remaining 15 characters support BM (or OU with marginal AICc difference with BM).

  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types (Fig. \@ref(figure5), right) in the diet. showed that shifts towards ostracod diet correlate with reductions in pedicle width and total haploneme volume. Shifts to copepod presence in the diet are associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths. Consistently with the patterns across extant species, transitions to decapod presence in the diet correlate with the evolution of more coiled cnidobands (SM10).

  Phylogenetic regressions of continuous characters against prey selectivity data produced additional insights. Specialization in a piscivorous diet is associated to increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths. Decapod rich diets are associated to increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number. Copepod-selective diets evolved in association to increasingly smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, heteronemes, tentacles, pedicles and elastic strands. Selectivity for ostracods  is associated to reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness. Heteroneme length and shape also correlates negatively with chaetognath selectivity.

  When some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] were tested for correlated evolution (Table 1), we found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet. The latter is likely a product of the larger species richness of crustacean eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.

![\label{table1} Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.](Final_tables/table1.png)

*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination, and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width. The only groups confounded were large crustacean specialists and generalists. For this analysis, we transformed the missing values in the data (due to character absence) to zeroes, thus accommodating more taxa and characters. When missing values are retained, the gelatinous-specialist guild is not included, and the DAPC only produces 81% discrimination, highlighting  cnidoband coiledness, cnidoband length, haploneme elongation, heteroneme volume, heteroneme elongation.

![\label{figure6} DAPC predicted feeding guilds for siphonophore species with measured tentilla morphology data but without any preliminary dietary data. Cell darkness indicates posterior probability of belonging to each guild. Training data set transformed so missing values would be computed as zeroes. Species colored according to their predicted feeding guild with highest probability score.](Figures_final/figure6.jpg)

  We used this discriminant function to predict the feeding guild of 45 species in our morphological data (Fig. \@ref(figure6)). When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists. The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width. Discriminant analyses and GLM were also applied to specific prey type presence and selectivity (Table \@ref(table2), highlighting the most relevant characters and their predictive power.

![\label{table2} Discriminant analysis of principal components for specific prey types using the morphological data. Loadings are ordered from highest to lowest significance. GLMs were fitted to predict prey type presence and selectivity for different combinations of the significant loadings and selected for the lowest AIC value. Only the best GLM is reported. Pseudo-R2 approximate the variance explained by the model.](Final_tables/table2.png)

*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (SuppTable x). Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals. 74% of  characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme to cnidoband length ratio had a phylogenetic signal  K > 1.  67% of characters support BM models, indicating a history of neutral constant divergence. No relationship between phylogenetic signal and BM model support was found. Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time. No character had support for a single-optimum OU model.

![\label{figure7} Bayesian cladogram with the main categorical character gains (green) and losses (red) mapped. The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters. In large complex-shaped tentilla, haplonemes were omitted for simplification. The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)

  Haploneme nematocysts are likely ancestrally present in the tentacles, since they are present in the tentacles of many other hydrozoans. Haplonemes diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora. Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re]. Similarly, while heteronemes exist in other tissues of cystonects, they only appear in the tentacles of codonophorans as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.

  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig. \@ref(figure4)) encompasses most of the extant Siphonophore species. Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig. \@ref(figure7)). Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis]. The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see Fig. \@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore type ancestral) nematocysts on the terminal filament (Fig. \@ref(figure7)), which would bear no other nematocyst type, and these would be arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling]. The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband. This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects. Calycophorans evolved unique novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore type heteronemes.

![\label{figure8} A. Correlogram showing strength of ordinary (upper triangle) and phylogenetic (lower triangle) correlations between characters. Both size and color of the circles indicate the strength of the correlation (R^2^). B. Scatterplot of phylogenetic correlation against ordinary correlation showing a strong linear relationship (R^2^ = 0.92, 95% confidence between 0.90 and 0.93). Light red and blue boxes indicate congruent negative and positive correlations respectively. Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](Figures_final/figure8.jpg)

*Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are very correlated to each other. Of the phylogenetic correlations (Fig. 8a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig. \@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative. Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5. Similarly, of the across-species correlations, 49.1%  were >0.5 and only 1.5% were < -0.5. 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients. Just 4% have negative phylogenetic and positive ordinary correlations, and vice versa for 9.9% of character pairs. These disparities can be caused by Simpson’s paradox [@blyth1972simpson], the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered. However, no character pair had correlation coefficient differences larger than 0.74 between ordinary and phylogenetic correlations.

![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters. A. Variance explained by each variable in the PC1-PC2 plane. Axis labels include the phylogenetic signal (K) for each component and p-value. B. Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg)

  In the raw (non-morphometric) PCA morphospace (Fig. \@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explains 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%. In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length). These results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement is independent of it.

*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species. There is one secondary return to more oval, less elongated haplonemes in Erenna, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae. Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this group, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).

![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled). Orange area delimits rod-shaped haplonemes, blue area covers oval and round shaped haplonemes. Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM. Species nodes in red were manually added to the plot. Cystonects have no tentacle heteronemes and are projected onto the haploneme axis. Apolemids have no tentacle haplonemes and are project onto the heteroneme axis. Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)

  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of variance in their shifts alongs the branches of the phylogeny. However, much of this correlation is due to the contrast between pyrostephids and its sister group. BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia*. For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig. \@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (most have rod-shaped anisorhizas, but *Erenna* has oval ones). No clear patterns were identified in the evolution of desmoneme and rhopaloneme shape, with the exception of accelerated rhopaloneme shape evolution in *Forskalia* and accelerated rate of desmoneme shape evolution in the clade formed among *Halistemma rubrum* and *Athorybia rosacea*.

*Functional morphology of tentillum and nematocyst discharge* – While the sample sizes of high speed measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.  For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002). This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively. T-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.

  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001). Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012). Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.

## Discussion {-}
  This core aim of this paper is to characterize the evolutionary history of siphonophore tentilla and its relationships with diet. In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.

*Evolution of tentilla morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod]. While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], potentially serving as trophic intermediaries between smaller zooplankton and higher trophic level predators. Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors. With a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question. Predators that use similar tools for prey capture tend to capture similar prey, so their abundance and coexisting species diversity trade-off through competition [@schluter2000ecological]. However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global]. We hypothesize that siphonophores have escaped this trade-off though specialization on different prey resources.

  The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution. This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].

  The evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition. Several studies  (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by their phenotypic specialization. Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.

  An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major]. The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification to unfold.

  Throughout this study, we evaluate our findings from an adaptive perspective, assessing whether our results are congruent with adaptation. However, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.

  One of the most common prey items found in siphonophore diets are copepods (Fig. \@ref(figure5)). Copepod-specialized diets have evolved convergently in *Cordagalma* and some Calycophorans. These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts. Tentilla are expensive single-use structures, therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological function. *Cordagalma*'s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia* spp. This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization.

[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora. The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives. Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst]. *Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review], a common feature of piscivorous cnidarians like cystonects or cubozoans.

[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration. The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and personal observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages. Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure. In fish-eating cystonects and erennids, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis. The accelerated rate of heteroneme shape evolution in the clade containing *Agalma* and *Nanomia* may indicate a rapid dietary differentiation. However, our limited ecological data does not show any significant dietary differentiation in this group.

When the diet-morphology correlation hypotheses supported in the literature were tested from a macroevolutionary perspective, we found that most of them were consistent with correlated evolution (Table 2). The ecomorphological association between rhopalonemes, desmonemes and crustacean eaters was not congruent with a scenario of correlated evolution. This could be due to our analysis with a broad set of taxa including multiple species without desmonemes or rhopalonemes that effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).

While our results unambiguously show that tentilla morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available. In addition, diet is a product of environmental prey availability and predator selectivity. Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for this study. For example, tentacle deploying behavior, positioning in the water column, or behavioral decisions on whether or not to discharge on or ingest an encountered animal. Further observations on these behaviors in the field are necessary to assess their relative importance in determining dietary composition. In addition to behavior, there is much biochemistry in the prey capture and digestion processes that remains unexplored. Part of the success in siphonophore prey capture is likely determined by the effectivity of the toxins delivered by the nematocysts on different taxa. Comparative toxin assays, and venom protein evolution studies could shed light on this question. Moreover, siphonophore trophic specialization may have brought changes in the digestive biochemistry of gastrozooids and palpons. A comparison of the gene expression levels for different enzymes in the gastrozooids of different species, together with digestive enzyme sequence evolution studies, and a toxicological assay of the different venoms in siphonophore nematocysts on different prey taxa, would provide a great complement to our results.

*Predicting siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can better predict the diets of siphonophores based on morphological characteristics. Our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone. The models produced by these analyses generated untested predictions about the diets of many species for which we only have morphological data of their tentacles. In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species. Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone. Interactions among the oceanic zooplankton have been treated as a black box in ecological models [@mitra2009closure]. The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient flow models from plankton trawl data.

*Phenotypic integration of siphonophore tentilla* – Tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution]. Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations.  In addition, these sub-structures must fit and work together in synchrony to ensnare prey successfully (functional integration). Character complexes that satisfy these conditions tend to be phenotypically integrated. Phenotypic integration is the set of functional and genetic correlations among the traits of an organism [@pigliucci2003phenotypic]. These correlations have been hypothesized to direct and constrain adaptive evolution [@wagner2000evolutionarily]. The siphonophore tentillum morphospace has a fairly low extant dimensionality due to an evolutionary history with many synchronous, correlated changes. This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve function.

  Part of the tentillum structural correlations are to be expected from shared regulatory networks for elements that develop together from common positional bud (budding tentilla in the tentacle). Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin. None of these explanations for correlated evolution are surprising, nor require natural selection. However, we also found correlations between nematocyst and tentillum characters. Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum. These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid). Once the cnidocytes have assembled the nematocyst, they migrate up the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation]. Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentilla morphologies. Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters is maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.

*Evolutionary history of tentilla morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships. This revealed for the first time that *Erenna* is the sister to *Stephanomia amphytridis*. *Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.

  Tentillum size, as well as the majority of the characters studied, supported BM evolutionary models. There are two alternative hypotheses about the generative process of BM. One hypothesis would suggest that these characters are not under selection, and therefore diverging neutrally [@lande1976natural]. The second hypothesis suggests that they are under selection, however, the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns on the phylogeny. Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (SM XX).

  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis]. The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition. In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.

A clear example of convergent evolution we found, is that the calycophoran tentillum morphospace (Fig. \@ref(figure9)) was secondarily occupied by *Frillagalma vityazi*. Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas. Unlike calycophorans, they lack paired elongate microbasic mastigophores. Instead, they bear 3 elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus. Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles. Most calycophoran diet studies have reported their prey to be small crustaceans such as copepods or ostracods. The diet of *Frillagalma vityazi* is unknown, but this morphological convergence presents the hypothesis that they evolved to capture similar kinds of prey. Our DAPCs predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.

*Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among the Hydrozoa remains an unresolved question [@munro2018improved]. The most recent work on this front sets them as sister group to all other Hydroidolina [@kayal2015phylogenetic]. All reconstructions of hydrozoan relationships recover siphonophores as an early diverging lineage within Hydroidolina, with many unique apomorphic characters. Therefore, there is a great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores. This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny). One of such characters is the shape of haploneme nematocysts. A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry]. This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation]. Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state. Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects are retaining this ancestral state. Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, associated with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.

Simultaneous with this shift in haploneme shape, heteroneme shape evolution also presents a single transition to elongation. In addition, the clade defined by the most recent common ancestor of *Agalma* and *Nanomia* shows an increased rate of divergence for heteroneme shape, spanning extremes (from oval *Nanomia* stenoteles to the elongate *Agalma okenii* stenoteles) in relatively short evolutionary time. While cystonects don't bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids, hypothetically used for defense rather than for prey capture. These stenotele heteronemes are rounded like those found in pyrostephids and apolemiids, which is consistent with the story of a single transition leading to the elongated heteronemes in the stem of Tendiculophora.

  The implications of these results to the evolution of nematocyst function suggests that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation. Elongate nematocysts can be tightly packed into cnidobands. We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation]. Tendiculophora is the most abundant, speciose and diverse (ecologically and morphologically) clade of siphonophores, containing Euphysonectae and Calycophorae. We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade. However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.

*Diversity of discharge dynamics* – A fundamental corollary in functional morphology is that structural morphology determines functional performance [@wainwright1994ecological]. We expected the discharge dynamics exhibited by of siphonophore tentilla should vary accordingly with their morphological diversity. Our results are consistent with this expectation, where we observe, for example, that cnidoband size largely determines cnidoband discharge speed. This suggests that prey escape response speed may determine the minimum cnidoband length for successful capture.

*Insights from tentilla morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts pervades across clades, from the overall shape and size, to the dimensions of the nematocysts. Siphonophores bear the largest nematocysts among Hydrozoans, and present a wide variety of nematocyst sizes within the clade. The largest nematocysts in our dataset (*Bargmannia lata* by volume and *Resomia dunni* by length), are the largest of all nematocysts reported for cnidarians, and therefore possibly the largest intracellular organelles among all living things.

  In addition to the insights produced in this study, the newly collected morphological data provide a unique resource for future studies, and a reference dataset for siphonophore identification. Many conspicuous categorical characters in siphonophore tentilla are very diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the red lures of *Erenna sirena*, the unique cnidoband shapes in different *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig. \@ref(figure7)). Some categorical characters are synapomorphic diagnostic characters for large clades, such as the proximal tentillum heteronemes of Eucladophora, the elastic strand, rhopalonemes, and desmonemes of Tendiculophora, the larval tentilla of Euphysonectae, the 2-sized isorhizas of Cystonectae, the saccus canal of Pyrostephidae, or the 7 rows of anisorhizas in Calycophorae. These characters should be used together with the classical nectophore and bract characters to identify species or at least impute phylogenetic affiliation from incomplete material.

  Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g. stenoteles, mastigophores, birhopaloids). Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis]. In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations. For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].

## Conclusions {-}

  Siphonophores play a wide variety of predatory roles in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores. The morphological attributes of predators are often finely tuned for their performance during the capture of their prey. With the diversification of prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey. Siphonophore tentilla and nematocysts display a plethora of forms, which are strongly associated with their prey type. The results presented here indicate that these associations are a product of correlated evolution in highly integrated traits. We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches through the evolution and diversification of extraordinary prey capture tools on their tentacles.

## Funding {-}

  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and Anela Choy). A.D.S. was supported by a Fulbright Spain Graduate Studies Scholarship.

## Acknowledgements {-}

  We wish to thank the crew and scientists onboard the R/V Western Flyer, who participated in the collection of many of the specimens used in this study. We also want to thank Lynne Christianson and Shannon Johnson from the Monterey Bay Aquarium Research Institute for their assistance in the field as well as for sequencing some of the species included in this phylogeny. In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections. We thank Joaquin Nunez for reviewing this manuscript. Finally, we thank Philip Pugh, who confirmed our specimen identifications and taught us invaluable knowledge about siphonophores.

## Author contributions {-}

  Alejandro Damian-Serrano (Yale University)  collected specimens and morphological data, executed phylogenetic analyses (tree inference and character evolution), elaborated the figures, wrote and reviewed the manuscript.

  Steven H.D. Haddock (Monterey Bay Aquarium Research Institute) contributed by facilitating the access to the field and collection tools, directing the ROV and blue water diving operations in the field. He also contributed extensive knowledge of the biology and ecology of the organisms, and reviewed the manuscript. The Haddock Lab contributed by sequencing many of the species included in the phylogeny presented here.

  Elizabeth D. Hetherington and C. Anela Choy (Scripps Institute of Oceanography) contributed by collating the literature and deep-sea video annotation data on siphonophore feeding observations, and by reviewing the manuscript.

  Casey W. Dunn (Yale University) contributed by collecting specimens, providing me with invaluable insights and mentoring, and by reviewing the manuscript. In addition, his graduate dissertation work produced many of the sequences used for our phylogenetic analysis.

## References {-}

### 2019-05-09 manuscript.rmd
preparing for submission, clean manuscript, clean code

@@
 }
-write.csv(PICp, "PICcorrelations_pvalues.csv")
+#write.csv(PICp, "PICcorrelations_pvalues.csv")
 

### 2019-05-09 Code_for_Analyses_and_Figures.R

@@ -1,0 +1,990 @@
+
+## LOAD PACKAGES ##
+#General
+library(tidyverse)
+library(stringr)
+library(readr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(adegenet)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(colorRamps)
+
+# Set paths to input data
+setwd("~/tentilla_morph")
+
+#Load raw data
+read.csv("byslide.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)
+
+#Define functions to deal with NAs and decimals
[…]

### 2019-05-13 manuscrip_clean.Rmd
supplementary material prep

@@
 
-We measured at least one specimen for 96 different species (SM3).
+We measured at least one specimen for 96 different species (SM3, Fig.
+\@ref(figure3)).
 Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade.
@@
 For the 10 species recorded, we measured total cnidoband discharge time (ms), average cnidoband discharge speed (mm/s), maximum cnidoband discharge speed (mm/s), heteroneme discharge speed (mm/s), haploneme discharge speed (mm/s), heteroneme shaft discharge speed (mm/s), and heteroneme filament length (microns) when possible (SM4).
-Morphological and kinematic data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+
+![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in SM3).
+Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
+Values scaled by character.
+Green indicates relatively small values, pink indicates relatively large values.](Figures_final/figure3.jpg)
 
@@
 ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred an unconstrained Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM7), which was topologically congruent with the ML tree.
+Additionally, we inferred an Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM7,SM9), which was topologically congruent with the unconstrained ML tree.
 The *alpha* priors were selected to minimize prior load in site variation.
-This tree was then used to inform a Bayesian strict molecular clock time-tree in RevBayes, using a birth-death process (*rho* parameter calculated from the known number of described siphonophore species) generating an ultrametric tree (SM8).
-Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-Scripts available in https://github.com/dunnlab/tentilla_morph/.
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources (SM 13), including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic], and ROV observation data [@choy2017deep;@hissmann2005situ].
+Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (SM6, SM7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) generating an ultrametric tree (SM8).
+ Scripts (SM9) available in https://github.com/dunnlab/tentilla_morph/.
+
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@mackie1987:uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (SM10).
 Since the sampling biases of ROV and gut content based methods are very different, the data was only combined to assign feeding guilds.
@@
 We extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species.
+To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (SM11).
 
-*Statistical analyses* – For subsequent comparative analyses, we use the constrained Bayesian ultrametric tree.
-We removed species present in the tree but not the morphology data, and vice versa.
+*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not the morphology data, and vice versa.
 While we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in  some of the species-level identifications, and some specimens were missing diagnostic zooids.
@@
 We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error.
+\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error (SM3).
 For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
@@
 We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model.
-We calculated model adequacy scores using the R package arbutus [@pennell2015model], which are reported in SMXX.
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing], and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].
+When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM12).
+We calculated model adequacy scores using the R package arbutus [@pennell2015model] (SM13).
+We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM12), and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].
+We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
 
@@
 First, we collapsed the diet data into five feeding guilds (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
-We reconstructed the feeding guild ancestral states using the maximum likelihood function ace (package ape [@paradis2019package]), removing tips with no feeding data.
+We reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
+The ML reconstruction was congruent with the consensus stochastic character mapping (SM18).
 Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model.
-Finally, we compared their AICc support values to select the best fitting model.
+Finally, we compared their AICc support values to select the best fitting model (SM14).
 
-To assess the predictive power of individual tentillum and nematocyst characters on the evolution of the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm).
+To model the relationships between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (SM17).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
@@
 
-To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant] in a set of 11 species.
-This set of taxa was selected to maximize the amount of morphological and dietary data represented without missing values.
-We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet.
+To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM15).
 For these specific groups, we then generated and compared generalized linear models (GLMs) with multiple predictors.
@@
 To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different nematocyst types, and identified the branches with the greatest shifts.
-We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
-In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on these characters to estimate the number and phylogenetic mapping of trait evolution rate regimes.
+In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on haploneme and heteroneme elongation to estimate the number and phylogenetic mapping of trait evolution rate regimes (SM16).
 
@@
 
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in SM0).
-Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.
-Green indicates relatively small values, pink indicates relatively large values.](Figures_final/figure3.jpg)
-
 ![\label{figure4} Bayesian time-tree built from 18S + 16S concatenate.
-Branch lengths estimated using strict molecular clock.
+Branch lengths estimated using relaxed molecular clock.
 Species names in red indicate replicated representation in the morphology data.
@@
 Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
-Diet data was obtained from the literature review in SMx.](Figures_final/figure5.jpg)
+Diet data was obtained from the literature review in SM10.](Figures_final/figure5.jpg)
 
@@
 Individual prey type presence reconstructions show that copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
-The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SMx).
+The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM14).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
@@
 Shifts to copepod presence in the diet are associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
-Consistently with the patterns across extant species, transitions to decapod presence in the diet correlate with the evolution of more coiled cnidobands (SM10).
+Consistently with the patterns across extant species, transitions to decapod presence in the diet correlate with the evolution of more coiled cnidobands (SM17).
 
@@
 
-*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination, and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width.
+*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (SM15), and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width.
 The only groups confounded were large crustacean specialists and generalists.
 For this analysis, we transformed the missing values in the data (due to character absence) to zeroes, thus accommodating more taxa and characters.
-When missing values are retained, the gelatinous-specialist guild is not included, and the DAPC only produces 81% discrimination, highlighting  cnidoband coiledness, cnidoband length, haploneme elongation, heteroneme volume, heteroneme elongation.
 
@@
 \@ref(figure6)).
-When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists.
+When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM15).
 The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width.
@@
 
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (SuppTable x).
+*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (SM12).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 
+The phylogenetic positions of the main categorical character shifts were reconstructed with stochastic character mappings (SM18), and summarized in Figure \@ref(figure7).
 Haploneme nematocysts are likely ancestrally present in the tentacles, since they are present in the tentacles of many other hydrozoans.
@@
 *Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species.
-There is one secondary return to more oval, less elongated haplonemes in Erenna, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae.
+There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
+\@ref(figure10)).
 Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
@@
 \@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (most have rod-shaped anisorhizas, but *Erenna* has oval ones).
-No clear patterns were identified in the evolution of desmoneme and rhopaloneme shape, with the exception of accelerated rhopaloneme shape evolution in *Forskalia* and accelerated rate of desmoneme shape evolution in the clade formed among *Halistemma rubrum* and *Athorybia rosacea*.
+No clear patterns were identified in the evolution of desmoneme and rhopaloneme shape.
 
@@
 The second hypothesis suggests that they are under selection, however, the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns on the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (SM XX).
+Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (SM14).
 
@@
 
+## Supplementary Materials {-}
+
+Data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+
 ## Funding {-}
@@
 In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections.
-We thank Joaquin Nunez for reviewing this manuscript.
-Finally, we thank Philip Pugh, who confirmed our specimen identifications and taught us invaluable knowledge about siphonophores.
+We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript.
+Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us invaluable knowledge about siphonophores.
 

### 2019-05-13 Code_for_Analyses_and_Figures.R

@@ -134,7 +134,7 @@ Ses[Ses == 0] = NA
 morphdata = cbind(castN, castmeans[,-1], Ses)
 morphdata = morphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
 names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
-write.csv(morphdata, "characterdata.csv")
+#write.csv(morphdata, "characterdata.csv")
 
 heatdata = as.matrix(castmean_logs[,-1])
 rownames(heatdata) = castmean_logs$Species
@@ -533,6 +533,7 @@ GC$species = as.character(GC$species)
 GC$species[which(GC$species == "Nanomia bijuga")] <- "Nanomia sp"
 GC$species[which(GC$species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
 GC$species[which(GC$species == "Agalma okeni")] <- "Agalma okenii"
+write.csv(GC, "gutcontentliteraturereview.csv")
 
 #Prune to tree species#
 GC = GC[which(GC$species %in% ultram$tip.label),]
@@ -718,6 +719,15 @@ plotTree(regimetree)
 nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
 RTorder = regimetree$tip.label
 diet[match(RTorder, rownames(diet)),] %>% as.matrix() %>% heatmap(Rowv=NA, Colv=NA, col=c("grey", "black"))
+
+##SIMMAP feeding guilds ##
+make.simmap(regimetree, hypdiet, nsim = 100) -> feeding_sim
+plotTree(regimetree, lwd = 4)
+feeding_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c( "black","green3","blue","cyan","red")
+names(colors) = c("Fish","Large crustacean","Mixed","Small crustacean","Gelatinous")
+nodelabels(pie=(describe.simmap(feeding_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 
[…]

### 2019-05-14 manuscrip_clean.Rmd
supplementary dryad and treebase materials

@@
 
-^1^ Osborn Memorial Laboratories, 165 Prospect St., New Haven, CT 06520, USA
+^1^ Osborn Memorial Laboratories, Department of Ecology and Evolutionary Biology, 165 Prospect St., Yale University, New Haven, CT 06520, USA
 
@@
 H - *Lilyopsis fluoracantha*, slide J10, 20x.
-I - *Abylopsis tetragona*, slide U6, 20x.](Figures_final/figure2.jpg)
+I - *Abylopsis tetragona*, slide U6, 20x.
+Slide metadata available in Dryad.](Figures_final/figure2.jpg)
 
@@
 
-*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in SM1).
-These specimens were collected intact across many years of fieldwork expeditions, by the means of Blue Water Diving [@haddock2005scientific], Remotely Operated Vehicles (ROVs), and human operated submersibles.
+*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1).
+These specimens had been collected intact across many years of fieldwork expeditions, by the means of blue-water Diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
 Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media.
 The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
-30 characters (defined in SM2) were measured using Fiji in ImageJ [@collins2007imagej;@schindelin2012fiji].
+Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
 We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to capture meaningful measurements.
-
-We measured at least one specimen for 96 different species (SM3, Fig.
-\@ref(figure3)).
+We measured at least one specimen for 96 different species (Appendix 3, Fig.
+\@(figure3)).
 Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade.
 Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
+
 In order to observe the discharge behavior of different tentilla, we recorded high speed footage (1000-3000 fps) of tentillum and nematocyst discharge by live siphonophore specimens (26 species) using a Phantom Miro 320S camera mounted on a stereoscopic microscope.
@@
 We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), average cnidoband discharge speed (mm/s), maximum cnidoband discharge speed (mm/s), heteroneme discharge speed (mm/s), haploneme discharge speed (mm/s), heteroneme shaft discharge speed (mm/s), and heteroneme filament length (microns) when possible (SM4).
-
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in SM3).
-Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.
-Green indicates relatively small values, pink indicates relatively large values.](Figures_final/figure3.jpg)
+For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (microns), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (Appendix 4).
 
 *Siphonophore phylogeny* – The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
-The gene sequences used in this study are available online (accession numbers in SM5).
+The gene sequences used in this study are available online (accession numbers in Appendix 5).
 Some of these sequences we used were accessioned in [@dunn2005molecular], others we extracted from the transcriptomes in [@munro2018improved].
@@
 (accession####) analyzed by Lynne Christianson were included and accessioned to NCBI.
-We aligned these sequences using MAFFT [@katoh2002mafft].
-We inferred a Maximum Likelihood (ML) phylogeny (SM6) was reconstructed from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates.
+We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
+We inferred a Maximum Likelihood (ML) phylogeny (Appendix 6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
 We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
@@
 ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred an Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM7,SM9), which was topologically congruent with the unconstrained ML tree.
+Additionally, we inferred an Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (Appendix 7,Appendix 9), which was topologically congruent with the unconstrained ML tree.
 The *alpha* priors were selected to minimize prior load in site variation.
 
-Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (SM6, SM7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) generating an ultrametric tree (SM8).
- Scripts (SM9) available in https://github.com/dunnlab/tentilla_morph/.
+Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6, Appendix 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) generating an ultrametric tree (Appendix 8).
+ Scripts (Appendix 9) available in https://github.com/dunnlab/tentilla_morph/.
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@mackie1987:uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (SM10).
-Since the sampling biases of ROV and gut content based methods are very different, the data was only combined to assign feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without a heavy load on any one prey group).
-We removed the gelatinous prey observations for *Praya dubia* and *Nanomia sp.* , since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey.
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@mackie1987:uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10).
+Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds.
+The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa and for *Nanomia* sp.
+eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear if the medusae were attempting to prey upon the siphonophores.
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh)  were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
 We extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (SM11).
+To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (Appendix 11).
 
-*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not the morphology data, and vice versa.
-While we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in  some of the species-level identifications, and some specimens were missing diagnostic zooids.
+*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and vice versa.
+Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
 Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
 All *Nanomia* sp.
-Observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
+observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
 We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error (SM3).
+\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error (Appendix 3).
 For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
@@
 We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM12).
-We calculated model adequacy scores using the R package arbutus [@pennell2015model] (SM13).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM12), and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].
+When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (Appendix 12).
+We calculated model adequacy scores using the R package arbutus [@pennell2015model] (Appendix 13).
+We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12), and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].
 We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
+R scripts available in Dryad.
 
@@
 We reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
-The ML reconstruction was congruent with the consensus stochastic character mapping (SM18).
+The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
 Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model.
-Finally, we compared their AICc support values to select the best fitting model (SM14).
+Finally, we compared their AICc support values to select the best fitting model (Appendix 14).
 
-To model the relationships between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (SM17).
+To model the relationships between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (Appendix 17).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
@@
 To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
-We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM15).
+We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
 For these specific groups, we then generated and compared generalized linear models (GLMs) with multiple predictors.
@@
 To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different nematocyst types, and identified the branches with the greatest shifts.
-In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on haploneme and heteroneme elongation to estimate the number and phylogenetic mapping of trait evolution rate regimes (SM16).
+In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on haploneme and heteroneme elongation to estimate the number and phylogenetic mapping of trait evolution rate regimes (Appendix 16).
 
 ## Results {-}
+
+![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in Appendix 3).
+Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
+Values scaled by character.](Figures_final/figure3.jpg)
+
+*Phylogeny* – Only 5 nodes in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree.
+The topology of the constrained tree presented here (Fig.
+\@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
 
@@
 Tips with black squares indicate the species with transcriptomes used in  (Munro *et al.* 2018).
-Tips with translucent squares indicate genus-level correspondence to taxa included in  (Munro *et al.* 2018).
+Tips with grey squares indicate genus-level correspondence to taxa included in  (Munro *et al.* 2018).
 The main clades are labeled: in black for described taxonomic units, and in grey for operation phylogenetic designations.](Figures_final/figure4.jpg)
-
-*Phylogeny* – Only 5 nodes in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree.
-The topology of the constrained tree presented here (Fig.
-\@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
 
@@
 
-![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the OUwie analyses.
-Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
-Diet data was obtained from the literature review in SM10.](Figures_final/figure5.jpg)
-
-*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guild show that generalism was not likely ancestral, and it appears to have evolved at least 2 times independently (Fig.
+*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism was not likely ancestral, and it appears to have evolved at least 2 times independently (Fig.
 \@ref(figure5)).
 Individual prey type presence reconstructions show that copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
-The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM14).
+The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (Appendix 14).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
-Most of these characters are found exclusively in Tendiculophora, thus this is reflecting processes that could be unique to this subtree.
+Most of these characters are found exclusively in Tendiculophora, thus this reflects processes that could be unique to this subtree.
 Five characters including cnidoband length, cnidoband shape, and haploneme length show maximal support for a diet-driven single-optimum OU model.
@@
 
-  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types (Fig.
-\@ref(figure5), right) in the diet.
-showed that shifts towards ostracod diet correlate with reductions in pedicle width and total haploneme volume.
-Shifts to copepod presence in the diet are associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
-Consistently with the patterns across extant species, transitions to decapod presence in the diet correlate with the evolution of more coiled cnidobands (SM17).
+![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the OUwie analyses.
+Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
+Diet data were obtained from the literature review in Appendix 10.](Figures_final/figure5.jpg)
+
+  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig.
+@\ref(figure5), right).
+Shifts toward ostracod presence in diet correlated with reductions in pedicle width and total haploneme volume.
+Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
+Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (Appendix 17).
 
   Phylogenetic regressions of continuous characters against prey selectivity data produced additional insights.
-Specialization in a piscivorous diet is associated to increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
-Decapod rich diets are associated to increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
-Copepod-selective diets evolved in association to increasingly smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, heteronemes, tentacles, pedicles and elastic strands.
-Selectivity for ostracods  is associated to reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
-Heteroneme length and shape also correlates negatively with chaetognath selectivity.
+Specialization in a piscivorous diet was associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
+Decapod-rich diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
+Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles and elastic strands.
+Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
+Heteroneme length and shape also correlated negatively with chaetognath selectivity.
 
@@
 
-*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (SM15), and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width.
+*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width.
 The only groups confounded were large crustacean specialists and generalists.
@@
 \@ref(figure6)).
-When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM15).
+When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15).
 The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width.
@@
 
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (SM12).
+*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (Appendix 12).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 
-The phylogenetic positions of the main categorical character shifts were reconstructed with stochastic character mappings (SM18), and summarized in Figure \@ref(figure7).
+The phylogenetic positions of the main categorical character shifts were reconstructed with stochastic character mappings (Appendix 18), and summarized in Figure \@ref(figure7).
 Haploneme nematocysts are likely ancestrally present in the tentacles, since they are present in the tentacles of many other hydrozoans.
@@
 The second hypothesis suggests that they are under selection, however, the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns on the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (SM14).
+Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
 

### 2019-05-14 Code_for_Analyses_and_Figures.R

@@ -829,6 +829,30 @@ for(c in 2:ncol(dprunedmatrix_logs)){
 OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
 write.csv(OUwie_matrix, "OU_diet_test.csv")
 
+#OUwie model adequacy
+#Model adequacy
+worthy_models = OUwie_matrix
+MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
+names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
+rownames(MAD) = worthy_models$Character
+for(m in 1:nrow(worthy_models)){
+  C = dprunedmatrix_logs[,which(names(dprunedmatrix_logs) == worthy_models$Character[m])]
+  names(C) = dprunedmatrix_logs$Species
+  C = C[!is.na(C)]
+  Ctree = drop.tip(regimetree, which(!(regimetree$tip.label %in% names(C))))
+  C = C[match(Ctree$tip.label, names(C))]
+  class(Ctree)="phylo"
+  FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
+  UTC <- make_unit_tree(FC)
+  picstat_data <- calculate_pic_stat(UTC)
+  sim <- simulate_char_unit(UTC)
+  picstat_sim <- calculate_pic_stat(sim)
+  compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
+}
+phy_models = data.frame(worthy_models,MAD)
+phy_models[,6:11] = apply(phy_models[,6:11], 2,round3)
+#write.csv(phy_models, "OUwie_model_adequacy.csv")
+
 ## DAPC ##
 #General prediction of feeding guild (transforming NAs to zeroes)
 ldamtrix = sharedmean_logs

### 2019-05-14 Supplementary_materials/Dryad/R_Code.R

@@ -1,0 +1,1049 @@
+
+## LOAD PACKAGES ##
+#General
+library(tidyverse)
+library(stringr)
+library(readr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(adegenet)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(colorRamps)
+
+# Set paths to input data
+setwd("~/tentilla_morph")
+
+#Load raw data
+read.csv("byslide.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)
+
+#Define functions to deal with NAs and decimals
[…]

### 2019-05-14 Supplementary_materials/Dryad/R_Code.R
fixed Rcode.R to work with the pathnames in Dryad

@@ -31,12 +31,12 @@ library(gridExtra)
 library(colorRamps)
 
 # Set paths to input data
-setwd("~/tentilla_morph")
+#setwd("~/tentilla_morph")
 
 #Load raw data
-read.csv("byslide.csv") -> numbers
+read.csv("raw_morphology_data.csv") -> numbers
 numbers$Species = as.character(numbers$Species)
-categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+categorical <- read.csv("raw_categorical_data.csv")[,-2]
 rownames(categorical) = categorical$Species
 
 #Correct species spellings
@@ -144,7 +144,7 @@ hcolors<-c(rep("#000000FF",10), hcolors)
 heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)
 
 #Load phylogenetic tree
-consensus = read.nexus("TimeTree_CT_truerho.tre") %>% drop.tip(56:61)
+consensus = read.nexus("../TreeBase/RB_constrained_timetree/TimeTree_siphs_mcmc_MAP.tre") %>% drop.tip(56:61)
 consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
 #Switch Nanomia bijuga for Nanaomia sp
 consensus$tip.label[which(consensus$tip.label == "Nanomia bijuga")] <- "Nanomia sp"
@@ -526,7 +526,7 @@ for(i in 2:length(traitlist)){
 
 ## Retrieve diet data ##
 #Retrieve diet info from literature BINARY
-GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5,6)] %>% .[which(grepl("diet",.$character) & .$state==1),]
+GC = read.csv("literature_diet_data.tsv", header = T, sep='\t')
 GC$character = factor(GC$character, levels=unique(GC$character))
 GC$species = as.character(GC$species)
 #Fix typos#
@@ -571,7 +571,7 @@ diet = rbind(diet, cladeB, krilleaters, gelateaters)
 #Decapod diet column actually encompasses decapods, krill, and mysids (large crustaceans/shrimp like animals)
 
 # Retrive ROV annotation data
-VARS <- read.csv("Choy2017.tsv", sep="\t")
+VARS <- read.csv("raw_ROV_data.csv")
[…]

### 2019-05-23 manuscrip_clean.Rmd
arranged and fixed the DAPC part with its supplement

@@
 Predators have evolved dedicated body parts to capture and subdue prey.
-As different lineages specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms.
-Studying this process requires a predator clade with structures used exclusively for prey capture that present significant morphological variation.
+As different predators specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms.
+Studying the evolution of predation is greatly facilitated by a predator clade with structures used exclusively for prey capture that present significant morphological variation.
 Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well, capturing prey with their tentilla (tentacle side branches).
@@
 We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured extensive morphological traits from fixed siphonophore specimens using microscopy and high speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) characterized the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
+To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) characterized the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
 Our results show that siphonophore tentilla structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey type specializations are linked to shifts in tentillum and nematocyst size and shape.
@@
 The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
-Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
+Understanding the relationships between predatory specializations and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
 
@@
 While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism upon encounter with prey.
-Tentilla undergo an extremely fast conformational change that wraps around the prey, maximizing the surface area of contact for nematocysts to fire on it [@Mackie:1987uy].
+When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy].
 In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent].
 
-  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor (~3000-11000m).
+  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
 This habitat has fairly homogeneous abiotic conditions and stable temporal patterns in the abundance of zooplanktonic animals [@robison2004deep].
 With a somewhat predictable prey availability, ecological theory would expect evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of specialization on a variety of prey types.
+If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
 
@@
 
-  The few studies have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+  The few pioneering studies that have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
 [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
@@
 Some of these sequences we used were accessioned in [@dunn2005molecular], others we extracted from the transcriptomes in [@munro2018improved].
-Two new 16S sequences for *Frillagalma vityazi* (accession####) and *Thermopalia* sp.
-(accession####) analyzed by Lynne Christianson were included and accessioned to NCBI.
+Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
+(MK958599) sequenced by Lynne Christianson were included and accessioned to NCBI.
 We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
@@
 
-Given the greater statistical power and credibility of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6, Appendix 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6, Appendix 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
 This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) generating an ultrametric tree (Appendix 8).
@@
 
-*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and vice versa.
+*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
 Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
@@
 To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
-We generated discriminant functions for feeding guild, presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
-For these specific groups, we then generated and compared generalized linear models (GLMs) with multiple predictors.
+We generated discriminant functions for feeding guild, soft/hard bodied prey, presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
+Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
+We tackled this with two alternative approaches.
+One approach was to selectively remove characters and taxa to maximize the total data mass.
+Another approach was to transform the “NA” states to zeroes.
+The drawbacks of first approach is that useful data is lost, and observations are biased towards taxa with more complex tentacles.
+The drawbacks of the second approach is that small state values become aligned with absences.
+The severity of these drawbacks depends on the specific aspect of diet being predicted, thus we chose our approach in a case-specific basis.
+For the specific prey types, we then generated and compared generalized linear models (GLMs) with multiple predictors.
 We chose predictors among the characters with significant loading contributions in each specific DAPC.
@@
 
-![\label{figure4} Bayesian time-tree built from 18S + 16S concatenate.
+![\label{figure4} Bayesian time-tree built from 18S + 16S concatenated sequences.
 Branch lengths estimated using relaxed molecular clock.
@@
 
-*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism was not likely ancestral, and it appears to have evolved at least 2 times independently (Fig.
+*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism was not likely ancestral, and it appears to have evolved at least two times independently (Fig.
 \@ref(figure5)).
@@
 
-*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Heteroneme size, involucrum length, total haploneme and heteroneme volume, cnidoband length, heteroneme/cnidoband length ratio, heteroneme width, and cnidoband length and width.
-The only groups confounded were large crustacean specialists and generalists.
-For this analysis, we transformed the missing values in the data (due to character absence) to zeroes, thus accommodating more taxa and characters.
+*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Total haploneme volume, total nematocyst volume, cnidoband length, heteroneme volume, involucrum length, pedicle width, and tentacle width.
+The only groups confounded were generalists and large crustacean specialists.
+For this analysis, we transformed the non-applicable states in the data (due to character absence) to zeroes, thus accommodating more taxa and characters and reducing sampling bias.
+Absent characters (such as tentilla, or particular nematocyst types) are likely to be very biologically relevant to prey capture, so we believe they should be accounted for.
+When the absent character data is simply removed, similar discrimination is achieved, with the same large crustacean and generalist ambiguity (Appendix 15).
+However, the predictions from this DAPC for the species with missing characters is largely inaccurate (*e.g.* *Rhizophysa eysenhardti*, a specialized fish eater, is predicted as a small crustacean specialist).
+When missing values are substituted by zeroes, the prediction accuracies improve greatly.
 
@@
 Training data set transformed so missing values would be computed as zeroes.
-Species colored according to their predicted feeding guild with highest probability score.](Figures_final/figure6.jpg)
+Species ordered and colored according to their predicted feeding guild with highest probability score.](Figures_final/figure6.jpg)
 
-  We used this discriminant function to predict the feeding guild of 45 species in our morphological data (Fig.
+  We used this discriminant function to predict the feeding guild of 45 species in our morphological data, removing taxa and characters with inapplicable character states (Fig.
 \@ref(figure6)).
 When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15).
+This is congruent with the large crustacean and generalist confounds in the feeding guild discrimination.
 The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width.
 Discriminant analyses and GLM were also applied to specific prey type presence and selectivity (Table \@ref(table2), highlighting the most relevant characters and their predictive power.
+These analyses were carried out in a subset of characters and species that minimized taxa and characters with inapplicable states (except for fish presence, which produced much better results upon transforming inapplicable states to zeroes).
+The non-piscivorous (fish excluding diet) tentacle morphospace is a subset of the piscivorous (fish inclusive diet) tentacle morphospace (Appendix 15).
+However, fish specialists occupy a very distinct region of the morphospace (Fig.
+@\ref(figure6)).
 
@@
 Only the best GLM is reported.
-Pseudo-R2 approximate the variance explained by the model.](Final_tables/table2.png)
+Pseudo-R2 approximate the variance explained by the model.
+Fish model built with NAs converted to zeroes.](Final_tables/table2.png)
 
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are more stochastically than phylogenetically distributed (Appendix 12).
+*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not likely to be phylogenetically distributed (Appendix 12).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 
-![\label{figure7} Bayesian cladogram with the main categorical character gains (green) and losses (red) mapped.
+![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
+Some branch lengths were modified from the bayesian chronogram to improve readability.
 The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
@@
 \@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore type ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which would bear no other nematocyst type, and these would be arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
+\@ref(figure7)), which bear no other nematocyst type.
+These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
 The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband.
@@
 *Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are very correlated to each other.
+The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement is independent of it.
 Of the phylogenetic correlations (Fig.
@@
 In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
-These results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement is independent of it.
 
@@
 ## Discussion {-}
-  This core aim of this paper is to characterize the evolutionary history of siphonophore tentilla and its relationships with diet.
+  This core aim of this study is to characterize the evolutionary history of siphonophore tentilla and its relationships with diet.
 In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
@@
 *Evolution of tentilla morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], potentially serving as trophic intermediaries between smaller zooplankton and higher trophic level predators.
+While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as trophic intermediaries between smaller zooplankton and higher trophic level predators.
 Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
@@
 
-  Throughout this study, we evaluate our findings from an adaptive perspective, assessing whether our results are congruent with adaptation.
+  Throughout this study, we assess whether our results are congruent with adaptation.
 However, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
@@
 The ecomorphological association between rhopalonemes, desmonemes and crustacean eaters was not congruent with a scenario of correlated evolution.
-This could be due to our analysis with a broad set of taxa including multiple species without desmonemes or rhopalonemes that effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
+This could be due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes that effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
 
@@
 
-A clear example of convergent evolution we found, is that the calycophoran tentillum morphospace (Fig.
-\@ref(figure9)) was secondarily occupied by *Frillagalma vityazi*.
+Our work identifies an interesting example of convergent evolution.
+The calycophoran tentillum morphospace (Fig.
+\@ref(figure9)) was independently occupied by *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 We expected the discharge dynamics exhibited by of siphonophore tentilla should vary accordingly with their morphological diversity.
-Our results are consistent with this expectation, where we observe, for example, that cnidoband size largely determines cnidoband discharge speed.
+Our results are consistent with this expectation, where we observe, for example, that cnidoband size largely correlates with cnidoband discharge speed.
 This suggests that prey escape response speed may determine the minimum cnidoband length for successful capture.

### 2019-05-23 Code_for_Analyses_and_Figures.R

@@ -880,14 +880,46 @@ preDIET <- predict(DAPClogs, predictionset[,-1])
 cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
 preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
 
-#Particular diet items that have enough variability (Copepods, fish, large crustaceans)
-prunediets = diet[which(rownames(diet) %in% ldamtrix$Species),]
+#Remove NAs from characters and species
+rowNAs = c(0,apply(sharedmean_logs[,-1], 1, function(x) sum(is.nan(x))))
+colNAs = c(0,apply(sharedmean_logs[,-1], 2, function(x) sum(is.nan(x))))
+ldamtrix = sharedmean_logs[,which(colNAs<6)]
+ldamtrix = ldamtrix[which(!is.nan(rowSums(ldamtrix[,-1]))),]
+ldamtrix = ldamtrix[which(rowNAs<1),]
+ldamtrix$Species = as.character(ldamtrix$Species)
+ldamtrix = ldamtrix[which(ldamtrix$Species %in% names(hypdiet)),]
+LDAtree = drop.tip(ultram, which(!(ultram$tip.label %in% ldamtrix$Species)))
+ldamtrix = ldamtrix[match(LDAtree$tip.label, ldamtrix$Species),]
+baselda=ldamtrix
 
+#Feeding guilds with NAs removed
+prunediets = hypdiet[which(names(hypdiet) %in% ldamtrix$Species)]
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, names(prunediets))])
+names(ldamtrix)[ncol(ldamtrix)]<-"Diet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$Diet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
+dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$Diet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
[…]

### 2019-05-23 Supplementary_materials/Dryad/R_Code.R

@@ -879,14 +879,38 @@ preDIET <- predict(DAPClogs, predictionset[,-1])
 cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
 preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
 
-#Particular diet items that have enough variability (Copepods, fish, large crustaceans)
-prunediets = diet[which(rownames(diet) %in% ldamtrix$Species),]
+#Remove NAs from characters and species
+rowNAs = c(0,apply(sharedmean_logs[,-1], 1, function(x) sum(is.nan(x))))
+colNAs = c(0,apply(sharedmean_logs[,-1], 2, function(x) sum(is.nan(x))))
+ldamtrix = sharedmean_logs[,which(colNAs<6)]
+ldamtrix = ldamtrix[which(!is.nan(rowSums(ldamtrix[,-1]))),]
+ldamtrix = ldamtrix[which(rowNAs<1),]
+ldamtrix$Species = as.character(ldamtrix$Species)
+ldamtrix = ldamtrix[which(ldamtrix$Species %in% names(hypdiet)),]
+LDAtree = drop.tip(ultram, which(!(ultram$tip.label %in% ldamtrix$Species)))
+ldamtrix = ldamtrix[match(LDAtree$tip.label, ldamtrix$Species),]
+baselda=ldamtrix
 
+#Feeding guilds with NAs removed
+prunediets = hypdiet[which(names(hypdiet) %in% ldamtrix$Species)]
+ldamtrix = cbind(baselda, prunediets[match(baselda$Species, names(prunediets))])
+names(ldamtrix)[ncol(ldamtrix)]<-"Diet"
+#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
+xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$Diet, n.pca.max = 300, training.set = 0.9,
+                 result = "groupMean", center = TRUE, scale = TRUE,
+                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
[…]

### 2019-05-24 Supplementary_materials/Dryad/R_Code.R
finished supplements, exported to PDF

@@ -1,4 +1,3 @@
-
 ## LOAD PACKAGES ##
 #General
 library(tidyverse)
@@ -904,6 +903,14 @@ contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
 scatter(DAPClogs, clabel = 0.5)
 assignplot(DAPClogs)
 compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
+predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
+predictionset[is.na(predictionset)]<-0
+rownames(predictionset)<-predictionset$Species
+predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),] #Remove taxa with many unmeasured NAs that create zero-biases
+predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
+preDIET <- predict(DAPClogs, predictionset[,-1])
+cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
 
 #Particular diet items that have enough variability (Copepods, fish, large crustaceans)
 #Copepods
@@ -941,10 +948,12 @@ predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia ta
 predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
 preDIET <- predict(DAPClogs, predictionset[,-1])
 cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
-preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="col", cexCol=0.5, col=c("white", "white", gray.colors(10)[10:1],"black", "black"),Colv=NA)
 
 #Fish
-ldamtrix = baselda
[…]

### 2019-05-28 manuscrip_clean.Rmd
latest text comments addressed

@@
 
+  Coexisting siphonophores feeding on the same planktonic community are potential competitors.
+Traditional ecological coexistence theory [@simpson1944tempo] predicts that competition between species would select for increasing ecological specialization.
+Moreover, specialization is often thought to be an evolutionary ‘dead end,’ meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource in which they are specialized [@futuyma1988evolution].
+However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition], and resource switching [@hoberg2008macroevolutionary].
+Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from different ancestral predatory specialists, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+
   The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
@@
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@mackie1987:uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10).
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10).
 Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds.
@@
 ## Discussion {-}
-  This core aim of this study is to characterize the evolutionary history of siphonophore tentilla and its relationships with diet.
+  This core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type.
+We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles.
 In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
@@
 
-  The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
-
 The evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
@@
 Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
+Among the evolutionary hypotheses considered, we find support for both hypotheses (2) and (3), but no support for hypothesis (1).
+The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution.
+This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
 
@@
 
+    Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g.
+stenoteles, mastigophores, birhopaloids).
+Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
+In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations.
+For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].
+Nonetheless, siphonophores have evolved unique nematocyst types, not present in any other cnidarian.
+For example, rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
+Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not been yet found in any other tissue of any other organism.
+The gain of extreme elongation in the haplonemes of Tendiculophora can be interpreted as part of the character shift to a novel anisorhiza subtype.
+
 *Diversity of discharge dynamics* – A fundamental corollary in functional morphology is that structural morphology determines functional performance [@wainwright1994ecological].
@@
 
-  Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g.
-stenoteles, mastigophores, birhopaloids).
-Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
-In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations.
-For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].
-
 ## Conclusions {-}
 
-  Siphonophores play a wide variety of predatory roles in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
-The morphological attributes of predators are often finely tuned for their performance during the capture of their prey.
-With the diversification of prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey.
-Siphonophore tentilla and nematocysts display a plethora of forms, which are strongly associated with their prey type.
-The results presented here indicate that these associations are a product of correlated evolution in highly integrated traits.
-We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches through the evolution and diversification of extraordinary prey capture tools on their tentacles.
+  Siphonophores have diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
+With the evolution of diversified prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey.
+The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.
+While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that  specialists on one prey type have directly evolved into specialists on other prey types.
+Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to predict the feeding habits of uncharacterized species.
+We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
 

### 2019-05-28 BAMM/BAMMplots.R
cleaned up repo

@@ -1,37 +1,0 @@
-# load libraries
-library(BAMMtools)
-library(geiger)
-library(coda)
-setwd("~/tentilla_morph/BAMM")
-# load tree
-tree <- read.tree("desmoneme_elongation_tree.tre")
-
-# ESS after 20% burnin
-mcmcout <- read.csv("mcmc_out.txt")
-burnstart <- floor(0.2*nrow(mcmcout))
-postburn <- mcmcout[burnstart:nrow(mcmcout), ]
-effectiveSize(postburn$N_shifts)
-effectiveSize(postburn$logLik)
-
-# load BAMM main output
-edata <- getEventData(tree, eventdata = "event_data.txt", burnin=0.2, type="trait")
-summary(edata)
-
-# the 6 most likely scenario's within the 95% credible scenarios
-# F value is the relative probability, F values from all scenarios add up to F=1
-pdf("BAMM_desmoneme_elongation_css.pdf", width=7, height=10)
-css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
-BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T, use.plot.bammdata = T)
-dev.off()
-
-# net diversification graph
-pdf("BAMM_desmoneme_elongation_netdiv.pdf", width=7, height=5)
-starttime <- max(branching.times(tree))
-plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
-dev.off()
-
-pdf("desmoneme_elongation_ratesplot.pdf",width=16,height=16)
-plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
-dev.off()
-
-#q()

### 2019-05-28 BAMM/BAMMsetpriors.R

@@ -1,15 +1,0 @@
-library(BAMMtools)
-library(stringr)
-library(readr)
-setwd("~/tentilla_morph/BAMM")
-tree <- read.tree("desmoneme_elongation_tree.tre")
-traits <- read.csv("desmoneme_elongation.txt", sep="\t", header = F)
-rownames(traits) = traits[,1]
-traits <- traits[tree$tip.label,]
-write_tsv(traits, "desmoneme_elongation.txt", col_names = FALSE)
-is.ultrametric(tree) # check for ultrametric
-is.binary.tree(tree) # check if there are no polytomies
-min(tree$edge.length) # check all branch lengths are > 0
-setBAMMpriors(phy = tree, traits = "desmoneme_elongation.txt")
-setwd("~/tentilla_morph/")
-#q()

### 2019-05-28 Code_for_Analyses_and_Figures.R

@@ -1,1083 +1,0 @@
-
-## LOAD PACKAGES ##
-#General
-library(tidyverse)
-library(stringr)
-library(readr)
-library(reshape2)
-## Biological
-library(Rphylip)
-library(arbutus)
-library(vegan)
-library(ape)
-library(phangorn)
-library(phytools)
-library(OUwie)
-library(picante)
-library(geiger)
-library(phylobase)
-library(fields)
-library(phylosignal)
-library(geomorph)
-library(phylopath)
-library(phylolm)
-library(adegenet)
-## Graphics
-library(FactoMineR)
-library(factoextra)
-library(corrplot)
-library(BAMMtools)
-library(gridExtra)
-library(colorRamps)
-
-# Set paths to input data
-setwd("~/tentilla_morph")
-
-#Load raw data
-read.csv("byslide.csv") -> numbers
-numbers$Species = as.character(numbers$Species)
-categorical <- read.csv("Homolog_Categorical.csv")[,-2]
-rownames(categorical) = categorical$Species
-
-#Correct species spellings
-numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
-numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
-numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
-
-#Merge Nanomias
-numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
-numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
-
-#Polish fields
-castnumbers = numbers
-castnumbers[castnumbers=="needDIC"] <- NA
-castnumbers[castnumbers=="needConfocal"] <- NA
-castnumbers[castnumbers=="needMature"] <- NA
-castnumbers[castnumbers=="needReslide"] <- NA
-castnumbers[castnumbers==-1] <- NA
-castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
-castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)
-
-#Define functions to deal with NAs and decimals
[…]

### 2019-05-28 Phylogeny_inference/Final_analyses/slurm_Timetree_ct_rb.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH --job-name=rb_time_with_constrain
-
-#SBATCH --partition=general
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=1
-
-#SBATCH --mem-per-cpu=1G
-#SBATCH --time=3-23:00:00
-
-./revbayes/projects/cmake/rb timetree_rev/mcmc_TimeTree_siphs_ct.Rev

### 2019-05-28 Phylogeny_inference/Final_analyses/slurm_Timetree_rb.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH --job-name=rbmpi_with_constrain
-
-#SBATCH --partition=general
-#SBATCH --ntasks=1
-#SBATCH --cpus-per-task=1
-
-#SBATCH --mem-per-cpu=1G
-#SBATCH --time=3-23:00:00
-
-./revbayes/projects/cmake/rb timetree_rev/mcmc_TimeTree_siphs.Rev

### 2019-05-28 Phylogeny_inference/Final_analyses/slurm_multitask.sh

@@ -1,19 +1,0 @@
-#!/bin/bash
-#SBATCH --job-name=revbayes_multitask
-#SBATCH --time=120:00:00
-#SBATCH --mem=48G
-#SBATCH --output=rb_out-%j_.out
-#SBATCH --error=rb_out-%j_error.out
-#SBATCH --array=1-3
-#SBATCH --ntasks-per-node=1
-sleep $((SLURM_ARRAY_TASK_ID*60))
-
-filenames = (
-	revbayes.rev
-	revbayes_ct.rev
-	)
-
-file = ${filenames[$SLURM_ARRAY_TASK_ID-1]}
-echo $file
-
-./rb $file

### 2019-05-28 Phylogeny_inference/Final_analyses/slurm_srun_constrain_rb.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH --job-name=rbmpi_with_constrain
-
-#SBATCH --partition=scavenge
-#SBATCH --ntasks=64
-#SBATCH --cpus-per-task=1
-
-#SBATCH --mem-per-cpu=1G
-#SBATCH --time=3-00:00:00
-
-srun ./revbayes/projects/cmake/rb-mpi revbayes_ct.rev

### 2019-05-28 Phylogeny_inference/Final_analyses/slurm_srun_rb.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#SBATCH --job-name=rbmpi_no_constrain
-
-#SBATCH --partition=scavenge
-#SBATCH --ntasks=64
-#SBATCH --cpus-per-task=1
-
-#SBATCH --mem-per-cpu=1G
-#SBATCH --time=3-00:00:00
-
-srun ./revbayes/projects/cmake/rb-mpi revbayes.rev

### 2019-05-28 Phylogeny_inference/agalma_16S18S_extraction.py

@@ -1,32 +1,0 @@
-import sqlite3
-
-conn = sqlite3.connect('agalma-siphonophora-20180401_reduced.sqlite')
-c = conn.cursor()
-
-species16S = [ "Lilyopsis fluoracantha", "Rudjakovia sp", "Bargmannia lata", "Physonect sp", "Erenna richardi", "Resomia ornicephala", "Physophora gilmeri" ]
-species18S = [ "Lychnagalma ultricularia", "Frillagalma vityazi", "Rudjakovia sp", "Bargmannia lata", "Apolemia rubriversa", "Erenna richardi", "Resomia ornicephala", "Physophora gilmeri", "Thermopalia taraxaca", "Marrus claudanielis" ]
-
-print "\n 16S"
-for species in species16S:
-	export16S = open("%s_16S.fasta" % species.replace(" ", "_"), "w")
-	c.execute("select c.species, m.genome_type, m.molecule_type, s.* from agalma_sequences as s join agalma_models as m on s.model_id=m.id join catalog as c on c.id=m.catalog_id where m.molecule_type='S' and m.genome_type='M' and c.species='%s';" % species)
-	out16S = c.fetchall()
-	print species
-	print len(out16S)
-	export16S.writelines([">{0}\n".format(item) for item in out16S])
-	export16S.close()
-
-c = conn.cursor()
-
-print "\n 18S"
-for species in species18S:
-	export18S = open("%s_18S.fasta" % species.replace(" ", "_"), "w")
-	c.execute("select c.species, m.genome_type, m.molecule_type, s.* from agalma_sequences as s join agalma_models as m on s.model_id=m.id join catalog as c on c.id=m.catalog_id where m.molecule_type='S' and m.genome_type='N' and c.species='%s';" % species)
-	out18S = c.fetchall()
-	print species
-	print len(out18S)
-	export18S.writelines([">{0}\n".format(item) for item in out18S])
-	export18S.close()
-
-conn.commit()
-conn.close()

### 2019-05-28 Phylogeny_inference/consensus_transcriptome/constraintree.R

@@ -1,30 +1,0 @@
-library(tidyverse)
-library(ape)
-library(phytools)
-library(seqinr)
-
-setwd("~/Dropbox/tentilla_phylogeny2019/consensus_transcriptome")
-
-rrna <- seqinr::read.fasta("../all18S_curated_sublist.fasta")
-rrna_names <- names(rrna)
-
-treelist = list()
-for(tr in 1:length(list.files("trees"))){
-  treelist[[tr]] = ape::read.tree(paste("./trees/", list.files("trees")[tr], sep=""))
-}
-root(treelist[[1]],25) -> treelist[[1]]
-root(treelist[[2]],25) -> treelist[[2]]
-root(treelist[[3]],25) -> treelist[[3]]
-root(treelist[[4]],17) -> treelist[[4]]
-root(treelist[[5]],17) -> treelist[[5]]
-root(treelist[[6]],17) -> treelist[[6]]
-str_consensus <- ape::consensus(treelist)
-str_consensus$tip.label[which(str_consensus$tip.label == "Prayidae_D27D2")] <- "Craseoa_lathetica"
-str_consensus$tip.label[which(str_consensus$tip.label == "Prayidae_D27SS7")] <- "Desmophyes_haematogaster"
-str_consensus$tip.label[which(str_consensus$tip.label == "Physonect_sp_")] <- "Physonect_sp"
-consensus_tl <- str_consensus$tip.label
-
-missingtaxa <- rrna_names[which(!(rrna_names %in% consensus_tl))]
-extrataxa <- consensus_tl[which(!(consensus_tl %in% rrna_names))]
-pending_transcriptome_taxa[]
-

### 2019-05-28 Phylogeny_inference/seqwrangling.R

@@ -1,110 +1,0 @@
-library(tidyverse)
-library(seqinr)
-library(msa)
-library(ape)
-setwd("~/Dropbox/tentilla_phylogeny2019")
-
-#Load FASTA files
-LIST_16S = list()
-for(f in 1:length(list.files("sequences16S"))){
-  LIST_16S[[f]] = seqinr::read.fasta(paste("./sequences16S/", list.files("sequences16S")[f], sep=""))
-}
-LIST_18S = list()
-for(f in 1:length(list.files("sequences18S"))){
-  LIST_18S[[f]] = seqinr::read.fasta(paste("./sequences18S/", list.files("sequences18S")[f], sep=""))
-}
-
-#Transform list of FASTAs into dataframes
-sequences16S = lapply(LIST_16S, getSequence) %>% lapply(function(x){lapply(x,function(y){paste(unlist(y), sep="", collapse="")})}) %>% unlist()
-names16S = lapply(LIST_16S, names) %>% unlist()
-annots16S = lapply(LIST_16S, getAnnot) %>% unlist()
-ALL16S = data.frame(names16S,annots16S, rep("16S", length(names16S)), sequences16S)
-names(ALL16S) = c("Taxon","Annotation","Gene","Sequence")
-
-sequences18S = lapply(LIST_18S, getSequence) %>% lapply(function(x){lapply(x,function(y){paste(unlist(y), sep="", collapse="")})}) %>% unlist()
-sequences18S = str_replace_all(sequences18S,"[^atgc]","")
-names18S = lapply(LIST_18S, names) %>% unlist()
-annots18S = lapply(LIST_18S, getAnnot) %>% unlist()
-ALL18S = data.frame(names18S,annots18S,rep("18S", length(names18S)),sequences18S)
-names(ALL18S) = c("Taxon","Annotation","Gene","Sequence")
-ALL16S = ALL16S[order(ALL16S$Taxon),]
-ALL18S = ALL18S[order(ALL18S$Taxon),]
-write.fasta(as.list(ALL16S$Sequence), names=paste(ALL16S$Annotation, 1:nrow(ALL16S))  , file.out = "all16S.fasta")
-write.fasta(as.list(ALL18S$Sequence), names=paste(ALL18S$Annotation, 1:nrow(ALL18S))  , file.out = "all18S.fasta")
-
-#Align by gene
-ALL16S_aligned = ALL16S
-ALL18S_aligned = ALL18S
[…]

### 2019-05-28 Scrap/manuscript.rmd
cleaned up repo

--- 2019-05-09 manuscript.rmd
@@
 nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
+
+##SIMMAP feeding guilds ##
+make.simmap(regimetree, hypdiet, nsim = 100) -> feeding_sim
+plotTree(regimetree, lwd = 4)
+feeding_sim %>% plotSimmap(lwd = 4, add = T)
+colors = c( "black","green3","blue","cyan","red")
+names(colors) = c("Fish","Large crustacean","Mixed","Small crustacean","Gelatinous")
+nodelabels(pie=(describe.simmap(feeding_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
+add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 

### 2019-05-28 manuscript_clean.Rmd
cleaned up repo

--- 2019-05-28 manuscrip_clean.Rmd
@@
 
-^1^ Osborn Memorial Laboratories, Department of Ecology and Evolutionary Biology, 165 Prospect St., Yale University, New Haven, CT 06520, USA
+^1^ Yale University, Department of Ecology and Evolutionary Biology, 165 Prospect St., New Haven, CT 06520, USA
 
@@
 We measured at least one specimen for 96 different species (Appendix 3, Fig.
-\@(figure3)).
+\@ref(figure3)).
 Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade.
@@
   Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig.
-@\ref(figure5), right).
+\@ref(figure5), right).
 Shifts toward ostracod presence in diet correlated with reductions in pedicle width and total haploneme volume.
@@
 ## Discussion {-}
-  This core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type.
+  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type.
 We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles.

### 2019-05-28 Scrap/BAMM/BAMMplots.R

@@ -1,0 +1,37 @@
+# load libraries
+library(BAMMtools)
+library(geiger)
+library(coda)
+setwd("~/tentilla_morph/BAMM")
+# load tree
+tree <- read.tree("desmoneme_elongation_tree.tre")
+
+# ESS after 20% burnin
+mcmcout <- read.csv("mcmc_out.txt")
+burnstart <- floor(0.2*nrow(mcmcout))
+postburn <- mcmcout[burnstart:nrow(mcmcout), ]
+effectiveSize(postburn$N_shifts)
+effectiveSize(postburn$logLik)
+
+# load BAMM main output
+edata <- getEventData(tree, eventdata = "event_data.txt", burnin=0.2, type="trait")
+summary(edata)
+
+# the 6 most likely scenario's within the 95% credible scenarios
+# F value is the relative probability, F values from all scenarios add up to F=1
+pdf("BAMM_desmoneme_elongation_css.pdf", width=7, height=10)
+css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
+BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T, use.plot.bammdata = T)
+dev.off()
+
+# net diversification graph
+pdf("BAMM_desmoneme_elongation_netdiv.pdf", width=7, height=5)
+starttime <- max(branching.times(tree))
+plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
+dev.off()
+
+pdf("desmoneme_elongation_ratesplot.pdf",width=16,height=16)
+plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
+dev.off()
+
+#q()

### 2019-05-28 Scrap/BAMM/BAMMsetpriors.R

@@ -1,0 +1,15 @@
+library(BAMMtools)
+library(stringr)
+library(readr)
+setwd("~/tentilla_morph/BAMM")
+tree <- read.tree("desmoneme_elongation_tree.tre")
+traits <- read.csv("desmoneme_elongation.txt", sep="\t", header = F)
+rownames(traits) = traits[,1]
+traits <- traits[tree$tip.label,]
+write_tsv(traits, "desmoneme_elongation.txt", col_names = FALSE)
+is.ultrametric(tree) # check for ultrametric
+is.binary.tree(tree) # check if there are no polytomies
+min(tree$edge.length) # check all branch lengths are > 0
+setBAMMpriors(phy = tree, traits = "desmoneme_elongation.txt")
+setwd("~/tentilla_morph/")
+#q()

### 2019-05-28 Scrap/Code_for_Analyses_and_Figures.R

@@ -1,0 +1,1083 @@
+
+## LOAD PACKAGES ##
+#General
+library(tidyverse)
+library(stringr)
+library(readr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(adegenet)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(colorRamps)
+
+# Set paths to input data
+setwd("~/tentilla_morph")
+
+#Load raw data
+read.csv("byslide.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("Homolog_Categorical.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)
+
+#Define functions to deal with NAs and decimals
[…]

### 2019-05-28 Scrap/Phylogeny_inference/Final_analyses/slurm_Timetree_ct_rb.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH --job-name=rb_time_with_constrain
+
+#SBATCH --partition=general
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=1
+
+#SBATCH --mem-per-cpu=1G
+#SBATCH --time=3-23:00:00
+
+./revbayes/projects/cmake/rb timetree_rev/mcmc_TimeTree_siphs_ct.Rev

### 2019-05-28 Scrap/Phylogeny_inference/Final_analyses/slurm_Timetree_rb.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH --job-name=rbmpi_with_constrain
+
+#SBATCH --partition=general
+#SBATCH --ntasks=1
+#SBATCH --cpus-per-task=1
+
+#SBATCH --mem-per-cpu=1G
+#SBATCH --time=3-23:00:00
+
+./revbayes/projects/cmake/rb timetree_rev/mcmc_TimeTree_siphs.Rev

### 2019-05-28 Scrap/Phylogeny_inference/Final_analyses/slurm_multitask.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+#SBATCH --job-name=revbayes_multitask
+#SBATCH --time=120:00:00
+#SBATCH --mem=48G
+#SBATCH --output=rb_out-%j_.out
+#SBATCH --error=rb_out-%j_error.out
+#SBATCH --array=1-3
+#SBATCH --ntasks-per-node=1
+sleep $((SLURM_ARRAY_TASK_ID*60))
+
+filenames = (
+	revbayes.rev
+	revbayes_ct.rev
+	)
+
+file = ${filenames[$SLURM_ARRAY_TASK_ID-1]}
+echo $file
+
+./rb $file

### 2019-05-28 Scrap/Phylogeny_inference/Final_analyses/slurm_srun_constrain_rb.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH --job-name=rbmpi_with_constrain
+
+#SBATCH --partition=scavenge
+#SBATCH --ntasks=64
+#SBATCH --cpus-per-task=1
+
+#SBATCH --mem-per-cpu=1G
+#SBATCH --time=3-00:00:00
+
+srun ./revbayes/projects/cmake/rb-mpi revbayes_ct.rev

### 2019-05-28 Scrap/Phylogeny_inference/Final_analyses/slurm_srun_rb.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+#SBATCH --job-name=rbmpi_no_constrain
+
+#SBATCH --partition=scavenge
+#SBATCH --ntasks=64
+#SBATCH --cpus-per-task=1
+
+#SBATCH --mem-per-cpu=1G
+#SBATCH --time=3-00:00:00
+
+srun ./revbayes/projects/cmake/rb-mpi revbayes.rev

### 2019-05-28 Scrap/Phylogeny_inference/consensus_transcriptome/constraintree.R

@@ -1,0 +1,30 @@
+library(tidyverse)
+library(ape)
+library(phytools)
+library(seqinr)
+
+setwd("~/Dropbox/tentilla_phylogeny2019/consensus_transcriptome")
+
+rrna <- seqinr::read.fasta("../all18S_curated_sublist.fasta")
+rrna_names <- names(rrna)
+
+treelist = list()
+for(tr in 1:length(list.files("trees"))){
+  treelist[[tr]] = ape::read.tree(paste("./trees/", list.files("trees")[tr], sep=""))
+}
+root(treelist[[1]],25) -> treelist[[1]]
+root(treelist[[2]],25) -> treelist[[2]]
+root(treelist[[3]],25) -> treelist[[3]]
+root(treelist[[4]],17) -> treelist[[4]]
+root(treelist[[5]],17) -> treelist[[5]]
+root(treelist[[6]],17) -> treelist[[6]]
+str_consensus <- ape::consensus(treelist)
+str_consensus$tip.label[which(str_consensus$tip.label == "Prayidae_D27D2")] <- "Craseoa_lathetica"
+str_consensus$tip.label[which(str_consensus$tip.label == "Prayidae_D27SS7")] <- "Desmophyes_haematogaster"
+str_consensus$tip.label[which(str_consensus$tip.label == "Physonect_sp_")] <- "Physonect_sp"
+consensus_tl <- str_consensus$tip.label
+
+missingtaxa <- rrna_names[which(!(rrna_names %in% consensus_tl))]
+extrataxa <- consensus_tl[which(!(consensus_tl %in% rrna_names))]
+pending_transcriptome_taxa[]
+

### 2019-05-28 Scrap/Phylogeny_inference/seqwrangling.R

@@ -1,0 +1,110 @@
+library(tidyverse)
+library(seqinr)
+library(msa)
+library(ape)
+setwd("~/Dropbox/tentilla_phylogeny2019")
+
+#Load FASTA files
+LIST_16S = list()
+for(f in 1:length(list.files("sequences16S"))){
+  LIST_16S[[f]] = seqinr::read.fasta(paste("./sequences16S/", list.files("sequences16S")[f], sep=""))
+}
+LIST_18S = list()
+for(f in 1:length(list.files("sequences18S"))){
+  LIST_18S[[f]] = seqinr::read.fasta(paste("./sequences18S/", list.files("sequences18S")[f], sep=""))
+}
+
+#Transform list of FASTAs into dataframes
+sequences16S = lapply(LIST_16S, getSequence) %>% lapply(function(x){lapply(x,function(y){paste(unlist(y), sep="", collapse="")})}) %>% unlist()
+names16S = lapply(LIST_16S, names) %>% unlist()
+annots16S = lapply(LIST_16S, getAnnot) %>% unlist()
+ALL16S = data.frame(names16S,annots16S, rep("16S", length(names16S)), sequences16S)
+names(ALL16S) = c("Taxon","Annotation","Gene","Sequence")
+
+sequences18S = lapply(LIST_18S, getSequence) %>% lapply(function(x){lapply(x,function(y){paste(unlist(y), sep="", collapse="")})}) %>% unlist()
+sequences18S = str_replace_all(sequences18S,"[^atgc]","")
+names18S = lapply(LIST_18S, names) %>% unlist()
+annots18S = lapply(LIST_18S, getAnnot) %>% unlist()
+ALL18S = data.frame(names18S,annots18S,rep("18S", length(names18S)),sequences18S)
+names(ALL18S) = c("Taxon","Annotation","Gene","Sequence")
+ALL16S = ALL16S[order(ALL16S$Taxon),]
+ALL18S = ALL18S[order(ALL18S$Taxon),]
+write.fasta(as.list(ALL16S$Sequence), names=paste(ALL16S$Annotation, 1:nrow(ALL16S))  , file.out = "all16S.fasta")
+write.fasta(as.list(ALL18S$Sequence), names=paste(ALL18S$Annotation, 1:nrow(ALL18S))  , file.out = "all18S.fasta")
+
+#Align by gene
+ALL16S_aligned = ALL16S
+ALL18S_aligned = ALL18S
[…]

### 2019-06-05 manuscript_clean.Rmd
DPAC and GLM redo

@@
 
-^3^ Scripps Institution of Oceanography, 9500 Gilman Dr., La Jolla, CA 92093, USA
+^3^ Scripps Institution of Oceanography, University of California San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA
 
@@
 To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) characterized the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
-Our results show that siphonophore tentilla structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey type specializations are linked to shifts in tentillum and nematocyst size and shape.
+Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
 In addition, we found that these morphological characters are useful for predicting siphonophore diets.
 Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This study contributes to understanding how morphological evolution has shaped the structure of present-day oceanic food-webs.
+This study contributes to understanding how morphological evolution has shaped present-day oceanic food-webs.
 
@@
   Most animal predators have characteristic biological tools that they use to capture and subdue prey.
-Raptor birds have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
+Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
 The functional morphology of these structures tend to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
-Long-term adaptive evolution in response to the defense mechanisms (e.g.
-avoidance, escape, protective barriers) of the prey leads to modifications that can tackle those defenses.
-The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
+Long-term adaptive evolution in response to the defense mechanisms of the prey (e.g.
+avoidance, escape, protective barriers) leads to modifications that can counter those defenses The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
 Understanding the relationships between predatory specializations and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
 
-  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture and present a significant morphological variation across species, which makes it ideal to study the relationships between functional traits and prey specialization.
+  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
+\@(figure1)).
+These present a significant morphological variation across species [@mapstone2014global] (Fig.
+\@ref(figure2)), which makes it ideal to study the relationships between functional traits and prey specialization.
 A siphonophore is a colony bearing many feeding polyps (Fig.
-\@ref(figure1)), each with a single tentacle, which branches into several tentilla bearing the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
-Tentilla function exclusively for prey capture and present a broad diversity of morphologies and sizes [@mapstone2014global].
+\@(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
 Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation], built into their tentilla.
-While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism upon encounter with prey.
+While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
 When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy].
-In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent].
+In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
 
   Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
-This habitat has fairly homogeneous abiotic conditions and stable temporal patterns in the abundance of zooplanktonic animals [@robison2004deep].
-With a somewhat predictable prey availability, ecological theory would expect evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
+This habitat has fairly homogeneous physical conditions and stable abundances of zooplanktonic animals [@robison2004deep].
+With a somewhat predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
 If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
 
-  Coexisting siphonophores feeding on the same planktonic community are potential competitors.
+  Coexisting siphonophores feeding on the same planktonic community may have substantial niche overlap and compete for prey resources.
 Traditional ecological coexistence theory [@simpson1944tempo] predicts that competition between species would select for increasing ecological specialization.
-Moreover, specialization is often thought to be an evolutionary ‘dead end,’ meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource in which they are specialized [@futuyma1988evolution].
+Moreover, specialization is often thought to be an evolutionary ‘dead end,’ meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
 However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition], and resource switching [@hoberg2008macroevolutionary].
@@
   The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
-Thus, the morphological diversity of tentilla has been only characterized for a few taxa, and their evolutionary history remains largely unexplored.
+Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
 Contemporary underwater sampling technology provides an unprecedented opportunity to explore the trophic ecology [@choy2017deep] and functional morphology [@costello2015multi] of siphonophores.
 In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved].
-These methodological advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.
+These advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.
 
@@
 [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
-These correlations, while found in a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
-We hypothesize that these relationships may reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
+These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
+We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
 Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate predictions about the diets of understudied siphonophore species.
 In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures.
-We aim to assess the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentilla morphologies on cnidoband discharge.
+We aim to assess the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
 
@@
 Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species.
-A - *Erenna laciniata*, slide E11, 10x.
-B - *Lychnagalma utricularia*, slide D7, 10x.
-C - *Agalma elegans*, slide J6, 10x.
-D - *Resomia ornicephala*, slide X11, 10x.
-E - *Frillagalma vityazi*, slide H1, 20x.
-F - *Bargmannia amoena*, slide L8, 10x.
-G - *Cordagalma* sp., reproduced from Carré 1968.
-H - *Lilyopsis fluoracantha*, slide J10, 20x.
-I - *Abylopsis tetragona*, slide U6, 20x.
-Slide metadata available in Dryad.](Figures_final/figure2.jpg)
+A - Erenna laciniata, 10x.
+B - Lychnagalma utricularia, 10x.
+C - Agalma elegans, 10x.
+D - Resomia ornicephala, 10x.
+E - Frillagalma vityazi, 20x.
+F - Bargmannia amoena, 10x.
+G - Cordagalma sp., reproduced from Carré 1968.
+H - Lilyopsis fluoracantha, 20x.
+I - Abylopsis tetragona, 20x.](Figures_final/figure2.jpg)
 
@@
 
-*Tentilla morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1).
-These specimens had been collected intact across many years of fieldwork expeditions, by the means of blue-water Diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
+*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1).
+These specimens were collected intact across many years of fieldwork expeditions, using of blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
 Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media.
-The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
+The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
 Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
-We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to capture meaningful measurements.
+We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to quantify.
 We measured at least one specimen for 96 different species (Appendix 3, Fig.
 \@ref(figure3)).
-Of these, we selected 38 focal siphonophore species based on specimen availability and phylogenetic representation from each clade.
+Of these, we selected 38 focal species across clades based on specimen availability and phylogenetic representation.
 Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
@@
 The gene sequences used in this study are available online (accession numbers in Appendix 5).
-Some of these sequences we used were accessioned in [@dunn2005molecular], others we extracted from the transcriptomes in [@munro2018improved].
+Some of these sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
 Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
@@
 ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred an Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (Appendix 7,Appendix 9), which was topologically congruent with the unconstrained ML tree.
+Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (Appendix 7 and 9), which was topologically congruent with the unconstrained ML tree.
 The *alpha* priors were selected to minimize prior load in site variation.
 
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6, Appendix 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) generating an ultrametric tree (Appendix 8).
- Scripts (Appendix 9) available in https://github.com/dunnlab/tentilla_morph/.
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6 and 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate an ultrametric tree (Appendix 8).
+Scripts are available in https://github.com/dunnlab/tentilla_morph/.
 
@@
 Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), the large crustacean specialist (feeding on large decapods, mysids, or krill), the fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), the gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and the generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
-We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa and for *Nanomia* sp.
-eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear if the medusae were attempting to prey upon the siphonophores.
+The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+These were selected to minimize the number of categories without merging the most different types of prey.
+We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
+eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh)  were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
@@
 We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous [@harmon2007geiger].
-The models compared were the white noise (WN) (non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
+The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
 We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
@@
 To identify evolutionary associations of diet with tentillum and nematocyst characters, we compared the performance of a neutral evolution model to that of a diet-driven directional selection model.
-First, we collapsed the diet data into five feeding guilds (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
+First, we collapsed the diet data into the five feeding guilds mentioned above (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
 We reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
 The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
-Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model.
+Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
 Finally, we compared their AICc support values to select the best fitting model (Appendix 14).
 
-To model the relationships between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (Appendix 17).
+To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (Appendix 17).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
@@
 Another approach was to transform the “NA” states to zeroes.
-The drawbacks of first approach is that useful data is lost, and observations are biased towards taxa with more complex tentacles.
-The drawbacks of the second approach is that small state values become aligned with absences.
+The drawbacks of first approach is that useful data are lost, and observations are biased towards taxa with more complex tentacles.
+The drawback of the second approach is that small state values become aligned with absences.
 The severity of these drawbacks depends on the specific aspect of diet being predicted, thus we chose our approach in a case-specific basis.
-For the specific prey types, we then generated and compared generalized linear models (GLMs) with multiple predictors.
+When the species with many inapplicable states are removed, we exclude a useful validation set of species (*Apolemia rubriversa*, *Rhizophysa eysenhardtii*, *Rhizophysa filiformis*, and *Physalia physalis*) for which the diet is known.
+We used the performance of the predictions on these taxa to select the approach used.
+For the specific prey type presence in the diet, we then generated and compared generalized linear models (GLMs) with multiple predictors.
 We chose predictors among the characters with significant loading contributions in each specific DAPC.
@@
 In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character data contains many gaps due to missing characters, we carried out these analyses on a the subset of species and characters that allowed the largest data volume.
+Since the character data contains many gaps due to missing characters, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
 In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
@@
 To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different nematocyst types, and identified the branches with the greatest shifts.
-In addition, we ran a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] on haploneme and heteroneme elongation to estimate the number and phylogenetic mapping of trait evolution rate regimes (Appendix 16).
+In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution  using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (Appendix 16).
 
@@
 
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores (raw data in Appendix 3).
+![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores clustered by similarity (raw data in Appendix 3).
 Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
@@
 
-  We define two new clades within Codonophora (Fig.
+  We retained the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], such as Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
+In addition, we define two new clades within Codonophora (Fig.
 \@ref(figure4)): Eucladophora as the clade containing *Agalma elegans* and all taxa that are more closely related to it than to *Apolemia lanosa*, and Tendiculophora as the clade containing *Agalma elegans* and all taxa more closely related to it than to *Bargmannia elongata*.
@@
 *Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism was not likely ancestral, and it appears to have evolved at least two times independently (Fig.
-\@ref(figure5)).
+\@(figure5)).
+Generalism evolves twice independently from large crustacean specialist lineages, supporting hypothesis 3.
+Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2.
 Individual prey type presence reconstructions show that copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
@@
   When some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] were tested for correlated evolution (Table 1), we found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
-The latter is likely a product of the larger species richness of crustacean eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.
+The latter is likely a product of the larger species richness of crustacean-eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.
 
-![\label{table1} Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.](Final_tables/table1.png)
+Table 1. Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.
 
-*Tentilla morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Total haploneme volume, total nematocyst volume, cnidoband length, heteroneme volume, involucrum length, pedicle width, and tentacle width.
+```{r tab1, echo=FALSE, out.width='100%'}
+knitr::include_graphics('Final_tables/table1.png')
+```
+
+*Tentillum morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Total haploneme volume, total nematocyst volume, cnidoband length, heteroneme volume, involucrum length, pedicle width, and tentacle width.
 The only groups confounded were generalists and large crustacean specialists.
@@
 Absent characters (such as tentilla, or particular nematocyst types) are likely to be very biologically relevant to prey capture, so we believe they should be accounted for.
-When the absent character data is simply removed, similar discrimination is achieved, with the same large crustacean and generalist ambiguity (Appendix 15).
-However, the predictions from this DAPC for the species with missing characters is largely inaccurate (*e.g.* *Rhizophysa eysenhardti*, a specialized fish eater, is predicted as a small crustacean specialist).
-When missing values are substituted by zeroes, the prediction accuracies improve greatly.
+When the absent character data was simply removed, similar discrimination is achieved, with the same large crustacean and generalist ambiguity (Appendix 15).
+However, the predictions from this DAPC for the validation species are largely inaccurate (*e.g.* *Rhizophysa eysenhardtii*, a specialized fish eater, is predicted as a small crustacean specialist).
 
-![\label{figure6} DAPC predicted feeding guilds for siphonophore species with measured tentilla morphology data but without any preliminary dietary data.
+![\label{figure6} DAPC predicted feeding guilds for siphonophore species with measured tentillum morphology data but without any preliminary dietary data.
 Cell darkness indicates posterior probability of belonging to each guild.
@@
 The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width.
-Discriminant analyses and GLM were also applied to specific prey type presence and selectivity (Table \@ref(table2), highlighting the most relevant characters and their predictive power.
+Discriminant analyses and GLM were also applied to specific prey type presence and selectivity (Table 2), highlighting the most relevant characters and their predictive power.
 These analyses were carried out in a subset of characters and species that minimized taxa and characters with inapplicable states (except for fish presence, which produced much better results upon transforming inapplicable states to zeroes).
-The non-piscivorous (fish excluding diet) tentacle morphospace is a subset of the piscivorous (fish inclusive diet) tentacle morphospace (Appendix 15).
-However, fish specialists occupy a very distinct region of the morphospace (Fig.
-@\ref(figure6)).
+The non-piscivorous (fish-excluding diet) tentacle morphospace is a subset of the piscivorous (fish-inclusive diet) tentacle morphospace (Appendix 15).
+However, fish specialists (primarily fish diet) can be unambiguously diagnosed in the feeding guild DAPC (Fig.
+\@ref(figure6)).
 
-![\label{table2} Discriminant analysis of principal components for specific prey types using the morphological data.
+Table 2.
+Discriminant analysis of principal components for specific prey types using the morphological data.
 Loadings are ordered from highest to lowest significance.
@@
 Only the best GLM is reported.
-Pseudo-R2 approximate the variance explained by the model.
-Fish model built with NAs converted to zeroes.](Final_tables/table2.png)
+Pseudo-R^2^ approximates the variance explained by the model.
+Fish model built with NAs converted to zeroes.
+
+```{r tab2, echo=FALSE, out.width='100%'}
+knitr::include_graphics('Final_tables/table2.png')
+```
 
@@
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
-74% of  characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme to cnidoband length ratio had a phylogenetic signal  K > 1.
+74% of characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal  K > 1.
 67% of characters support BM models, indicating a history of neutral constant divergence.
@@
 ![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
-Some branch lengths were modified from the bayesian chronogram to improve readability.
+Some branch lengths were modified from the Bayesian chronogram to improve readability.
 The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
@@
 \@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore type ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bear no other nematocyst type.
+\@ref(figure7)), which bear no other nematocyst type (Fig.
+\@ref(figure1)).
 These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
-The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband.
+The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig.
+\@ref(figure2)).
 This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
-Calycophorans evolved unique novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore type heteronemes.
+Calycophorans evolved unique novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
+While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
+Nonetheless, they have spreaded over a broad span of variation in nematocyst and cnidoband sizes.
 
@@
 
-*Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are very correlated to each other.
+*Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
 The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement is independent of it.
 Of the phylogenetic correlations (Fig.
-8a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
+\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
 \@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
@@
 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
-Just 4% have negative phylogenetic and positive ordinary correlations, and vice versa for 9.9% of character pairs.
+Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or  haploneme elongation ~ heteroneme number), and vice versa for 9.9% of character pairs (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
 These disparities can be caused by Simpson’s paradox [@blyth1972simpson], the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
-However, no character pair had correlation coefficient differences larger than 0.74 between ordinary and phylogenetic correlations.
+However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54).
+Rhopaloneme shape shows the most incongruences between phylogenetic and ordinary correlations with other characters.
 
@@
 
-  In the raw (non-morphometric) PCA morphospace (Fig.
-\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explains 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
+  In the non-phylogenetic PCA morphospace using only simple characters (Fig.
+\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
 In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
@@
 Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
-Apolemids have no tentacle haplonemes and are project onto the heteroneme axis.
+Apolemids have no tentacle haplonemes and are projected onto the heteroneme axis.
 Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)
 
-  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of variance in their shifts alongs the branches of the phylogeny.
-However, much of this correlation is due to the contrast between pyrostephids and its sister group.
+  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of variance in their shifts along the branches of the phylogeny.
+However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig.
+\@ref(figure4)).
 BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia*.
 For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
-\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (most have rod-shaped anisorhizas, but *Erenna* has oval ones).
+\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects.
+Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
+Most of these taxa have rod-shaped anisorhizas, but *Erenna* has oval ones).
 No clear patterns were identified in the evolution of desmoneme and rhopaloneme shape.
 
-*Functional morphology of tentillum and nematocyst discharge* – While the sample sizes of high speed measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
+*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in Appendix 4.
+While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
 For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively.
-T-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
+This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
 
@@
 ## Discussion {-}
-  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niche, and identify the morphological characters that evolve with changes in prey type.
-We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory, and whether the diets of siphonophores can be discriminated by observing their tentacles.
-In addition, we produced novel findings on tentilla morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
+  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niches, and identify the morphological characters that evolve with changes in prey type.
+We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be discriminated by observing their tentacles.
+In addition, we produced novel findings on tentillum morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
 
-*Evolution of tentilla morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
+*Evolution of tentillum morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
 While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as trophic intermediaries between smaller zooplankton and higher trophic level predators.
 Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
-With a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
-Predators that use similar tools for prey capture tend to capture similar prey, so their abundance and coexisting species diversity trade-off through competition [@schluter2000ecological].
+Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
+Predators that use similar tools for prey capture tend to capture similar prey, so their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
 However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
-We hypothesize that siphonophores have escaped this trade-off though specialization on different prey resources.
+We hypothesize that siphonophores have escaped this by specializing on different prey resources.
 
-The evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
-Several studies  (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by their phenotypic specialization.
+According to our reconstructions, the evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
+Several studies  (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by phenotypic specialization.
 Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
-Among the evolutionary hypotheses considered, we find support for both hypotheses (2) and (3), but no support for hypothesis (1).
-The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution.
-This strategy is particularly important in open ocean ecosystems, a homogeneous abiotic environment where the only niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
+Among the evolutionary hypotheses considered, we find support for both hypotheses 2 (specialist resource switching) and 3 (specialist to generalist), but no support for hypothesis 1 (generalist to specialist).
+The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
+This strategy is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
 
-  An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification to unfold.
-
-  Throughout this study, we assess whether our results are congruent with adaptation.
-However, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
-
-  One of the most common prey items found in siphonophore diets are copepods (Fig.
+  One of the most common prey items found in siphonophore diets is copepods (Fig.
 \@ref(figure5)).
@@
 [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
+The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and Rhodaliids) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
 Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review], a common feature of piscivorous cnidarians like cystonects or cubozoans.
+*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (pers.
+obs.), a common feature of piscivorous cnidarians like cystonects or cubozoans.
 
@@
 Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
-In fish-eating cystonects and erennids, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
+In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
 The accelerated rate of heteroneme shape evolution in the clade containing *Agalma* and *Nanomia* may indicate a rapid dietary differentiation.
-However, our limited ecological data does not show any significant dietary differentiation in this group.
+However, our limited ecological data do not show any significant dietary differentiation in this group.
 
-When the diet-morphology correlation hypotheses supported in the literature were tested from a macroevolutionary perspective, we found that most of them were consistent with correlated evolution (Table 2).
-The ecomorphological association between rhopalonemes, desmonemes and crustacean eaters was not congruent with a scenario of correlated evolution.
-This could be due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes that effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
+When we tested the diet-morphology correlation hypotheses supported in the literature from a macroevolutionary perspective, we found that most of them were consistent with correlated evolution (Table 2).
+The ecomorphological association between rhopalonemes, desmonemes, and crustacean eaters was not congruent with a scenario of correlated evolution.
+This could be due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes but which effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
 
-While our results unambiguously show that tentilla morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available.
-In addition, diet is a product of environmental prey availability and predator selectivity.
+While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available.
+Moreover, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
+When interpreting these results, it is important to remember that diet is a product of environmental prey availability and predator selectivity.
 Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for this study.
-For example, tentacle deploying behavior, positioning in the water column, or behavioral decisions on whether or not to discharge on or ingest an encountered animal.
+For example, tentacle-deploying behavior, positioning in the water column, or thresholds for  discharging on or ingesting an encountered animal.
 Further observations on these behaviors in the field are necessary to assess their relative importance in determining dietary composition.
@@
 Part of the success in siphonophore prey capture is likely determined by the effectivity of the toxins delivered by the nematocysts on different taxa.
-Comparative toxin assays, and venom protein evolution studies could shed light on this question.
+Comparative toxin assays and venom protein evolution studies could shed light on this question.
 Moreover, siphonophore trophic specialization may have brought changes in the digestive biochemistry of gastrozooids and palpons.
@@
 *Predicting siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can better predict the diets of siphonophores based on morphological characteristics.
-Our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
+Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
 The models produced by these analyses generated untested predictions about the diets of many species for which we only have morphological data of their tentacles.
+While the limited dataset used here is informative for generating tentative hypotheses, the empirical data are still scarce and insufficient to cast robust predictions.
+This reveals the need to extensively characterize siphonophore diets and feeding habits.
 In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
 Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
-Interactions among the oceanic zooplankton have been treated as a black box in ecological models [@mitra2009closure].
+Interactions among the oceanic zooplankton have been treated as a black box in many ecological models [@mitra2009closure].
 The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient flow models from plankton trawl data.
@@
 These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid).
-Once the cnidocytes have assembled the nematocyst, they migrate up the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
-Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentilla morphologies.
+Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
+Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies.
 Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters is maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
 
-*Evolutionary history of tentilla morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+*Evolutionary history of tentillum morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
 This revealed for the first time that *Erenna* is the sister to *Stephanomia amphytridis*.
 *Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
+Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review].
+Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
+The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey classes.
 
@@
 One hypothesis would suggest that these characters are not under selection, and therefore diverging neutrally [@lande1976natural].
-The second hypothesis suggests that they are under selection, however, the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns on the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet (feeding guild) driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
+The second hypothesis suggests that they are under selection, but the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns across the phylogeny.
+Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet- driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
 
@@
 
+  The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
+An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
+The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification to unfold.
+
 Our work identifies an interesting example of convergent evolution.
 The calycophoran tentillum morphospace (Fig.
-\@ref(figure9)) was independently occupied by *Frillagalma vityazi*.
+\@ref(figure9)) was independently occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
 Unlike calycophorans, they lack paired elongate microbasic mastigophores.
-Instead, they bear 3 elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
+Instead, they bear three elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
 Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
@@
 This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
-One of such characters is the shape of haploneme nematocysts.
+One such character is the shape of haploneme nematocysts.
 A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
@@
 Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
-Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects are retaining this ancestral state.
+Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
 Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, associated with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
@@
 In addition, the clade defined by the most recent common ancestor of *Agalma* and *Nanomia* shows an increased rate of divergence for heteroneme shape, spanning extremes (from oval *Nanomia* stenoteles to the elongate *Agalma okenii* stenoteles) in relatively short evolutionary time.
-While cystonects don't bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids, hypothetically used for defense rather than for prey capture.
+While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids, hypothetically used for defense rather than for prey capture.
 These stenotele heteronemes are rounded like those found in pyrostephids and apolemiids, which is consistent with the story of a single transition leading to the elongated heteronemes in the stem of Tendiculophora.
@@
 We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Tendiculophora is the most abundant, speciose and diverse (ecologically and morphologically) clade of siphonophores, containing Euphysonectae and Calycophorae.
+Tendiculophora is the most abundant, speciose, and diverse (ecologically and morphologically) clade of siphonophores, containing Euphysonectae and Calycophorae.
 We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade.
@@
 For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].
-Nonetheless, siphonophores have evolved unique nematocyst types, not present in any other cnidarian.
-For example, rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
+Nonetheless, siphonophores have evolved unique nematocyst types, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
 Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not been yet found in any other tissue of any other organism.
@@
 *Diversity of discharge dynamics* – A fundamental corollary in functional morphology is that structural morphology determines functional performance [@wainwright1994ecological].
-We expected the discharge dynamics exhibited by of siphonophore tentilla should vary accordingly with their morphological diversity.
-Our results are consistent with this expectation, where we observe, for example, that cnidoband size largely correlates with cnidoband discharge speed.
+We expected the discharge dynamics exhibited by siphonophore tentilla should vary with their morphological diversity.
+Our results are consistent with this expectation, and we observe, for example, that cnidoband size largely correlates with cnidoband discharge speed.
 This suggests that prey escape response speed may determine the minimum cnidoband length for successful capture.
 
-*Insights from tentilla morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts pervades across clades, from the overall shape and size, to the dimensions of the nematocysts.
+*Insights from tentillum morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts spans clades, from the overall shape and size, to the dimensions of the nematocysts.
 Siphonophores bear the largest nematocysts among Hydrozoans, and present a wide variety of nematocyst sizes within the clade.
@@
   In addition to the insights produced in this study, the newly collected morphological data provide a unique resource for future studies, and a reference dataset for siphonophore identification.
-Many conspicuous categorical characters in siphonophore tentilla are very diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the red lures of *Erenna sirena*, the unique cnidoband shapes in different *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
+Many conspicuous categorical characters in siphonophore tentilla are very diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the bioluminescent lures of *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the buoyant medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
 \@ref(figure7)).
-Some categorical characters are synapomorphic diagnostic characters for large clades, such as the proximal tentillum heteronemes of Eucladophora, the elastic strand, rhopalonemes, and desmonemes of Tendiculophora, the larval tentilla of Euphysonectae, the 2-sized isorhizas of Cystonectae, the saccus canal of Pyrostephidae, or the 7 rows of anisorhizas in Calycophorae.
+Some categorical characters are synapomorphic diagnostic characters for large clades, such as the proximal tentillum heteronemes of Eucladophora, the elastic strand, rhopalonemes, and desmonemes of Tendiculophora, the larval tentilla of Euphysonectae, the two-sized isorhizas of Cystonectae, the saccus canal of Pyrostephidae, or the seven rows of anisorhizas in Calycophorae.
 These characters should be used together with the classical nectophore and bract characters to identify species or at least impute phylogenetic affiliation from incomplete material.
@@
   Siphonophores have diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
-With the evolution of diversified prey type specializations, comes the evolution of morphologies adapted to the challenges posed by different prey.
+With the evolution of diversified prey type specializations comes the evolution of morphologies adapted to the challenges posed by different prey.
 The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.
@@
 
-  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and Anela Choy).
+  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.A.C.).
 A.D.S.
@@
 
-We wish to thank the crew and scientists onboard the R/V Western Flyer, who participated in the collection of many of the specimens used in this study.
+We wish to thank the crew and scientists of the R/V Western Flyer, who participated in the collection of many of the specimens used in this study.
 We also want to thank Lynne Christianson and Shannon Johnson from the Monterey Bay Aquarium Research Institute for their assistance in the field as well as for sequencing some of the species included in this phylogeny.
@@
 We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript.
-Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us invaluable knowledge about siphonophores.
+Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us valuable knowledge about siphonophores.
 
@@
   Casey W.
-Dunn (Yale University) contributed by collecting specimens, providing me with invaluable insights and mentoring, and by reviewing the manuscript.
+Dunn (Yale University) contributed by collecting specimens, providing invaluable insights and mentoring, and by reviewing the manuscript.
 In addition, his graduate dissertation work produced many of the sequences used for our phylogenetic analysis.

### 2019-06-05 Supplementary_materials/Dryad/BAMMplots.R

@@ -1,0 +1,38 @@
+# load libraries
+library(BAMMtools)
+library(geiger)
+library(coda)
+#setwd("~/tentilla_morph/Supplementary_Materials/Dryad/BAMM")
+# load specific character subtree made in the R_Code ## BAMM ## block
+
+tree <- read.tree("haploneme_elongation_tree.tre")
+
+# ESS after 20% burnin
+mcmcout <- read.csv("mcmc_out.txt")
+burnstart <- floor(0.2*nrow(mcmcout))
+postburn <- mcmcout[burnstart:nrow(mcmcout), ]
+effectiveSize(postburn$N_shifts)
+effectiveSize(postburn$logLik)
+
+# load BAMM main output
+edata <- getEventData(tree, eventdata = "event_data.txt", burnin=0.2, type="trait")
+summary(edata)
+
+# the 6 most likely scenario's within the 95% credible scenarios
+# F value is the relative probability, F values from all scenarios add up to F=1
+pdf("BAMM_haploneme_elongation_css.pdf", width=7, height=10)
+css <- credibleShiftSet(edata, expectedNumberOfShifts = 1, threshold=5, set.limit=0.95)
+BAMMtools:::plot.credibleshiftset(css, plotmax = 6, pal = "temperature", legend=T, use.plot.bammdata = T)
+dev.off()
+
+# net diversification graph
+pdf("BAMM_haploneme_elongation_netdiv.pdf", width=7, height=5)
+starttime <- max(branching.times(tree))
+plotRateThroughTime(edata, intervalCol="darkgreen", avgCol="darkgreen", start.time=starttime, ylim=c(0,25))
+dev.off()
+
+pdf("haplooneme_elongation_ratesplot.pdf",width=16,height=16)
+plot.bammdata(edata,lwd=2,legend=T,labels=T,cex=0.9,logcolor=T,breaksmethod="jenks",pal=c("#0D0887", "#CC4678", "#F0F921"))
+dev.off()
+
+#q()

### 2019-06-05 Supplementary_materials/Dryad/BAMMsetpriors.R

@@ -1,0 +1,14 @@
+library(BAMMtools)
+library(stringr)
+library(readr)
+#setwd("~/tentilla_morph/Supplementary_Materials/Dryad")
+tree <- read.tree("haploneme_elongation_tree.tre")
+traits <- read.csv("haploneme_elongation.txt", sep="\t", header = F)
+rownames(traits) = traits[,1]
+traits <- traits[tree$tip.label,]
+write_tsv(traits, "haploneme_elongation.txt", col_names = FALSE)
+is.ultrametric(tree) # check for ultrametric
+is.binary.tree(tree) # check if there are no polytomies
+min(tree$edge.length) # check all branch lengths are > 0
+setBAMMpriors(phy = tree, traits = "haploneme_elongation.txt")
+#q()

### 2019-06-05 Supplementary_materials/Dryad/R_Code.R

@@ -28,9 +28,10 @@ library(corrplot)
 library(BAMMtools)
 library(gridExtra)
 library(colorRamps)
+library(PerformanceAnalytics)
 
 # Set paths to input data
-#setwd("~/tentilla_morph")
+#setwd("~/tentilla_morph/Supplementary_Materials/Dryad/")
 
 #Load raw data
 read.csv("raw_morphology_data.csv") -> numbers
@@ -96,7 +97,7 @@ volume_ellipsoid <- function(L, W){
 SAV_haploneme = surface_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)/volume_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)
 names(SAV_haploneme) = castnumbers$Species
 SAV_heteroneme = surface_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)/volume_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)
-names(SAV_heteroneme) = sharedmeans$Species
+names(SAV_heteroneme) = castnumbers$Species
 
 #Combine all morphometric variables
 morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index, SAV_haploneme)
@@ -466,17 +467,32 @@ combicorr = phy_corr
 combicorr[upper.tri(combicorr)] = intra_corr[upper.tri(intra_corr)]
 rownames(combicorr) = colnames(C)
 colnames(combicorr) = colnames(C)
-corrplot(combicorr, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs intraspecific correlations
+phylointramatrix <-corrplot(combicorr, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs intraspecific correlations
 PICOLS = combicorr
 PICOLS[upper.tri(PICOLS)]=cor(C)[upper.tri(cor(C))]
[…]

### 2019-06-12 manuscript_clean.Rmd
Final versions for BioRxiv submission

@@
 indent: TRUE
+header-includes:
+  - \usepackage[left]{lineno}
+  - \linenumbers
 ---
@@
 
-Alejandro Damian-Serrano^1^^,‡^, Steven H.D. Haddock^2^, Elizabeth D. Hetherington^3^, C. Anela Choy^3^, Casey W. Dunn^1^
+Alejandro Damian-Serrano^1^^,‡^, Steven H.D. Haddock^2^, Casey W. Dunn^1^
 
@@
 ^2^ Monterey Bay Aquarium Research Institute, 7700 Sandholdt Rd., Moss Landing, CA 95039, USA
-
-^3^ Scripps Institution of Oceanography, University of California San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA
 
@@
 Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
-In addition, we found that these morphological characters are useful for predicting siphonophore diets.
+In addition, we generated hypotheses about the diets of understudied siphonophore species based on these characters.
 Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
@@
 The functional morphology of these structures tend to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
-Long-term adaptive evolution in response to the defense mechanisms of the prey (e.g.
-avoidance, escape, protective barriers) leads to modifications that can counter those defenses The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
+Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.* avoidance, escape, protective barriers) leads to modifications that can counter those defenses The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
 Understanding the relationships between predatory specializations and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
@@
   Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
-\@(figure1)).
+\@ref(figure1)).
 These present a significant morphological variation across species [@mapstone2014global] (Fig.
@@
 A siphonophore is a colony bearing many feeding polyps (Fig.
-\@(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
+\@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
 Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation], built into their tentilla.
@@
 This habitat has fairly homogeneous physical conditions and stable abundances of zooplanktonic animals [@robison2004deep].
-With a somewhat predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
+With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
 If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
@@
 Traditional ecological coexistence theory [@simpson1944tempo] predicts that competition between species would select for increasing ecological specialization.
-Moreover, specialization is often thought to be an evolutionary ‘dead end,’ meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
-However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition], and resource switching [@hoberg2008macroevolutionary].
-Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from different ancestral predatory specialists, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+This specialization is often thought to be an evolutionary ‘dead end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
+However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition] and resource switching [@hoberg2008macroevolutionary].
+Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predatory specialists which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
 
@@
 We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
-Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate predictions about the diets of understudied siphonophore species.
+Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
 In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures.
-We aim to assess the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
+In particular, we aim to address the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
 
@@
 ![\label{figure1} Siphonophore anatomy.
-A - Nanomia sp.
+A - *Nanomia* sp.
 siphonophore colony (photo by Catriona Munro).
-B,C - Illustration of a Nanomia colony, gastrozooid, and tentacle (by Freya Goetz).
+B,C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
 D - *Nanomia* sp.
@@
 Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species.
-A - Erenna laciniata, 10x.
-B - Lychnagalma utricularia, 10x.
-C - Agalma elegans, 10x.
-D - Resomia ornicephala, 10x.
-E - Frillagalma vityazi, 20x.
-F - Bargmannia amoena, 10x.
-G - Cordagalma sp., reproduced from Carré 1968.
-H - Lilyopsis fluoracantha, 20x.
-I - Abylopsis tetragona, 20x.](Figures_final/figure2.jpg)
+A - *Erenna laciniata*, 10x.
+B - *Lychnagalma utricularia*, 10x.
+C - *Agalma elegans*, 10x.
+D - *Resomia ornicephala*, 10x.
+E - *Frillagalma vityazi*, 20x.
+F - *Bargmannia amoena*, 10x.
+G - *Cordagalma* sp., reproduced from Carré 1968.
+H - *Lilyopsis fluoracantha*, 20x.
+I - *Abylopsis tetragona*, 20x.](Figures_final/figure2.jpg)
 
@@
 
-*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (catalog numbers in Appendix 1).
+*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Appendix 1).
 These specimens were collected intact across many years of fieldwork expeditions, using of blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
@@
 We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (microns), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (Appendix 4).
+For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (µm), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data in Appendix 4).
 
 *Siphonophore phylogeny* – The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
-The gene sequences used in this study are available online (accession numbers in Appendix 5).
-Some of these sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
+The gene sequences we used in this study are available online (accession numbers in Appendix 5).
+Some of the sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
 Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
@@
 
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced congruent results (Appendix 6 and 7)) fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This tree was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate an ultrametric tree (Appendix 8).
-Scripts are available in https://github.com/dunnlab/tentilla_morph/.
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced fully congruent topologies (Appendix 6 and 7)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (Appendix 8).
+Scripts available in Appendix 9.
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] (Appendix 10).
-Since the sampling biases of ROV and gut content based methods are very different, the data were merged to the level of feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
-These were selected to minimize the number of categories without merging the most different types of prey.
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and Anela Choy (Appendix 10).
 We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
@@
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
+In order to detect coarse-level patterns in the feeding habits, the data were merged into feeding guilds.
+The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+These were selected to minimize the number of categories while keeping the most different types of prey separate.
 We extracted copepod prey length data from [@purcell1984functions].
@@
 \@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error (Appendix 3).
+R scripts available in Dryad.
 For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
@@
 
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous [@harmon2007geiger].
+We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
 The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
@@
 When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (Appendix 12).
-We calculated model adequacy scores using the R package arbutus [@pennell2015model] (Appendix 13).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12), and for the morphological dataset as a whole using the R package geomorph [@adams2016geomorph].
+We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (Appendix 13).
+We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12), and for the morphological dataset as a whole using the R package *geomorph* [@adams2016geomorph].
 We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
@@
 The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
-Then, using the package OUwie [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
+Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
 Finally, we compared their AICc support values to select the best fitting model (Appendix 14).
@@
 
-To identify the morphological characters with the greatest ability to diagnose and predict diet, we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+This function allowed us to incorporate more predictors than individuals.
 We generated discriminant functions for feeding guild, soft/hard bodied prey, presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
 Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
-We tackled this with two alternative approaches.
-One approach was to selectively remove characters and taxa to maximize the total data mass.
-Another approach was to transform the “NA” states to zeroes.
-The drawbacks of first approach is that useful data are lost, and observations are biased towards taxa with more complex tentacles.
-The drawback of the second approach is that small state values become aligned with absences.
-The severity of these drawbacks depends on the specific aspect of diet being predicted, thus we chose our approach in a case-specific basis.
-When the species with many inapplicable states are removed, we exclude a useful validation set of species (*Apolemia rubriversa*, *Rhizophysa eysenhardtii*, *Rhizophysa filiformis*, and *Physalia physalis*) for which the diet is known.
-We used the performance of the predictions on these taxa to select the approach used.
-For the specific prey type presence in the diet, we then generated and compared generalized linear models (GLMs) with multiple predictors.
-We chose predictors among the characters with significant loading contributions in each specific DAPC.
-We then selected the best GLM for each prey type based on the lowest AIC scores.
+We tackled this by transforming the absent states to zeroes.
+This approach allows us to incorporate all the data, but creates an attraction bias between small character states (*e.g.* small tentilla) and absent states (*e.g.* no tentilla).
+Absent characters are likely to be very biologically relevant to prey capture and we believe they should be accounted for.
+We limited the number of linear discriminant functions retained to the number of groupings in each case.
+We selected the number of principal components retained using the a-score optimization function (R adegenet::optim.a.score) [@jombart2010discriminant] with 100 iterations, which yielded more stable results than the cross validation function (R adegenet::xval).
+This optimization aims to find the compromise value with highest discrimination power with the least overfitting.
+From these DAPCs we obtained the highest contributing morphological characters to the discriminaton (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
+For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (Appendix 15).
+In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
+We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary] (in Appendix 11).
 
 In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character data contains many gaps due to missing characters, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
+Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
+This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters.
 In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
@@
 Tips with grey squares indicate genus-level correspondence to taxa included in (Munro *et al.* 2018).
-The main clades are labeled: in black for described taxonomic units, and in grey for operation phylogenetic designations.](Figures_final/figure4.jpg)
+The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.jpg)
 
@@
 Eucladophora is characterized by bearing spatially differentiated tentilla with proximal heteronemes and a narrower terminal filament region.
-The etymology derives from the Greek for “true branch bearers”.
+The etymology derives from the Greek *eu*+*kládos*+*phóros* for “true branch bearers”.
 Tendiculophora are characterized by bearing rhopalonemes and desmonemes in the terminal filament, having a pair of elastic strands, and developing proximally detachable cnidobands.
-The etymology of this clade is derived from the Latin tendicula for “snare or noose”.
+The etymology of this clade is derived from the Latin *tendicula* for “snare or noose” and the Greek *phóros* for "carriers".
 
-*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism was not likely ancestral, and it appears to have evolved at least two times independently (Fig.
-\@(figure5)).
+*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
+\@ref(figure5)).
 Generalism evolves twice independently from large crustacean specialist lineages, supporting hypothesis 3.
@@
   Phylogenetic regressions of continuous characters against prey selectivity data produced additional insights.
-Specialization in a piscivorous diet was associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
-Decapod-rich diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
+Fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
+Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
 Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles and elastic strands.
@@
 
+\
+
 Table 1. Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.
@@
 ```
+\
 
-*Tentillum morphology as a predictor of siphonophore diet and prey selectivity* – The discriminant analysis of principal components for feeding guild produced 86% discrimination (Appendix 15), and significant loadings were found for the characters (ordered from highest to lowest): Total haploneme volume, total nematocyst volume, cnidoband length, heteroneme volume, involucrum length, pedicle width, and tentacle width.
-The only groups confounded were generalists and large crustacean specialists.
-For this analysis, we transformed the non-applicable states in the data (due to character absence) to zeroes, thus accommodating more taxa and characters and reducing sampling bias.
-Absent characters (such as tentilla, or particular nematocyst types) are likely to be very biologically relevant to prey capture, so we believe they should be accounted for.
-When the absent character data was simply removed, similar discrimination is achieved, with the same large crustacean and generalist ambiguity (Appendix 15).
-However, the predictions from this DAPC for the validation species are largely inaccurate (*e.g.* *Rhizophysa eysenhardtii*, a specialized fish eater, is predicted as a small crustacean specialist).
-
-![\label{figure6} DAPC predicted feeding guilds for siphonophore species with measured tentillum morphology data but without any preliminary dietary data.
-Cell darkness indicates posterior probability of belonging to each guild.
-Training data set transformed so missing values would be computed as zeroes.
-Species ordered and colored according to their predicted feeding guild with highest probability score.](Figures_final/figure6.jpg)
-
-  We used this discriminant function to predict the feeding guild of 45 species in our morphological data, removing taxa and characters with inapplicable character states (Fig.
-\@ref(figure6)).
-When predicting soft and hard bodies prey specialization, the DAPC achieves 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15).
-This is congruent with the large crustacean and generalist confounds in the feeding guild discrimination.
-The main characters driving the discrimination are cnidoband coiledness, cnidoband length, tentacle width, haploneme elongation, and cnidoband width.
-Discriminant analyses and GLM were also applied to specific prey type presence and selectivity (Table 2), highlighting the most relevant characters and their predictive power.
-These analyses were carried out in a subset of characters and species that minimized taxa and characters with inapplicable states (except for fish presence, which produced much better results upon transforming inapplicable states to zeroes).
-The non-piscivorous (fish-excluding diet) tentacle morphospace is a subset of the piscivorous (fish-inclusive diet) tentacle morphospace (Appendix 15).
-However, fish specialists (primarily fish diet) can be unambiguously diagnosed in the feeding guild DAPC (Fig.
-\@ref(figure6)).
+*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (Appendix 15.1).
+We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (Fig.
+\@(figure6)).
+This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa*, and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
 
 Table 2.
-Discriminant analysis of principal components for specific prey types using the morphological data.
-Loadings are ordered from highest to lowest significance.
-GLMs were fitted to predict prey type presence and selectivity for different combinations of the significant loadings and selected for the lowest AIC value.
-Only the best GLM is reported.
-Pseudo-R^2^ approximates the variance explained by the model.
-Fish model built with NAs converted to zeroes.
+Discriminant analysis of principal components for the presence of specific prey types using the morphological data.
+Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest.
+Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
+The sign of the slope of each predictor is reported, and highlighted green if significant (p value < 0.05).
+Pseudo-R^2^ (%) approximates the percent variance explained by the model.
 
-```{r tab2, echo=FALSE, out.width='100%'}
+```{r tab2, echo=FALSE, out.width='60%'}
 knitr::include_graphics('Final_tables/table2.png')
 ```
+
+  When predicting soft and hard bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
+The main characters driving the discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
+Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2), revealing the sign of their predictive relationship to each prey type.
+We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
+While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (Appendix 15), specialization on fish or large crustacean prey can be fully disentangled (Appendix 15.1).
+For each prey type studied, tentilla morphology is a much better predictor of prey selectivity than of prey presence, despite prey selectivity data being available for a smaller subset of species.
+Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2).
+
+  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC (in Appendix 15.1).
+Cell darkness indicates posterior probability of belonging to each guild.
+Training data set transformed so inapplicable states are computed as zeroes.
+Species ordered and colored according to their predicted feeding guild.](Figures_final/figure6.jpg)
 
@@
 Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time.
-No character had support for a single-optimum OU model.
+No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).
 
@@
 
-The phylogenetic positions of the main categorical character shifts were reconstructed with stochastic character mappings (Appendix 18), and summarized in Figure \@ref(figure7).
+The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mappings (Appendix 18), and summarized in Figure \@ref(figure7).
 Haploneme nematocysts are likely ancestrally present in the tentacles, since they are present in the tentacles of many other hydrozoans.
@@
   Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure4)) encompasses most of the extant Siphonophore species.
+\@ref(figure4)) encompasses most of the extant Siphonophore species (178 of 186).
 Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
@@
 The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see Fig.
-\@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore type ancestral) nematocysts on the terminal filament (Fig.
+\@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
 \@ref(figure7)), which bear no other nematocyst type (Fig.
@@
 *Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
-The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement is independent of it.
+The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it.
 Of the phylogenetic correlations (Fig.
@@
 Most of these taxa have rod-shaped anisorhizas, but *Erenna* has oval ones).
-No clear patterns were identified in the evolution of desmoneme and rhopaloneme shape.
+No clear regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
 
@@
   The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niches, and identify the morphological characters that evolve with changes in prey type.
-We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be discriminated by observing their tentacles.
+We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
 In addition, we produced novel findings on tentillum morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
@@
 [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and Rhodaliids) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
+The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
 Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (pers.
+*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
 obs.), a common feature of piscivorous cnidarians like cystonects or cubozoans.
@@
 [@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
-The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and personal observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
+The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and our unpublished observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
 Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
 In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
-The accelerated rate of heteroneme shape evolution in the clade containing *Agalma* and *Nanomia* may indicate a rapid dietary differentiation.
+The accelerated rate of heteroneme shape diversification in the smallest clade containing *Agalma* and *Nanomia* may indicate a rapid dietary differentiation.
 However, our limited ecological data do not show any significant dietary differentiation in this group.
@@
 
-*Predicting siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can better predict the diets of siphonophores based on morphological characteristics.
+*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
 Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
-The models produced by these analyses generated untested predictions about the diets of many species for which we only have morphological data of their tentacles.
+The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
 While the limited dataset used here is informative for generating tentative hypotheses, the empirical data are still scarce and insufficient to cast robust predictions.
@@
 Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
-Interactions among the oceanic zooplankton have been treated as a black box in many ecological models [@mitra2009closure].
-The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient flow models from plankton trawl data.
+In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
+The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient flow models constructed from plankton community composition data.
 
 *Phenotypic integration of siphonophore tentilla* – Tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution].
-Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations.
+Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations [@wagner2000evolutionarily].
 In addition, these sub-structures must fit and work together in synchrony to ensnare prey successfully (functional integration).
@@
 Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies.
-Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters is maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
+Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
 
@@
 Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
-The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey classes.
+The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
 
@@
 The second hypothesis suggests that they are under selection, but the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns across the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, for when a diet- driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
+Some of the BM supported characters are likely to have evolved under the second hypothesis, since when a diet-driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
 
@@
 The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification to unfold.
-
-Our work identifies an interesting example of convergent evolution.
+In addition, our work identifies an interesting example of convergent evolution.
 The calycophoran tentillum morphospace (Fig.
@@
 We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Tendiculophora is the most abundant, speciose, and diverse (ecologically and morphologically) clade of siphonophores, containing Euphysonectae and Calycophorae.
+Tendiculophora is the most abundant, speciose, and diverse (ecologically and morphologically) clade of siphonophores, containing the clades Euphysonectae and Calycophorae.
 We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade.
@@
 For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].
-Nonetheless, siphonophores have evolved unique nematocyst types, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
+Nonetheless, siphonophores have evolved unique nematocyst types and subtypes, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
 Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not been yet found in any other tissue of any other organism.
@@
 While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to predict the feeding habits of uncharacterized species.
+Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
 We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
@@
 Data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+(Temporarily, for pre-print purposes, the Supplementary Materials and Online Appendices are all available in https://github.com/dunnlab/tentilla_morph/Supplementary_materials)
 
@@
 
-  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.A.C.).
+  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.
+Anela Choy).
 A.D.S.
@@
 We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript.
+Furthermore, we thank Elizabeth D.
+Hetherington and C.
+Anela Choy for collating the data on siphonophore feeding and for reviewing the manuscript.
 Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us valuable knowledge about siphonophores.
@@
 
-  Elizabeth D.
-Hetherington and C.
-Anela Choy (Scripps Institute of Oceanography) contributed by collating the literature and deep-sea video annotation data on siphonophore feeding observations, and by reviewing the manuscript.
-
   Casey W.

### 2019-06-12 Supplementary_materials/Dryad/R_Code.R

@@ -495,12 +495,24 @@ opposites[which(opposites$R2_regular<0),] %>% .[order(.$R2_regular-.$R2_phylo),]
 #phyreg_full[which(phyreg_full$R2_regular>0.5 & phyreg_full$R2_phylo>0 & phyreg_full$R2_phylo<0.3),] %>% .[order(.$R2_regular-.$R2_phylo),]
 
 ## PCA ##
+Q_sharedmean_logs = sharedmean_logs[,-1]
+#Q_sharedmean_logs = castmean_logs[,-1]
+#rownames(Q_sharedmean_logs) = castmean_logs$Species
+rownames(Q_sharedmean_logs) = sharedmean_logs$Species
+raw_matrix = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[which(!is.na(rowSums(.))),]
+raw_matrix_notf = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[,c(1:7,12:17)] %>% .[which(!is.na(rowSums(.))),]
+raw_matrix_NaZeroes = Q_sharedmean_logs[,c(1:2,4:20)]
+raw_matrix_NaZeroes[is.na(raw_matrix_NaZeroes)]<-0
+compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
 
 #Using simple characters
+#PCA(raw_matrix_NaZeroes) -> Pca_raw
 PCA(raw_matrix_notf) -> Pca_raw
 Pca_raw %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
 Pca_raw %>% fviz_contrib(choice="var", axes=2, sort.val="desc")
 Pca_raw %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE) #For figure A
+Pca_raw %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE, axes=c(3,4)) 
+raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
 phylomorphospace(tree=raw_tree, Pca_raw$ind$coord[,1:2], label = "horizontal", xlab = "PC1", ylab = "PC2") #For figure B
 multiPhylosignal(Pca_raw$ind$coord, raw_tree)
 physignal(Pca_raw$ind$coord, raw_tree)
[…]

### 2019-07-23 manuscript_clean.Rmd
VCV analysis supplement

@@
 indent: TRUE
+monofont: "Times New Roman"
+fontsize: 12pt
 header-includes:
@@
   - \linenumbers
+  - \usepackage{setspace}
+  - \doublespacing
 ---
@@
 
-To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phytools::phyloglm) (Appendix 17).
+To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (Appendix 17).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
@@
 
-![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the OUwie analyses.
+![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the *OUwie* analyses.
 Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
@@
 Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
-In this group, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).
+In this group, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).
 
@@
 
-Data available from the Dryad Digital Repository: http://dx.doi.org/10.5061/dryad.[NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
-(Temporarily, for pre-print purposes, the Supplementary Materials and Online Appendices are all available in https://github.com/dunnlab/tentilla_morph/Supplementary_materials)
+Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+Online Appendices are available in [https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices](https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices)
 
@@
 
-## Author contributions {-}
-
-  Alejandro Damian-Serrano (Yale University)  collected specimens and morphological data, executed phylogenetic analyses (tree inference and character evolution), elaborated the figures, wrote and reviewed the manuscript.
-
-  Steven H.D.
-Haddock (Monterey Bay Aquarium Research Institute) contributed by facilitating the access to the field and collection tools, directing the ROV and blue water diving operations in the field.
-He also contributed extensive knowledge of the biology and ecology of the organisms, and reviewed the manuscript.
-The Haddock Lab contributed by sequencing many of the species included in the phylogeny presented here.
-
-  Casey W.
-Dunn (Yale University) contributed by collecting specimens, providing invaluable insights and mentoring, and by reviewing the manuscript.
-In addition, his graduate dissertation work produced many of the sequences used for our phylogenetic analysis.
-
 ## References {-}

### 2019-07-23 Supplementary_materials/Dryad/R_Code.R

@@ -763,40 +763,6 @@ names(colors) = c("Fish","Large crustacean","Mixed","Small crustacean","Gelatino
 nodelabels(pie=(describe.simmap(feeding_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 
-##VCV analysis###
-regimematrix = sharedmean_logs
-rownames(regimematrix) = regimematrix$Species
-regimematrix[is.na(regimematrix)] <- 0
-simple.vcv <- evol.vcv(tree=ultram, as.matrix(regimematrix[,2:22]))
-simple.vcv.corrs <- cov2cor(simple.vcv$R.single)
-corrplot(simple.vcv.corrs)
-
-dietregimematrix = dprunedmatrix_logs
-rownames(dietregimematrix) = dietregimematrix$Species
-dietregimematrix[is.na(dietregimematrix)] <- 0
-diet.simple.vcv <- evol.vcv(tree=regimetree, as.matrix(dietregimematrix[,2:22]))
-diet.simple.vcv.corrs <- cov2cor(diet.simple.vcv$R.single)
-corrplot(diet.simple.vcv.corrs)
-diet.complex.vcv <- evol.vcv(tree=feeding_sim[[89]], as.matrix(dietregimematrix[,2:22]))
-
-#Loop for evol.vcvlite character pairs
-VCVlist <- list()
-it = 0
-for(i in 2:ncol(dietregimematrix)){
-  for(j in 2:ncol(dietregimematrix)){
-    IJmatrix = dietregimematrix[which(rowSums(dietregimematrix[,c(i,j)])!=0),]
-    #IJmatrix[,-1] = sapply(IJmatrix[,-1], jitter)
-    IJtree = drop.tip(feeding_sim[[89]], which(!(feeding_sim[[89]]$tip.label %in% IJmatrix$Species)))
-    kappa(t(as.matrix(IJmatrix[,c(i,j)])) %*% as.matrix(IJmatrix[,c(i,j)]))
-    if(i != j & min(cor(IJmatrix[,c(i,j)]))<0.95){
-      it <- it+1
-      tryCatch(evcvIJ <- evolvcv.lite(IJtree, IJmatrix[,c(i,j)])), error=function(e))
-      VCVlist[[it]] <- evcvIJ
[…]

### 2019-07-24 manuscript_clean.Rmd
VCV analysis methods section

@@
 In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
+In order to study correlations between the rates of evolution of each character, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
+When fitting all covariance terms simultaneously, we selected the largest set of characters that would allow the analysis to run without computational singularities.
+This excluded many of the morphometric characters which are linearly dependent on other characters.
+Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
+To test whether phenotypic integration changes across selective regimes determined by the reconstrcuted feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
+These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
+All the pairwise analyses were carried out transforming abstent states to zeroes.
+Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
 

### 2019-07-24 manuscript_clean.Rmd
VCV analysis results section

@@
 Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstrcuted feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-All the pairwise analyses were carried out transforming abstent states to zeroes.
+All the pairwise analyses were carried out transforming absent states to zeroes.
 Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
@@
 Rhopaloneme shape shows the most incongruences between phylogenetic and ordinary correlations with other characters.
+
+The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
+\@ref(figure8)a.
+However, this analysis reveals more clearly the diagonal blocks that constitute integration modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
+These results were not very sensitive to transformation of inapplicable states and taxon sampling.
+When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that about half (53%) of the character pairs presented different correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.5-20.6).
+For example, haploneme and heteroneme lengths hold a strong positive correlation under a crustacean specialist regime, which reverses to a strong negative relationship in fish specialists.
+Gelatinous specialist correlations cannot be effectively interpreted since they correspond to a monotypic branch (*Apolemia*) which has lost many characters.
+Under a generalist trophic regime, rhopaloneme width becomes negatively correlated with elastic strand width, haploneme width, heteroneme length, heteroneme shaft size, and positively correlated with involucrum length.
+Desmoneme length also shows a unique suite of negative correlations under the generalist regime, such as with desmoneme width, haploneme and heteroneme length, heteroneme shaft width, and pedicle width, but again a strong positive correlation with involucrum.
+This is consistent with the characteristic morphology of *Agalma* and *Athorybia* tentilla and nematocysts.
+Soft bodied specialists (fish and gelatinous prey) present a large suite of unique negative correlations corresponding to the different ways in which nematocyst types and structures are reduced.
+Both crustacean specialist regimes (large and small) share positive correlations of haploneme and elastic strand widths with other characters.
+however, small crustacean specialists differ from large crustacean specialists by their negative correlation between cnidoband length and heteroneme number, involucrum length and pedicle width, involucrum length and cnidoband free length, and involucrum length with heteroneme volume.
+In addition, tentacle and pedicle width become strongly positively correlated with desmoneme and rhopaloneme sizes when specializing on smaller prey, while showing a strong opposite relationship in large crustacean specialists.
 

### 2019-07-26 manuscript_clean.Rmd
redid VCV comparisons without transforming NA->zero and contrasting each regime against its preceding one, not the whole tree matrix

@@
 *Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species.
-There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
+There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
 \@ref(figure10)).

### 2019-07-26 Supplementary_materials/Dryad/R_Code.R

@@ -1,6 +1,7 @@
 ## LOAD PACKAGES ##
 #General
 library(tidyverse)
+library(magrittr)
 library(stringr)
 library(readr)
 library(reshape2)
@@ -1114,10 +1115,11 @@ simple.vcv.corrs <- cov2cor(simple.vcv$R.single)
 corrplot(simple.vcv.corrs)
 
 #For the taxa with diet data
+par(ask=F)
 dietregimematrix = dprunedmatrix_logs
 rownames(dietregimematrix) = dietregimematrix$Species
 #Nas to zeroes
-dietregimematrix[is.na(dietregimematrix)] <- 0
+#dietregimematrix[is.na(dietregimematrix)] <- 0
 diet.simple.vcv <- evol.vcv(tree=regimetree, as.matrix(dietregimematrix[,2:22]))
 diet.simple.vcv.corrs <- cov2cor(diet.simple.vcv$R.single)
 corrplot(diet.simple.vcv.corrs)
@@ -1138,7 +1140,7 @@ for(i in 2:22){
   for(j in 2:22){
     IJmatrix = dietregimematrix[which(rowSums(dietregimematrix[,c(i,j)])!=0),]
     #IJmatrix[,-1] = sapply(IJmatrix[,-1], jitter)
-    IJtree = drop.tip(feeding_sim[[89]], which(!(feeding_sim[[89]]$tip.label %in% IJmatrix$Species)))
+    IJtree = drop.tip(feeding_sim[[91]], which(!(feeding_sim[[89]]$tip.label %in% IJmatrix$Species)))
     kappa(t(as.matrix(IJmatrix[,c(i,j)])) %*% as.matrix(IJmatrix[,c(i,j)]))
     it <- it+1
     if(i != j ){

### 2019-07-29 Supplementary_materials/Dryad/R_Code.R
fixing issues with VCV lite

@@ -756,6 +756,7 @@ nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);ti
 RTorder = regimetree$tip.label
 
 ##SIMMAP feeding guilds ##
+set.seed(1111111)
 make.simmap(regimetree, hypdiet, nsim = 100) -> feeding_sim
 plotTree(regimetree, lwd = 4)
 feeding_sim %>% plotSimmap(lwd = 4, add = T)
@@ -763,6 +764,7 @@ colors = c( "black","green3","blue","cyan","red")
 names(colors) = c("Fish","Large crustacean","Mixed","Small crustacean","Gelatinous")
 nodelabels(pie=(describe.simmap(feeding_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
+par(ask=F)
 
 #PGLS of characters vs Purcell Selectivity
 pGLSp_sel = as.data.frame(matrix(nrow=ncol(Sprunedmatrix_logs[,-1]), ncol=ncol(selectivity)))
@@ -1138,10 +1140,10 @@ VCVlist <- list()
 it = 0
 for(i in 2:22){
   for(j in 2:22){
-    IJmatrix = dietregimematrix[which(rowSums(dietregimematrix[,c(i,j)])!=0),]
+    IJmatrix = dietregimematrix[which(!is.na(rowSums(dietregimematrix[,c(i,j)]))),]
     #IJmatrix[,-1] = sapply(IJmatrix[,-1], jitter)
-    IJtree = drop.tip(feeding_sim[[91]], which(!(feeding_sim[[89]]$tip.label %in% IJmatrix$Species)))
-    kappa(t(as.matrix(IJmatrix[,c(i,j)])) %*% as.matrix(IJmatrix[,c(i,j)]))
+    IJtree = drop.tip.simmap(feeding_sim[[16]], feeding_sim[[16]]$tip.label[which(!(feeding_sim[[16]]$tip.label %in% IJmatrix$Species))])
+    IJmatrix = IJmatrix[match(IJtree$tip.label, rownames(IJmatrix)),]
     it <- it+1
     if(i != j ){
       evcvIJ <- try(evolvcv.lite(IJtree, IJmatrix[,c(i,j)]), silent=T)
[…]

### 2019-07-30 manuscript_clean.Rmd
fixing more issues with VCV lite

--- 2019-07-24 manuscript_clean.Rmd
@@
 Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstrcuted feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-All the pairwise analyses were carried out transforming abstent states to zeroes.
-Finally, we compared regime-specific variance covariance matrices to the general matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
+Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*.
 
@@
 
+The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
+\@ref(figure8)a.
+However, this analysis reveals more clearly the diagonal blocks that constitute the integration modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
+These results were not very sensitive to transformation of inapplicable states and taxon sampling.
+When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented different correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.6).
+Similarly, when we contrasted these matrices to the large crustacean (ancestral) matrix, we identified the main shifts in character dependencies associated to regime shifts.
+
+Under the majority of SIMMAP outcomes, large crustaceans specialists are the first regime to appear, and other regimes evolve in a shift from this ancestral specialization.
+Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme shape and tentillum size, as well as with involucrum length.
+With the appearance of generalists (*Forskalia* and Agalmatids), terminal filament nematocyst (desmonemes and rhopalonemes) sizes become negatively correlated with the sizes of most characters.
+In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
+When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which developed a strong positive relationship with tentillum size.
+Simultaneously, in these small crustacean specialists, haploneme elongation became positively correlated with heteroneme size.
+With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (in Clade B), and the surface area to volume ratio of haploneme nematocysts switched from the strong negative relationship with cnidoband size found in every other regime to a positively correlation.
+Gelatinous specialization, albeit appearing only once, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are effective at anchoring gelatinous tissue.
+
 ![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.

### 2019-07-30 Supplementary_materials/Dryad/R_Code.R

@@ -1120,6 +1120,8 @@ corrplot(simple.vcv.corrs)
 par(ask=F)
 dietregimematrix = dprunedmatrix_logs
 rownames(dietregimematrix) = dietregimematrix$Species
+fmode<-setNames(hypdiet,names(hypdiet))
+fmode
 #Nas to zeroes
 #dietregimematrix[is.na(dietregimematrix)] <- 0
 diet.simple.vcv <- evol.vcv(tree=regimetree, as.matrix(dietregimematrix[,2:22]))
@@ -1138,15 +1140,19 @@ corrplot(diet.simple.vcv.corrs)
 #Loop for evol.vcvlite with character pairs
 VCVlist <- list()
 it = 0
-for(i in 2:22){
-  for(j in 2:22){
+for(i in 2:ncol(dietregimematrix)){
+  for(j in 2:ncol(dietregimematrix)){
     IJmatrix = dietregimematrix[which(!is.na(rowSums(dietregimematrix[,c(i,j)]))),]
-    #IJmatrix[,-1] = sapply(IJmatrix[,-1], jitter)
-    IJtree = drop.tip.simmap(feeding_sim[[16]], feeding_sim[[16]]$tip.label[which(!(feeding_sim[[16]]$tip.label %in% IJmatrix$Species))])
+    IJtree = drop.tip.simmap(feeding_sim[[19]], feeding_sim[[19]]$tip.label[which(!(feeding_sim[[19]]$tip.label %in% IJmatrix$Species))])
+    #remaining_states = IJtree$node.states %>% as.vector() %>%  unique()
+    #Qmod = IJtree$Q
+    #Qmod = Qmod[which(rownames(Qmod) %in% remaining_states),which(colnames(Qmod) %in% remaining_states)]
+    #IJtree$Q <- Qmod
+    IJtree$node.label=NULL
     IJmatrix = IJmatrix[match(IJtree$tip.label, rownames(IJmatrix)),]
     it <- it+1
     if(i != j ){
-      evcvIJ <- try(evolvcv.lite(IJtree, IJmatrix[,c(i,j)]), silent=T)
+      evcvIJ <- try(evolvcv.lite(IJtree, as.matrix(IJmatrix[,c(i,j)])), silent=T)
       VCVlist[[it]] <- evcvIJ
       names(VCVlist)[it] <- paste(names(IJmatrix)[i], names(IJmatrix)[j], collapse = " ~ ")
     }
[…]

### 2019-08-07 manuscript_clean.Rmd
wrote discussion chunk and added bibs for VCV analysis

@@
 
+  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated, but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
+This may be indicative of the underlying genetic and developmental dependencies of homologous nematocyst types (desmonemes and rhopalonemes) and structures.
+In addition, these evolutionary modules point to hypothetical functional modules.
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).
+
+  While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
+This evolution of character relationships can allow lineages to explore new regions of the morphospace and facilitate the appearance of ecological novelties.
+Our results show that the patterns of phenotypic integration in siphonophore tentilla vary among clades, and appear to display different relationships across shifting feeding specializations.
+Similarly to what has been found in the feeding morphologies of fish (Collar 2005, Collar Revell 2009), siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
+For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring small crustaceans or fish.
+The evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today in siphonophores.
+
 *Evolutionary history of tentillum morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.

### 2019-08-12 manuscript_clean.Rmd
added Ntaxa to VCV analyses

@@
 These present a significant morphological variation across species [@mapstone2014global] (Fig.
-\@ref(figure2)), which makes it ideal to study the relationships between functional traits and prey specialization.
+\@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
 A siphonophore is a colony bearing many feeding polyps (Fig.
@@
   Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
-This habitat has fairly homogeneous physical conditions and stable abundances of zooplanktonic animals [@robison2004deep].
+This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
 With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
@@
 
-  The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
+  The study of siphonophore tentilla and diets was limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
 Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
@@
 observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
-We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error (Appendix 3).
+We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
+\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it (Appendix 3).
 R scripts available in Dryad.
@@
 We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (Appendix 13).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12), and for the morphological dataset as a whole using the R package *geomorph* [@adams2016geomorph].
-We reconstructed ancestral states using Maximum Likelihood (anc.ML [@revell2012phytools]), and stochastic character mapping (make.simmap) for categorical characters.
+We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12).
+We reconstructed ancestral states using Maximum Likelihood (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
 R scripts available in Dryad.
@@
 First, we collapsed the diet data into the five feeding guilds mentioned above (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
-We reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
+Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
 The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
@@
 To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
-To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls).
+To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
 
@@
 This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, soft/hard bodied prey, presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
+We generated discriminant functions for feeding guild, soft/hard bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
 Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
@@
 This approach allows us to incorporate all the data, but creates an attraction bias between small character states (*e.g.* small tentilla) and absent states (*e.g.* no tentilla).
-Absent characters are likely to be very biologically relevant to prey capture and we believe they should be accounted for.
+Absent characters are likely to be very biologically relevant to prey capture and we believe they should be accounted for in a predictive approach.
 We limited the number of linear discriminant functions retained to the number of groupings in each case.
@@
 In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
-In order to study correlations between the rates of evolution of each character, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
-When fitting all covariance terms simultaneously, we selected the largest set of characters that would allow the analysis to run without computational singularities.
+
+In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
+When fitting all covariance terms simultaneously (Appendix 20.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities.
 This excluded many of the morphometric characters which are linearly dependent on other characters.
@@
 Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*.
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
 
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different nematocyst types, and identified the branches with the greatest shifts.
+To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
 In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (Appendix 16).
@@
 Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2.
-Individual prey type presence reconstructions show that copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
+Copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
 The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (Appendix 14).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
-Most of these characters are found exclusively in Tendiculophora, thus this reflects processes that could be unique to this subtree.
+Most of these characters are found exclusively in Tendiculophora, thus this may reflect processes that could be unique to this subtree.
 Five characters including cnidoband length, cnidoband shape, and haploneme length show maximal support for a diet-driven single-optimum OU model.
@@
 Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
-Heteroneme length and shape also correlated negatively with chaetognath selectivity.
+Heteroneme length and elongation also correlated negatively with chaetognath selectivity.
 
@@
   When predicting soft and hard bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
-The main characters driving the discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
+The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
 Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2), revealing the sign of their predictive relationship to each prey type.
@@
 
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not likely to be phylogenetically distributed (Appendix 12).
+*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (Appendix 12).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
-In large complex-shaped tentilla, haplonemes were omitted for simplification.
+In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
 The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)
 
-The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mappings (Appendix 18), and summarized in Figure \@ref(figure7).
-Haploneme nematocysts are likely ancestrally present in the tentacles, since they are present in the tentacles of many other hydrozoans.
-Haplonemes diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
+The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (Appendix 18), and summarized in Figure 7.
+Haploneme nematocysts are likely ancestrally present in siphonophore tentacles, since they are present in the tentacles of many other hydrozoans.
+Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
 Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they only appear in the tentacles of codonophorans as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
+Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
 
@@
 \@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bear no other nematocyst type (Fig.
+\@ref(figure7)), which bears no other nematocyst type (Fig.
 \@ref(figure1)).
@@
 \@ref(figure8)a.
-However, this analysis reveals more clearly the diagonal blocks that constitute the integration modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
+However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
 These results were not very sensitive to transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented different correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
 When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.6).
-Similarly, when we contrasted these matrices to the large crustacean (ancestral) matrix, we identified the main shifts in character dependencies associated to regime shifts.
 
 Under the majority of SIMMAP outcomes, large crustaceans specialists are the first regime to appear, and other regimes evolve in a shift from this ancestral specialization.
-Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme shape and tentillum size, as well as with involucrum length.
-With the appearance of generalists (*Forskalia* and Agalmatids), terminal filament nematocyst (desmonemes and rhopalonemes) sizes become negatively correlated with the sizes of most characters.
+Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
+With the appearance of generalists (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters.
 In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
-When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which developed a strong positive relationship with tentillum size.
+When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which in turn developed a strong positive relationship with tentillum size.
 Simultaneously, in these small crustacean specialists, haploneme elongation became positively correlated with heteroneme size.
-With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (in Clade B), and the surface area to volume ratio of haploneme nematocysts switched from the strong negative relationship with cnidoband size found in every other regime to a positively correlation.
-Gelatinous specialization, albeit appearing only once, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are effective at anchoring gelatinous tissue.
+With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positively correlation.
+Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
 
@@
 There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
-\@ref(figure10)).
-Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
-In this group, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).
+\@ref(figure10).
+Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
+In this clade, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
+\@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
 
@@
 Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
-Apolemids have no tentacle haplonemes and are projected onto the heteroneme axis.
+Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.
 Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)
@@
 Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
-Predators that use similar tools for prey capture tend to capture similar prey, so their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
+Predators that use similar tools for prey capture tend to capture similar prey, thus their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
 However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
@@
 \@ref(figure5)).
-Copepod-specialized diets have evolved convergently in *Cordagalma* and some Calycophorans.
+Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
 These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
-Tentilla are expensive single-use structures, therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological function.
-*Cordagalma*'s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia* spp.
-This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization.
+Tentilla are expensive single-use structures, therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
+*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia* spp.
+This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization on smaller prey.
 
@@
 In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
-The accelerated rate of heteroneme shape diversification in the smallest clade containing *Agalma* and *Nanomia* may indicate a rapid dietary differentiation.
-However, our limited ecological data do not show any significant dietary differentiation in this group.
 
-When we tested the diet-morphology correlation hypotheses supported in the literature from a macroevolutionary perspective, we found that most of them were consistent with correlated evolution (Table 2).
+When we tested the diet-morphology correlation hypotheses supported in the literature from a macroevolutionary perspective (Table 1), we found that most of them were consistent with correlated evolution.
 The ecomorphological association between rhopalonemes, desmonemes, and crustacean eaters was not congruent with a scenario of correlated evolution.
-This could be due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes but which effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
+This is probably due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes but which effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
 
@@
 Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for this study.
-For example, tentacle-deploying behavior, positioning in the water column, or thresholds for  discharging on or ingesting an encountered animal.
+For example, tentacle-deploying behavior, positioning in the water column, sensitivity thresholds for nematocyst discharge, or chemical cues to ingest a captured animal.
 Further observations on these behaviors in the field are necessary to assess their relative importance in determining dietary composition.
@@
 Part of the success in siphonophore prey capture is likely determined by the effectivity of the toxins delivered by the nematocysts on different taxa.
-Comparative toxin assays and venom protein evolution studies could shed light on this question.
+Comparative toxin assays and venom protein evolution studies would shed light on this question.
 Moreover, siphonophore trophic specialization may have brought changes in the digestive biochemistry of gastrozooids and palpons.
@@
 The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
-While the limited dataset used here is informative for generating tentative hypotheses, the empirical data are still scarce and insufficient to cast robust predictions.
+While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.
 This reveals the need to extensively characterize siphonophore diets and feeding habits.
@@
 
-*Phenotypic integration of siphonophore tentilla* – Tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution].
+*Phenotypic integration of siphonophore tentilla* – Many tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution].
 Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations [@wagner2000evolutionarily].
@@
   Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated, but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
-This may be indicative of the underlying genetic and developmental dependencies of homologous nematocyst types (desmonemes and rhopalonemes) and structures.
+This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
 In addition, these evolutionary modules point to hypothetical functional modules.
@@
 Our results show that the patterns of phenotypic integration in siphonophore tentilla vary among clades, and appear to display different relationships across shifting feeding specializations.
-Similarly to what has been found in the feeding morphologies of fish (Collar 2005, Collar Revell 2009), siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
+Similarly to what has been found in the feeding morphologies of fish [@collar2005comparative;@revell2009phylogenetic], siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
 For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring small crustaceans or fish.
-The evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today in siphonophores.
+Finally, the evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today across siphonophores.
 
 *Evolutionary history of tentillum morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
-This revealed for the first time that *Erenna* is the sister to *Stephanomia amphytridis*.
+This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
 *Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
@@
 An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification to unfold.
+The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
 In addition, our work identifies an interesting example of convergent evolution.
@@
 Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
-Most calycophoran diet studies have reported their prey to be small crustaceans such as copepods or ostracods.
-The diet of *Frillagalma vityazi* is unknown, but this morphological convergence presents the hypothesis that they evolved to capture similar kinds of prey.
+Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
+The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
 Our DAPCs predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.
@@
 The most recent work on this front sets them as sister group to all other Hydroidolina [@kayal2015phylogenetic].
-All reconstructions of hydrozoan relationships recover siphonophores as an early diverging lineage within Hydroidolina, with many unique apomorphic characters.
 Therefore, there is a great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
@@
 Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
-Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, associated with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
+Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
 
-Simultaneous with this shift in haploneme shape, heteroneme shape evolution also presents a single transition to elongation.
-In addition, the clade defined by the most recent common ancestor of *Agalma* and *Nanomia* shows an increased rate of divergence for heteroneme shape, spanning extremes (from oval *Nanomia* stenoteles to the elongate *Agalma okenii* stenoteles) in relatively short evolutionary time.
+In parallel with haploneme shape, heteroneme shape evolution also presents a single, large, early transition towards elongation.
 While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids, hypothetically used for defense rather than for prey capture.
@@
 
-  The implications of these results to the evolution of nematocyst function suggests that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
+  The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
 Elongate nematocysts can be tightly packed into cnidobands.
@@
 Nonetheless, siphonophores have evolved unique nematocyst types and subtypes, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
-Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not been yet found in any other tissue of any other organism.
+Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not yet been found in any other tissue of any other organism.
 The gain of extreme elongation in the haplonemes of Tendiculophora can be interpreted as part of the character shift to a novel anisorhiza subtype.
@@
 
-*Insights from tentillum morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts spans clades, from the overall shape and size, to the dimensions of the nematocysts.
-Siphonophores bear the largest nematocysts among Hydrozoans, and present a wide variety of nematocyst sizes within the clade.
+*Insights from tentillum morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts is remarkable, both in their range of shapes and sizes, as in the dimensions and subtypes of the nematocysts they bear.
+Siphonophores bear the largest nematocysts among Hydrozoans.
 The largest nematocysts in our dataset (*Bargmannia lata* by volume and *Resomia dunni* by length), are the largest of all nematocysts reported for cnidarians, and therefore possibly the largest intracellular organelles among all living things.
@@
   In addition to the insights produced in this study, the newly collected morphological data provide a unique resource for future studies, and a reference dataset for siphonophore identification.
-Many conspicuous categorical characters in siphonophore tentilla are very diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the bioluminescent lures of *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the buoyant medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
+Many conspicuous categorical characters in siphonophore tentilla are singularly diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the bioluminescent lures of *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the buoyant medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
 \@ref(figure7)).

### 2019-08-12 Supplementary_materials/Dryad/R_Code.R

@@ -1120,8 +1120,6 @@ corrplot(simple.vcv.corrs)
 par(ask=F)
 dietregimematrix = dprunedmatrix_logs
 rownames(dietregimematrix) = dietregimematrix$Species
-fmode<-setNames(hypdiet,names(hypdiet))
-fmode
 #Nas to zeroes
 #dietregimematrix[is.na(dietregimematrix)] <- 0
 diet.simple.vcv <- evol.vcv(tree=regimetree, as.matrix(dietregimematrix[,2:22]))
@@ -1158,6 +1156,21 @@ for(i in 2:ncol(dietregimematrix)){
     }
   }
 }
+
+ntaxamatrix = matrix(ncol=ncol(dietregimematrix)-1,nrow=ncol(dietregimematrix)-1) %>% as.data.frame()
+names(ntaxamatrix) <- names(dietregimematrix)[-1]
+rownames(ntaxamatrix) <- names(dietregimematrix)[-1]
+
+#Get the number of taxa per character pair
+for(i in 2:ncol(dietregimematrix)){
+  for(j in 2:ncol(dietregimematrix)){
+    which(!is.na(rowSums(dietregimematrix[,c(i,j)]))) %>% length() -> ntaxamatrix[i-1,j-1] #%>% print()
+  }
+}
+ntaxamelt <- cbind(rep(rownames(ntaxamatrix),ncol(ntaxamatrix)), melt(ntaxamatrix, id.var = NULL))
+names(ntaxamelt) <- c("Character_1","Character_2","Ntaxa")
+ggplot(ntaxamelt, aes(Character_1, Character_2)) + geom_tile(aes(fill = Ntaxa), colour = "black") + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
 
 VCVshortlist <- VCVlist[which(lapply(VCVlist, class)=="evolvcv.lite")]
 bestmodel_number = lapply(VCVshortlist, function(y){lapply(y,function(x){x$AIC}) %>% unlist() %>% .[which(. == min(.))] %>% names()})

### 2019-08-27 manuscript_clean.Rmd
incorporated round of coauthor's comments

@@
 As different predators specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms.
-Studying the evolution of predation is greatly facilitated by a predator clade with structures used exclusively for prey capture that present significant morphological variation.
+Studying the evolution of predation is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation.
 Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well, capturing prey with their tentilla (tentacle side branches).
@@
 We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) characterized the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
+To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high-speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
 Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
@@
 Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This study contributes to understanding how morphological evolution has shaped present-day oceanic food-webs.
+This study contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
 
@@
 \@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
-Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation], built into their tentilla.
+Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla.
 While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
@@
 This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@hardin1960competitive;@hutchinson1961paradox].
+With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
 If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
 
-  Coexisting siphonophores feeding on the same planktonic community may have substantial niche overlap and compete for prey resources.
-Traditional ecological coexistence theory [@simpson1944tempo] predicts that competition between species would select for increasing ecological specialization.
-This specialization is often thought to be an evolutionary ‘dead end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
+Specialization is often thought to be an evolutionary ‘dead end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
 However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition] and resource switching [@hoberg2008macroevolutionary].
-Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predatory specialists which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
 
-  The study of siphonophore tentilla and diets was limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
+  The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
 Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
@@
 Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
+
 In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures.
-In particular, we aim to address the evolutionary origins of giant tentilla, the phenotypic integration of tentilla, the evolution of the extreme shapes of siphonophore haploneme nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
+In particular, we aim to address the evolutionary origins of giant tentilla, the character integration of tentilla, the evolution of the extreme shapes of siphonophore nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
 
@@
 Tentillum illustration and main parts.
-E - Transmission micrograph of the tentillum illustrated in D.
+E - Differential interference contrast micrograph of the tentillum illustrated in D.
 F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum.
@@
 *Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Appendix 1).
-These specimens were collected intact across many years of fieldwork expeditions, using of blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
-Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted into slides with Canada Balsam or Permount mounting media.
+These specimens were collected intact across many years of fieldwork expeditions, using  blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
+Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted onto slides with Canada Balsam or Permount mounting media.
 The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
@@
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and Anela Choy (Appendix 10).
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
+Anela Choy (Appendix 10).
 We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
@@
 In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character data contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
+Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
 This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters.
@@
 Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite) such as models where correlations are the same across the whole tree and models where correlations differ between selective regimes.
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes.
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
@@
 
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of log(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
+To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
 In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (Appendix 16).
@@
 
-*Phylogeny* – Only 5 nodes in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree.
+*Phylogeny* – Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the 18S+16S tree.
 The topology of the constrained tree presented here (Fig.
@@
 Tips with grey squares indicate genus-level correspondence to taxa included in (Munro *et al.* 2018).
-The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.jpg)
+The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.jpg){height=600px}
 
@@
 
-*Evolutionary dynamics between diet and tentillum morphology* – The reconstructions of feeding guilds show that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
+*Evolutionary dynamics between diet and tentillum morphology* – Reconstructions of feeding guilds shows that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
 \@ref(figure5)).
-Generalism evolves twice independently from large crustacean specialist lineages, supporting hypothesis 3.
+Large crustacean specialists evolve into generalists twice independently, supporting hypothesis 3.
 Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2.
-Copepod specialization and fish specialization evolved twice, ostracod specialization evolved at least once.
+Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
+
 The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (Appendix 14).
@@
 Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
-The sign of the slope of each predictor is reported, and highlighted green if significant (p value < 0.05).
+The sign of the slope of each predictor is reported, marked with an asterisk if significant, and highlighted grey if it differs between prey presence in diet and prey selectivity.
+green if significant (p value < 0.05).
 Pseudo-R^2^ (%) approximates the percent variance explained by the model.
@@
 
-  When predicting soft and hard bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
+  When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
 The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
@@
 While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (Appendix 15), specialization on fish or large crustacean prey can be fully disentangled (Appendix 15.1).
-For each prey type studied, tentilla morphology is a much better predictor of prey selectivity than of prey presence, despite prey selectivity data being available for a smaller subset of species.
+For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
 Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2).
@@
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
-74% of characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal K > 1.
+74% of characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K > 1.
 67% of characters support BM models, indicating a history of neutral constant divergence.
@@
   Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure4)) encompasses most of the extant Siphonophore species (178 of 186).
+\@ref(figure4)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
 Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
@@
 This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
-Calycophorans evolved unique novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
+Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
 While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
@@
 Light red and blue boxes indicate congruent negative and positive correlations respectively.
-Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](Figures_final/figure8.jpg)
+Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](Figures_final/figure8.jpg){height=600px}
 
@@
 Similarly, of the across-species correlations, 49.1% were >0.5 and only 1.5% were < -0.5.
-13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
-Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and vice versa for 9.9% of character pairs (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
-These disparities can be caused by Simpson’s paradox [@blyth1972simpson], the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
+We found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
+Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
+These disparities can be caused by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
 However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54).
-Rhopaloneme shape shows the most incongruences between phylogenetic and ordinary correlations with other characters.
+Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
 
@@
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
-With the appearance of generalists (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters.
+With the appearance of generalists (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
 In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
 When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which in turn developed a strong positive relationship with tentillum size.
-Simultaneously, in these small crustacean specialists, haploneme elongation became positively correlated with heteroneme size.
+In other words, as tentilla get smaller in this group, heteronemes get shorter and haplonemes get larger.
+The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*.
 With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positively correlation.
@@
 B.
-Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg)
+Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg){height=600px}
 
@@
 
-*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species.
+*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
 There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
@@
 Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
-Predators that use similar tools for prey capture tend to capture similar prey, thus their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
+Predators that use morphologically similar tools for prey capture tend to capture similar prey, thus their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
 However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
@@
 In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
-The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient flow models constructed from plankton community composition data.
+The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
 
@@
 
-  Part of the tentillum structural correlations are to be expected from shared regulatory networks for elements that develop together from common positional bud (budding tentilla in the tentacle).
+  Structural correlations within the tentillum are expected from shared regulatory networks within a common developmental bud (budding tentilla in the tentacle).
 Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin.
@@
 In addition, our work identifies an interesting example of convergent evolution.
-The calycophoran tentillum morphospace (Fig.
-\@ref(figure9)) was independently occupied by the physonect *Frillagalma vityazi*.
+The region of the tentillum morphospace (Fig.
+\@ref(figure9)) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 In parallel with haploneme shape, heteroneme shape evolution also presents a single, large, early transition towards elongation.
-While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids, hypothetically used for defense rather than for prey capture.
+While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids [@totton1965synopsis], hypothetically used for defense rather than for prey capture.
 These stenotele heteronemes are rounded like those found in pyrostephids and apolemiids, which is consistent with the story of a single transition leading to the elongated heteronemes in the stem of Tendiculophora.
@@
 We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Tendiculophora is the most abundant, speciose, and diverse (ecologically and morphologically) clade of siphonophores, containing the clades Euphysonectae and Calycophorae.
+Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
+Among these, are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
 We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade.
@@
 stenoteles, mastigophores, birhopaloids).
-Siphonophores bear nematocysts in different parts of the colony (tentacles, gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
+In addition to the tentacles, siphonophores may bear nematocysts in other parts of the colony (gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
 In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations.
-For instance, stenoteles (a type of heteroneme) are absent from the tentacles of *Physalia* and seem to reappear in Euphysonectae, but we know that *Physalia* has stenoteles in other body parts [@totton1965synopsis].
 Nonetheless, siphonophores have evolved unique nematocyst types and subtypes, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
@@
 Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We conclude that the siphonophores were able to establish as abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
+We conclude that the siphonophores were able to become abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
 

### 2019-08-27 Supplementary_materials/Dryad/R_Code.R

@@ -140,8 +140,14 @@ names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
 heatdata = as.matrix(castmean_logs[,-1])
 rownames(heatdata) = castmean_logs$Species
 heatdata[is.nan(heatdata)]<- -1
-hcolors = grDevices::terrain.colors(20)
-hcolors<-c(rep("#000000FF",10), hcolors)
+#hcolors = grDevices::terrain.colors(20)
+library(colorspace)
+sequential_hcl()
+hcolors <- colorRampPalette(c("#e0ecf4","#9ebcda","#8856a7"), bias=1)
+hcolors <- colorRampPalette(c("#ffeda0","#feb24c","#f03b20"), bias=1)
+hcolors <- colorRampPalette(c("yellow","purple"), bias=1)
+#hcolors <- sequential_hcl(17, h = 245, c = c(40, 75, 0), l = c(30, 95), power = 1)
+hcolors <- c(rep("#000000FF",10), hcolors(30))
 heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)
 
 #Load phylogenetic tree

### 2019-08-28 manuscript_clean.Rmd
fleshed out readme

@@
 Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
-The sign of the slope of each predictor is reported, marked with an asterisk if significant, and highlighted grey if it differs between prey presence in diet and prey selectivity.
-green if significant (p value < 0.05).
+The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
 Pseudo-R^2^ (%) approximates the percent variance explained by the model.

### 2019-08-30 Manuscript_postsubmission.Rmd
added post submission version of manuscript to include further improvements and corrections

--- 2019-08-28 manuscript_clean.Rmd
@@
 In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
+Siphonophores bear four major nematocyst types in their tentacles and tentilla.
+The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule.
+These are typically found flanking the proximal end of the cnidoband.
+The most abundant type, haplonemes, have no distinct shaft, but similarly to heteronemes, their tubules have open tips and can be found in the cnidoband.
+Both heteronemes and haplonemes bear short spines along the tubule and can be toxic and penetrate the surface of some prey types.
+In the terminal filament, siphonophores bear two other types of nematocysts, characterized by their adhesive function, closed tip tubules, and lack of spines on the tubule.
+These are the desmonemes (a type of adhesive coiled-tubule spironeme), and rhopalonemes (a siphonophore-exclusive nematocyst type with wide tubules).
 
@@
 In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
-When fitting all covariance terms simultaneously (Appendix 20.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities.
+When fitting all covariance terms simultaneously (Appendix 19.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities.
 This excluded many of the morphometric characters which are linearly dependent on other characters.
@@
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
+Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 19).
 Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
@@
 
-The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
+The variance covariance matrices (Appendix 19.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
 \@ref(figure8)a.
@@
 These results were not very sensitive to transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
-When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.6).
+When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 19.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 19.6).
 
@@
 In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections.
-We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript.
+We thank Dennis Pilarczyk for organizing the prey selectivity data, Michael Landis for helping design the Bayesian analyses, and Joaquin Nunez for reviewing this manuscript.
 Furthermore, we thank Elizabeth D.

### 2019-10-31 Manuscript_postsubmission.Rmd
revamping the manuscript for re-submission, making shortened version and separate supplement for stuff removed from the main manuscript

@@
 bibliography: manuscript.bib
-csl: systematic-biology.csl
+csl: the-american-naturalist.csl
 site: "bookdown::bookdown_site"
@@
 Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
+We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
 In addition, we generated hypotheses about the diets of understudied siphonophore species based on these characters.

### 2019-10-31 Manuscript_short.Rmd
revamping the manuscript for re-submission, making shortened version and separate supplement for stuff removed from the main manuscript

--- 2019-10-31 Manuscript_postsubmission.Rmd
@@
 bibliography: manuscript.bib
-csl: the-american-naturalist.csl
+csl: systematic-biology.csl
 site: "bookdown::bookdown_site"
@@
   - \doublespacing
+  - \usepackage{natbib}
+  - \citep
 ---
@@
 We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-In addition, we generated hypotheses about the diets of understudied siphonophore species based on these characters.
 Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
@@
 
+![\label{figure1} Siphonophore anatomy.
+A - *Nanomia* sp.
+siphonophore colony (photo by Catriona Munro).
+B,C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
+D - *Nanomia* sp.
+Tentillum illustration and main parts.
+E - Differential interference contrast micrograph of the tentillum illustrated in D.
+F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum.
+Undischarged to the left, discharged to the right.](Figures_final/figure1.jpg)
+
   Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
@@
 
-In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures.
-In particular, we aim to address the evolutionary origins of giant tentilla, the character integration of tentilla, the evolution of the extreme shapes of siphonophore nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
-
   In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.
-
-![\label{figure1} Siphonophore anatomy.
-A - *Nanomia* sp.
-siphonophore colony (photo by Catriona Munro).
-B,C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
-D - *Nanomia* sp.
-Tentillum illustration and main parts.
-E - Differential interference contrast micrograph of the tentillum illustrated in D.
-F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum.
-Undischarged to the left, discharged to the right.](Figures_final/figure1.jpg)
 
@@
 Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
-
-In order to observe the discharge behavior of different tentilla, we recorded high speed footage (1000-3000 fps) of tentillum and nematocyst discharge by live siphonophore specimens (26 species) using a Phantom Miro 320S camera mounted on a stereoscopic microscope.
-We mechanically elicited tentillum and nematocyst discharge using a fine metallic pin.
-We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (µm), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data in Appendix 4).
 
@@
 
-To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
-This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, soft/hard bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
-Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
-We tackled this by transforming the absent states to zeroes.
-This approach allows us to incorporate all the data, but creates an attraction bias between small character states (*e.g.* small tentilla) and absent states (*e.g.* no tentilla).
-Absent characters are likely to be very biologically relevant to prey capture and we believe they should be accounted for in a predictive approach.
-We limited the number of linear discriminant functions retained to the number of groupings in each case.
-We selected the number of principal components retained using the a-score optimization function (R adegenet::optim.a.score) [@jombart2010discriminant] with 100 iterations, which yielded more stable results than the cross validation function (R adegenet::xval).
-This optimization aims to find the compromise value with highest discrimination power with the least overfitting.
-From these DAPCs we obtained the highest contributing morphological characters to the discriminaton (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
-For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (Appendix 15).
-In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
-We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary] (in Appendix 11).
-
-In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
-This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters.
-In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
-
 In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
@@
 ## Results {-}
-
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores clustered by similarity (raw data in Appendix 3).
-Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.](Figures_final/figure3.jpg)
 
@@
 
-*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (Appendix 15.1).
-We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (Fig.
-\@(figure6)).
-This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa*, and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
-
-Table 2.
-Discriminant analysis of principal components for the presence of specific prey types using the morphological data.
-Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest.
-Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
-The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
-Pseudo-R^2^ (%) approximates the percent variance explained by the model.
-
-```{r tab2, echo=FALSE, out.width='60%'}
-knitr::include_graphics('Final_tables/table2.png')
-```
-
-  When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
-The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
-Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2), revealing the sign of their predictive relationship to each prey type.
-We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
-While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (Appendix 15), specialization on fish or large crustacean prey can be fully disentangled (Appendix 15.1).
-For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
-Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2).
-
-  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC (in Appendix 15.1).
-Cell darkness indicates posterior probability of belonging to each guild.
-Training data set transformed so inapplicable states are computed as zeroes.
-Species ordered and colored according to their predicted feeding guild.](Figures_final/figure6.jpg)
-
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (Appendix 12).
-Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
-74% of characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K > 1.
-67% of characters support BM models, indicating a history of neutral constant divergence.
-No relationship between phylogenetic signal and BM model support was found.
-Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time.
-No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).
-
-![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
-Some branch lengths were modified from the Bayesian chronogram to improve readability.
-The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
-In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)
-
-The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (Appendix 18), and summarized in Figure 7.
-Haploneme nematocysts are likely ancestrally present in siphonophore tentacles, since they are present in the tentacles of many other hydrozoans.
-Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
-Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
-
-  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure4)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
-Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
-\@ref(figure7)).
-Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis].
-The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see Fig.
-\@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bears no other nematocyst type (Fig.
-\@ref(figure1)).
-These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
-The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig.
-\@ref(figure2)).
-This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
-Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
-While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
-Nonetheless, they have spreaded over a broad span of variation in nematocyst and cnidoband sizes.
-
-![\label{figure8} A.
-Correlogram showing strength of ordinary (upper triangle) and phylogenetic (lower triangle) correlations between characters.
-Both size and color of the circles indicate the strength of the correlation (R^2^).
-B.
-Scatterplot of phylogenetic correlation against ordinary correlation showing a strong linear relationship (R^2^ = 0.92, 95% confidence between 0.90 and 0.93).
-Light red and blue boxes indicate congruent negative and positive correlations respectively.
-Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](Figures_final/figure8.jpg){height=600px}
-
 *Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
 The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it.
-Of the phylogenetic correlations (Fig.
-\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
-\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
-Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
-Similarly, of the across-species correlations, 49.1% were >0.5 and only 1.5% were < -0.5.
-We found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
-Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
-These disparities can be caused by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
-However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54).
-Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
-
 The variance covariance matrices (Appendix 19.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
@@
 Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
-
-![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.
-A.
-Variance explained by each variable in the PC1-PC2 plane.
-Axis labels include the phylogenetic signal (K) for each component and p-value.
-B.
-Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg){height=600px}
-
-  In the non-phylogenetic PCA morphospace using only simple characters (Fig.
-\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
-In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
 
@@
 No clear regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
-
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in Appendix 4.
-While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
-For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
-
-  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
-Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
-Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
 
@@
 
-  Tentillum size, as well as the majority of the characters studied, supported BM evolutionary models.
-There are two alternative hypotheses about the generative process of BM.
-One hypothesis would suggest that these characters are not under selection, and therefore diverging neutrally [@lande1976natural].
-The second hypothesis suggests that they are under selection, but the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns across the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, since when a diet-driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
-
   Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
@@
 
-In parallel with haploneme shape, heteroneme shape evolution also presents a single, large, early transition towards elongation.
-While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids [@totton1965synopsis], hypothetically used for defense rather than for prey capture.
-These stenotele heteronemes are rounded like those found in pyrostephids and apolemiids, which is consistent with the story of a single transition leading to the elongated heteronemes in the stem of Tendiculophora.
-
   The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
@@
 However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
-
-Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g.
-stenoteles, mastigophores, birhopaloids).
-In addition to the tentacles, siphonophores may bear nematocysts in other parts of the colony (gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
-In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations.
-Nonetheless, siphonophores have evolved unique nematocyst types and subtypes, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
-Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not yet been found in any other tissue of any other organism.
-The gain of extreme elongation in the haplonemes of Tendiculophora can be interpreted as part of the character shift to a novel anisorhiza subtype.
-
-*Diversity of discharge dynamics* – A fundamental corollary in functional morphology is that structural morphology determines functional performance [@wainwright1994ecological].
-We expected the discharge dynamics exhibited by siphonophore tentilla should vary with their morphological diversity.
-Our results are consistent with this expectation, and we observe, for example, that cnidoband size largely correlates with cnidoband discharge speed.
-This suggests that prey escape response speed may determine the minimum cnidoband length for successful capture.
-
-*Insights from tentillum morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts is remarkable, both in their range of shapes and sizes, as in the dimensions and subtypes of the nematocysts they bear.
-Siphonophores bear the largest nematocysts among Hydrozoans.
-The largest nematocysts in our dataset (*Bargmannia lata* by volume and *Resomia dunni* by length), are the largest of all nematocysts reported for cnidarians, and therefore possibly the largest intracellular organelles among all living things.
-
-  In addition to the insights produced in this study, the newly collected morphological data provide a unique resource for future studies, and a reference dataset for siphonophore identification.
-Many conspicuous categorical characters in siphonophore tentilla are singularly diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the bioluminescent lures of *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the buoyant medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
-\@ref(figure7)).
-Some categorical characters are synapomorphic diagnostic characters for large clades, such as the proximal tentillum heteronemes of Eucladophora, the elastic strand, rhopalonemes, and desmonemes of Tendiculophora, the larval tentilla of Euphysonectae, the two-sized isorhizas of Cystonectae, the saccus canal of Pyrostephidae, or the seven rows of anisorhizas in Calycophorae.
-These characters should be used together with the classical nectophore and bract characters to identify species or at least impute phylogenetic affiliation from incomplete material.
 

### 2019-10-31 Supplement_forShort.Rmd
revamping the manuscript for re-submission, making shortened version and separate supplement for stuff removed from the main manuscript

--- 2019-08-28 manuscript_clean.Rmd
@@
 
-# The Evolution of Siphonophore Tentilla as Specialized Tools for Prey Capture {-}
-
-Alejandro Damian-Serrano^1^^,‡^, Steven H.D. Haddock^2^, Casey W. Dunn^1^
-
-^1^ Yale University, Department of Ecology and Evolutionary Biology, 165 Prospect St., New Haven, CT 06520, USA
-
-^2^ Monterey Bay Aquarium Research Institute, 7700 Sandholdt Rd., Moss Landing, CA 95039, USA
-
-\‡ Corresponding author: Alejandro Damian-Serrano, email: alejandro.damianserrano@yale.edu
-
-## Abstract {-}
-
-Predators have evolved dedicated body parts to capture and subdue prey.
-As different predators specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms.
-Studying the evolution of predation is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation.
-Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well, capturing prey with their tentilla (tentacle side branches).
-Earlier work has shown that extant siphonophore diets correlate with the different morphologies and sizes of their tentilla and nematocysts.
-We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high-speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
-Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
-In addition, we generated hypotheses about the diets of understudied siphonophore species based on these characters.
-Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This study contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
-
-## Keywords {-}
-
-Siphonophores, tentilla, nematocysts, predation, specialization, character evolution
-
-##   {-}
-
-  Most animal predators have characteristic biological tools that they use to capture and subdue prey.
-Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
-The functional morphology of these structures tend to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
-Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.* avoidance, escape, protective barriers) leads to modifications that can counter those defenses The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
-Understanding the relationships between predatory specializations and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
-
-  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
-\@ref(figure1)).
-These present a significant morphological variation across species [@mapstone2014global] (Fig.
-\@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
-A siphonophore is a colony bearing many feeding polyps (Fig.
-\@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
-Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla.
-While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
-When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy].
-In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
-
-  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
-This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
-
-Specialization is often thought to be an evolutionary ‘dead end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
-However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition] and resource switching [@hoberg2008macroevolutionary].
-Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
-
-  The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
-Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
-Contemporary underwater sampling technology provides an unprecedented opportunity to explore the trophic ecology [@choy2017deep] and functional morphology [@costello2015multi] of siphonophores.
-In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved].
-These advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.
-
-  The few pioneering studies that have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
-[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
-These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
-We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
-Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
-
-In addition, our study design allows us to address other interesting questions about the morphology and evolution of these unique structures.
-In particular, we aim to address the evolutionary origins of giant tentilla, the character integration of tentilla, the evolution of the extreme shapes of siphonophore nematocysts [@thomason1988allometry], and the mechanical implications of tentillum morphologies on cnidoband discharge.
-
-  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.
-
-![\label{figure1} Siphonophore anatomy.
-A - *Nanomia* sp.
-siphonophore colony (photo by Catriona Munro).
-B,C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
-D - *Nanomia* sp.
-Tentillum illustration and main parts.
-E - Differential interference contrast micrograph of the tentillum illustrated in D.
-F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum.
-Undischarged to the left, discharged to the right.](Figures_final/figure1.jpg)
-
-![\label{figure2} Tentillum diversity plate.
-The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow).
-Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species.
-A - *Erenna laciniata*, 10x.
-B - *Lychnagalma utricularia*, 10x.
-C - *Agalma elegans*, 10x.
-D - *Resomia ornicephala*, 10x.
-E - *Frillagalma vityazi*, 20x.
-F - *Bargmannia amoena*, 10x.
-G - *Cordagalma* sp., reproduced from Carré 1968.
-H - *Lilyopsis fluoracantha*, 20x.
-I - *Abylopsis tetragona*, 20x.](Figures_final/figure2.jpg)
-
-## Methods {-}
-
-*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Appendix 1).
-These specimens were collected intact across many years of fieldwork expeditions, using  blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
-Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted onto slides with Canada Balsam or Permount mounting media.
-The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
-Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
-We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to quantify.
-We measured at least one specimen for 96 different species (Appendix 3, Fig.
-\@ref(figure3)).
-Of these, we selected 38 focal species across clades based on specimen availability and phylogenetic representation.
-Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
-
-In order to observe the discharge behavior of different tentilla, we recorded high speed footage (1000-3000 fps) of tentillum and nematocyst discharge by live siphonophore specimens (26 species) using a Phantom Miro 320S camera mounted on a stereoscopic microscope.
-We mechanically elicited tentillum and nematocyst discharge using a fine metallic pin.
-We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (µm), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data in Appendix 4).
-
-*Siphonophore phylogeny* – The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
-The gene sequences we used in this study are available online (accession numbers in Appendix 5).
-Some of the sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
-Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
-(MK958599) sequenced by Lynne Christianson were included and accessioned to NCBI.
-We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
-We inferred a Maximum Likelihood (ML) phylogeny (Appendix 6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
-We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
-to assess relative model fit.
-ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (Appendix 7 and 9), which was topologically congruent with the unconstrained ML tree.
-The *alpha* priors were selected to minimize prior load in site variation.
-
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced fully congruent topologies (Appendix 6 and 7)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (Appendix 8).
-Scripts available in Appendix 9.
-
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
-Anela Choy (Appendix 10).
-We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
-eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
-Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
-In order to detect coarse-level patterns in the feeding habits, the data were merged into feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
-These were selected to minimize the number of categories while keeping the most different types of prey separate.
-We extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (Appendix 11).
-
-*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
-Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
-Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
-All *Nanomia* sp.
-observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
-We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it (Appendix 3).
-R scripts available in Dryad.
-For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
-We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.
-
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
-We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (Appendix 12).
-We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (Appendix 13).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12).
-We reconstructed ancestral states using Maximum Likelihood (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
-R scripts available in Dryad.
-
-In order to study the evolution of predatory specialization, we reconstructed components of the diet and prey selectivity on the phylogeny using ML (R phytools::anc.ML).
-To identify evolutionary associations of diet with tentillum and nematocyst characters, we compared the performance of a neutral evolution model to that of a diet-driven directional selection model.
-First, we collapsed the diet data into the five feeding guilds mentioned above (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
-Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
-The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
-Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
-Finally, we compared their AICc support values to select the best fitting model (Appendix 14).
-
-To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (Appendix 17).
-In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
-To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting].
-To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
-To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
+## Supplementary Methods {-}
 
@@
 
-In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
-When fitting all covariance terms simultaneously (Appendix 20.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities.
-This excluded many of the morphometric characters which are linearly dependent on other characters.
-Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes.
-These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 20).
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
-
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
-In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (Appendix 16).
-
-## Results {-}
+## Supplementary Results {-}
 
@@
 Values scaled by character.](Figures_final/figure3.jpg)
-
-*Phylogeny* – Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the 18S+16S tree.
-The topology of the constrained tree presented here (Fig.
-\@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
-
-![\label{figure4} Bayesian time-tree built from 18S + 16S concatenated sequences.
-Branch lengths estimated using relaxed molecular clock.
-Species names in red indicate replicated representation in the morphology data.
-Species marked with an asterisk were recorded using high speed video.
-Nodes labeled with bayesian posteriors (BP).
-Green circles indicate BP = 1.
-Blue circles indicate nodes constrained to be congruent with (Munro *et al.* 2018).
-Tips with black squares indicate the species with transcriptomes used in (Munro *et al.* 2018).
-Tips with grey squares indicate genus-level correspondence to taxa included in (Munro *et al.* 2018).
-The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.jpg){height=600px}
-
-  We retained the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], such as Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
-In addition, we define two new clades within Codonophora (Fig.
-\@ref(figure4)): Eucladophora as the clade containing *Agalma elegans* and all taxa that are more closely related to it than to *Apolemia lanosa*, and Tendiculophora as the clade containing *Agalma elegans* and all taxa more closely related to it than to *Bargmannia elongata*.
-Eucladophora is characterized by bearing spatially differentiated tentilla with proximal heteronemes and a narrower terminal filament region.
-The etymology derives from the Greek *eu*+*kládos*+*phóros* for “true branch bearers”.
-Tendiculophora are characterized by bearing rhopalonemes and desmonemes in the terminal filament, having a pair of elastic strands, and developing proximally detachable cnidobands.
-The etymology of this clade is derived from the Latin *tendicula* for “snare or noose” and the Greek *phóros* for "carriers".
-
-*Evolutionary dynamics between diet and tentillum morphology* – Reconstructions of feeding guilds shows that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
-\@ref(figure5)).
-Large crustacean specialists evolve into generalists twice independently, supporting hypothesis 3.
-Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2.
-Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
-
-The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (Appendix 14).
-These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
-Most of these characters are found exclusively in Tendiculophora, thus this may reflect processes that could be unique to this subtree.
-Five characters including cnidoband length, cnidoband shape, and haploneme length show maximal support for a diet-driven single-optimum OU model.
-The remaining 15 characters support BM (or OU with marginal AICc difference with BM).
-
-![\label{figure5} Left - Subset phylogeny showing the mapped feeding guild regimes that were used to inform the *OUwie* analyses.
-Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
-Diet data were obtained from the literature review in Appendix 10.](Figures_final/figure5.jpg)
-
-  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig.
-\@ref(figure5), right).
-Shifts toward ostracod presence in diet correlated with reductions in pedicle width and total haploneme volume.
-Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
-Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (Appendix 17).
-
-  Phylogenetic regressions of continuous characters against prey selectivity data produced additional insights.
-Fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
-Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
-Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles and elastic strands.
-Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
-Heteroneme length and elongation also correlated negatively with chaetognath selectivity.
-
-  When some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] were tested for correlated evolution (Table 1), we found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
-The latter is likely a product of the larger species richness of crustacean-eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.
-
-\
-
-Table 1. Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.
-
-```{r tab1, echo=FALSE, out.width='100%'}
-knitr::include_graphics('Final_tables/table1.png')
-```
-\
 
@@
 
-*Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
-The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it.
-Of the phylogenetic correlations (Fig.
+*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (Fig.
 \@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
@@
 
-The variance covariance matrices (Appendix 20.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
-\@ref(figure8)a.
-However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
-These results were not very sensitive to transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 20.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
-When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 20.6).
-
-Under the majority of SIMMAP outcomes, large crustaceans specialists are the first regime to appear, and other regimes evolve in a shift from this ancestral specialization.
-Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
-With the appearance of generalists (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
-In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
-When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which in turn developed a strong positive relationship with tentillum size.
-In other words, as tentilla get smaller in this group, heteronemes get shorter and haplonemes get larger.
-The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*.
-With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positively correlation.
-Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
-
-![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.
-A.
-Variance explained by each variable in the PC1-PC2 plane.
-Axis labels include the phylogenetic signal (K) for each component and p-value.
-B.
-Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg){height=600px}
-
-  In the non-phylogenetic PCA morphospace using only simple characters (Fig.
-\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
-In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
-
-*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
-There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
-\@ref(figure10).
-Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
-In this clade, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
-\@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
-
-![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled).
-Orange area delimits rod-shaped haplonemes, blue area covers oval and round shaped haplonemes.
-Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
-Species nodes in red were manually added to the plot.
-Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
-Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.
-Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)
-
-  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of variance in their shifts along the branches of the phylogeny.
-However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig.
-\@ref(figure4)).
-BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia*.
-For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
-\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects.
-Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
-Most of these taxa have rod-shaped anisorhizas, but *Erenna* has oval ones).
-No clear regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
-
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in Appendix 4.
-While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
-For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
-
-  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
-Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
-Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
-
-## Discussion {-}
-  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niches, and identify the morphological characters that evolve with changes in prey type.
-We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
-In addition, we produced novel findings on tentillum morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
-
-*Evolution of tentillum morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as trophic intermediaries between smaller zooplankton and higher trophic level predators.
-Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
-Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
-Predators that use morphologically similar tools for prey capture tend to capture similar prey, thus their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
-However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
-We hypothesize that siphonophores have escaped this by specializing on different prey resources.
-
-According to our reconstructions, the evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
-Several studies (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by phenotypic specialization.
-Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
-Among the evolutionary hypotheses considered, we find support for both hypotheses 2 (specialist resource switching) and 3 (specialist to generalist), but no support for hypothesis 1 (generalist to specialist).
-The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
-This strategy is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
-
-  One of the most common prey items found in siphonophore diets is copepods (Fig.
-\@ref(figure5)).
-Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
-These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
-Tentilla are expensive single-use structures, therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
-*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia* spp.
-This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization on smaller prey.
-
-[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
-Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
-obs.), a common feature of piscivorous cnidarians like cystonects or cubozoans.
-
-[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
-The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and our unpublished observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
-Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
-In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
-
-When we tested the diet-morphology correlation hypotheses supported in the literature from a macroevolutionary perspective (Table 1), we found that most of them were consistent with correlated evolution.
-The ecomorphological association between rhopalonemes, desmonemes, and crustacean eaters was not congruent with a scenario of correlated evolution.
-This is probably due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes but which effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
-
-While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available.
-Moreover, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
-When interpreting these results, it is important to remember that diet is a product of environmental prey availability and predator selectivity.
-Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for this study.
-For example, tentacle-deploying behavior, positioning in the water column, sensitivity thresholds for nematocyst discharge, or chemical cues to ingest a captured animal.
-Further observations on these behaviors in the field are necessary to assess their relative importance in determining dietary composition.
-In addition to behavior, there is much biochemistry in the prey capture and digestion processes that remains unexplored.
-Part of the success in siphonophore prey capture is likely determined by the effectivity of the toxins delivered by the nematocysts on different taxa.
-Comparative toxin assays and venom protein evolution studies would shed light on this question.
-Moreover, siphonophore trophic specialization may have brought changes in the digestive biochemistry of gastrozooids and palpons.
-A comparison of the gene expression levels for different enzymes in the gastrozooids of different species, together with digestive enzyme sequence evolution studies, and a toxicological assay of the different venoms in siphonophore nematocysts on different prey taxa, would provide a great complement to our results.
-
-*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
-Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
-The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
-While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.
-This reveals the need to extensively characterize siphonophore diets and feeding habits.
-In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
-Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
-In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
-The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
-
-*Phenotypic integration of siphonophore tentilla* – Many tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution].
-Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations [@wagner2000evolutionarily].
-In addition, these sub-structures must fit and work together in synchrony to ensnare prey successfully (functional integration).
-Character complexes that satisfy these conditions tend to be phenotypically integrated.
-Phenotypic integration is the set of functional and genetic correlations among the traits of an organism [@pigliucci2003phenotypic].
-These correlations have been hypothesized to direct and constrain adaptive evolution [@wagner2000evolutionarily].
-The siphonophore tentillum morphospace has a fairly low extant dimensionality due to an evolutionary history with many synchronous, correlated changes.
-This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve function.
-
-  Structural correlations within the tentillum are expected from shared regulatory networks within a common developmental bud (budding tentilla in the tentacle).
-Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin.
-None of these explanations for correlated evolution are surprising, nor require natural selection.
-However, we also found correlations between nematocyst and tentillum characters.
-Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum.
-These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid).
-Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
-Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies.
-Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
-
-  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated, but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
-This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).
-
-  While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
-This evolution of character relationships can allow lineages to explore new regions of the morphospace and facilitate the appearance of ecological novelties.
-Our results show that the patterns of phenotypic integration in siphonophore tentilla vary among clades, and appear to display different relationships across shifting feeding specializations.
-Similarly to what has been found in the feeding morphologies of fish [@collar2005comparative;@revell2009phylogenetic], siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
-For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring small crustaceans or fish.
-Finally, the evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today across siphonophores.
-
-*Evolutionary history of tentillum morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
-This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
-*Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
-Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review].
-Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
-The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
-
-  Tentillum size, as well as the majority of the characters studied, supported BM evolutionary models.
-There are two alternative hypotheses about the generative process of BM.
-One hypothesis would suggest that these characters are not under selection, and therefore diverging neutrally [@lande1976natural].
-The second hypothesis suggests that they are under selection, but the adaptive landscape was rapidly shifting [@hansen1996translating], without leaving clear patterns across the phylogeny.
-Some of the BM supported characters are likely to have evolved under the second hypothesis, since when a diet-driven regime tree was provided, these characters preferentially supported an OU model (Appendix 14).
-
-  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
-The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.
-
-  The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-In addition, our work identifies an interesting example of convergent evolution.
-The region of the tentillum morphospace (Fig.
-\@ref(figure9)) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
-Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
-Unlike calycophorans, they lack paired elongate microbasic mastigophores.
-Instead, they bear three elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
-Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
-Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
-The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-Our DAPCs predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.
-
-*Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among the Hydrozoa remains an unresolved question [@munro2018improved].
-The most recent work on this front sets them as sister group to all other Hydroidolina [@kayal2015phylogenetic].
-Therefore, there is a great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
-This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
-One such character is the shape of haploneme nematocysts.
-A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
-This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation].
-Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
-Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
-Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
-
-In parallel with haploneme shape, heteroneme shape evolution also presents a single, large, early transition towards elongation.
-While cystonects do not bear heteronemes in their tentacles, *Physalia physalis* bears stenoteles in other zooids [@totton1965synopsis], hypothetically used for defense rather than for prey capture.
-These stenotele heteronemes are rounded like those found in pyrostephids and apolemiids, which is consistent with the story of a single transition leading to the elongated heteronemes in the stem of Tendiculophora.
-
-  The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
-Elongate nematocysts can be tightly packed into cnidobands.
-We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
-Among these, are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
-We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade.
-However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
-
-Some siphonophore clades have more nematocyst types than others in the tentacles (Tendiculophora has 4 types, Cystonectae and Apolemiidae have 1), or different subtypes (e.g.
-stenoteles, mastigophores, birhopaloids).
-In addition to the tentacles, siphonophores may bear nematocysts in other parts of the colony (gastrozooids, papons, palpacles, bracts, nectophores, and gonozooids) [@totton1965synopsis].
-In this paper we only look at the presence of nematocyst types in the tentacles, therefore the gains and losses reported are not necessarily morphological innovations, but developmental allocations.
-Nonetheless, siphonophores have evolved unique nematocyst types and subtypes, not present in any other cnidarian, such as the two types of rhopalonemes (acrophores and anacrophores), and the haploneme homotrichous anisorhizas [@werner1965nesselkapseln].
-Both these nematocyst types evolved in the stem to Tendiculophora, and are likely morphological innovations, since they have not yet been found in any other tissue of any other organism.
-The gain of extreme elongation in the haplonemes of Tendiculophora can be interpreted as part of the character shift to a novel anisorhiza subtype.
-
-*Diversity of discharge dynamics* – A fundamental corollary in functional morphology is that structural morphology determines functional performance [@wainwright1994ecological].
-We expected the discharge dynamics exhibited by siphonophore tentilla should vary with their morphological diversity.
-Our results are consistent with this expectation, and we observe, for example, that cnidoband size largely correlates with cnidoband discharge speed.
-This suggests that prey escape response speed may determine the minimum cnidoband length for successful capture.
-
-*Insights from tentillum morphology* – The measurements taken illustrate that the morphological diversity of siphonophore tentilla and nematocysts is remarkable, both in their range of shapes and sizes, as in the dimensions and subtypes of the nematocysts they bear.
-Siphonophores bear the largest nematocysts among Hydrozoans.
-The largest nematocysts in our dataset (*Bargmannia lata* by volume and *Resomia dunni* by length), are the largest of all nematocysts reported for cnidarians, and therefore possibly the largest intracellular organelles among all living things.
-
-  In addition to the insights produced in this study, the newly collected morphological data provide a unique resource for future studies, and a reference dataset for siphonophore identification.
-Many conspicuous categorical characters in siphonophore tentilla are singularly diagnostic, such as: the fluorescent lures of *Resomia ornicephala*, the bioluminescent lures of *Erenna* species, the unique branched vesicle of *Frillagalma vityazi*, the buoyant medusa-resembling vesicle of *Lychnagalma* with 8 pseudo-tentacles, the zig-zag morphology of *Resomia* species, the inverted orientation of *Physophora* cnidobands, the button-like tentilla of *Physalia*, or the acorn-shaped minute tentilla of *Cordagalma* species (Fig.
-\@ref(figure7)).
-Some categorical characters are synapomorphic diagnostic characters for large clades, such as the proximal tentillum heteronemes of Eucladophora, the elastic strand, rhopalonemes, and desmonemes of Tendiculophora, the larval tentilla of Euphysonectae, the two-sized isorhizas of Cystonectae, the saccus canal of Pyrostephidae, or the seven rows of anisorhizas in Calycophorae.
-These characters should be used together with the classical nectophore and bract characters to identify species or at least impute phylogenetic affiliation from incomplete material.
-
-## Conclusions {-}
-
-  Siphonophores have diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
-With the evolution of diversified prey type specializations comes the evolution of morphologies adapted to the challenges posed by different prey.
-The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.
-While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We conclude that the siphonophores were able to become abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
-
-## Supplementary Materials {-}
-
-Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
-Online Appendices are available in [https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices](https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices)
-
-## Funding {-}
-
-  This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.
-Anela Choy).
-A.D.S.
-was supported by a Fulbright Spain Graduate Studies Scholarship.
-
-## Acknowledgements {-}
-
-We wish to thank the crew and scientists of the R/V Western Flyer, who participated in the collection of many of the specimens used in this study.
-We also want to thank Lynne Christianson and Shannon Johnson from the Monterey Bay Aquarium Research Institute for their assistance in the field as well as for sequencing some of the species included in this phylogeny.
-In addition, we wish to thank Lourdes Rojas, Daniel Drew, and Eric Lazo-Wasem for their assistance in imaging the fixed specimens and managing the collections.
-We thank Dennis Pilarczyk for organizing the prey selectivity data, and Joaquin Nunez for reviewing this manuscript.
-Furthermore, we thank Elizabeth D.
-Hetherington and C.
-Anela Choy for collating the data on siphonophore feeding and for reviewing the manuscript.
-Finally, we thank Philip Pugh, who confirmed many of our specimen identifications and taught us valuable knowledge about siphonophores.
-
 ## References {-}

### 2019-10-31 Post-Submission modifications/R_code_postsubmission.R

@@ -1,0 +1,1345 @@
+## LOAD PACKAGES ##
+#General
+library(tidyverse)
+library(magrittr)
+library(stringr)
+library(readr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(adegenet)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(colorRamps)
+library(PerformanceAnalytics)
+
+# Set paths to input data
+#setwd("~/tentilla_morph/Supplementary_Materials/Dryad/")
+
+#Load raw data
+read.csv("raw_morphology_data.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("raw_categorical_data.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
[…]

### 2019-11-06 Manuscript_short.Rmd
PLOS Bio resubmission prep

@@
   - \doublespacing
-  - \usepackage{natbib}
-  - \citep
 ---
@@
 We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high-speed video techniques, (2) built a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
+To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high-speed video techniques, (2) mapped these data to a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
 Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
@@
 
-## Methods {-}
-
-*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Appendix 1).
-These specimens were collected intact across many years of fieldwork expeditions, using  blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
-Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted onto slides with Canada Balsam or Permount mounting media.
-The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
-Thirty characters (defined in Appendix 2) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
-We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to quantify.
-We measured at least one specimen for 96 different species (Appendix 3, Fig.
-\@ref(figure3)).
-Of these, we selected 38 focal species across clades based on specimen availability and phylogenetic representation.
-Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
-
-*Siphonophore phylogeny* – The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
-The gene sequences we used in this study are available online (accession numbers in Appendix 5).
-Some of the sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
-Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
-(MK958599) sequenced by Lynne Christianson were included and accessioned to NCBI.
-We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
-We inferred a Maximum Likelihood (ML) phylogeny (Appendix 6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
-We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
-to assess relative model fit.
-ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (Appendix 7 and 9), which was topologically congruent with the unconstrained ML tree.
-The *alpha* priors were selected to minimize prior load in site variation.
-
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced fully congruent topologies (Appendix 6 and 7)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (Appendix 8).
-Scripts available in Appendix 9.
-
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
-Anela Choy (Appendix 10).
-We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
-eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
-Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
-In order to detect coarse-level patterns in the feeding habits, the data were merged into feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
-These were selected to minimize the number of categories while keeping the most different types of prey separate.
-We extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (Appendix 11).
-
-*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
-Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
-Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
-All *Nanomia* sp.
-observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
-We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it (Appendix 3).
-R scripts available in Dryad.
-For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
-We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.
-
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
-We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (Appendix 12).
-We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (Appendix 13).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (Appendix 12).
-We reconstructed ancestral states using Maximum Likelihood (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
-R scripts available in Dryad.
-
-In order to study the evolution of predatory specialization, we reconstructed components of the diet and prey selectivity on the phylogeny using ML (R phytools::anc.ML).
-To identify evolutionary associations of diet with tentillum and nematocyst characters, we compared the performance of a neutral evolution model to that of a diet-driven directional selection model.
-First, we collapsed the diet data into the five feeding guilds mentioned above (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
-Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
-The ML reconstruction was congruent with the consensus stochastic character mapping (Appendix 18).
-Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
-Finally, we compared their AICc support values to select the best fitting model (Appendix 14).
-
-To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (Appendix 17).
-In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
-To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting].
-To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
-To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
-
-In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
-When fitting all covariance terms simultaneously (Appendix 19.1-20.3), we selected the largest set of characters that would allow the analysis to run without computational singularities.
-This excluded many of the morphometric characters which are linearly dependent on other characters.
-Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes.
-These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (see Appendix 19).
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
-
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
-In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (Appendix 16).
-
 ## Results {-}
@@
 Species names in red indicate replicated representation in the morphology data.
-Species marked with an asterisk were recorded using high speed video.
-Nodes labeled with bayesian posteriors (BP).
+Species marked with a red asterisk were recorded using high speed video.
+Newly accessioned 16S data was used for species marked with a blue circle.
+Nodes labeled with Bayesian posteriors (BP).
 Green circles indicate BP = 1.
 Blue circles indicate nodes constrained to be congruent with (Munro *et al.* 2018).
+This phylogeny expands the taxon sampling of the (Munro *et al.* 2018) transcriptome tree and is congruent with it.
 Tips with black squares indicate the species with transcriptomes used in (Munro *et al.* 2018).
 Tips with grey squares indicate genus-level correspondence to taxa included in (Munro *et al.* 2018).
-The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.jpg){height=600px}
+The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
 
@@
 
-The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (Appendix 14).
+The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM15).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
@@
 Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
-Diet data were obtained from the literature review in Appendix 10.](Figures_final/figure5.jpg)
+Diet data were obtained from the literature review, available in the Dryad repository.](Figures_final/figure5.jpg)
 
@@
 Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
-Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (Appendix 17).
+Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (SM21).
 
@@
 
+*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
+We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (SM2).
+This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa*, and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
+
+Table 2.
+Discriminant analysis of principal components for the presence of specific prey types using the morphological data.
+Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest.
+Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
+The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
+Pseudo-R^2^ (%) approximates the percent variance explained by the model.
+
+```{r tab2, echo=FALSE, out.width='60%'}
+knitr::include_graphics('Final_tables/table2.png')
+```
+
 *Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
 The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it.
-The variance covariance matrices (Appendix 19.1-20.2) are congruent with the abundant positive correlations observed among simple measurement characters in Fig.
-\@ref(figure8)a.
+The variance covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
 However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
 These results were not very sensitive to transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (Appendix 19.4), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
-When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (Appendix 19.6).
+When we compared the rate covariance terms between characters across the different feeding guild regimes (SM41), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (SM42).
 
@@
 Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
+
+![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
+Some branch lengths were modified from the Bayesian chronogram to improve readability.
+The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
+In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
+The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)
+
+The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (SM), and summarized in \@ref(figure7).
+Haploneme nematocysts are likely ancestrally present in siphonophore tentacles, since they are present in the tentacles of many other hydrozoans.
+Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
+Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re].
+Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
+
+  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see main text Fig.
+3) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
+Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
+\@ref(figure7)).
+Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis].
+The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see main text Fig.
+3) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
+\@ref(figure7)), which bears no other nematocyst type (main text Fig.
+1).
+These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
+The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (main text Fig.
+2).
+This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
+Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
+While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
+Nonetheless, they have spreaded over a broad span of variation in nematocyst and cnidoband sizes.
 
@@
 Among the evolutionary hypotheses considered, we find support for both hypotheses 2 (specialist resource switching) and 3 (specialist to generalist), but no support for hypothesis 1 (generalist to specialist).
+This is consistent with the findings of recent studies on phytophagous insects [@nosil2002transition], where the rate of evolution from generalists to specialists is comparable to the reverse, thus specialization does not limit further evolution.
+However, [@nosil2005testing] found that ancestral reconstruction methods can be biased, and tend to infer higher transition rates toward the more frequent state.
+With this in mind, we should expect to find a predominance of transitions from generalists to specialists (the more common state across the tips).
+Nonetheless, we observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
+Our results are also consistent with [@hardy2014specialization]'s study on lepidopterans, where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
@@
 
+Our work identifies an interesting example of convergent evolution.
+The region of the tentillum morphospace (Supplementary Figure XX) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
+Unlike calycophorans, they lack paired elongate microbasic mastigophores.
+Instead, they bear three elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
+Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
+Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
+The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
+Our DAPCs (Supp.
+Fig XXX) predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.
+
 While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available.
@@
 A comparison of the gene expression levels for different enzymes in the gastrozooids of different species, together with digestive enzyme sequence evolution studies, and a toxicological assay of the different venoms in siphonophore nematocysts on different prey taxa, would provide a great complement to our results.
-
-*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
-Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
-The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
-While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.
-This reveals the need to extensively characterize siphonophore diets and feeding habits.
-In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
-Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
-In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
-The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
 
@@
 
-*Evolutionary history of tentillum morphology* – This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
-This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
-*Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
-Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review].
-Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
-The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
-
-  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
-The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.
-
-  The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-In addition, our work identifies an interesting example of convergent evolution.
-The region of the tentillum morphospace (Fig.
-\@ref(figure9)) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
-Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
-Unlike calycophorans, they lack paired elongate microbasic mastigophores.
-Instead, they bear three elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
-Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
-Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
-The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-Our DAPCs predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.
-
 *Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among the Hydrozoa remains an unresolved question [@munro2018improved].
@@
 Among these, are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
-We hypothesize that this packing-efficient haploeme morphology may have been a key innovation leading to the diversification of this clade.
+We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
 However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
@@
 Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We conclude that the siphonophores were able to become abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
+We find that the evolutionary diversification of tools for prey capture contributed to the diversification of trophic interactions.
+Therefore, we identify organismal trait evolution as a key driver in the emergence of food web complexity.
+
+## Materials and Methods {-}
+
+*Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Dryad repository).
+These specimens were collected intact across many years of fieldwork expeditions, using  blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
+Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted onto slides with Canada Balsam or Permount mounting media.
+The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
+Thirty characters (defined in SM5) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
+We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to quantify.
+We measured at least one specimen for 96 different species (see raw data by species in Dryad).
+Of these, we selected 38 focal species across clades based on specimen availability and phylogenetic representation.
+Three to five tentacle specimens from each one of these selected species were measured to capture intraspecific variation.
+
+*Siphonophore phylogeny* – While the main goal of this work is not to elucidate a novel phylogeny for Siphonophora, we did expand on the most recent transcriptome based phylogeny [@munro2018improved] to accommodate a larger taxon sampling.
+In order to do this, we ran a constrained analysis on an extensive 18S+16S dataset.
+The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
+The gene sequences we used in this study are available online (accession numbers in Dryad Repository).
+Some of the sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
+Two new 16S sequences for *Frillagalma vityazi* (MK958598) and *Thermopalia* sp.
+(MK958599) sequenced by Lynne Christianson using the primers from [@cunningham1993molecular] (read 3' to 5' F: TCGACTGTTTACCAAAAACATAGC , R:  ACGGAATGAACTCAAATCATGTAAG) were included and accessioned to NCBI.
+We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
+We inferred a Maximum Likelihood (ML) phylogeny (SM6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
+We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
+to assess relative model fit.
+ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
+Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9,SM11), which was topologically congruent with the unconstrained ML tree.
+The *alpha* priors were selected to minimize prior load in site variation.
+
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced fully congruent topologies (SM8, SM10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (SM11,SM12).
+Scripts available in the Dryad repository.
+
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
+Anela Choy (available in Dryad repository).
+We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
+eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
+Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
+In order to detect coarse-level patterns in the feeding habits, the data were merged into feeding guilds.
+The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+These were selected to minimize the number of categories while keeping the most different types of prey separate.
+We extracted copepod prey length data from [@purcell1984functions].
+To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in Dryad repository).
+
+*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
+Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
+Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
+All *Nanomia* sp.
+observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
+We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
+\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it.
+R scripts and summarized species-collapsed data available in the Dryad repository.
+For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
+We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.
+
+We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
+The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
+We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
+When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM13).
+We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM14).
+We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM13).
+We reconstructed ancestral states using Maximum Likelihood (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
+R scripts available in Dryad.
+
+In order to study the evolution of predatory specialization, we reconstructed components of the diet and prey selectivity on the phylogeny using ML (R phytools::anc.ML).
+To identify evolutionary associations of diet with tentillum and nematocyst characters, we compared the performance of a neutral evolution model to that of a diet-driven directional selection model.
+First, we collapsed the diet data into the five feeding guilds mentioned above (fish specialist, small crustacean specialist, large crustacean specialist, gelatinous specialist, generalist), based on which prey types they were observed consuming most frequently.
+Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
+The ML reconstruction was congruent with the consensus stochastic character mapping (SM31).
+Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
+Finally, we compared their AICc support values to select the best fitting model (SM15).
+
+To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (SM21).
+In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
+To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting].
+To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
+To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
+
+In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
+When fitting all covariance terms simultaneously (SM36-38), we selected the largest set of characters that would allow the analysis to run without computational singularities.
+This excluded many of the morphometric characters which are linearly dependent on other characters.
+Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (SM42).
+These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
+Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (SM43).
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
+
+To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+This function allowed us to incorporate more predictors than individuals.
+We generated discriminant functions for feeding guild, soft/hard bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
+From these DAPCs we obtained the highest contributing morphological characters to the discriminaton (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
+For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (SM16-20).
+In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
+We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary].
+Additional details on the optimization are available in the Supplementary Materials.
+
+To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
+In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
 
@@
 Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
-Online Appendices are available in [https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices](https://github.com/dunnlab/tentilla_morph/Supplementary_materials/Online_Appendices)
+Supplementary Materials are available in [https://github.com/dunnlab/tentilla_morph/Supplement_forShort.pdf](https://github.com/dunnlab/tentilla_morph/Supplement_forShort.pdf)
 

### 2019-11-06 Supplement_forShort.Rmd
PLOS Bio resubmission prep

@@
 fontsize: 12pt
+language:
+  label:
+    fig: "**Figure S**"
+    tab: "**Table S**"
 header-includes:
@@
 
+# Supplementary Materials File {-}
+
+Alejandro Damian-Serrano, Steven H.D. Haddock, Casey W. Dunn
+
 ## Supplementary Methods {-}
 
-To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
-This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, soft/hard bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (Appendix 15).
-Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
+DAPC optimization: Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
 We tackled this by transforming the absent states to zeroes.
@@
 This optimization aims to find the compromise value with highest discrimination power with the least overfitting.
-From these DAPCs we obtained the highest contributing morphological characters to the discriminaton (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
-For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (Appendix 15).
-In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
-We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary] (in Appendix 11).
 
@@
 
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores clustered by similarity (raw data in Appendix 3).
+![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores clustered by similarity (raw data in Dryad repository).
 Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
@@
 
-*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (Appendix 15.1).
-We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (Fig.
-\@(figure6)).
-This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa*, and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
+*Generating dietary hypotheses using tentillum morphology* – When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM\@ref(DAPCsofthard)).
+The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
+Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2 int he main text), revealing the sign of their predictive relationship to each prey type.
+We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
+While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (SM\@ref(DAPCfish),SM\@ref(DAPCcrustacean)), specialization on fish or large crustacean prey can be fully disentangled (SM\@ref(DPACguilds)).
+For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
+Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2 in the main text).
 
-Table 2.
-Discriminant analysis of principal components for the presence of specific prey types using the morphological data.
-Top quartile variable (character) contributions to the linear discriminants are ordered from highest to lowest.
-Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
-The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
-Pseudo-R^2^ (%) approximates the percent variance explained by the model.
-
-```{r tab2, echo=FALSE, out.width='60%'}
-knitr::include_graphics('Final_tables/table2.png')
-```
-
-  When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (Appendix 15.4).
-The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
-Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2), revealing the sign of their predictive relationship to each prey type.
-We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
-While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (Appendix 15), specialization on fish or large crustacean prey can be fully disentangled (Appendix 15.1).
-For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
-Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2).
-
-  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC (in Appendix 15.1).
+  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
 Cell darkness indicates posterior probability of belonging to each guild.
@@
 
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (Appendix 12).
+*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).
-
-![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
-Some branch lengths were modified from the Bayesian chronogram to improve readability.
-The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
-In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)
-
-The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (Appendix 18), and summarized in Figure 7.
-Haploneme nematocysts are likely ancestrally present in siphonophore tentacles, since they are present in the tentacles of many other hydrozoans.
-Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
-Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
-
-  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure4)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
-Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
-\@ref(figure7)).
-Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis].
-The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see Fig.
-\@ref(figure4)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bears no other nematocyst type (Fig.
-\@ref(figure1)).
-These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
-The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig.
-\@ref(figure2)).
-This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
-Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
-While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
-Nonetheless, they have spreaded over a broad span of variation in nematocyst and cnidoband sizes.
 
@@
 
-*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (Fig.
-\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
-\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
+*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (SM\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (SM\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
 Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
@@
 
+![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.
+A.
+Variance explained by each variable in the PC1-PC2 plane.
+Axis labels include the phylogenetic signal (K) for each component and p-value.
+B.
+Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg){height=600px}
+
+  In the non-phylogenetic PCA morphospace using only simple characters (SM\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
+In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
+
+*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
+While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
+For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
+This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
+
+  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
+Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
+Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
+
+## Supplementary Discussion {-}
+
+*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
+Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
+The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
+While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.
+This reveals the need to extensively characterize siphonophore diets and feeding habits.
+In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
+Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
+In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
+The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
+
+*Evolutionary history of tentillum morphology* –This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
+*Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
+Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review].
+Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
+The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
+
+  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
+The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
+In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.
+
+  The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
+An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
+The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
+
+\newpage
+
+## Supplementary Materials {-}
+
+![\label{appendix2} Character definitions. ](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Appendix2.png){height=500px}
+
+Other trees inferred in this work include:
+
+![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained.
+Node labels are bootstrap support values.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/MLunconstrained.png){height=300px}
+
+The constrained tree inferences utilized the following constrain topology:
+
+![\label{Transcriptome_constraint} Topology used to constrain analyses (minimal topological statements based on the incongruences between the unconstrained tree and Munro et al.
+(2018).
+](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/constrain.png){height=400px}
+
+![\label{ML_constrained} Constrained IQTree ML inference.
+Node labels are bootstrap support values.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/MLconstrained.png){height=300px}
+
+![\label{Bayes_unconstrained} Unconstrained Bayesian topology inference in RevBayes (node labels are Bayesian posteriors).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/BAYESunconstrained.png){height=300px}
+
+![\label{Bayes_constrained} Clade constrained Bayesian inference in RevBayes (node labels are Bayesian posteriors).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/BayesConstrained.png){height=300px}
+
+![\label{unconstrained_timetree} Unconstrained ultrametric Bayesian time tree branch length and topology inference in RevBayes (node labels are Bayesian posteriors).
+Arbitrary rooting.).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Unconstrained timetree.png){height=400px}
+
+![\label{constrained_timetree} Ultrametric Bayesian time tree branch length inference in RevBayes (node labels are bayesian posteriors).
+Topology clamped to the Bayesian constrained topology inference in \@ref{Bayes_constrained}.
+Tree rooted using outgroup constraint.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/constrainedTimetree.png){height=500px}
+
+\newpage
+
+![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character.
+Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}
+
+![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character.
+Cvar = coefficient of variation of the absolute value of the contrasts.
+Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances.
+Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node.
+Shgt = slope of the contrasts against node depth.
+Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.
+](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
+
+![\label{ModelSupportOUwie} Model support (delta AICc) for each morphological character analyzed on the feeding guild reconstruction regime tree.
+OU1 = Single-optimum Ornstein-Uhlenbeck.
+OUm = Multi-optima Ornstein-Uhlenbeck.
+Model adequacy scores calculated for the best supported model only.
+Msig = mean of squared contrasts.
+Cvar = coefficient of variation of the absolute value of the contrasts.
+Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances.
+Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node.
+Shgt = slope of the contrasts against node depth.
+Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/OUwie_modelsupport.png)
+
+\newpage
+
+DAPC discriminant analyses:
+
+![\label{DAPCguilds} DAPC for Feeding guilds.
+Six PCs retained after a-score optimization (100 iterations).
+Four LDA functions used.
+Discriminant power on training set: 100%.
+Prediction posterior distribution heat map in main text Figure 6.
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_guilds.png){height=500px}
+
+![\label{DAPCcopepods} DAPC for copepod presence in the diet.
+Eight PCs retained after a-score optimization (100 iterations).
+One LDA functions used.
+Discriminant power on training set: 95.4%.
+Grayscale heat map shows the posterior probability distribution of the predictions.
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_copepod.png)
+
+![\label{DAPCfish} DAPC for fish presence in the diet.
+Three PCs retained after a-score optimization (100 iterations).
+One LDA function used.
+Discriminant power on training set: 68.1%.
+Grayscale heat map shows the posterior probability distribution of the predictions.
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_fish.png)
+
+![\label{DAPCcrustacean} DAPC for large crustacean presence in the diet.
+Four PCs retained after a-score optimization (100 iterations).
+One LDA function used.
+Discriminant power on training set: 81.8%.
+Grayscale heat map shows the posterior probability distribution of the predictions.
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_crustacean.png)
+
+![\label{DAPCsofthard} DAPC for soft-bodied vs.
+hard bodied prey specialization.
+Six PCs retained after a-score optimization (100 iterations).
+Two LDA functions used.
+Discriminant power on training set: 90.9%.
+Grayscale heat map shows the posterior probability distribution of the predictions.
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_softhard.png)
+
+\newpage
+
+Ordinary and phylogenetic logistinc regression of morphological characters and the presence/absence of prey types:
+
+![\label{GLMs} Logistic regressions between continuous morphological characters and prey type presences.
+Ntaxa = number of taxa used in the analyses after removing taxa with missing diet data and inapplicable character states.
+phyloGLM = Phylogenetic generalized logistic regression model.
+GLM = Generalized logistic regression model.
+P = p-value.
+b = slope.
+Only cases with significant GLM fits were retained.
+Cells colored blue indicate phyloGLM p-value < 0.05.
+Cells colored green indicate GLM p-value < 0.05](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/PhyloGLM.png){height=300px}
+
+\newpage
+
+SIMMAP ancestral reconstructions of categorical characters:
+
+![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/tentillaPresenceSIM.png)
+
+![\label{SIMMAPproxhet} SIMMAP Cnidoband proximal heteroneme presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/proxhet_presence.png)
+
+![\label{SIMMAPdesmorhopalo} SIMMAP Desmoneme+Rhopaloneme presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/desmorhopalo_SIM.png)
+
+![\label{SIMMAPdischarge} SIMMAP Actively discharging cnidobands presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/discharge_SIM.png)
+
+![\label{SIMMAP_ES} SIMMAP Elastic strands presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Elasticstrands_SIM.png)
+
+![\label{SIMMAP_distalDesmo} SIMMAP Cnidoband distal desmonemes presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/distalDesmo_SIM.png)
+
+![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoaband phenotype presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)
+
+![\label{SIMMAP_HetType} SIMMAP Heteroneme type.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/hettype_SIM.png)
+
+![\label{SIMMAP_HapType} SIMMAP Haploneme type.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/haptype_SIM.png)
+
+![\label{SIMMAPguilds} SIMMAP Feeding guilds.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/guild_SIM.png)
+
+\newpage
+
+Bayesian Analysis of Macroevolutionary Mixtures (BAMM) results:
+
+![\label{BAMM_HetElon} Siphonophore ultrametric tree with estimated trait diversification rates of heteroneme elongation, estimated by BAMM.
+Yellow = Rate acceleration.
+Purple = Rate slowdown.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HetElon_BAMM.png)
+
+![\label{BAMM_HetElon_cred} Bayesian 95% credible rate regime shift set for heteroneme elongation.
+Red = rate acceleration.
+Blue = rate slowdown.
+f values are the fraction of the probability of the data accounted for.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HetElon_Cred.png)
+
+![\label{BAMM_HapElon} Siphonophore ultrametric tree with estimated trait diversification rates of haploneme elongation, estimated by BAMM.
+Yellow = Rate acceleration.
+Purple = Rate slowdown.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HapElon_BAMM.png)
+
+![\label{BAMM_HapElon_cred} Bayesian 95% credible rate regime shift set for haploneme elongation.
+Red = rate acceleration.
+Blue = rate slowdown.
+f values are the fraction of the probability of the data accounted for.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HapElon_Cred.png)
+
+\newpage
+
+Variance-Covariance Matrix analyses of phenotypic intergation and evolutionary modularity:
+
+![\label{VCV_NAZero} Rate covariance matrix for the whole tree using all taxa (45 species), transforming inapplicable states to zeroes.
+Covariances scaled to correlations.
+All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_Nazero.png)
+
+![\label{VCV_NAremove} Rate covariance matrix for the whole tree using only taxa without inapplicable states (24 species).
+Covariances scaled to correlations.
+All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_NAremove.png)
+
+![\label{VCV_dietaxa} Rate covariance matrix for the whole tree using only taxa with diet data (22 species), transforming inapplicable states to zeroes.
+Covariances scaled to correlations.
+All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_dietaxa.png)
+
+![\label{VCV_bestmodels} Best models (lowest AIC) supported in a pairwise character rate covariance analysis comparing correlated Brownian Motion models across the five selective regimes.
+Selective regimes were mapped onto the tree using an ancestral state reconstruction of the feeding guilds.
+Blank cells represent computationally singular contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVbestModels.png)
+
+![\label{VCV_ntaxa} Number of taxa used for each pairwise contrast in the VCV analyses, given the number of taxa without inapplicable states.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_ntaxa.png)
+
+![\label{VCV_regimes} Pairwise estimated rate covariance matrices across the five selective regimes, using only taxa with diet data.
+Covariances scaled to correlations.
+Selective regimes were mapped onto the tree (22 species with diet data) using a stochastic mapping of the feeding guilds.
+Tree is pruned to taxa with no inapplicable states for a given character pair.
+Not all regimes are represented in all contrasts.
+Question marks represent computationally singular contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_regimes.png){height=600px}
+
+![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the whole tree covariance matrix.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
+
+![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
+
+ ~ ~ ~
+
 ## References {-}

### 2019-11-18 Manuscript_short.Rmd
latest manuscript edits for PLOS Biology

@@
 bibliography: manuscript.bib
-csl: systematic-biology.csl
+csl: plos-biology.csl
 site: "bookdown::bookdown_site"
@@
 Predators have evolved dedicated body parts to capture and subdue prey.
-As different predators specialize on distinct prey taxa, their tools for prey capture diverge into a variety of adaptive forms.
+As a clade of predators specialize in distinct prey taxa, their tools for prey capture diversify into a variety of adaptive forms.
 Studying the evolution of predation is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation.
@@
 We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological traits from fixed siphonophore specimens using microscopy and high-speed video techniques, (2) mapped these data to a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between siphonophore nematocyst characters and prey type data from the literature.
-Our results show that siphonophore tentillum structure has strong evolutionary associations with prey type and size specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
-We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+To test this hypothesis, we: (1) measured multiple morphological characters from siphonophore tentacle specimens, (2) mapped these data to a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
+Our results show that the siphonophore tentillum morphology has strong evolutionary associations with prey type specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
+We found that predatory specialists can evolve into generalists and that specialists on one prey type have directly evolved into specialists on other prey types.
+With changes in trophic niche regimes, both trait optima and trait correlation patterns showed significant shifts.
 Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
@@
 
-##   {-}
+## Introduction {-}
 
@@
 Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
-The functional morphology of these structures tend to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
-Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.* avoidance, escape, protective barriers) leads to modifications that can counter those defenses The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
-Understanding the relationships between predatory specializations and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
+The functional morphology of these structures tends to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
+Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses.
+The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
+Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
 
-  Siphonophores (Cnidaria : Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
+  Siphonophores (Cnidaria: Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
 \@ref(figure1)).
-These present a significant morphological variation across species [@mapstone2014global] (Fig.
+These present significant morphological variation across species [@mapstone2014global] (Fig.
 \@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
@@
 \@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
-Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla.
+Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla (tentacle side branches).
 While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
@@
 In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
-Siphonophores bear four major nematocyst types in their tentacles and tentilla.
+Siphonophores bear four major nematocyst types in their tentacles and tentilla (Fig.
+\@ref(figure1)F)..
 The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule.
@@
 siphonophore colony (photo by Catriona Munro).
-B,C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
+B, C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
 D - *Nanomia* sp.
@@
 With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increased specialization on a variety of prey types in different siphonophore lineages.
+If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
 
-Specialization is often thought to be an evolutionary ‘dead end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
-However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition] and resource switching [@hoberg2008macroevolutionary].
+  Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
+However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition; @nosil2002transition] and resource switching [@hoberg2008macroevolutionary; @hardy2014specialization].
 Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
@@
 These advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.
-
-  The few pioneering studies that have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
-[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
-These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
-We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
-Furthermore, we hypothesize that with an extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
-
-  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.
 
@@
 
+  The few pioneering studies that have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
+These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
+We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
+Furthermore, we hypothesize that with extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
+
+  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.
+
 ## Results {-}
 
-*Phylogeny* – Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the 18S+16S tree.
+*Phylogeny* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with extensive taxonomic representation using ribosomal genes.
+Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the 18S+16S tree.
 The topology of the constrained tree presented here (Fig.
 \@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
+However, with the unprecedented inclusion of *Stephanomia amphytridis*, this phylogeny reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
 
 ![\label{figure4} Bayesian time-tree built from 18S + 16S concatenated sequences.
-Branch lengths estimated using relaxed molecular clock.
+Branch lengths estimated using a relaxed molecular clock.
 Species names in red indicate replicated representation in the morphology data.
-Species marked with a red asterisk were recorded using high speed video.
+Species marked with a red asterisk were recorded using high-speed video.
 Newly accessioned 16S data was used for species marked with a blue circle.
@@
 
-*Evolutionary dynamics between diet and tentillum morphology* – Reconstructions of feeding guilds shows that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
+*Evolutionary associations between diet and tentillum morphology* – Reconstructions of feeding guilds show that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
 \@ref(figure5)).
@@
 Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
-Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles and elastic strands.
-Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
-Heteroneme length and elongation also correlated negatively with chaetognath selectivity.
+Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles, and elastic strands.
+Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme numbers, and cnidoband coiledness.
+Heteroneme length and elongation also correlated negatively with chaetognath selectivity (SM21).
 
@@
 
-*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
+*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination between guilds, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
 We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (SM2).
-This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa*, and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
+This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
 
@@
 Logistic regressions and GLMs were fitted to predict prey type presence and selectivity respectively.
-The sign of the slope of each predictor is reported, marked with an asterisk if significant (p value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
+The sign of the slope of each predictor is reported, marked with an asterisk if significant (p-value < 0.05), and highlighted grey if it differs between prey presence in diet and prey selectivity.
 Pseudo-R^2^ (%) approximates the percent variance explained by the model.
@@
 *Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
-The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it.
-The variance covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
+The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (SM4).
+The variance-covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
 However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
-These results were not very sensitive to transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (SM41), we found that half (48%) of the character pairs presented distinct correlation coefficients across different regimes, indicating that the mode of phenotypic integration may also shift with trophic niche.
+These results were not sensitive to the transformation of inapplicable states and taxon sampling.
+When we compared the rate covariance terms between characters across the different feeding guild regimes (SM41), we found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
 When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (SM42).
 
-Under the majority of SIMMAP outcomes, large crustaceans specialists are the first regime to appear, and other regimes evolve in a shift from this ancestral specialization.
+Under the majority of SIMMAP outcomes, large crustaceans specialists are the ancestral regime, and allß other regimes evolve from this ancestral specialization.
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
@@
 The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*.
-With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positively correlation.
+With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positive correlation.
 Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
@@
 
-The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (SM), and summarized in \@ref(figure7).
-Haploneme nematocysts are likely ancestrally present in siphonophore tentacles, since they are present in the tentacles of many other hydrozoans.
+The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
+Haploneme nematocysts are likely ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
 Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
-Haplonemes were likely lost in the tentacles of *Apolemia*, but spherical isorhizas are retained in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, ancestral stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
+Haplonemes were likely lost in the tentacles of *Apolemia* but retained as spherical isorhizas in other *Apolemia* tissues [@siebert2013re].
+Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
 
-  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see main text Fig.
-3) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
+  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
+\@ref(figure3)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
 Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
@@
 Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis].
-The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, see main text Fig.
-3) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bears no other nematocyst type (main text Fig.
-1).
+The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, Fig.
+\@ref(figure3)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
+\@ref(figure7)), which bears no other nematocyst type (Fig.
+\@ref(figure1)).
 These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
-The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (main text Fig.
-2).
+The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig.
+\@ref(figure2)).
 This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
@@
 While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
-Nonetheless, they have spreaded over a broad span of variation in nematocyst and cnidoband sizes.
+Nonetheless, they have spread over a broad span of variation in nematocyst and cnidoband sizes.
 
@@
 There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
-\@ref(figure10).
+\@ref(figure10)).
 Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
-In this clade, evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
+In this clade, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
 \@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
@@
 ![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled).
-Orange area delimits rod-shaped haplonemes, blue area covers oval and round shaped haplonemes.
+Orange area delimits rod-shaped haplonemes, blue area covers oval and round-shaped haplonemes.
 Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
@@
 
-  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of variance in their shifts along the branches of the phylogeny.
+  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
 However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig.
 \@ref(figure4)).
-BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia*.
+BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
 For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
-\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects.
+\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (SM35).
 Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
 Most of these taxa have rod-shaped anisorhizas, but *Erenna* has oval ones).
-No clear regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
+No significant regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
 
 ## Discussion {-}
+
   The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niches, and identify the morphological characters that evolve with changes in prey type.
@@
 However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
-We hypothesize that siphonophores have escaped this by specializing on different prey resources.
+We hypothesize that siphonophores have escaped this by specializing in different prey resources.
 
 According to our reconstructions, the evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
-Several studies (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead end due to the constraints posed by phenotypic specialization.
+Several studies (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
 Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
@@
 Nonetheless, we observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
-Our results are also consistent with [@hardy2014specialization]'s study on lepidopterans, where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
+Our results are also consistent with the [@hardy2014specialization] study on lepidopterans, where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
-This strategy is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
+This evolutionary mechanism is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
 
@@
 These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
-Tentilla are expensive single-use structures, therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
-*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia* spp.
+Tentilla are expensive single-use structures [@Mackie:1987uy], therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
+*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*.
 This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization on smaller prey.
@@
 *Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
-obs.), a common feature of piscivorous cnidarians like cystonects or cubozoans.
+obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
 
@@
 Our work identifies an interesting example of convergent evolution.
-The region of the tentillum morphospace (Supplementary Figure XX) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+The region of the tentillum morphospace (SM4) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
 Unlike calycophorans, they lack paired elongate microbasic mastigophores.
-Instead, they bear three elongated stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
+Instead, they bear exactly three oval stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
 Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
@@
 The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-Our DAPCs (Supp.
-Fig XXX) predict that *Frillagalma* has a generalist niche with both soft and hard bodied prey, including copepods.
+Our DAPCs (SM16-20) predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
 
@@
 When interpreting these results, it is important to remember that diet is a product of environmental prey availability and predator selectivity.
-Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for this study.
+Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for in this study.
 For example, tentacle-deploying behavior, positioning in the water column, sensitivity thresholds for nematocyst discharge, or chemical cues to ingest a captured animal.
@@
 These correlations have been hypothesized to direct and constrain adaptive evolution [@wagner2000evolutionarily].
-The siphonophore tentillum morphospace has a fairly low extant dimensionality due to an evolutionary history with many synchronous, correlated changes.
-This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve function.
+The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
+This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies tentilla can present.
 
-  Structural correlations within the tentillum are expected from shared regulatory networks within a common developmental bud (budding tentilla in the tentacle).
-Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin.
-None of these explanations for correlated evolution are surprising, nor require natural selection.
+  Structural correlations within the tentillum are expected without the need to invoke natural selection since most characters develop from a common bud (budding tentilla near the base of the tentacle).
+Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
 However, we also found correlations between nematocyst and tentillum characters.
@@
 
-  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated, but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
+  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
 In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).
 
@@
 Similarly to what has been found in the feeding morphologies of fish [@collar2005comparative;@revell2009phylogenetic], siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
-For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring small crustaceans or fish.
+For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring prey with different combinations of defensive traits.
 Finally, the evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today across siphonophores.
@@
 *Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among the Hydrozoa remains an unresolved question [@munro2018improved].
-The most recent work on this front sets them as sister group to all other Hydroidolina [@kayal2015phylogenetic].
-Therefore, there is a great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
+The most recent work on this front sets them as the sister group to all other Hydroidolina [@kayal2015phylogenetic].
+Therefore, there is great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
 This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
@@
 While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+We find that the evolutionary optima and genetic correlations of many tentillum characters have evolved following these shifts in trophic niche.
 Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We find that the evolutionary diversification of tools for prey capture contributed to the diversification of trophic interactions.
+In light of these results, we conclude that the evolutionary diversification of tools for prey capture contributed to the diversification of trophic interactions.
 Therefore, we identify organismal trait evolution as a key driver in the emergence of food web complexity.
@@
 Thirty characters (defined in SM5) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
-We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles), since they are too variable to quantify.
+We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles) since they are too variable to quantify.
 We measured at least one specimen for 96 different species (see raw data by species in Dryad).
@@
 The phylogenetic analysis included 55 siphonophore species and 6 outgroup cnidarian species (*Clytia hemisphaerica*, *Hydra circumcincta*, *Ectopleura dumortieri*, *Porpita porpita*, *Velella velella*, *Staurocladia wellingtoni*).
-The gene sequences we used in this study are available online (accession numbers in Dryad Repository).
+The gene sequences we used in this study are available online (accession numbers in Dryad repository).
 Some of the sequences we used were accessioned in [@dunn2005molecular], and others we extracted from the transcriptomes in [@munro2018improved].
@@
 We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
-to assess relative model fit.
+to assess the relative model fit.
 ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9,SM11), which was topologically congruent with the unconstrained ML tree.
+Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9 and SM11), which was topologically congruent with the unconstrained ML tree.
 The *alpha* priors were selected to minimize prior load in site variation.
 
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian timetree approaches, which produced fully congruent topologies (SM8, SM10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (SM11,SM12).
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (SM8 and SM10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (SM11-12).
 Scripts available in the Dryad repository.
@@
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
-In order to detect coarse-level patterns in the feeding habits, the data were merged into feeding guilds.
+In order to detect coarse-level patterns in feeding habits, the data were merged into feeding guilds.
 The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
@@
 We extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in Dryad repository).
+To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in the Dryad repository).
 
@@
 We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM13).
-We reconstructed ancestral states using Maximum Likelihood (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
-R scripts available in Dryad.
+We reconstructed ancestral states using ML (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
+R scripts available in the Dryad repository.
 
@@
 
-In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
+In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance-covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
 When fitting all covariance terms simultaneously (SM36-38), we selected the largest set of characters that would allow the analysis to run without computational singularities.
@@
 Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (SM42).
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (SM42).
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Finally, we compared regime-specific variance covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (SM43).
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia*, and should be interpreted with care.
+Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (SM43).
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia* and should be interpreted with care.
 
@@
 This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, soft/hard bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
-From these DAPCs we obtained the highest contributing morphological characters to the discriminaton (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
+We generated discriminant functions for feeding guild, soft/hard-bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
+From these DAPCs we obtained the highest contributing morphological characters to the discrimination (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
 For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (SM16-20).
@@
 
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types, and identified the branches with the greatest shifts.
+To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types and identified the branches with the greatest shifts.
 In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).

### 2020-01-10 Manuscript_short.Rmd
jcbn comments incorporated toms

@@
 
-# The Evolution of Siphonophore Tentilla as Specialized Tools for Prey Capture {-}
+# Shaped to Kill: The Evolution of Siphonophore Tentilla as Tools for Prey Capture {-}
 
@@
 Predators have evolved dedicated body parts to capture and subdue prey.
-As a clade of predators specialize in distinct prey taxa, their tools for prey capture diversify into a variety of adaptive forms.
+As a clade of predators evolve to feed on different prey taxa, their tools for prey capture adapt into a variety of forms.
 Studying the evolution of predation is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation.
@@
 Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
+However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other.
+The primary questions we set out to answer are: how do predator specialists and generalists evolve, and how does predatory specialization shape morphological evolution?
 
@@
 This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory would predict evolution to drive coexisting siphonophore lineages towards specialization, increasing their feeding efficiencies and reducing interspecific competition [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
+With a relatively predictable prey availability, ecological theory would expect competition to inhibit the coexistence of closely-related species, unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
 If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
@@
 However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition; @nosil2002transition] and resource switching [@hoberg2008macroevolutionary; @hardy2014specialization].
-Here we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+We seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open ocean tactile predators.
+To do so, we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
 
@@
 
-  The few pioneering studies that have addressed the relationships between tentilla and diet suggest that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and show that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
 [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
 These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
-We hypothesize that these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
-Furthermore, we hypothesize that with extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
+Our study will elucidate whether these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
+Furthermore, with extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
 
@@
 
-*Phylogeny* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with extensive taxonomic representation using ribosomal genes.
-Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the 18S+16S tree.
-The topology of the constrained tree presented here (Fig.
-\@ref(figure4)) is congruent with the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
-However, with the unprecedented inclusion of *Stephanomia amphytridis*, this phylogeny reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
+*Novel phylogenetic relationships* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with extensive taxonomic representation using ribosomal genes.
+The topology of our tree recapitulates the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
+Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the constrained 18S+16S tree inference (Fig.
+\@ref(figure4)).
+, Moreover, with the unprecedented inclusion of *Stephanomia amphytridis* sequences, this phylogeny reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
 
@@
 
-  We retained the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], such as Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
+  We used the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], such as Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
 In addition, we define two new clades within Codonophora (Fig.
@@
 \@ref(figure5)).
-Large crustacean specialists evolve into generalists twice independently, supporting hypothesis 3.
-Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2.
+Large crustacean specialists evolve into generalists twice independently, supporting hypothesis 3 (generalists evolving from specialists).
+Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2 (specialists evolving to feed on a different resource).
 Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
 
-The OUwie model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM15).
+To test whether the morphological characters measured evolved in association to shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding regimes reconstructed on it.
+We fitted different models generating the observed data distribution given the phylogeny for each continuous character.
+The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
+The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM15).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
@@
 
-  Phylogenetic logistic regressions identified evolutionary associations between individual characters and the presence of particular prey types in the diet (Fig.
+  In order to investigate the associations between the evolutionary history of morphological characters and specific prey types, we used phylogenetic logistic regressions.
+We found that several characters were significantly correlated with the gains and losses of these prey types (Fig.
 \@ref(figure5), right).
@@
 Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (SM21).
+Evolutionary shifts in these characters likely allowed the inclusion of these prey types in the diet.
 
-  Phylogenetic regressions of continuous characters against prey selectivity data produced additional insights.
-Fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
+   In addition to the analyses above, we also tested for correlations between shits in specific prey selectivity and morphological characters using phylogenetic regressions.
+We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
 Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
@@
 
-*Generating dietary hypotheses using tentillum morphology* – The discriminant analysis of principal components for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination between guilds, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
+*Generating dietary hypotheses using tentillum morphology* – To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC).
+The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
 We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (SM2).
-This projection predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
+This extrapolation predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
 
@@
 
-*Phenotypic integration of the tentillum* – The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
-The results indicate that the dimensionality of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (SM4).
+*Phenotypic integration of the tentillum* – In order to study patterns among the correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance-covariance matrices [@revell2009phylogenetic].
+The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
+The results indicate that the dimensionality (number of independent axes of variation) of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (SM4).
 The variance-covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
-However, this analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
+This analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
 These results were not sensitive to the transformation of inapplicable states and taxon sampling.
-When we compared the rate covariance terms between characters across the different feeding guild regimes (SM41), we found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
+These results indicate that siphonophore tentilla and nematocysts are phenotypically integrated and co-evolve within discrete evolutionary modules.
+
+ In addition, we compared the rate covariance terms between characters across the different feeding guild regimes (SM41).
+We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
 When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (SM42).
+These results indicate that the evolutionary dependencies in these integrated modules are changing across the phylogeny, and evolving together with changes in prey type specializations.
 
-Under the majority of SIMMAP outcomes, large crustaceans specialists are the ancestral regime, and allß other regimes evolve from this ancestral specialization.
+ Under the majority of SIMMAP outcomes, large crustacean specialists are the ancestral feeding regime, and all other feeding regimes evolve from this ancestral specialization.
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
@@
 
-The phylogenetic positions of the main categorical character shifts were reconstructed using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
+We reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
 Haploneme nematocysts are likely ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
@@
 
-  Eucladophora (the clade containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
+  The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
 \@ref(figure3)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
@@
 \@ref(figure4)).
-BAMM identified a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
+We identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
+BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
 For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
@@
 
-  The core aims of this study are to examine the evolutionary history of siphonophore tentilla and diet, characterize the evolutionary shifts in their trophic niches, and identify the morphological characters that evolve with changes in prey type.
-We inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
+  In this study we inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
+We address these questions by examining the evolutionary history of siphonophore tentilla and diet, characterizing the evolutionary shifts in their trophic niches, and identifying the morphological characters that evolve with changes in prey type.
 In addition, we produced novel findings on tentillum morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
@@
 Several studies (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
-Our reconstructions show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
+Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
 Among the evolutionary hypotheses considered, we find support for both hypotheses 2 (specialist resource switching) and 3 (specialist to generalist), but no support for hypothesis 1 (generalist to specialist).
@@
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
+In more familiar predators, the prey capture apparatus is well integrated in the body, leading to trade-offs and whole body adaptations to feeding specialization.
+The extreme modularity of the siphonophore prey capture apparatus could release them from the constraints typically imposed by adaptation to ecological specialization.
 This evolutionary mechanism is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
 
+  In addition to ordinary character evolution, heterochrony [@gould1977ontogeny], shifting the timing of ontogenetic stages, can also lead to drastic morphological changes and speed up the ecological shifts in a lineage [@raff1989heterochrony].
 One of the most common prey items found in siphonophore diets is copepods (Fig.
@@
 
-Our work identifies an interesting example of convergent evolution.
+Our work identifies a novel example of convergent evolution.
 The region of the tentillum morphospace (SM4) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
@@
 Comparative toxin assays and venom protein evolution studies would shed light on this question.
-Moreover, siphonophore trophic specialization may have brought changes in the digestive biochemistry of gastrozooids and palpons.
-A comparison of the gene expression levels for different enzymes in the gastrozooids of different species, together with digestive enzyme sequence evolution studies, and a toxicological assay of the different venoms in siphonophore nematocysts on different prey taxa, would provide a great complement to our results.
+
+ Our results strongly support the presence of deviations from the generalist-to-specialist evolution model.
+However, we cannot strongly reject the possibility of transitions from generalists to specialists for two reasons.
+First, some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization.
+Second, some of the taxa not included in our dataset could be undiscovered generalists.
+Thus, while we do not find any evidence of transitions from generalist to specialist in our data, additional taxon sampling and more extensive dietary characterization may reveal additional transitions.
+These caveats, considering with the robust and extensive phylogeny and morphological dataset presented here, clearly indicate that the limiting factor for these questions is more extensive dietary characterization.
 
@@
 
-  Structural correlations within the tentillum are expected without the need to invoke natural selection since most characters develop from a common bud (budding tentilla near the base of the tentacle).
+  Since most characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected.
 Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
@@
 
-  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters.
+  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
@@
 
-*Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among the Hydrozoa remains an unresolved question [@munro2018improved].
+*Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among Hydrozoa remains an unresolved question [@munro2018improved].
 The most recent work on this front sets them as the sister group to all other Hydroidolina [@kayal2015phylogenetic].
@@
 We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
 We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
@@
 
-To test how many times extreme nematocyst morphologies evolved, we reconstructed the ancestral states of *log*(length/width) of the different cnidoband nematocyst types and identified the branches with the greatest shifts.
-In addition to characterizing the shifts in the state values of haploneme and heteroneme elongation, we identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
-
 ## Supplementary Materials {-}

### 2020-01-13 Manuscript_short.Rmd
cwd comments incorporated - first part

@@
 
-Predators have evolved dedicated body parts to capture and subdue prey.
-As a clade of predators evolve to feed on different prey taxa, their tools for prey capture adapt into a variety of forms.
-Studying the evolution of predation is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation.
-Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well, capturing prey with their tentilla (tentacle side branches).
+As predators evolve to feed on different prey taxa, their tools for prey capture can adapt into a variety of forms.
+The study of this evolutionary process is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation in these structures.
+Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well.
+Their tentilla (tentacle side branches) are the exclusive means of prey capture and have no other known function.
 Earlier work has shown that extant siphonophore diets correlate with the different morphologies and sizes of their tentilla and nematocysts.
 We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological characters from siphonophore tentacle specimens, (2) mapped these data to a phylogenetic tree of 45 species, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
-Our results show that the siphonophore tentillum morphology has strong evolutionary associations with prey type specialization, and suggest that shifts between prey-type specializations are linked to shifts in tentillum and nematocyst size and shape.
-We found that predatory specialists can evolve into generalists and that specialists on one prey type have directly evolved into specialists on other prey types.
-With changes in trophic niche regimes, both trait optima and trait correlation patterns showed significant shifts.
-Thus, the evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This study contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
+To test this hypothesis, we: (1) measured multiple morphological characters from siphonophore tentacle specimens from 45 species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
+Our results show that the siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey type are linked to shifts in tentillum and nematocyst size and shape.
+We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+When there are changes in trophic niche regimes, both trait optima and trait correlation patterns showed significant shifts.
+The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
+This contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
 
@@
 
-  Most animal predators have characteristic biological tools that they use to capture and subdue prey.
+  Most animal predators use specific structures to capture and subdue prey.
 Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
-The functional morphology of these structures tends to be finely attuned to their ability to successfully capture specific prey [@schmitz2017predator].
+The functional morphology of these structures is critical to their ability to successfully capture specific prey [@schmitz2017predator].
 Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses.
 The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
-Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, and to quantify the importance of ecological diversification in generating this diversity.
+Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
 However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other.
@@
 \@ref(figure1)).
-These present significant morphological variation across species [@mapstone2014global] (Fig.
+The tentilla have great morphological variation across species [@mapstone2014global] (Fig.
 \@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
-A siphonophore is a colony bearing many feeding polyps (Fig.
-\@ref(figure1)), each with a single tentacle, which branches into several tentilla carrying the functional cnidocytes (specialized neural cells carrying nematocysts, the stinging capsules).
-Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation] built into their tentilla (tentacle side branches).
+Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
+\@ref(figure1)).
+Each siphonophore polyp has a single tentacle, which bears a series of side branches known as tentilla.
+Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes.
+Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation]  which are located in their tentilla.
 While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
@@
 In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
+
   Siphonophores bear four major nematocyst types in their tentacles and tentilla (Fig.
@@
 This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory would expect competition to inhibit the coexistence of closely-related species, unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
+With a relatively predictable prey availability, ecological theory would predict competition to inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
+If this prediction holds true, we would expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
 
   Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
-However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution; @johnson2009competition; @nosil2002transition] and resource switching [@hoberg2008macroevolutionary; @hardy2014specialization].
-We seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open ocean tactile predators.
-To do so, we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from ancestral predators which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
+In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open ocean tactile predators.
+To do so, we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+These hypotheses are non-exclusive, and each could apply to different transitions along the siphonophore phylogeny.
 
@@
 In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved].
-These advances allow for the examination of relationships between modern siphonophore form, function, and ecology, as well as reconstructing their evolutionary history.
+These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.
 
@@
   Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and show that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
-[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores.
-These correlations, while studied for a small subset of extant epipelagic siphonophore species, might be generalizable to all siphonophores.
-Our study will elucidate whether these relationships reflect correlated evolution between prey selection and tentillum (and nematocyst) traits.
-Furthermore, with extensive characterization of tentilla morphology, we can generate hypotheses about the diets of understudied siphonophore species.
+[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
 
@@
 
-*Novel phylogenetic relationships* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with extensive taxonomic representation using ribosomal genes.
+*Novel phylogenetic relationships* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with broader taxonomic representation using ribosomal genes.
 The topology of our tree recapitulates the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
@@
 \@ref(figure4)).
-, Moreover, with the unprecedented inclusion of *Stephanomia amphytridis* sequences, this phylogeny reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
+Moreover, with the unprecedented inclusion of *Stephanomia amphytridis* sequences, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
 
@@
 
-*Evolutionary associations between diet and tentillum morphology* – Reconstructions of feeding guilds show that generalism is not likely to be ancestral, and it appears to have evolved at least two times independently (Fig.
+*Evolutionary associations between diet and tentillum morphology* – Reconstructions of feeding guilds do not recover ancestral diet generalism.
+None of the transitions in diet are consistent with hypothesis 1.
+Feeding guild specializations have shifted from an alternative ancestral state at least five times, consistent with instances of supporting hypothesis 2 (specialists evolving to feed on a different resource).
+Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
+We also recover multiple independent origins of generalism from specialist ancestors (Fig.
 \@ref(figure5)).
-Large crustacean specialists evolve into generalists twice independently, supporting hypothesis 3 (generalists evolving from specialists).
-Feeding guild specializations have shifted from an alternative ancestral state at least five times, supporting hypothesis 2 (specialists evolving to feed on a different resource).
-Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
+Large crustacean specialists evolve into generalists twice independently, consistent with instances of hypothesis 3 (generalists evolving from specialists).
 
-To test whether the morphological characters measured evolved in association to shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding regimes reconstructed on it.
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character.
+To test whether the measured morphological characters evolved in association with shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding regimes reconstructed on it.
+We fitted and compared alternative evolutionary models for each continuous character.
 The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
@@
 
-  In order to investigate the associations between the evolutionary history of morphological characters and specific prey types, we used phylogenetic logistic regressions.
+  In order to investigate the associations between the evolutionary history of morphological characters and specific prey types found in the diet, we used phylogenetic logistic regressions.
 We found that several characters were significantly correlated with the gains and losses of these prey types (Fig.
@@
 
-   In addition to the analyses above, we also tested for correlations between shits in specific prey selectivity and morphological characters using phylogenetic regressions.
+   We also tested for correlations between shifts in prey selectivity and morphological characters using phylogenetic linear models.
 We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
@@
 Heteroneme length and elongation also correlated negatively with chaetognath selectivity (SM21).
+These results indicate that not only diet but also differential feeding selectivity has evolved in correlation with changes in the prey capture apparatus of siphonophores.
 
-  When some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] were tested for correlated evolution (Table 1), we found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
+  We tested some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] for correlated evolution (Table 1).
+We found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
 The latter is likely a product of the larger species richness of crustacean-eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.
@@
 
-*Generating dietary hypotheses using tentillum morphology* – To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC).
+*Generating dietary hypotheses using tentillum morphology* – To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported using tentacle morphology data, we carried out linear discriminant analysis of principal components (DAPC).
 The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
-We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological data (SM2).
-This extrapolation predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* may be a fish specialist like *Erenna richardi*.
+We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological dataset (SM2).
+This extrapolation predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* might be a fish specialist like *Erenna richardi*.
 
@@
 
- In addition, we compared the rate covariance terms between characters across the different feeding guild regimes (SM41).
+ In order to test whether rate covariance matrices changed with evolutionary shifts in feeding regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (SM41).
 We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
@@
 
+ We were able to identify specific character correlations that shifted with the evolution of new diets.
 Under the majority of SIMMAP outcomes, large crustacean specialists are the ancestral feeding regime, and all other feeding regimes evolve from this ancestral specialization.
@@
 
-We reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
+In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
 Haploneme nematocysts are likely ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
@@
 
+  The new clades defined in this work are characterized by unique evolutionary innovations in their tentilla.
 The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
@@
 While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
-Nonetheless, they have spread over a broad span of variation in nematocyst and cnidoband sizes.
+Nonetheless, they have evolved a wide variation in nematocyst and cnidoband sizes.
 
-*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
+*Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
 There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
@@
 ![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled).
-Orange area delimits rod-shaped haplonemes, blue area covers oval and round-shaped haplonemes.
+Orange area delimits rod-shaped haplonemes, the blue area covers oval and round-shaped haplonemes.
 Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
@@
 \@ref(figure4)).
-We identified and located regime shifts for the rate of evolution using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
+We searched for regime shifts in the rate of evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
 BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
@@
 Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
-Most of these taxa have rod-shaped anisorhizas, but *Erenna* has oval ones).
+Most of these taxa have rod-shaped anisorhizas, but *Erenna* have oval ones.
 No significant regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
@@
 
-  In this study we inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
+  In this study, we inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
 We address these questions by examining the evolutionary history of siphonophore tentilla and diet, characterizing the evolutionary shifts in their trophic niches, and identifying the morphological characters that evolve with changes in prey type.
@@
 
-  In addition to ordinary character evolution, heterochrony [@gould1977ontogeny], shifting the timing of ontogenetic stages, can also lead to drastic morphological changes and speed up the ecological shifts in a lineage [@raff1989heterochrony].
+  In addition to ordinary character evolution, heterochrony [@gould1977ontogeny] (shifting the timing of ontogenetic stages) can also lead to drastic morphological changes and speed up the ecological shifts in a lineage [@raff1989heterochrony].
 One of the most common prey items found in siphonophore diets is copepods (Fig.
@@
 Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna* anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
+*Erenna*'s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
 obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
@@
 Moreover, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
-When interpreting these results, it is important to remember that diet is a product of environmental prey availability and predator selectivity.
-Selectivity differences across siphonophore species could be driven by other phenotypes not accounted for in this study.
+When interpreting these results, it is important to remember that diet is also dependent on environmental prey availability.
+Selectivity differences across siphonophore species could be also driven by other phenotypes not accounted for in this study.
 For example, tentacle-deploying behavior, positioning in the water column, sensitivity thresholds for nematocyst discharge, or chemical cues to ingest a captured animal.
@@
 The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
-This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies tentilla can present.
+This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies tentilla present.
 
@@
 For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring prey with different combinations of defensive traits.
-Finally, the evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today across siphonophores.
 
@@
 Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
-Among these, are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
+Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
 We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
@@
 
-  Siphonophores have diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
+  Siphonophores occupy diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
 With the evolution of diversified prey type specializations comes the evolution of morphologies adapted to the challenges posed by different prey.
@@
 While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-We find that the evolutionary optima and genetic correlations of many tentillum characters have evolved following these shifts in trophic niche.
+We find that the character states, evolutionary optima, and genetic correlations of many tentillum characters have evolved following these shifts in trophic niche.
 Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
@@
 We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles) since they are too variable to quantify.
-We measured at least one specimen for 96 different species (see raw data by species in Dryad).
+We measured at least one specimen for 96 different species (raw data available in Dryad).
 Of these, we selected 38 focal species across clades based on specimen availability and phylogenetic representation.
@@
 *Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
-Anela Choy (available in Dryad repository).
+Anela Choy (data available in Dryad repository).
 We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
-eating *Aegina*, since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
+eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
@@
 We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-We then ranked the models in order of increasing parametric complexity (WN,BM,EB,OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
+We then ranked the models in order of increasing parametric complexity (WN, BM, EB, OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
 When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM13).
@@
 
-To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported (but for which we have tentacle morphology data), we carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+We carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
 This function allowed us to incorporate more predictors than individuals.

### 2020-01-16 Manuscript_short.Rmd
cwd comments incorporated - second part

@@
 
-As predators evolve to feed on different prey taxa, their tools for prey capture can adapt into a variety of forms.
+As predators evolve to feed on different prey taxa, their apparatus for prey capture can adapt into a variety of forms.
 The study of this evolutionary process is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation in these structures.
 Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well.
-Their tentilla (tentacle side branches) are the exclusive means of prey capture and have no other known function.
+Their tentilla (tentacle side branches) are the exclusive means of prey capture for the large majority of species and have no other known function.
 Earlier work has shown that extant siphonophore diets correlate with the different morphologies and sizes of their tentilla and nematocysts.
@@
 We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-When there are changes in trophic niche regimes, both trait optima and trait correlation patterns showed significant shifts.
+When there are changes in trophic niche, both trait optima and trait correlation patterns showed significant shifts.
 The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
+The extreme modularity of tentilla may have released siphonophores from the evolutionary constraints of adaptation to ecologically specialized niches.
 This contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
@@
 Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses.
-The more specialized the diet of a predator is, the more specialized its tools need to be to meet the specific challenges posed by the prey.
+The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the specific challenges posed by the prey.
 Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
@@
 Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes.
-Unlike most other cnidarians, siphonophores carry their tentacle nematocysts in extremely complex and organized batteries [@skaer1988formation]  which are located in their tentilla.
+Unlike the prey capture apparatus of most other cnidarians, siphonophore tentacles carry their cnidocytes in extremely complex and organized batteries [@skaer1988formation] which are located in their tentilla.
 While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey.
@@
 
-  Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution].
+  Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization].
 However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
 In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open ocean tactile predators.
-To do so, we examine three alternative hypotheses on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
-These hypotheses are non-exclusive, and each could apply to different transitions along the siphonophore phylogeny.
+To do so, we examine three alternative scenarios on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+These scenarios are non-exclusive, and each could apply to different transitions along the siphonophore phylogeny.
 
-  The study of siphonophore tentilla and diets has been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
+  The study of siphonophore tentilla and diets have been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
 Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
@@
 
-![\label{figure2} Tentillum diversity plate.
+![\label{figure2} Tentillum diversity.
 The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow).
@@
 
-To test whether the measured morphological characters evolved in association with shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding regimes reconstructed on it.
+To test whether the measured morphological characters evolved in association with shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding guilds reconstructed on it as hypothetical selective regimes.
 We fitted and compared alternative evolutionary models for each continuous character.
@@
 
-  We tested some of the diet-morphology associations reported in the literature [@purcell1984functions;@purcell1988correlation] for correlated evolution (Table 1).
-We found that most were consistent with an evolutionary explanation except the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
+  We tested some of the diet-morphology associations previously proposed in the literature [@purcell1984functions;@purcell1988correlation] for correlated evolution (Table 1).
+We found that most, such as heteroneme volume and copepod prey size, do show correlated evolution, consistent with these earlier hypotheses.
+The sole exception was the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
+Analyses that do not take phylogeny into account do recover this correlation across the extant species studied, but it is not consistent with correlated evolution.
 The latter is likely a product of the larger species richness of crustacean-eating species with terminal filament nematocysts, rather than simultaneous evolutionary gains.
@@
 
-*Generating dietary hypotheses using tentillum morphology* – To generate hypotheses about the diets of understudied siphonophores for which no feeding observations have yet been reported using tentacle morphology data, we carried out linear discriminant analysis of principal components (DAPC).
+*Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
+We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using a linear discriminant analysis of principal components (DAPC).
+This provides concrete predictions to be tested in future work, and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
+
   The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
 We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological dataset (SM2).
-This extrapolation predicts that two other *Apolemia* species may also be gelatinous prey specialists like *Apolemia rubriversa* and that *Erenna laciniata* might be a fish specialist like *Erenna richardi*.
+This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*.
 
@@
 
-*Phenotypic integration of the tentillum* – In order to study patterns among the correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance-covariance matrices [@revell2009phylogenetic].
+*Evolution of the integrated tentillum morphology* – Phenotypic integration results in correlation patterns between morphological characters and their rates of evolution.
+To study these patterns, we fit a set of evolutionary variance-covariance matrices [@revell2009phylogenetic].
 The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
@@
 The variance-covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
-This analysis reveals more clearly the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
+This analysis more clearly reveals the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
 These results were not sensitive to the transformation of inapplicable states and taxon sampling.
@@
 
- In order to test whether rate covariance matrices changed with evolutionary shifts in feeding regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (SM41).
+ In order to test whether rate covariance matrices changed with evolutionary shifts in feeding guild regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (SM41).
 We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
@@
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
-With the appearance of generalists (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
+Within generalist clades (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
 In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
@@
 In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
-Haploneme nematocysts are likely ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
+Some of these characters include the gain and loss of nematocyst types.
+Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
 Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
@@
 The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure3)) encompasses most of the extant Siphonophore species (178 of 186) other than Cystonects and *Apolemia*.
-Innovations evolved in the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
+\@ref(figure3)) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*.
+Innovations that arose along the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
 \@ref(figure7)).
@@
 \@ref(figure4)).
-We searched for regime shifts in the rate of evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
+We searched for rate regime shifts in the evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
 BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
@@
 
-  In this study, we inquire whether the relationships between form and function observed in extant taxa are due to correlated evolution or non-evolutionary causes, whether the evolution of their trophic specializations supports or challenges traditional ecological theory (such as the idea specialists evolve from generalists), and whether the diets of siphonophores can be hypothesized by observing their tentacles.
-We address these questions by examining the evolutionary history of siphonophore tentilla and diet, characterizing the evolutionary shifts in their trophic niches, and identifying the morphological characters that evolve with changes in prey type.
-In addition, we produced novel findings on tentillum morphology, siphonophore phylogeny, nematocyst character evolution, and tentillum discharge dynamics.
-
-*Evolution of tentillum morphology with diet* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as trophic intermediaries between smaller zooplankton and higher trophic level predators.
+*Evolution of siphonophore trophic niche* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
+While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
 Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
-Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and diversified predators in today’s oceans remains an open question.
-Predators that use morphologically similar tools for prey capture tend to capture similar prey, thus their abundance and coexisting species diversity are inversely related due to competitive exclusion by resource limitation [@schluter2000ecological].
-However, this is not consistent with what we observe in siphonophores, which have been found to be both very abundant and locally diverse [@longhurst1985structure, @mapstone2014global].
-We hypothesize that siphonophores have escaped this by specializing in different prey resources.
+Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and trophically diverse predators in today’s oceans remains an open question.
 
 According to our reconstructions, the evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
-Several studies (reviewed in [@futuyma1988evolution]) have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
-Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently at least twice.
-Among the evolutionary hypotheses considered, we find support for both hypotheses 2 (specialist resource switching) and 3 (specialist to generalist), but no support for hypothesis 1 (generalist to specialist).
+Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
+Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently from specialists at least twice.
+Among the evolutionary scenarios considered, we find support for both scenario 2 (specialist resource switching) and 3 (specialist to generalist), but no support for scenario 1 (generalist to specialist).
+This finding is particularly given in that it is the opposite of known technical biases in ancestral state reconstruction.
+[@nosil2005testing] found that such methods tend to infer higher transition rates toward the more frequent state.
+In this case, that would lead to a bias for an increased rate from generalists (the rarer state across the tips) to specialists (the more common state across the tips).
+We observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
+
 This is consistent with the findings of recent studies on phytophagous insects [@nosil2002transition], where the rate of evolution from generalists to specialists is comparable to the reverse, thus specialization does not limit further evolution.
-However, [@nosil2005testing] found that ancestral reconstruction methods can be biased, and tend to infer higher transition rates toward the more frequent state.
-With this in mind, we should expect to find a predominance of transitions from generalists to specialists (the more common state across the tips).
-Nonetheless, we observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
-Our results are also consistent with the [@hardy2014specialization] study on lepidopterans, where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
+Our results are also consistent with analyses of lepidopterans [@hardy2014specialization], where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
-In more familiar predators, the prey capture apparatus is well integrated in the body, leading to trade-offs and whole body adaptations to feeding specialization.
+In more familiar predators, the prey capture apparatus is well integrated in the body (such as claws and jaws), leading to trade-offs and whole body adaptations to feeding specialization.
 The extreme modularity of the siphonophore prey capture apparatus could release them from the constraints typically imposed by adaptation to ecological specialization.
@@
 
-  In addition to ordinary character evolution, heterochrony [@gould1977ontogeny] (shifting the timing of ontogenetic stages) can also lead to drastic morphological changes and speed up the ecological shifts in a lineage [@raff1989heterochrony].
-One of the most common prey items found in siphonophore diets is copepods (Fig.
-\@ref(figure5)).
-Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
+*Heterochrony and convergence in the evolution of tentilla with diet* - Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
 These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
@@
 *Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*.
-This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphosis associated with predatory specialization on smaller prey.
-
-[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have been observed primarily feeding on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) present an accelerated rate of haploneme shape evolution towards more compact haplonemes, significantly distinct from their closest relatives.
-Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna*'s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
-obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
-
-[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
-The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and our unpublished observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
-Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
-In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
-
-When we tested the diet-morphology correlation hypotheses supported in the literature from a macroevolutionary perspective (Table 1), we found that most of them were consistent with correlated evolution.
-The ecomorphological association between rhopalonemes, desmonemes, and crustacean eaters was not congruent with a scenario of correlated evolution.
-This is probably due to the broader set of taxa in our analyses, including multiple species without desmonemes or rhopalonemes but which effectively capture crustaceans (such as *Cordagalma ordinatum*, *Lychnagalma utricularia*, and *Bargmannia amoena*).
+This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphic heterochrony associated with predatory specialization on smaller prey.
 
@@
 
-While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited by the sparse dietary data available.
-Moreover, our analyses are not sufficient to adequately test hypotheses of adaptation, since that would require evidence of changes within a population exposed to different selective pressures.
-When interpreting these results, it is important to remember that diet is also dependent on environmental prey availability.
+*Limitations* - While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited in several ways.
+The biggest challenge at present is the sparse dietary data available in the literature.
+Moreover, our analyses are not sufficient to test hypotheses of adaptation.
+When interpreting these results, it is also important to remember that diet is also dependent on environmental prey availability.
 Selectivity differences across siphonophore species could be also driven by other phenotypes not accounted for in this study.
-For example, tentacle-deploying behavior, positioning in the water column, sensitivity thresholds for nematocyst discharge, or chemical cues to ingest a captured animal.
-Further observations on these behaviors in the field are necessary to assess their relative importance in determining dietary composition.
-In addition to behavior, there is much biochemistry in the prey capture and digestion processes that remains unexplored.
-Part of the success in siphonophore prey capture is likely determined by the effectivity of the toxins delivered by the nematocysts on different taxa.
-Comparative toxin assays and venom protein evolution studies would shed light on this question.
-
+Further observations on behavior, digestion biochemistry, and toxin composition are necessary to assess their relative importance in determining diet.
 Our results strongly support the presence of deviations from the generalist-to-specialist evolution model.
-However, we cannot strongly reject the possibility of transitions from generalists to specialists for two reasons.
+However, additional dietary characterization could reveal transitions from generalists to specialists for two reasons.
 First, some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization.
 Second, some of the taxa not included in our dataset could be undiscovered generalists.
-Thus, while we do not find any evidence of transitions from generalist to specialist in our data, additional taxon sampling and more extensive dietary characterization may reveal additional transitions.
-These caveats, considering with the robust and extensive phylogeny and morphological dataset presented here, clearly indicate that the limiting factor for these questions is more extensive dietary characterization.
 
-*Phenotypic integration of siphonophore tentilla* – Many tentillum characters, such as nematocysts, arose from the subfunctionalization of serial homologs [@david2008evolution].
-Serial homologs have shared genetic elements underlying their development, and are expected to have phylogenetic correlations [@wagner2000evolutionarily].
-In addition, these sub-structures must fit and work together in synchrony to ensnare prey successfully (functional integration).
-Character complexes that satisfy these conditions tend to be phenotypically integrated.
-Phenotypic integration is the set of functional and genetic correlations among the traits of an organism [@pigliucci2003phenotypic].
-These correlations have been hypothesized to direct and constrain adaptive evolution [@wagner2000evolutionarily].
-The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
+ *Evolution of nematocyst shape* –  The phylogenetic relationship of siphonophores to other hydrozoans remains an unresolved question [@munro2018improved].
+The most recent work on this front sets them as the sister group to all other Hydroidolina [@kayal2015phylogenetic].
+Therefore, there is great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
+This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
+One such character is the shape of haploneme nematocysts.
+A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
+This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation].
+Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
+Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
+Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
+[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
+The two clades that have converged to feed primarily on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) have also converged morphologically toward more compact haplonemes, significantly distinct from their closest relatives.
+Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
+*Erenna*’s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
+obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
+
+  The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
+Elongate nematocysts can be tightly packed into cnidobands.
+We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
+[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
+The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and our unpublished observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
+Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
+In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
+Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
+Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
+We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
+However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
+
+*Phenotypic integration of siphonophore tentilla* – The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
 This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies tentilla present.
-
-  Since most characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected.
-Similarly, correlations between nematocyst subtypes are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
+Since most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected.
+Similarly, correlations between the features of different nematocyst subtypes within a species are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
 However, we also found correlations between nematocyst and tentillum characters.
@@
 
-  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+  Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
@@
 
-*Evolution of nematocyst shape* –  The phylogenetic placement of siphonophores among Hydrozoa remains an unresolved question [@munro2018improved].
-The most recent work on this front sets them as the sister group to all other Hydroidolina [@kayal2015phylogenetic].
-Therefore, there is great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
-This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
-One such character is the shape of haploneme nematocysts.
-A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
-This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation].
-Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
-Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
-Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
-
-  The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
-Elongate nematocysts can be tightly packed into cnidobands.
-We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
-Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
-We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
-However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
-
 ## Conclusions {-}
@@
 The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.
-While much of the literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+While much of the feeding ecology literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
 We find that the character states, evolutionary optima, and genetic correlations of many tentillum characters have evolved following these shifts in trophic niche.
-Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-In light of these results, we conclude that the evolutionary diversification of tools for prey capture contributed to the diversification of trophic interactions.
-Therefore, we identify organismal trait evolution as a key driver in the emergence of food web complexity.
+Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of siphonophore taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
+We identify key aspects of organismal trait evolution that are central to understanding the emergence of food web complexity.
 

### 2020-01-29 Manuscript_short.Rmd
Steve's comment addressed, changes in figures, STOPPING POINT VERSION BEFORE CARVING OUT THE NATURAL HISTORY

@@
 
-# Shaped to Kill: The Evolution of Siphonophore Tentilla as Tools for Prey Capture {-}
+# Shaped to kill: The evolution of siphonophore tentilla for specialized prey capture in the open ocean {-}
 
@@
 To test this hypothesis, we: (1) measured multiple morphological characters from siphonophore tentacle specimens from 45 species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
-Our results show that the siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey type are linked to shifts in tentillum and nematocyst size and shape.
+Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey type are linked to shifts in tentillum and nematocyst size and shape.
 We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
@@
 Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles.
-The functional morphology of these structures is critical to their ability to successfully capture specific prey [@schmitz2017predator].
+The functional morphology of these structures is critical to their ability to successfully capture prey [@schmitz2017predator].
 Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses.
-The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the specific challenges posed by the prey.
+The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey.
 Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
@@
 \@ref(figure1)).
-Each siphonophore polyp has a single tentacle, which bears a series of side branches known as tentilla.
+Each feeding polyp has a single tentacle, which bears a series of side branches known as tentilla.
 Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes.
@@
 
-  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the oceanic seafloor.
+  Many siphonophore species inhabit the deep pelagic ocean, which spans from ~200m to the abyssal seafloor (~4000m).
 This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory would predict competition to inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
+With a relatively predictable prey availability, ecological theory predicts that interspecific competition would inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
 If this prediction holds true, we would expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
@@
 However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
-In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open ocean tactile predators.
-To do so, we examine three alternative scenarios on siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which specialized on a different resource, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
+In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open-ocean tactile predators.
+To do so, we examine three alternative scenarios of siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which targeted different resources, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
 These scenarios are non-exclusive, and each could apply to different transitions along the siphonophore phylogeny.
@@
 
-  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and show that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
 [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
 
-  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining a broad taxon sampling of ribosomal gene sequences with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations among diet, tentillum, and nematocyst characters.
+  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
 
@@
 The topology of our tree recapitulates the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
-Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained during estimation of the constrained 18S+16S tree inference (Fig.
+Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
 \@ref(figure4)).
-Moreover, with the unprecedented inclusion of *Stephanomia amphytridis* sequences, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
+Moreover, with the inclusion of *Stephanomia amphytridis* sequences, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
 
@@
 Species marked with a red asterisk were recorded using high-speed video.
-Newly accessioned 16S data was used for species marked with a blue circle.
+Newly accessioned 16S data was used for species with names in bold.
 Nodes labeled with Bayesian posteriors (BP).
 Green circles indicate BP = 1.
-Blue circles indicate nodes constrained to be congruent with (Munro *et al.* 2018).
-This phylogeny expands the taxon sampling of the (Munro *et al.* 2018) transcriptome tree and is congruent with it.
-Tips with black squares indicate the species with transcriptomes used in (Munro *et al.* 2018).
-Tips with grey squares indicate genus-level correspondence to taxa included in (Munro *et al.* 2018).
+Blue circles indicate nodes constrained to be congruent with Munro *et al.* (2018).
+Tips with black squares indicate the species with transcriptomes used in Munro *et al.* (2018).
+Tips with grey squares indicate genus-level correspondence to taxa included in Munro *et al.* (2018).
 The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
 
-  We used the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], such as Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
+  We used the clade nomenclature defined in [@dunn2005molecular] and [@munro2018improved], including Codonophora to indicate the sister group to Cystonectae, Euphysonectae to indicate the sister group to Calycophorae, Clade A and B to indicate the two main lineages within Euphysonectae.
 In addition, we define two new clades within Codonophora (Fig.
@@
 *Evolutionary associations between diet and tentillum morphology* – Reconstructions of feeding guilds do not recover ancestral diet generalism.
-None of the transitions in diet are consistent with hypothesis 1.
-Feeding guild specializations have shifted from an alternative ancestral state at least five times, consistent with instances of supporting hypothesis 2 (specialists evolving to feed on a different resource).
+None of the transitions in diet are consistent with scenario 1 (specialists evolving from generalists).
+Feeding guild specializations have shifted from an alternative ancestral state at least five times, consistent with instances supporting scenario 2 (specialists evolving to feed on a different resource).
 Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
@@
 \@ref(figure5)).
-Large crustacean specialists evolve into generalists twice independently, consistent with instances of hypothesis 3 (generalists evolving from specialists).
+Large crustacean specialists evolve into generalists twice independently, consistent with instances of scenario 3 (generalists evolving from specialists).
+This finding is particularly compelling given in that it is the opposite of known biases in ancestral state reconstruction.
+[@nosil2005testing] found that such methods tend to infer higher transition rates toward the more frequent state.
+In this case, that would lead to a bias for an increased rate of transition from generalists (the rarer state across the tips) to specialists (the more common state across the tips).
+We observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
 
-To test whether the measured morphological characters evolved in association with shifts in the feeding ecology, we analyzed the evolutionary history of each character on the phylogeny with the feeding guilds reconstructed on it as hypothetical selective regimes.
+To test whether measured morphological characters evolved in association with shifts in feeding ecology, we analyzed the evolutionary history of each character on the phylogeny, with the feeding guilds reconstructed on it as hypothetical selective regimes.
 We fitted and compared alternative evolutionary models for each continuous character.
@@
    We also tested for correlations between shifts in prey selectivity and morphological characters using phylogenetic linear models.
-We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and increased size of the cnidoband, elastic strand, pedicle and tentacle widths.
+We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and larger the cnidoband, elastic strand, pedicle and tentacle widths.
 Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
@@
 Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
-Because there is a total absence of siphonophores in the fossil record, how they became established as the ubiquitous and trophically diverse predators in today’s oceans remains an open question.
+Because there is a total absence of siphonophores in the fossil record, how they became established as such ubiquitous and trophically diverse predators in today’s oceans remains an open question.
 
-According to our reconstructions, the evolutionary history of siphonophore diets indicates that being a specialist was an ancestral aspect of their trophic niche, while trophic generalism is likely a derived condition.
 Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
-Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times, and generalism has evolved independently from specialists at least twice.
-Among the evolutionary scenarios considered, we find support for both scenario 2 (specialist resource switching) and 3 (specialist to generalist), but no support for scenario 1 (generalist to specialist).
-This finding is particularly given in that it is the opposite of known technical biases in ancestral state reconstruction.
-[@nosil2005testing] found that such methods tend to infer higher transition rates toward the more frequent state.
-In this case, that would lead to a bias for an increased rate from generalists (the rarer state across the tips) to specialists (the more common state across the tips).
-We observe the opposite, indicating strong evidence that these generalists are indeed a derived state.
+Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times.
+We find no support for any transitions from generalist to specialist (scenario 1, as described in the Introduction).
+We do find support for at least 3 instances of specialists switching from one prey type to another prey type, (scenario 2) and two switches from specialist to generalist (scenario 3).
 
@@
 
-*Heterochrony and convergence in the evolution of tentilla with diet* - Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
+*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, our work reveals the specific morphological changes in the prey capture apparatus associated with these changes.
+Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
 These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
@@
 Our DAPCs (SM16-20) predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
-
-*Limitations* - While our results unambiguously show that tentillum morphology evolved with diet, the conclusions we can draw from these analyses are limited in several ways.
-The biggest challenge at present is the sparse dietary data available in the literature.
-Moreover, our analyses are not sufficient to test hypotheses of adaptation.
-When interpreting these results, it is also important to remember that diet is also dependent on environmental prey availability.
-Selectivity differences across siphonophore species could be also driven by other phenotypes not accounted for in this study.
-Further observations on behavior, digestion biochemistry, and toxin composition are necessary to assess their relative importance in determining diet.
-Our results strongly support the presence of deviations from the generalist-to-specialist evolution model.
-However, additional dietary characterization could reveal transitions from generalists to specialists for two reasons.
-First, some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization.
-Second, some of the taxa not included in our dataset could be undiscovered generalists.
 
@@
 
-  The implications of these results to the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
+  The implications of these results for the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
 Elongate nematocysts can be tightly packed into cnidobands.
@@
 In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
 
@@
 Our results show that the patterns of phenotypic integration in siphonophore tentilla vary among clades, and appear to display different relationships across shifting feeding specializations.
-Similarly to what has been found in the feeding morphologies of fish [@collar2005comparative;@revell2009phylogenetic], siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
+Similar to what has been found in the feeding morphologies of fish [@collar2005comparative;@revell2009phylogenetic], siphonophore tentilla may have accommodated new diets by altering the correlations between characters.
 For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring prey with different combinations of defensive traits.
+
+*Limitations* - While our results unambiguously show that tentillum morphology evolved with diet, and strongly support deviations from the generalist-to-specialist evolution scenario, the conclusions we can draw from these analyses are limited in several ways.
+The biggest challenge at present is the sparse dietary data available in the literature.
+Additional dietary data could reveal transitions from generalists to specialists we were unable to detect for two reasons.
+First, some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization.
+Second, some of the taxa not included in our dataset could be undiscovered generalists.
+When interpreting these results, it is also important to remember that diet is also dependent on environmental prey availability.
+In addition, selectivity differences across siphonophore species could be also driven by other phenotypes not accounted for in this study.
+Finally, further observations on behavior, digestion biochemistry, and toxin composition are necessary to assess their relative importance in determining diet.
 
@@
 
-  Siphonophores occupy diverse predatory niches in the open ocean, ranging from mid-trophic small crustacean eaters to piscivorous super-carnivores.
-With the evolution of diversified prey type specializations comes the evolution of morphologies adapted to the challenges posed by different prey.
+  Siphonophores occupy diverse predatory niches in the open ocean, ranging from mid-trophic small-crustacean eaters to piscivorous super-carnivores.
+With the evolution of diversified prey type specialization comes the evolution of morphologies adapted to the challenges posed by different prey.
 The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.

### 2020-01-29 Manuscript_supershort.Rmd
added supershort version

--- 2020-01-29 Manuscript_short.Rmd
@@
 \@ref(figure1)).
-The tentilla have great morphological variation across species [@mapstone2014global] (Fig.
-\@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
+The tentilla have great morphological variation across species [@mapstone2014global], which makes them an ideal system to study the relationships between functional traits and prey specialization.
 Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
@@
 These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.
-
-![\label{figure2} Tentillum diversity.
-The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow).
-Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species.
-A - *Erenna laciniata*, 10x.
-B - *Lychnagalma utricularia*, 10x.
-C - *Agalma elegans*, 10x.
-D - *Resomia ornicephala*, 10x.
-E - *Frillagalma vityazi*, 20x.
-F - *Bargmannia amoena*, 10x.
-G - *Cordagalma* sp., reproduced from Carré 1968.
-H - *Lilyopsis fluoracantha*, 20x.
-I - *Abylopsis tetragona*, 20x.](Figures_final/figure2.jpg)
 
@@
 
-*Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
-We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using a linear discriminant analysis of principal components (DAPC).
-This provides concrete predictions to be tested in future work, and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
-
-  The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
-We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in our morphological dataset (SM2).
-This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*.
-
 Table 2.
@@
 
-![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
-Some branch lengths were modified from the Bayesian chronogram to improve readability.
-The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters.
-In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](Figures_final/figure7.jpg)
-
-In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
-Some of these characters include the gain and loss of nematocyst types.
-Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
-Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
-Haplonemes were likely lost in the tentacles of *Apolemia* but retained as spherical isorhizas in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
-
-  The new clades defined in this work are characterized by unique evolutionary innovations in their tentilla.
-The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae, see Fig.
-\@ref(figure3)) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*.
-Innovations that arose along the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig.
-\@ref(figure7)).
-Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis].
-The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae, Fig.
-\@ref(figure3)) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig.
-\@ref(figure7)), which bears no other nematocyst type (Fig.
-\@ref(figure1)).
-These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling].
-The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig.
-\@ref(figure2)).
-This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects.
-Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes.
-While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor.
-Nonetheless, they have evolved a wide variation in nematocyst and cnidoband sizes.
-
 *Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
@@
 Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)
-
-  Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
-However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig.
-\@ref(figure4)).
-We searched for rate regime shifts in the evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
-BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
-For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
-\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (SM35).
-Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
-Most of these taxa have rod-shaped anisorhizas, but *Erenna* have oval ones.
-No significant regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
 
@@
 This evolutionary mechanism is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
-
-*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, our work reveals the specific morphological changes in the prey capture apparatus associated with these changes.
-Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
-These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
-Tentilla are expensive single-use structures [@Mackie:1987uy], therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
-*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*.
-This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphic heterochrony associated with predatory specialization on smaller prey.
-
-Our work identifies a novel example of convergent evolution.
-The region of the tentillum morphospace (SM4) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
-Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
-Unlike calycophorans, they lack paired elongate microbasic mastigophores.
-Instead, they bear exactly three oval stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus.
-Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
-Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
-The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-Our DAPCs (SM16-20) predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
 
@@
 
-*Phenotypic integration of siphonophore tentilla* – The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
-This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies tentilla present.
-Since most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected.
-Similarly, correlations between the features of different nematocyst subtypes within a species are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
-However, we also found correlations between nematocyst and tentillum characters.
-Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum.
-These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid).
-Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
-Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies.
-Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
-
-  Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+*Phenotypic integration of siphonophore tentilla* – Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.

### 2020-01-29 Supplement_forSupershort.Rmd
added supershort version

--- 2019-11-06 Supplement_forShort.Rmd
@@
 
-In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
-This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters.
-In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
-
-## Supplementary Results {-}
-
-![\label{figure3} Heatmap summarizing the morphological diversity measured for 96 species of siphonophores clustered by similarity (raw data in Dryad repository).
-Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.](Figures_final/figure3.jpg)
-
-*Generating dietary hypotheses using tentillum morphology* – When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM\@ref(DAPCsofthard)).
-The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
-Discriminant analyses and GLM logistic regressions were also applied to specific prey type presence and selectivity (Table 2 int he main text), revealing the sign of their predictive relationship to each prey type.
-We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
-While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (SM\@ref(DAPCfish),SM\@ref(DAPCcrustacean)), specialization on fish or large crustacean prey can be fully disentangled (SM\@ref(DPACguilds)).
-For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
-Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2 in the main text).
-
-  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
-Cell darkness indicates posterior probability of belonging to each guild.
-Training data set transformed so inapplicable states are computed as zeroes.
-Species ordered and colored according to their predicted feeding guild.](Figures_final/figure6.jpg)
-
-*Evolution of tentillum and nematocyst characters* – One third of the characters measured support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)).
-Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
-74% of characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K > 1.
-67% of characters support BM models, indicating a history of neutral constant divergence.
-No relationship between phylogenetic signal and BM model support was found.
-Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time.
-No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).
-
-![\label{figure8} A.
-Correlogram showing strength of ordinary (upper triangle) and phylogenetic (lower triangle) correlations between characters.
-Both size and color of the circles indicate the strength of the correlation (R^2^).
-B.
-Scatterplot of phylogenetic correlation against ordinary correlation showing a strong linear relationship (R^2^ = 0.92, 95% confidence between 0.90 and 0.93).
-Light red and blue boxes indicate congruent negative and positive correlations respectively.
-Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](Figures_final/figure8.jpg){height=600px}
-
-*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (SM\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (SM\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
-Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
-Similarly, of the across-species correlations, 49.1% were >0.5 and only 1.5% were < -0.5.
-We found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
-Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
-These disparities can be caused by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
-However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54).
-Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
-
-![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.
-A.
-Variance explained by each variable in the PC1-PC2 plane.
-Axis labels include the phylogenetic signal (K) for each component and p-value.
-B.
-Phylogenetic relationships between the species points distributed in that same space.](Figures_final/figure9.jpg){height=600px}
-
-  In the non-phylogenetic PCA morphospace using only simple characters (SM\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
-In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
-
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
-While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
-For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
-
-  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
-Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
-Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
-
-## Supplementary Discussion {-}
-
-*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
-Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
-The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
-While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.
-This reveals the need to extensively characterize siphonophore diets and feeding habits.
-In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
-Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
-In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure].
-The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
-
-*Evolutionary history of tentillum morphology* –This study produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
-This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
-*Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla.
-Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review].
-Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
-The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
-
-  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
-The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.
-
-  The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-
-\newpage
-
 ## Supplementary Materials {-}
@@
 
-\newpage
-
 DAPC discriminant analyses:
@@
 
-![\label{DAPCsofthard} DAPC for soft-bodied vs.
-hard bodied prey specialization.
-Six PCs retained after a-score optimization (100 iterations).
-Two LDA functions used.
-Discriminant power on training set: 90.9%.
-Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_softhard.png)
-
 \newpage
 
-Ordinary and phylogenetic logistinc regression of morphological characters and the presence/absence of prey types:
+Ordinary and phylogenetic logistic regression of morphological characters and the presence/absence of prey types:
 
@@
 
-\newpage
-
-SIMMAP ancestral reconstructions of categorical characters:
-
-![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/tentillaPresenceSIM.png)
-
-![\label{SIMMAPproxhet} SIMMAP Cnidoband proximal heteroneme presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/proxhet_presence.png)
-
-![\label{SIMMAPdesmorhopalo} SIMMAP Desmoneme+Rhopaloneme presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/desmorhopalo_SIM.png)
-
-![\label{SIMMAPdischarge} SIMMAP Actively discharging cnidobands presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/discharge_SIM.png)
-
-![\label{SIMMAP_ES} SIMMAP Elastic strands presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Elasticstrands_SIM.png)
-
-![\label{SIMMAP_distalDesmo} SIMMAP Cnidoband distal desmonemes presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/distalDesmo_SIM.png)
-
-![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoaband phenotype presence/absence.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)
-
-![\label{SIMMAP_HetType} SIMMAP Heteroneme type.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/hettype_SIM.png)
-
-![\label{SIMMAP_HapType} SIMMAP Haploneme type.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/haptype_SIM.png)
-
 ![\label{SIMMAPguilds} SIMMAP Feeding guilds.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/guild_SIM.png)
-
-\newpage
-
-Bayesian Analysis of Macroevolutionary Mixtures (BAMM) results:
-
-![\label{BAMM_HetElon} Siphonophore ultrametric tree with estimated trait diversification rates of heteroneme elongation, estimated by BAMM.
-Yellow = Rate acceleration.
-Purple = Rate slowdown.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HetElon_BAMM.png)
-
-![\label{BAMM_HetElon_cred} Bayesian 95% credible rate regime shift set for heteroneme elongation.
-Red = rate acceleration.
-Blue = rate slowdown.
-f values are the fraction of the probability of the data accounted for.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HetElon_Cred.png)
-
-![\label{BAMM_HapElon} Siphonophore ultrametric tree with estimated trait diversification rates of haploneme elongation, estimated by BAMM.
-Yellow = Rate acceleration.
-Purple = Rate slowdown.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HapElon_BAMM.png)
-
-![\label{BAMM_HapElon_cred} Bayesian 95% credible rate regime shift set for haploneme elongation.
-Red = rate acceleration.
-Blue = rate slowdown.
-f values are the fraction of the probability of the data accounted for.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/HapElon_Cred.png)
 
@@
 
- ~ ~ ~
-
 ## References {-}

### 2020-02-03 First_Shortening_version/Manuscript_short.Rmd
cleanup of previous submission materials and versions, organized to move forward with PlosBio/PNAS version

--- 2020-01-29 Manuscript_short.Rmd
@@
 The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey.
-Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
+Understanding the relationships between morphology and predatory specialization is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
 However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other.
@@
 The tentilla have great morphological variation across species [@mapstone2014global] (Fig.
-\@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization.
+\@ref(figure2)), which together with their unconfounded function, makes them an ideal system to study the relationships between functional traits and prey specialization.
 Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
@@
 The most abundant type, haplonemes, have no distinct shaft, but similarly to heteronemes, their tubules have open tips and can be found in the cnidoband.
-Both heteronemes and haplonemes bear short spines along the tubule and can be toxic and penetrate the surface of some prey types.
+Both heteronemes and haplonemes bear short spines along the tubule.
+Both can be toxic and penetrate the surface of some prey types.
 In the terminal filament, siphonophores bear two other types of nematocysts, characterized by their adhesive function, closed tip tubules, and lack of spines on the tubule.
@@
   Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
-[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
+Purcell (1984) and Purcell (1988) showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
 

### 2020-02-03 Manuscript_supershort.Rmd
cleanup of previous submission materials and versions, organized to move forward with PlosBio/PNAS version

@@
 bibliography: manuscript.bib
-csl: plos-biology.csl
+csl: pnas.csl
 site: "bookdown::bookdown_site"
@@
 
+## Significance Statement {-}
+
 ## Introduction {-}
@@
 \@ref(figure1)).
-The tentilla have great morphological variation across species [@mapstone2014global], which makes them an ideal system to study the relationships between functional traits and prey specialization.
+The tentilla have great morphological variation across species [@mapstone2014global], which together with their unconfounded function, makes them an ideal system to study the relationships between functional traits and prey specialization.
 Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
@@
 siphonophore colony (photo by Catriona Munro).
-B, C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle (by Freya Goetz).
+B, C - Illustration of a *Nanomia* colony, gastrozooid, and tentacle closeup (by Freya Goetz).
 D - *Nanomia* sp.
@@
   Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization].
-However, recent studies have found that interspecific competition can favor the evolution of resource generalism [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
+However, recent studies have found that interspecific competition can favor the evolution of generalists from specialists [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and specialist resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
 In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open-ocean tactile predators.
@@
 
-  The study of siphonophore tentilla and diets have been limited in the past due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
+  In the past, the study of siphonophore tentilla and diets have been limited due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
 Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
@@
   Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
-[@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
+Purcell [@purcell1984functions;@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
 
-  In this study, we characterize the morphological diversity of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, we expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and we explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
+  In this study, we present the most extensive morphological characterization of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, summarize decades of literature on siphonophore diets, expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
+Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and genetic correlations in their prey capture apparatus.
+These findings show how studying elusive non-bilaterian predators can challenge traditional views on the evolution of predatory specialization.
 
@@
 
-*Novel phylogenetic relationships* – We built upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with broader taxonomic representation using ribosomal genes.
+*Novel phylogenetic relationships* – In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we reconstructed a phylogeny with extensive taxonomic representation.
+This phylogeny builds upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with broader taxonomic representation using ribosomal genes (18S & 16S).
 The topology of our tree recapitulates the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
@@
 Species names in red indicate replicated representation in the morphology data.
-Species marked with a red asterisk were recorded using high-speed video.
 Newly accessioned 16S data was used for species with names in bold.
@@
 
-*Evolutionary associations between diet and tentillum morphology* – Reconstructions of feeding guilds do not recover ancestral diet generalism.
+*Evolutionary associations between diet and tentillum morphology* – We reconstructed the evolutionary history of feeding guilds using stochastic mapping on the new phylogeny.
+Our reconstructions do not recover ancestral diet generalism.
 None of the transitions in diet are consistent with scenario 1 (specialists evolving from generalists).
@@
    We also tested for correlations between shifts in prey selectivity and morphological characters using phylogenetic linear models.
-We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme SA/V ratios, and larger the cnidoband, elastic strand, pedicle and tentacle widths.
+We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme surface area to volume ratio (SA/V), and larger the cnidoband, elastic strand, pedicle and tentacle widths.
 Decapod-selective diets were associated with increasing cnidoband size and coiledness, haploneme row number, elastic strand width, and heteroneme number.
 Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles, and elastic strands.
-Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, reductions in cnidoband size, number of haploneme rows, heteroneme numbers, and cnidoband coiledness.
+Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, cnidoband size, number of haploneme rows, heteroneme numbers, and cnidoband coiledness.
 Heteroneme length and elongation also correlated negatively with chaetognath selectivity (SM21).
@@
   We tested some of the diet-morphology associations previously proposed in the literature [@purcell1984functions;@purcell1988correlation] for correlated evolution (Table 1).
-We found that most, such as heteroneme volume and copepod prey size, do show correlated evolution, consistent with these earlier hypotheses.
+We found that most, such as heteroneme volume and copepod prey size, do show evidence for correlated evolution.
 The sole exception was the relationship between terminal filament nematocysts (rhopalonemes and desmonemes) and crustaceans in the diet.
@@
 
-Table 1. Tests of correlated evolution between morphological characters and aspects of the diet found correlated in the literature.
+Table 1.
+Table 1.
+Tests of correlated evolution between siphonophore morphological characters and aspects of the diet found correlated in the literature.
+We report the direction and significance of the evolutionary association, the number of taxa used for the analysis, and the literature source where the morphology-diet association was first reported.
 
@@
  We were able to identify specific character correlations that shifted with the evolution of new diets.
-Under the majority of SIMMAP outcomes, large crustacean specialists are the ancestral feeding regime, and all other feeding regimes evolve from this ancestral specialization.
+Under the majority of stochastic character mapping outcomes, large crustacean specialists are the ancestral feeding regime, and all other feeding regimes evolve from this ancestral specialization.
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
@@
 The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*.
-With the evolution of fish prey specialization in cystonects and within Clade B, haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positive correlation.
+With the evolution of fish prey specialization in cystonects and within Clade B (Fig.
+\@ref(figure1)), haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positive correlation.
 Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
@@
 Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
-Species nodes in red were manually added to the plot.
+Species nodes in red lack either haplonemes or heteronemes, and their values projected onto the axis of the nematocyst type they bear.
 Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
-Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.
-Colored branches and nodes correspond to BAMM regimes of accelerated haploneme shape (green) and heteroneme shape (violet) evolution.](Figures_final/figure10.jpg)
+Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.](Figures_final/figure10-01.jpg)
 
@@
 
-*Evolution of siphonophore trophic niche* – Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
-Siphonophore species have been observed to feed on a variety of prey with very different sizes, traits, and behaviors.
-Because there is a total absence of siphonophores in the fossil record, how they became established as such ubiquitous and trophically diverse predators in today’s oceans remains an open question.
-
-Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
+*Evolution of siphonophore trophic niche* – Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
 Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times.
@@
 
- *Evolution of nematocyst shape* –  The phylogenetic relationship of siphonophores to other hydrozoans remains an unresolved question [@munro2018improved].
-The most recent work on this front sets them as the sister group to all other Hydroidolina [@kayal2015phylogenetic].
-Therefore, there is great uncertainty around the ancestral plesiomorphies of the common ancestor of all siphonophores.
-This is especially true for those characters that present extreme differences between Cystonectae and Codonophora (the earliest split in the siphonophore phylogeny).
-One such character is the shape of haploneme nematocysts.
-A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
+Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
+While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
+Our findings on the unique evolutionary history of siphonophore trophic specialization elucidate how they arrived to play this fundamental role in the oceanic food web.
+
+ *Evolution of nematocyst shape* –  A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
 This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation].
@@
 [@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
-The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey ([@purcell1984functions] and our unpublished observations), and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
+The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey [@purcell1984functions], and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
 Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
@@
 
-*Phenotypic integration of siphonophore tentilla* – Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
-This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
-
-  While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
+*Phenotypic integration of siphonophore tentilla* – While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
 This evolution of character relationships can allow lineages to explore new regions of the morphospace and facilitate the appearance of ecological novelties.
@@
 
-*Limitations* - While our results unambiguously show that tentillum morphology evolved with diet, and strongly support deviations from the generalist-to-specialist evolution scenario, the conclusions we can draw from these analyses are limited in several ways.
+Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
+In addition, these evolutionary modules point to hypothetical functional modules.
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers.
+obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
+
+*Limitations* - Our results unambiguously show that tentillum morphology evolved with diet and strongly support deviations from the generalist-to-specialist evolution scenario.
+However, the conclusions we can draw from these analyses are limited in several ways.
 The biggest challenge at present is the sparse dietary data available in the literature.
@@
 *Tentillum morphology* – The morphological work was carried out on siphonophore specimens fixed in 4% formalin from the Yale Peabody Museum Invertebrate Zoology (YPM-IZ) collection (accession numbers in Dryad repository).
-These specimens were collected intact across many years of fieldwork expeditions, using blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), and human-operated submersibles.
+These specimens were collected intact across many years of fieldwork expeditions, using blue-water diving [@haddock2005scientific], remotely operated vehicles (ROVs), plankton net trawls, and human-operated submersibles.
 Tentacles were dissected from non-larval gastrozooids, sequentially dehydrated into 100% ethanol, cleared in methyl salicylate, and mounted onto slides with Canada Balsam or Permount mounting media.
@@
 (MK958599) sequenced by Lynne Christianson using the primers from [@cunningham1993molecular] (read 3' to 5' F: TCGACTGTTTACCAAAAACATAGC , R:  ACGGAATGAACTCAAATCATGTAAG) were included and accessioned to NCBI.
-We aligned these sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
-We inferred a Maximum Likelihood (ML) phylogeny (SM6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
-We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
-to assess the relative model fit.
-ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9 and SM11), which was topologically congruent with the unconstrained ML tree.
-The *alpha* priors were selected to minimize prior load in site variation.
+Additional details on the phylogenetic inference methods are available in the Supplementary Methods.
 
@@
 Anela Choy (data available in Dryad repository).
-We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
-eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
-Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
 In order to detect coarse-level patterns in feeding habits, the data were merged into feeding guilds.
-The feeding guilds described here are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
-These were selected to minimize the number of categories while keeping the most different types of prey separate.
-We extracted copepod prey length data from [@purcell1984functions].
+For more details on how the diet data was curated and summarized into guilds, please see Supplementary Methods.
+
+  We also extracted copepod prey length data from [@purcell1984functions].
 To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in the Dryad repository).
 
-*Statistical analyses* – For subsequent comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
-Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
-Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
-All *Nanomia* sp.
-observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
-We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it.
-R scripts and summarized species-collapsed data available in the Dryad repository.
-For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
-We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.
-
+*Statistical analyses* – We used a series of phylogenetic comparative methods to test the evolutionary hypotheses presented in this study.
 We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
@@
 We reconstructed ancestral states using ML (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
+For more details on the data wrangling prior to these analyses, please see the Supplementary Methods.
 R scripts available in the Dryad repository.
@@
 Finally, we compared their AICc support values to select the best fitting model (SM15).
-
 To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (SM21).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
-To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting].
-To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
-To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
 
 In order to study correlations between the rates of evolution between different characters, we fitted a set of evolutionary variance-covariance matrices [@revell2009phylogenetic] (R phytools::evol.vcv).
-When fitting all covariance terms simultaneously (SM36-38), we selected the largest set of characters that would allow the analysis to run without computational singularities.
-This excluded many of the morphometric characters which are linearly dependent on other characters.
-Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
+For more details on the data wrangling preceding these analyses, please see Supplementary Methods.
 To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (SM42).
-These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependence unique to each regime (SM43).
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia* and should be interpreted with care.
+Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependences unique to each regime (SM43).
 
-We carried out linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
+We carried out a linear discriminant analysis of principal components (DAPC) using the dapc function (R adegenet::dapc) [@jombart2010discriminant].
 This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, soft/hard-bodied prey, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
+We generated discriminant functions for feeding guild, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
 From these DAPCs we obtained the highest contributing morphological characters to the discrimination (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
-For each DAPC we generated hypotheses about the diets of siphonophores outside the training set (R adegenet::predict.dapc), incorporating prediction uncertainty as posterior probabilities (SM16-20).
 In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
 We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary].
-Additional details on the optimization are available in the Supplementary Materials.
+Additional details on the DAPC optimization are available in the Supplementary Materials.
 

### 2020-02-03 Supplement_forSupershort.Rmd
cleanup of previous submission materials and versions, organized to move forward with PlosBio/PNAS version

@@
 bibliography: manuscript.bib
-csl: systematic-biology.csl
+csl: pnas.csl
 site: "bookdown::bookdown_site"
@@
 
+Phylogenetic inference: We aligned the sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
+We inferred a Maximum Likelihood (ML) phylogeny (SM6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
+We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
+to assess the relative model fit.
+ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
+Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9 and SM11), which was topologically congruent with the unconstrained ML tree.
+The *alpha* priors were selected to minimize prior load in site variation.
+
+Diet data curation: We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp.
+eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
+Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
+
+The feeding guilds decalred in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+These were selected to minimize the number of categories while keeping the most different types of prey separate.
+
+Data wrangling for comparative analyses: For comparative analyses, we removed species present in the tree but not represented in the morphology data, and *vice versa*.
+Although we measured specimens labeled as *Nanomia bijuga* and *Nanomia cara*, we are not confident in some of the species-level identifications, and some specimens were missing diagnostic zooids.
+Thus, we decided to collapse these into a single taxonomic concept (*Nanomia* sp.).
+All *Nanomia* sp.
+observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
+We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
+\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it.
+R scripts and summarized species-collapsed data available in the Dryad repository.
+For each character (or character pair) analyzed, we removed species with missing data and reported the number of taxa included.
+We tested each character for normality using the Shapiro-Wilk test [@shapiro1965analysis], and log-transformed those that were non-normal.
+
+Data wrangling for the variance-covariance analyses: When fitting all variance-covariance terms simultaneously (SM36-38), we selected the largest set of characters that would allow the analysis to run without computational singularities.
+This excluded many of the morphometric characters which are linearly dependent on other characters.
+Since the functions do not tolerate missing data, we ran the analyses in two ways: One including all taxa but transforming absent states to zeroes, and another removing the taxa with absent states.
+These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia* and should be interpreted with care.
+
+Comparative tools used to test character associations: To test for correlated evolution among binary characters, we used Pagel’s test [@pagel1994detecting].
+To characterize and evaluate the relationship between continuous characters, we used phylogenetic generalized least squares regressions (PGLS) [@grafen1989phylogenetic].
+To compare the evolution of continuous characters with categorical aspects of the diet, we carried out a phylogenetic logistic regression (R nlme::gls using the 'corBrownian' function for the argument ‘correlation’).
+
 DAPC optimization: Some taxa have inapplicable states for certain absent characters (such as the length of a nematocyst subtype that is not present in a species), which are problematic for DAPC analyses.
@@
 
+The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
+
 ## Supplementary Materials {-}
 
-![\label{appendix2} Character definitions. ](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Appendix2.png){height=500px}
+![\label{appendix2} Character definitions. ](Supplementary_materials/Online_appendices/PNGs/Appendix2.png){height=500px}
 
@@
 
-![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained.
-Node labels are bootstrap support values.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/MLunconstrained.png){height=300px}
+![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/PNGs/MLunconstrained.png){height=300px}
 
@@
 (2018).
-](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/constrain.png){height=400px}
+](Supplementary_materials/Online_appendices/PNGs/constrain.png){height=400px}
 
-![\label{ML_constrained} Constrained IQTree ML inference.
-Node labels are bootstrap support values.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/MLconstrained.png){height=300px}
+![\label{ML_constrained} Constrained IQTree ML inference. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/PNGs/MLconstrained.png){height=300px}
 
-![\label{Bayes_unconstrained} Unconstrained Bayesian topology inference in RevBayes (node labels are Bayesian posteriors).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/BAYESunconstrained.png){height=300px}
+![\label{Bayes_unconstrained} Unconstrained Bayesian topology inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/PNGs/BAYESunconstrained.png){height=300px}
 
-![\label{Bayes_constrained} Clade constrained Bayesian inference in RevBayes (node labels are Bayesian posteriors).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/BayesConstrained.png){height=300px}
+![\label{Bayes_constrained} Clade constrained Bayesian inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/PNGs/BayesConstrained.png){height=300px}
 
 ![\label{unconstrained_timetree} Unconstrained ultrametric Bayesian time tree branch length and topology inference in RevBayes (node labels are Bayesian posteriors).
-Arbitrary rooting.).](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Unconstrained timetree.png){height=400px}
+Arbitrary rooting.).](Supplementary_materials/Online_appendices/PNGs/Unconstrained timetree.png){height=400px}
 
@@
 Topology clamped to the Bayesian constrained topology inference in \@ref{Bayes_constrained}.
-Tree rooted using outgroup constraint.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/constrainedTimetree.png){height=500px}
+Tree rooted using outgroup constraint.](Supplementary_materials/Online_appendices/PNGs/constrainedTimetree.png){height=500px}
 
@@
 ![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character.
-Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}
+Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}
 
@@
 Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.
-](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
+](Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
 
@@
 Shgt = slope of the contrasts against node depth.
-Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/OUwie_modelsupport.png)
+Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.](Supplementary_materials/Online_appendices/PNGs/OUwie_modelsupport.png)
 
@@
 Prediction posterior distribution heat map in main text Figure 6.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_guilds.png){height=500px}
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_guilds.png){height=500px}
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_copepod.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_copepod.png)
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_fish.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_fish.png)
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_crustacean.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_crustacean.png)
 
@@
 Cells colored blue indicate phyloGLM p-value < 0.05.
-Cells colored green indicate GLM p-value < 0.05](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/PhyloGLM.png){height=300px}
+Cells colored green indicate GLM p-value < 0.05](Supplementary_materials/Online_appendices/PNGs/PhyloGLM.png){height=300px}
 
-![\label{SIMMAPguilds} SIMMAP Feeding guilds.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/guild_SIM.png)
+![\label{SIMMAPguilds} SIMMAP Feeding guilds.](Supplementary_materials/Online_appendices/PNGs/guild_SIM.png)
 
@@
 Covariances scaled to correlations.
-All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_Nazero.png)
+All characters estimated simultaneously under Brownian Motion.](Supplementary_materials/Online_appendices/PNGs/VCV_Nazero.png)
 
@@
 Covariances scaled to correlations.
-All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_NAremove.png)
+All characters estimated simultaneously under Brownian Motion.](Supplementary_materials/Online_appendices/PNGs/VCV_NAremove.png)
 
@@
 Covariances scaled to correlations.
-All characters estimated simultaneously under Brownian Motion.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_dietaxa.png)
+All characters estimated simultaneously under Brownian Motion.](Supplementary_materials/Online_appendices/PNGs/VCV_dietaxa.png)
 
@@
 Selective regimes were mapped onto the tree using an ancestral state reconstruction of the feeding guilds.
-Blank cells represent computationally singular contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVbestModels.png)
+Blank cells represent computationally singular contrasts.](Supplementary_materials/Online_appendices/PNGs/VCVbestModels.png)
 
-![\label{VCV_ntaxa} Number of taxa used for each pairwise contrast in the VCV analyses, given the number of taxa without inapplicable states.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_ntaxa.png)
+![\label{VCV_ntaxa} Number of taxa used for each pairwise contrast in the VCV analyses, given the number of taxa without inapplicable states.](Supplementary_materials/Online_appendices/PNGs/VCV_ntaxa.png)
 
@@
 Not all regimes are represented in all contrasts.
-Question marks represent computationally singular contrasts.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCV_regimes.png){height=600px}
+Question marks represent computationally singular contrasts.](Supplementary_materials/Online_appendices/PNGs/VCV_regimes.png){height=600px}
 
-![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the whole tree covariance matrix.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
+![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
 
-![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
+![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
 

### 2020-02-03 SysBio_Submission/Manuscript_postsubmission.Rmd
cleanup of previous submission materials and versions, organized to move forward with PlosBio/PNAS version

--- 2019-10-31 Manuscript_postsubmission.Rmd
@@
 Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We conclude that the siphonophores were able to become abundant oceanic predators by occupying a variety of trophic niches facilitated by the evolution and diversification of extraordinary prey capture tools on their tentacles.
+We find that the evolutionary diversification of tools for prey capture contributed to the diversification of trophic interactions.
+Therefore, we identify organismal trait evolution as a key driver in the emergence of food web complexity.
 

### 2020-02-03 Supplementary_materials/Dryad/R_Code.R

@@ -318,145 +318,6 @@ names(elon_data) = c("Heteroneme elongation (log um)", "Haploneme elongation (lo
 elon_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(hap_el))))
 phylomorphospace(elon_tree, elon_data, label="horizontal")
 
-## SIMMAPS used to make categorical evolution figure ##
-par(ask=F)
-tentilla = sharedcategorical$Tentilla
-names(tentilla) = rownames(sharedcategorical)
-prox_het = sharedcategorical$Proximal.heteronemes
-names(prox_het) = rownames(sharedcategorical)
-desmo = sharedcategorical$Desmonemes
-names(desmo) = rownames(sharedcategorical)
-rhopalo = sharedcategorical$Rhopalonemes
-names(rhopalo) = rownames(sharedcategorical)
-dyn_cnido = sharedcategorical$Dynamic.cnidoband
-names(dyn_cnido) = rownames(sharedcategorical)
-elastic = sharedcategorical$Elastic.strand
-names(elastic) = rownames(sharedcategorical)
-distal_desmo = sharedcategorical$Distal.cnidoband.desmonemes
-names(distal_desmo) = rownames(sharedcategorical)
-coiled = sharedcategorical$Coiled.tentilla
-names(coiled) = rownames(sharedcategorical)
-heterotype = sharedcategorical$Heteroneme.type
-heterotype=as.character(heterotype)
-names(heterotype) = rownames(sharedcategorical)
-haplotype = sharedcategorical$Haploneme.type
-haplotype=as.character(haplotype)
-names(haplotype) = rownames(sharedcategorical)
-
-Simmap_list = list()
-###SIMMAP Tentilla:
-make.simmap(ultram_cat, tentilla, nsim = 100) -> tentilla_sim
-Simmap_list[[1]] <- tentilla_sim
-plotTree(ultram_cat, lwd = 4)
-tentilla_sim %>% plotSimmap(lwd = 4, add = T)
-colors = c("black", "red")
-names(colors) = c("Present", "Absent")
-nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
[…]

### 2020-02-03 SysBio_Submission/Supplementary_materials/Dryad/R_Code.R

@@ -1,0 +1,1318 @@
+## LOAD PACKAGES ##
+#General
+library(tidyverse)
+library(magrittr)
+library(stringr)
+library(readr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(OUwie)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(adegenet)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(colorRamps)
+library(PerformanceAnalytics)
+
+# Set paths to input data
+#setwd("~/tentilla_morph/Supplementary_Materials/Dryad/")
+
+#Load raw data
+read.csv("raw_morphology_data.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("raw_categorical_data.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
+castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
[…]

### 2020-03-03 Manuscript_supershort.Rmd
further reductions

@@
 Their tentilla (tentacle side branches) are the exclusive means of prey capture for the large majority of species and have no other known function.
-Earlier work has shown that extant siphonophore diets correlate with the different morphologies and sizes of their tentilla and nematocysts.
-We hypothesize that evolutionary specialization on different prey types has driven the phenotypic evolution of these characters.
-To test this hypothesis, we: (1) measured multiple morphological characters from siphonophore tentacle specimens from 45 species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
+Siphonophores are known to range from generalists to specialists on a broad variety of prey taxa.
+Here we use siphonophores to study how predator specialists and generalists evolve, and how predatory specialization shapes morphological evolution.
+To answer these questions, we: (1) measured 29 morphological characters from siphonophore tentacle specimens from 45 species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
 Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey type are linked to shifts in tentillum and nematocyst size and shape.
@@
 The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-The extreme modularity of tentilla may have released siphonophores from the evolutionary constraints of adaptation to ecologically specialized niches.
 This contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
@@
 ## Significance Statement {-}
+
+Understanding the mechanisms and  processes that give rise to food web structure is fundamental to the study of ecosystem resilience and nutrient flow.
+A key component of these mechanisms is the evolution of predator functional morphology and diet.
+Here we introduce siphonophores as a study system.
+These animals differ in many ways from commonly-known predators, using modular weapons for prey capture (the tentilla) that are fully decoupled from other structures and body functions.
+Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and genetic correlations in their prey capture apparatus.
+These findings show how studying elusive non-bilaterian predators can challenge traditional views on the evolution of predatory specialization.
 
@@
 Understanding the relationships between morphology and predatory specialization is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
-However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other.
+However, for many clades of predators, there is scarce knowledge on how these specializations evolved.
 The primary questions we set out to answer are: how do predator specialists and generalists evolve, and how does predatory specialization shape morphological evolution?
 
-  Siphonophores (Cnidaria: Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig.
+  Siphonophores (Cnidaria: Hydrozoa) are a clade of predatory, gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (fish, crustaceans, jellyfish… etc.).
+Siphonophores carry modular structures that are exclusively used for prey capture: the tentilla (Fig.
 \@ref(figure1)).
-The tentilla have great morphological variation across species [@mapstone2014global], which together with their unconfounded function, makes them an ideal system to study the relationships between functional traits and prey specialization.
+The tentilla have great morphological variation across species [@mapstone2014global].
+Together with their unconfounded function, this makes them an ideal system to study the relationships between functional traits and prey specialization.
 Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
 \@ref(figure1)).
-Each feeding polyp has a single tentacle, which bears a series of side branches known as tentilla.
+Each feeding polyp has a single tentacle, which branches into a series of tentilla (side branches).
 Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes.
@@
 This habitat has fairly homogeneous physical conditions and stable zooplankton abundances and composition [@robison2004deep].
-With a relatively predictable prey availability, ecological theory predicts that interspecific competition would inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we would expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of increasing specialization on a variety of prey types in different siphonophore lineages.
+With relatively predictable prey availability, ecological theory predicts that interspecific competition would inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
+If this prediction holds true, we would expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of specializations on a variety of prey types in different siphonophore lineages.
 
@@
 However, recent studies have found that interspecific competition can favor the evolution of generalists from specialists [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and specialist resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
-In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in open-ocean tactile predators.
+In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in these open-ocean tactile predators.
 To do so, we examine three alternative scenarios of siphonophore trophic specialization: (1) predatory specialists evolved from generalist ancestors; (2) predatory specialists evolved from specialist ancestors which targeted different resources, switching their primary prey type; and (3) predatory generalists evolved from specialist ancestors.
@@
 In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved].
-These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.
-
-  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
 Purcell [@purcell1984functions;@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
@@
 
-*Novel phylogenetic relationships* – In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we reconstructed a phylogeny with extensive taxonomic representation.
-This phylogeny builds upon the published siphonophore transcriptome phylogeny [@munro2018improved] to produce a tree with broader taxonomic representation using ribosomal genes (18S & 16S).
-The topology of our tree recapitulates the resolved nodes in [@dunn2005molecular] and [@munro2018improved].
-Only 5 nodes (blue dots in Figure \@ref(figure4)) in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, and these were constrained to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
-\@ref(figure4)).
-Moreover, with the inclusion of *Stephanomia amphytridis* sequences, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
+*Novel phylogenetic relationships* – In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we needed a siphonophore phylogeny that had broader taxonomic sampling than is available in previously published analyses.
+We first inferred a new tree with the needed taxon sampling with with publicly available ribosomal RNA genes (18S & 16S) and new data from one species.
+This tree is essentially an extended version of that published in [@dunn2005molecular], and the two are congruent.
+We then compared the new extended ribosomal RNA tree to a recently published siphonophore transcriptome phylogeny [@munro2018improved].
+The topology of the extended ribosomal RNA tree recapitulates the resolved nodes in [@dunn2005molecular] and most of the nodes in [@munro2018improved].
+Only 5 nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, 4 of them were poorly supported (bootstrap values <84), and one of them was strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
+Since the transcriptome based topology is based on a much larger amount of data, we constrained the incongruent nodes to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
+\@ref(figure4)).Moreover, with the inclusion of sequences from *Stephanomia amphytridis* and multiple *Erenna* species, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
 
-![\label{figure4} Bayesian time-tree built from 18S + 16S concatenated sequences.
+![\label{figure4} Bayesian time-tree inferred from 18S + 16S concatenated sequences and constrained to be congruent with a published transcriptome phylogeny.
 Branch lengths estimated using a relaxed molecular clock.
 Species names in red indicate replicated representation in the morphology data.
-Newly accessioned 16S data was used for species with names in bold.
+All data was publicly available, apart from new sequences produced for Thermopalia taraxaca and Frillaglma vityazi.
 Nodes labeled with Bayesian posteriors (BP).
@@
 Tips with black squares indicate the species with transcriptomes used in Munro *et al.* (2018).
-Tips with grey squares indicate genus-level correspondence to taxa included in Munro *et al.* (2018).
+Tips with purple squares indicate genus-level correspondence to taxa included in Munro *et al.* (2018).
 The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
@@
 *Evolutionary associations between diet and tentillum morphology* – We reconstructed the evolutionary history of feeding guilds using stochastic mapping on the new phylogeny.
-Our reconstructions do not recover ancestral diet generalism.
+Our reconstructions do not recover generalism as the ancestral siphonophore diet.
 None of the transitions in diet are consistent with scenario 1 (specialists evolving from generalists).
 Feeding guild specializations have shifted from an alternative ancestral state at least five times, consistent with instances supporting scenario 2 (specialists evolving to feed on a different resource).
-Copepod specialization and fish specialization evolved twice, and ostracod specialization evolved at least once.
 We also recover multiple independent origins of generalism from specialist ancestors (Fig.
@@
 To test whether measured morphological characters evolved in association with shifts in feeding ecology, we analyzed the evolutionary history of each character on the phylogeny, with the feeding guilds reconstructed on it as hypothetical selective regimes.
-We fitted and compared alternative evolutionary models for each continuous character.
-The models compared were the white noise (WN; non-phylogenetic model that assumes all values come from a single normal distribution with no covariance structure among species), the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Early Burst (EB) model of decreasing rate of evolutionary change [@harmon2010early], and the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic].
-The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima multi-rate OU model (SM15).
+We fit and compared alternative evolutionary models for each continuous character.
+The models compared were the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a single fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic], and an OU model with multiple optima corresponding to each reconstructed selective regime (feeding guild).
+The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima OU model (SM15).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
@@
   In order to investigate the associations between the evolutionary history of morphological characters and specific prey types found in the diet, we used phylogenetic logistic regressions.
-We found that several characters were significantly correlated with the gains and losses of these prey types (Fig.
+We found that several characters were significantly correlated with the gains and losses of specific prey types (Fig.
 \@ref(figure5), right).
@@
 Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (SM21).
-Evolutionary shifts in these characters likely allowed the inclusion of these prey types in the diet.
+Evolutionary shifts in these characters may have allowed the inclusion of these prey types in the diet.
 
-   We also tested for correlations between shifts in prey selectivity and morphological characters using phylogenetic linear models.
+   In addition to studying correlations with prey type presence/absence, we also tested for correlations between morphological characters and shifts in prey selectivity using phylogenetic linear models.
+Prey selectivity values were calculated from [@purcell1981dietary] by contrasting the gut content frequencies to the corresponding environmental abundances of prey.
 We found that fish selectivity is associated with increased number of heteronemes per tentillum, increased roundness of nematocysts (desmonemes and haplonemes), larger heteronemes, reduced heteroneme/cnidoband length ratios, smaller rhopalonemes, lower haploneme surface area to volume ratio (SA/V), and larger the cnidoband, elastic strand, pedicle and tentacle widths.
@@
 
-*Evolution of the integrated tentillum morphology* – Phenotypic integration results in correlation patterns between morphological characters and their rates of evolution.
+*Evolution of relationships between characters with diet* – Phenotypic integration results in correlation patterns between morphological characters and their rates of evolution.
 To study these patterns, we fit a set of evolutionary variance-covariance matrices [@revell2009phylogenetic].
@@
 
-*Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
-There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
-\@ref(figure10)).
-Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
-In this clade, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
-\@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
-
-![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled).
-Orange area delimits rod-shaped haplonemes, the blue area covers oval and round-shaped haplonemes.
-Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
-Species nodes in red lack either haplonemes or heteronemes, and their values projected onto the axis of the nematocyst type they bear.
-Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
-Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.](Figures_final/figure10-01.jpg)
-
 ## Discussion {-}
 
-*Evolution of siphonophore trophic niche* – Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
+Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
 Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times.
@@
 We do find support for at least 3 instances of specialists switching from one prey type to another prey type, (scenario 2) and two switches from specialist to generalist (scenario 3).
-
 This is consistent with the findings of recent studies on phytophagous insects [@nosil2002transition], where the rate of evolution from generalists to specialists is comparable to the reverse, thus specialization does not limit further evolution.
@@
 
-Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
-Our findings on the unique evolutionary history of siphonophore trophic specialization elucidate how they arrived to play this fundamental role in the oceanic food web.
-
- *Evolution of nematocyst shape* –  A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry].
-This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation].
-Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
-Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
-Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
-[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have converged to feed primarily on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) have also converged morphologically toward more compact haplonemes, significantly distinct from their closest relatives.
-Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna*’s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
-obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
-
-  The implications of these results for the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation.
-Elongate nematocysts can be tightly packed into cnidobands.
-We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
-The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey [@purcell1984functions], and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
-Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure.
-In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis.
-Tendiculophora, comprised of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species.
-Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
-We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
-However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
-
-*Phenotypic integration of siphonophore tentilla* – While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
+While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating].
 This evolution of character relationships can allow lineages to explore new regions of the morphospace and facilitate the appearance of ecological novelties.
@@
 
-Our evolutionary rate covariance results (SM36-38) indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
-This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers.
-obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
-
-*Limitations* - Our results unambiguously show that tentillum morphology evolved with diet and strongly support deviations from the generalist-to-specialist evolution scenario.
+Our results unambiguously show that tentillum morphology evolved with diet and strongly support deviations from the generalist-to-specialist evolution scenario.
 However, the conclusions we can draw from these analyses are limited in several ways.
@@
 Finally, further observations on behavior, digestion biochemistry, and toxin composition are necessary to assess their relative importance in determining diet.
+
+Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
+While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
+Our findings on the unique evolutionary history of siphonophore trophic specialization elucidate how they arrived to play this fundamental role in the oceanic food web.
 
@@
 Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
-Supplementary Materials are available in [https://github.com/dunnlab/tentilla_morph/Supplement_forShort.pdf](https://github.com/dunnlab/tentilla_morph/Supplement_forShort.pdf)
+Supplementary Materials are available in [https://github.com/dunnlab/tentilla_morph/Supplement_forSupershort.pdf](https://github.com/dunnlab/tentilla_morph/Supplement_forSupershort.pdf)
 

### 2020-03-10 Manuscript_supershort.Rmd
changes to abstract and significance statement, commit to PNAS

@@
 
-As predators evolve to feed on different prey taxa, their apparatus for prey capture can adapt into a variety of forms.
-The study of this evolutionary process is facilitated by a predator clade with structures used exclusively for prey capture and with significant morphological variation in these structures.
-Siphonophores, a clade of colonial cnidarians, satisfy these criteria particularly well.
-Their tentilla (tentacle side branches) are the exclusive means of prey capture for the large majority of species and have no other known function.
-Siphonophores are known to range from generalists to specialists on a broad variety of prey taxa.
-Here we use siphonophores to study how predator specialists and generalists evolve, and how predatory specialization shapes morphological evolution.
-To answer these questions, we: (1) measured 29 morphological characters from siphonophore tentacle specimens from 45 species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
-Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey type are linked to shifts in tentillum and nematocyst size and shape.
-We found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-When there are changes in trophic niche, both trait optima and trait correlation patterns showed significant shifts.
-The evolutionary history of tentilla shows that siphonophores are an example of ecological niche diversification via morphological innovation and evolution.
-This contributes to understanding how morphological evolution has shaped present-day oceanic food webs.
+For predators to specialize on different prey taxa, their apparatus for prey capture has to evolve into a variety of forms.
+Specialization has been considered an evolutionary ‘dead-end’ due to the constraints associated with these morphological changes.
+However, in predators with modular structures used exclusively for prey capture, this may not be the case.
+Siphonophores, a clade of colonial cnidarians, use tentilla (tentacle side branches armed with nematocysts) exclusively for prey capture.
+Here we study how siphonophore specialists and generalists evolve, and how their predatory specialization shapes morphological evolution.
+To answer these questions, we: (1) measured 29 morphological characters of tentacles from 45 siphonophore species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
+Instead of a dead-end, we found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey types are linked to shifts in the morphology, mode of evolution, and genetic correlations of tentilla and their nematocysts.
+The evolutionary history of tentilla shows that siphonophores are a unique example of ecological niche diversification via morphological innovation and evolution.
+These findings contribute to understanding how specialization and morphological evolution have shaped present-day food webs.
 
@@
 
-Understanding the mechanisms and  processes that give rise to food web structure is fundamental to the study of ecosystem resilience and nutrient flow.
-A key component of these mechanisms is the evolution of predator functional morphology and diet.
-Here we introduce siphonophores as a study system.
-These animals differ in many ways from commonly-known predators, using modular weapons for prey capture (the tentilla) that are fully decoupled from other structures and body functions.
-Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and genetic correlations in their prey capture apparatus.
-These findings show how studying elusive non-bilaterian predators can challenge traditional views on the evolution of predatory specialization.
+Predatory specialization is often associated with the evolution of modifications in the morphology of the prey capture apparatus.
+Specialization has been considered an evolutionary ‘dead-end’ due to the constraints associated with these morphological changes.
+However, in predators like siphonophores, armed with modular structures used exclusively for prey capture, this assumption becomes challenged.
+Our results show that siphonophores can evolve new prey type specializations and generalism by modifying the morphological states, modes of evolution, and genetic correlations among the parts of their prey capture apparatus.
+These findings demonstrate how studying open-ocean non-bilaterian predators can reveal novel patterns and mechanisms in the evolution of specialization.
+Understanding these evolutionary processes is fundamental to the study of food web structure and complexity.
 
@@
 The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey.
-Understanding the relationships between morphology and predatory specialization is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure.
+Characterizing the relationships between morphology and predatory specialization is necessary to understand how the phenotypic diversity of predators determines food web structure.
 However, for many clades of predators, there is scarce knowledge on how these specializations evolved.
@@
 
-  Siphonophores (Cnidaria: Hydrozoa) are a clade of predatory, gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (fish, crustaceans, jellyfish… etc.).
+  Siphonophores (Cnidaria: Hydrozoa) are a clade of predatory, gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (often fish, crustaceans, and jellyfish).
 Siphonophores carry modular structures that are exclusively used for prey capture: the tentilla (Fig.
@@
 The tentilla have great morphological variation across species [@mapstone2014global].
-Together with their unconfounded function, this makes them an ideal system to study the relationships between functional traits and prey specialization.
+Together with their well understood function, this makes them an ideal system to study the relationships between functional traits and prey specialization.
 Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig.
@@
 With relatively predictable prey availability, ecological theory predicts that interspecific competition would inhibit the coexistence of closely-related species unless evolution towards specialization reduces the breadth of each species’ niche [@simpson1944tempo;@hardin1960competitive;@hutchinson1961paradox].
-If this prediction holds true, we would expect the prey capture apparatus morphologies of siphonophores to diversify with the evolution of specializations on a variety of prey types in different siphonophore lineages.
+If this prediction holds true, we would expect the prey-capture apparatus morphologies of siphonophores to diversify with the evolution of specializations on a variety of prey types in different siphonophore lineages.
 
@@
 
-  In the past, the study of siphonophore tentilla and diets have been limited due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
+  In the past, the study of siphonophore tentilla and diets has been limited due to the inaccessibility of their oceanic habitat and the difficulties associated with the collection of fragile siphonophores.
 Thus, the morphological diversity of tentilla has only been characterized for a few taxa, and their evolutionary history remains largely unexplored.
@@
 
-  In this study, we present the most extensive morphological characterization of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, summarize decades of literature on siphonophore diets, expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
+  In this study, we present an extensive morphological characterization of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, summarize the literature on siphonophore diets, expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
 Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and genetic correlations in their prey capture apparatus.
@@
 
-*Novel phylogenetic relationships* – In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we needed a siphonophore phylogeny that had broader taxonomic sampling than is available in previously published analyses.
-We first inferred a new tree with the needed taxon sampling with with publicly available ribosomal RNA genes (18S & 16S) and new data from one species.
+*Novel phylogenetic relationships* –  In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we needed a siphonophore phylogeny that had broader taxonomic sampling than was available in previously published analyses.
+We first inferred a new tree with the needed taxon sampling with publicly available ribosomal RNA genes (18S & 16S) and new data from one species.
 This tree is essentially an extended version of that published in [@dunn2005molecular], and the two are congruent.
@@
 The topology of the extended ribosomal RNA tree recapitulates the resolved nodes in [@dunn2005molecular] and most of the nodes in [@munro2018improved].
-Only 5 nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, 4 of them were poorly supported (bootstrap values <84), and one of them was strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
-Since the transcriptome based topology is based on a much larger amount of data, we constrained the incongruent nodes to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
-\@ref(figure4)).Moreover, with the inclusion of sequences from *Stephanomia amphytridis* and multiple *Erenna* species, our tree reveals a novel phylogenetic relationship between the genus *Erenna* and *Stephanomia*.
+Only 5 nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, 4 of them were poorly supported (bootstrap values <84), and only one of them was strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
+We constrained the incongruent nodes to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
+\@ref(figure4)).
+Since the transcriptome-based placement of *Nanomia bijuga* is more consistent with the morphological data, that relationship was also constrained.
+Moreover, with the inclusion of sequences from *Stephanomia amphytridis* and multiple *Erenna* species, our tree reveals a novel sister relationship between the genus *Erenna* and *Stephanomia*.
 
@@
 The models compared were the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a single fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic], and an OU model with multiple optima corresponding to each reconstructed selective regime (feeding guild).
-The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima OU model (SM15).
+The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima OU model (S15).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
@@
 Shifts to copepod presence in the diet were associated with reductions in haploneme width, cnidoband length and width, total haploneme and heteroneme volumes, and tentacle and pedicle widths.
-Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (SM21).
+Consistently, transitions to decapod presence in the diet correlated with more coiled cnidobands (S21).
 Evolutionary shifts in these characters may have allowed the inclusion of these prey types in the diet.
@@
 Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, cnidoband size, number of haploneme rows, heteroneme numbers, and cnidoband coiledness.
-Heteroneme length and elongation also correlated negatively with chaetognath selectivity (SM21).
+Heteroneme length and elongation also correlated negatively with chaetognath selectivity (S21).
 These results indicate that not only diet but also differential feeding selectivity has evolved in correlation with changes in the prey capture apparatus of siphonophores.
@@
 The quantitative characters we measured from tentilla and their nematocysts are highly correlated.
-The results indicate that the dimensionality (number of independent axes of variation) of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (SM4).
-The variance-covariance matrices (SM36-38) are congruent with the abundant positive correlations observed among simple measurement characters in SM3.
+The results indicate that the dimensionality (number of independent axes of variation) of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (S4).
+The variance-covariance matrices (S36-38) are congruent with the abundant positive correlations observed among simple measurement characters in S3.
 This analysis more clearly reveals the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
@@
 
- In order to test whether rate covariance matrices changed with evolutionary shifts in feeding guild regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (SM41).
-We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (SM39), indicating that the mode of phenotypic integration also shifts with trophic niche.
-When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (SM42).
+ In order to test whether rate covariance matrices changed with evolutionary shifts in feeding guild regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (S41).
+We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (S39), indicating that the mode of phenotypic integration also shifts with trophic niche.
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (S42).
 These results indicate that the evolutionary dependencies in these integrated modules are changing across the phylogeny, and evolving together with changes in prey type specializations.
@@
 
-  Siphonophores occupy diverse predatory niches in the open ocean, ranging from mid-trophic small-crustacean eaters to piscivorous super-carnivores.
-With the evolution of diversified prey type specialization comes the evolution of morphologies adapted to the challenges posed by different prey.
-The results presented here indicate that the associations found between siphonophore tentilla and their prey are a product of correlated evolution in highly integrated traits.
+Most studies on the evolution of predation have focused on vertebrate systems with a prey capture apparatus (such as jaws and limbs) deeply integrated into their bodies, serving multiple functions.
+This has led to a biased understanding of the evolutionary outcomes of specialization, where extreme morphological evolution constrains further shifts in their ecology.
+Siphonophores differ in many ways from commonly-known predators, using modular weapons for prey capture (the tentilla) that are fully decoupled from other structures and body functions.
+Our analysis of the evolutionary history of dietary specialization and morphological change in these elusive animals has revealed notable deviations from traditional expectations.
 While much of the feeding ecology literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-We find that the character states, evolutionary optima, and genetic correlations of many tentillum characters have evolved following these shifts in trophic niche.
-Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of siphonophore taxa and characters, and can be used to generate hypotheses on the feeding habits of uncharacterized species.
-We identify key aspects of organismal trait evolution that are central to understanding the emergence of food web complexity.
+We find that the character states, evolutionary optima, and genetic correlations of many morphological characters have evolved following these ecological shifts.
+Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of siphonophore taxa and characters.
+These findings are central to understanding the evolutionary mechanisms driving the emergence of food web complexity.
 
@@
 The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
-Thirty characters (defined in SM5) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
+Thirty characters (defined in S5) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
 We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles) since they are too variable to quantify.
@@
 
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (SM8 and SM10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (SM11-12).
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (S8 and S10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (S11-12).
 Scripts available in the Dryad repository.
@@
 *Statistical analyses* – We used a series of phylogenetic comparative methods to test the evolutionary hypotheses presented in this study.
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-We then ranked the models in order of increasing parametric complexity (WN, BM, EB, OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM13).
-We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM14).
-We calculated phylogenetic signal in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM13).
 We reconstructed ancestral states using ML (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
@@
 Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
-The ML reconstruction was congruent with the consensus stochastic character mapping (SM31).
-Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
-Finally, we compared their AICc support values to select the best fitting model (SM15).
-To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (SM21).
+The ML reconstruction was congruent with the consensus stochastic character mapping (S31).
+Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution (OUm) matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
+We then ranked the models in order of increasing parametric complexity (BM, OU, OUm), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
+When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (S15).
+In addition, we calculated and reported the model adequacy scores using the R package *arbutus* [@pennell2015model].
+To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (S21).
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
@@
 For more details on the data wrangling preceding these analyses, please see Supplementary Methods.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (SM42).
-Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependences unique to each regime (SM43).
+To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (S42).
+Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependences unique to each regime (S43).
 
@@
 This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (SM16-20).
+We generated discriminant functions for feeding guild, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (S16-20).
 From these DAPCs we obtained the highest contributing morphological characters to the discrimination (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).

### 2020-03-10 Supplement_forSupershort.Rmd
further reductions
changes to abstract and significance statement, commit to PNAS

@@
 
-![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character.
-Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}
-
-![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character.
-Cvar = coefficient of variation of the absolute value of the contrasts.
-Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances.
-Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node.
-Shgt = slope of the contrasts against node depth.
-Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.
-](Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
-
 ![\label{ModelSupportOUwie} Model support (delta AICc) for each morphological character analyzed on the feeding guild reconstruction regime tree.
@@
 
+\newpage
+
 ## References {-}

### 2020-03-16 Manuscript_supershort.Rmd
SHDH comments incorporated. Title page for PNAS

@@
 
+# Classification: Biological Sciences {-}
+
 # Shaped to kill: The evolution of siphonophore tentilla for specialized prey capture in the open ocean {-}
@@
 
-\‡ Corresponding author: Alejandro Damian-Serrano, email: alejandro.damianserrano@yale.edu
+## ORCID: Alejandro Damian-Serrano: 0000-0002-2544-0489; Steven H.D. Haddock: 0000-0001-9420-4482; Casey Dunn: 0000-0003-0628-5150
+
+\‡ Corresponding author: Alejandro Damian-Serrano. Address: 165 Prospect St., New Haven, CT, 06511. Phone: (401) 441-9613. Email: alejandro.damianserrano@yale.edu.
+
+## Keywords {-}
+
+Siphonophores, nematocysts, predation, specialization, character evolution
+
+\newpage
 
@@
 
-## Keywords {-}
-
-Siphonophores, tentilla, nematocysts, predation, specialization, character evolution
-
 ## Significance Statement {-}
@@
 Specialization has been considered an evolutionary ‘dead-end’ due to the constraints associated with these morphological changes.
-However, in predators like siphonophores, armed with modular structures used exclusively for prey capture, this assumption becomes challenged.
-Our results show that siphonophores can evolve new prey type specializations and generalism by modifying the morphological states, modes of evolution, and genetic correlations among the parts of their prey capture apparatus.
+However, in predators like siphonophores, armed with modular structures used exclusively for prey capture, this assumption is challenged.
+Our results show that siphonophores can evolve generalism and new prey-type specializations by modifying the morphological states, modes of evolution, and genetic correlations between the parts of their prey capture apparatus.
 These findings demonstrate how studying open-ocean non-bilaterian predators can reveal novel patterns and mechanisms in the evolution of specialization.
-Understanding these evolutionary processes is fundamental to the study of food web structure and complexity.
+Understanding these evolutionary processes is fundamental to the study of food-web structure and complexity.
 
@@
 The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey.
-Characterizing the relationships between morphology and predatory specialization is necessary to understand how the phenotypic diversity of predators determines food web structure.
+Characterizing the relationships between morphology and predatory specialization is necessary to understand how the phenotypic diversity of predators determines food-web structure.
 However, for many clades of predators, there is scarce knowledge on how these specializations evolved.
@@
 
-  Siphonophores (Cnidaria: Hydrozoa) are a clade of predatory, gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (often fish, crustaceans, and jellyfish).
+  Siphonophores (Cnidaria: Hydrozoa) are a clade of gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (often fish, crustaceans, and jellyfish).
 Siphonophores carry modular structures that are exclusively used for prey capture: the tentilla (Fig.
@@
 
-*Novel phylogenetic relationships* –  In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we needed a siphonophore phylogeny that had broader taxonomic sampling than was available in previously published analyses.
+*Novel phylogenetic relationships* –  In order to analyze the relationships between morphology and diet across the evolutionary history of siphonophores, we generated a siphonophore phylogeny that had broader taxonomic sampling than was available in previously published analyses.
 We first inferred a new tree with the needed taxon sampling with publicly available ribosomal RNA genes (18S & 16S) and new data from one species.
@@
 The topology of the extended ribosomal RNA tree recapitulates the resolved nodes in [@dunn2005molecular] and most of the nodes in [@munro2018improved].
-Only 5 nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, 4 of them were poorly supported (bootstrap values <84), and only one of them was strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
+Only five nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, with four of them poorly supported (bootstrap values <84), and only one of them strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
 We constrained the incongruent nodes to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
@@
 Species names in red indicate replicated representation in the morphology data.
-All data was publicly available, apart from new sequences produced for Thermopalia taraxaca and Frillaglma vityazi.
+All data were publicly available, apart from new sequences produced for Thermopalia taraxaca and Frillaglma vityazi.
 Nodes labeled with Bayesian posteriors (BP).
@@
 Tips with purple squares indicate genus-level correspondence to taxa included in Munro *et al.* (2018).
-The main clades are labeled: in black for described taxonomic units, and in grey for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
+The main clades are labeled: with black bars for described taxonomic units, and grey bars for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
 
@@
 
-*Evolutionary associations between diet and tentillum morphology* – We reconstructed the evolutionary history of feeding guilds using stochastic mapping on the new phylogeny.
+*Evolutionary associations between diet and tentillum morphology* – We reconstructed the evolutionary history of feeding guilds using stochastic mapping on the new phylogeny (Fig.
+\@ref(figure5)).
 Our reconstructions do not recover generalism as the ancestral siphonophore diet.
@@
 We fit and compared alternative evolutionary models for each continuous character.
-The models compared were the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a single fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic], and an OU model with multiple optima corresponding to each reconstructed selective regime (feeding guild).
+The models compared were the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a single fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic], and an OU model with multiple optima (OUm) corresponding to each reconstructed selective regime (feeding guild).
 The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima OU model (S15).
@@
 
-   In addition to studying correlations with prey type presence/absence, we also tested for correlations between morphological characters and shifts in prey selectivity using phylogenetic linear models.
+   In addition to studying correlations with prey type presence/absence in the diet, we also tested for correlations between morphological characters and shifts in prey selectivity using phylogenetic linear models.
 Prey selectivity values were calculated from [@purcell1981dietary] by contrasting the gut content frequencies to the corresponding environmental abundances of prey.
@@
 The results indicate that the dimensionality (number of independent axes of variation) of tentillum morphology is low, that many traits are associated with size, but that nematocyst arrangement and shape are independent of it (S4).
-The variance-covariance matrices (S36-38) are congruent with the abundant positive correlations observed among simple measurement characters in S3.
+The variance-covariance matrices (S21-23) are congruent with the abundant positive correlations observed among simple measurement characters in S3.
 This analysis more clearly reveals the diagonal blocks that constitute the evolutionary modules, such as the heteroneme block, the terminal filament nematocyst block, and the cnidoband-pedicle-tentacle block.
@@
 
- In order to test whether rate covariance matrices changed with evolutionary shifts in feeding guild regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (S41).
-We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (S39), indicating that the mode of phenotypic integration also shifts with trophic niche.
-When contrasting the regime-specific rate correlation matrices to the whole-tree matrix, we were able to identify the character dependencies that are unique to each predatory niche (S42).
-These results indicate that the evolutionary dependencies in these integrated modules are changing across the phylogeny, and evolving together with changes in prey type specializations.
+  In order to test whether rate covariance matrices changed with evolutionary shifts in feeding guild regimes, we compared the rate covariance terms between characters across the subtrees occupied by the different feeding guild regimes (S21).
+We found that half (48%) of the character pairs presented significantly distinct correlation coefficients across different regimes (S19), indicating that the mode of phenotypic integration also shifts with trophic niche.
+When contrasting the regime-specific rate correlation matrices to the whole-tree matrix and to the preceding ancestral regime matrix, we were able to identify the character dependencies that are unique to each predatory niche (S22-23).
 
@@
 Compared to the rate correlation matrix estimated over the whole tree, large crustacean specialists present strong negative correlations between haploneme elongation and heteroneme size, and between rhopaloneme elongation and tentillum size, as well as with involucrum length.
-Within generalist clades (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmonemes and rhopalonemes) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
+Within generalist clades (*Forskalia* and the *Agalma-Athorybia* clade), terminal filament nematocyst (desmoneme and rhopaloneme) sizes became negatively correlated with the sizes of most characters, meaning that as some tentilla became larger, their individual terminal nematocysts became smaller, observed to the extreme in *Agalma*.
 In addition, heteroneme and rhopaloneme elongation became positively correlated with cnidoband size.
@@
 \@ref(figure1)), haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positive correlation.
+This is consistent with Clade B haplonemes becoming rounder, more similar to Cystonect haplonemes specialized in fish prey penetration and envenomation.
 Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
@@
 
-Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization is an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
+Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization can be an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
 Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times.
@@
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
-In more familiar predators, the prey capture apparatus is well integrated in the body (such as claws and jaws), leading to trade-offs and whole body adaptations to feeding specialization.
-The extreme modularity of the siphonophore prey capture apparatus could release them from the constraints typically imposed by adaptation to ecological specialization.
+In more familiar predators, the prey capture apparatus (such as claws and jaws) is well integrated in the body, leading to trade-offs and whole-body adaptations for feeding specialization.
+The extreme modularity of the siphonophore prey capture apparatus could release them from constraints typically imposed by adaptation to ecological specialization.
 This evolutionary mechanism is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
@@
 
-Most studies on the evolution of predation have focused on vertebrate systems with a prey capture apparatus (such as jaws and limbs) deeply integrated into their bodies, serving multiple functions.
+Most studies on the evolution of predation have focused on vertebrate systems with an integrated feeding apparatus serving multiple functions.
 This has led to a biased understanding of the evolutionary outcomes of specialization, where extreme morphological evolution constrains further shifts in their ecology.
@@
 We find that the character states, evolutionary optima, and genetic correlations of many morphological characters have evolved following these ecological shifts.
-Our extended morphological characterization shows that the relationships between form and ecology hold across a large set of siphonophore taxa and characters.
+We find that the relationships between form and ecology hold across a large set of siphonophore taxa and characters.
 These findings are central to understanding the evolutionary mechanisms driving the emergence of food web complexity.
@@
 The slides were imaged as tiled z-stacks using differential interference contrast (DIC) on an automated stage at YPM-IZ (with the assistance of Daniel Drew and Eric Lazo-Wasem) and with laser point confocal microscopy using a 488 nm Argon laser that excited autofluorescence in the tissues.
-Thirty characters (defined in S5) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
+Thirty characters (defined in S1) were measured using Fiji [@collins2007imagej;@schindelin2012fiji].
 We did not measure the lengths of contractile structures (terminal filaments, pedicles, gastrozooids, and tentacles) since they are too variable to quantify.
@@
 (MK958599) sequenced by Lynne Christianson using the primers from [@cunningham1993molecular] (read 3' to 5' F: TCGACTGTTTACCAAAAACATAGC , R:  ACGGAATGAACTCAAATCATGTAAG) were included and accessioned to NCBI.
-Additional details on the phylogenetic inference methods are available in the Supplementary Methods.
+Additional details on the phylogenetic inference methods can be found in the Supplementary Methods.
 
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (S8 and S10)) after fixing the 5 nodes that were incongruent with the topology of the consensus tree in [@munro2018improved].
-This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (S11-12).
-Scripts available in the Dryad repository.
+Unconstrained ML and Bayesian phylogenies were congruent (S2,S5).
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (S4,S6)) after clamping the 5 nodes (S3) that were incongruent with the topology of the consensus tree in [@munro2018improved].
+This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (S7-8).
+Scripts and tree files available in the Dryad repository.
 
@@
 We also extracted copepod prey length data from [@purcell1984functions].
-To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in the Dryad repository).
+To calculate specific prey selectivities, we extracted quantitative diet and zooplankton composition data from [@purcell1981dietary], matched each diet assessment to each prey field quantification by site, calculated Ivlev’s electivity indices [@jacobs1974quantitative], and averaged those by species (data available in Dryad repository).
 
@@
 Then, we reconstructed the feeding guild ancestral states using the ML function ace (package ape [@paradis2019package]), removing tips with no feeding data.
-The ML reconstruction was congruent with the consensus stochastic character mapping (S31).
+The ML reconstruction was congruent with the consensus stochastic character mapping (S15).
 Then, using the package *OUwie* [@beaulieu2012ouwie], we fitted an OU model with multiple optima and rates of evolution (OUm) matched to the reconstructed ancestral diet regimes, a single optimum OU model, and a BM null model, inspired by the analyses in [@cressler2015detecting].
 We then ranked the models in order of increasing parametric complexity (BM, OU, OUm), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (S15).
+When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (S9).
 In addition, we calculated and reported the model adequacy scores using the R package *arbutus* [@pennell2015model].
-To model the evolutionary associations between individual tentillum and nematocyst characters and the ability to capture particular prey types in the diet, we ran a series of phylogenetic generalized linear models (R phylolm::phyloglm) (S21).
-In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
 
@@
 For more details on the data wrangling preceding these analyses, please see Supplementary Methods.
-To test whether phenotypic integration changes across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (S42).
-Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependences unique to each regime (S43).
+To test whether phenotypic integration changed across selective regimes determined by the reconstructed feeding guilds, we carried out character-pairwise variance-covariance analysis comparing alternative models (R phytools::evolvcv.lite), including those where correlations are the same across the whole tree and models where correlations differ between selective regimes (S19).
+Number of taxa used in each pairwise comparison is reported in S20.
+Finally, we compared regime-specific variance-covariance matrices to the general matrix and to their preceding regime matrix to identify the changes in character dependences unique to each regime (S21-22).
 
@@
 This function allowed us to incorporate more predictors than individuals.
-We generated discriminant functions for feeding guild, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (S16-20).
+We generated discriminant functions for feeding guild, and for the presence of copepods, fish, and shrimp (large crustaceans) in the diet (S10-13).
 From these DAPCs we obtained the highest contributing morphological characters to the discrimination (characters in the top quartile of the weighted sum of the linear discriminant loadings controlling for the eigenvalue of each discriminant).
-In order to identify the sign of the relationship between the predictor characters prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) with the top contributing characters (from the corresponding DAPC) as predictors.
+In order to identify the sign of the relationship between the predictor characters and prey type presence in the diet, we then generated generalized logistic regression models (as a type of generalized linear model, or GLM using R stats::glm) and phylogenetic generalized linear models (R phylolm::phyloglm) with the top contributing characters (from the corresponding DAPC) as predictors (S14).
 We also carried out these GLMs on the Ivlev’s selectivity indices for each prey type calculated from [@purcell1981dietary].
+In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
 Additional details on the DAPC optimization are available in the Supplementary Materials.

### 2020-03-16 Supplement_forSupershort.Rmd
SHDH comments incorporated. Title page for PNAS

@@
 Phylogenetic inference: We aligned the sequences using MAFFT [@katoh2002mafft] (alignments available in Dryad).
-We inferred a Maximum Likelihood (ML) phylogeny (SM6) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
+We inferred a Maximum Likelihood (ML) phylogeny (S2) from 16S and 18S ribosomal rRNA genes using IQTree [@nguyen2014iq] with 1000 bootstrap replicates (iqtree -s alignment.fa -nt AUTO -bb 1000).
 We used ModelFinder [@kalyaanamoorthy2017modelfinder] implemented in IQTree v1.5.5.
@@
 ModelFinder selected GTR+R4 for having the lowest Bayesian Information Criterion score.
-Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (SM9 and SM11), which was topologically congruent with the unconstrained ML tree.
+Additionally, we inferred a Bayesian tree with each gene as an independent partition in RevBayes [@hohna2016revbayes] (S5), which was topologically congruent with the unconstrained ML tree.
 The *alpha* priors were selected to minimize prior load in site variation.
@@
 Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
-
-The feeding guilds decalred in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
+The feeding guilds declared in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
 These were selected to minimize the number of categories while keeping the most different types of prey separate.
@@
 observations were matched to the phylogenetic position of *Nanomia bijuga* in the tree.
-We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (Fig.
-\@ref(figure4)), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it.
+We carried out all phylogenetic comparative statistical analyses in the programming environment R [@team2017r], using the Bayesian ultrametric species tree (S8), and incorporating intraspecific variation estimated from the specimen data as standard error whenever the analysis tool allowed it.
 R scripts and summarized species-collapsed data available in the Dryad repository.
@@
 
-Data wrangling for the variance-covariance analyses: When fitting all variance-covariance terms simultaneously (SM36-38), we selected the largest set of characters that would allow the analysis to run without computational singularities.
+Data wrangling for the variance-covariance analyses: When fitting all variance-covariance terms simultaneously (S16-18), we selected the largest set of characters that would allow the analysis to run without computational singularities.
 This excluded many of the morphometric characters which are linearly dependent on other characters.
@@
 These analyses could only be carried out on the subset of taxa for which diet data is available, and only among character pairs that are not computationally singular for that taxonomic subset.
-Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia* and should be interpreted with care.
+Gelatinous specialist correlations could only be estimated for a small subset of characters present in *Apolemia* (S21F, S22E, S23D) and should be interpreted with care.
 
@@
 This optimization aims to find the compromise value with highest discrimination power with the least overfitting.
-
-The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (SM21).
+The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width (S10).
 

### 2020-04-07 Manuscript_supershort.Rmd
SHDH final comments and error proofing

@@
 
-## ORCID: Alejandro Damian-Serrano: 0000-0002-2544-0489; Steven H.D. Haddock: 0000-0001-9420-4482; Casey Dunn: 0000-0003-0628-5150
+ORCID: Alejandro Damian-Serrano: 0000-0002-2544-0489; Steven H.D. Haddock: 0000-0001-9420-4482; Casey Dunn: 0000-0003-0628-5150
 
@@
 
-For predators to specialize on different prey taxa, their apparatus for prey capture has to evolve into a variety of forms.
-Specialization has been considered an evolutionary ‘dead-end’ due to the constraints associated with these morphological changes.
-However, in predators with modular structures used exclusively for prey capture, this may not be the case.
-Siphonophores, a clade of colonial cnidarians, use tentilla (tentacle side branches armed with nematocysts) exclusively for prey capture.
-Here we study how siphonophore specialists and generalists evolve, and how their predatory specialization shapes morphological evolution.
+Predator specialization has often been considered an evolutionary ‘dead-end’ due to the constraints associated with the evolution of morphological and functional optimizations throughout the organism.
+However, in some predators, these changes are localized in separate structures dedicated to prey capture.
+One of the most extreme cases of this modularity can be observed in siphonophores, a clade of pelagic colonial cnidarians that use tentilla (tentacle side branches armed with nematocysts) exclusively for prey capture.
+Here we study how siphonophore specialists and generalists evolve, and what morphological changes are associated with these transitions.
 To answer these questions, we: (1) measured 29 morphological characters of tentacles from 45 siphonophore species, (2) mapped these data to a phylogenetic tree, and (3) analyzed the evolutionary associations between morphological characters and prey type data from the literature.
-Instead of a dead-end, we found that predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
+Instead of a dead-end, we found that siphonophore specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
 Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey types are linked to shifts in the morphology, mode of evolution, and genetic correlations of tentilla and their nematocysts.
-The evolutionary history of tentilla shows that siphonophores are a unique example of ecological niche diversification via morphological innovation and evolution.
+The evolutionary history of siphonophore specialization helps build a broader perspective on predatory niche diversification via morphological innovation and evolution.
 These findings contribute to understanding how specialization and morphological evolution have shaped present-day food webs.
@@
   Siphonophores bear four major nematocyst types in their tentacles and tentilla (Fig.
-\@ref(figure1)F)..
+\@ref(figure1)F).
 The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule.
@@
 In addition, well-supported phylogenies based on molecular data are now available for these organisms [@munro2018improved].
-These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
+These advances allow for the examination of the evolutionary relationships between modern siphonophore form, function, and ecology.
+Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and have shown that siphonophores are a robust system for the study of predatory specialization via morphological diversification.
 Purcell [@purcell1984functions;@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
@@
 The topology of the extended ribosomal RNA tree recapitulates the resolved nodes in [@dunn2005molecular] and most of the nodes in [@munro2018improved].
-Only five nodes in the unconstrained tree inference were incongruent with the [@munro2018improved] transcriptome tree, with four of them poorly supported (bootstrap values <84), and only one of them strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
+Only five nodes in the unconstrained tree inference were incongruent with the transcriptome tree in [@munro2018improved], with four of them poorly supported (bootstrap values <84), and only one of them strongly supported (*Frillagalma vityazi*-*Nanomia bijuga*, 100 bootstrap support).
 We constrained the incongruent nodes to the [@munro2018improved] topology during estimation of the constrained 18S+16S tree inference (Fig.
@@
 Species names in red indicate replicated representation in the morphology data.
-All data were publicly available, apart from new sequences produced for Thermopalia taraxaca and Frillaglma vityazi.
+All data were publicly available, apart from new sequences produced for *Thermopalia taraxaca* and *Frillaglma vityazi* (bold).
 Nodes labeled with Bayesian posteriors (BP).
@@
 This finding is particularly compelling given in that it is the opposite of known biases in ancestral state reconstruction.
-[@nosil2005testing] found that such methods tend to infer higher transition rates toward the more frequent state.
+Nosil and Mooers [@nosil2005testing] found that such methods tend to infer higher transition rates toward the more frequent state.
 In this case, that would lead to a bias for an increased rate of transition from generalists (the rarer state across the tips) to specialists (the more common state across the tips).
@@
 The models compared were the Brownian Motion (BM) model of neutral divergent evolution [@martins1996phylogenies], the Ornstein-Uhlenbeck (OU) model of stabilizing selection around a single fitted optimum state [@uhlenbeck1930theory;@butler2004phylogenetic], and an OU model with multiple optima (OUm) corresponding to each reconstructed selective regime (feeding guild).
-The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven multi-optima OU model (S15).
+The model comparison shows that out of 30 characters, 10 show significantly stronger support for the diet-driven OUm (S15).
 These characters include terminal filament nematocyst size and shape, involucrum length, elastic strand width, and heteroneme number.
-Most of these characters are found exclusively in Tendiculophora, thus this may reflect processes that could be unique to this subtree.
+Most of these characters are found exclusively in Tendiculophora, thus this may reflect processes that could be unique to this clade.
 Five characters including cnidoband length, cnidoband shape, and haploneme length show maximal support for a diet-driven single-optimum OU model.
@@
 Copepod-selective diets evolved in association with smaller heteroneme and total nematocyst volumes, smaller cnidobands, rounder rhopalonemes, elongated heteronemes, narrower haplonemes with higher SA/V ratios, and smaller heteronemes, tentacles, pedicles, and elastic strands.
-Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, cnidoband size, number of haploneme rows, heteroneme numbers, and cnidoband coiledness.
+Selectivity for ostracods was associated with reductions in size and number of heteroneme nematocysts, cnidoband size, number of haploneme rows, heteroneme number, and cnidoband coiledness.
 Heteroneme length and elongation also correlated negatively with chaetognath selectivity (S21).
 These results indicate that not only diet but also differential feeding selectivity has evolved in correlation with changes in the prey capture apparatus of siphonophores.
+For each prey type studied, tentillum morphology is a much better predictor of prey selectivity than of prey presence in the diet, despite prey selectivity data being available for a smaller subset of species.
+Interestingly, many of the morphological predictors had opposite slope signs when predicting prey selectivity *versus* predicting prey presence in the diet (Table 2).
 
@@
 
-Table 1.
 Table 1.
@@
 When large crustacean specialists switched to small crustacean prey in *Cordagalma* and calycophorans, haploneme size became inversely correlated with heteroneme elongation, which in turn developed a strong positive relationship with tentillum size.
-In other words, as tentilla get smaller in this group, heteronemes get shorter and haplonemes get larger.
-The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*.
+The extremes of this gradient can be seen in *Cordagalma* and *Hippopodius*, genera subspecialized in copepods and ostracods respectively.
 With the evolution of fish prey specialization in cystonects and within Clade B (Fig.
 \@ref(figure1)), haploneme elongation became negatively correlated with heteroneme elongation (signal driven by Clade B, since cystonects lack tentacular heteronemes), and the surface area to volume ratio of haploneme nematocysts switched from a strong negative relationship with cnidoband size (found in every other regime) to a positive correlation.
-This is consistent with Clade B haplonemes becoming rounder, more similar to Cystonect haplonemes specialized in fish prey penetration and envenomation.
-Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts that are likely effective at anchoring gelatinous tissue (see reference to Narcomedusae nematocysts in [@purcell1988correlation]).
+This is consistent with Clade B haplonemes becoming rounder, more similar to cystonect haplonemes specialized in fish prey penetration and envenomation.
+Gelatinous specialization, albeit appearing only once in our tree, also carries a unique signature in character rate correlation shifts, with an increase in the strength of the correlation between heteroneme shape and shaft width, consistent with the appearance of birrhopaloid nematocysts with swollen shafts.
+These are likely effective at anchoring gelatinous tissue in a similar way to the nematocysts of the Narcomedusae [@purcell1988correlation].
 
@@
 The extreme modularity of the siphonophore prey capture apparatus could release them from constraints typically imposed by adaptation to ecological specialization.
-This evolutionary mechanism is particularly important in a deep open ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
+This evolutionary mechanism is particularly important in a deep open-ocean ecosystem, which is a relatively homogeneous physical environment, where the primary niche heterogeneity available is the potential interactions between organisms [@robison2004deep].
 
@@
 The biggest challenge at present is the sparse dietary data available in the literature.
-Additional dietary data could reveal transitions from generalists to specialists we were unable to detect for two reasons.
-First, some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization.
-Second, some of the taxa not included in our dataset could be undiscovered generalists.
+Additional dietary data could reveal transitions from generalists to specialists we were unable to detect for two reasons: some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization; and some of the taxa not included in our dataset could be undiscovered generalists.
 When interpreting these results, it is also important to remember that diet is also dependent on environmental prey availability.
@@
 
-Siphonophores are an abundant group of zooplankton in oceanic ecosystems [@longhurst1985structure;@o2007copepod].
-While little is known about siphonophore trophic ecology, what is known indicates that they occupy a central position in midwater food webs [@choy2017deep], serving as important trophic intermediaries between smaller zooplankton and higher trophic level predators.
-Our findings on the unique evolutionary history of siphonophore trophic specialization elucidate how they arrived to play this fundamental role in the oceanic food web.
-
 ## Conclusions {-}
@@
 Most studies on the evolution of predation have focused on vertebrate systems with an integrated feeding apparatus serving multiple functions.
-This has led to a biased understanding of the evolutionary outcomes of specialization, where extreme morphological evolution constrains further shifts in their ecology.
+This has led to a narrow understanding of the evolutionary outcomes of specialization, where extreme morphological evolution constrains further shifts in their ecology.
 Siphonophores differ in many ways from commonly-known predators, using modular weapons for prey capture (the tentilla) that are fully decoupled from other structures and body functions.
@@
 Unconstrained ML and Bayesian phylogenies were congruent (S2,S5).
-Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (S4,S6)) after clamping the 5 nodes (S3) that were incongruent with the topology of the consensus tree in [@munro2018improved].
+Given the broader sequence sampling of the transcriptome phylogeny, we ran constrained inferences (using both ML and Bayesian approaches, which produced fully congruent topologies (S4,S6)) after clamping the 5 nodes (S3, blue circles in Fig.
+\@ref(figure4)) that were incongruent with the topology of the consensus tree in [@munro2018improved].
 This topology was then used to inform a Bayesian relaxed molecular clock time-tree in RevBayes, using a birth-death process (sampling probability calculated from the known number of described siphonophore species) to generate ultrametric branch lengths (S7-8).
@@
 In addition, we ran a series of comparative analyses to address hypotheses of diet-tentillum relationships posed in the literature.
-Additional details on the DAPC optimization are available in the Supplementary Materials.
+Additional details on the DAPC optimization are available in the Supplementary Methods.
 
@@
 
-Data available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
-Supplementary Materials are available in [https://github.com/dunnlab/tentilla_morph/Supplement_forSupershort.pdf](https://github.com/dunnlab/tentilla_morph/Supplement_forSupershort.pdf)
+Data will be available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+Supplementary Materials (Supplementary Methods and figures) are appended following this manuscript text, data available in [https://github.com/dunnlab/tentilla_morph/tree/master/Supplementary_materials](https://github.com/dunnlab/tentilla_morph/tree/master/Supplementary_materials)
 
-## Funding {-}
+## Acknowledgements {-}
 
@@
 was supported by a Fulbright Spain Graduate Studies Scholarship.
-
-## Acknowledgements {-}
-
 We wish to thank the crew and scientists of the R/V Western Flyer, who participated in the collection of many of the specimens used in this study.

### 2020-04-07 Supplement_forPNAS.Rmd
SHDH final comments and error proofing

--- 2020-03-16 Supplement_forSupershort.Rmd
@@
   - \doublespacing
+  - \usepackage{placeins}
 ---
@@
 
-Alejandro Damian-Serrano, Steven H.D. Haddock, Casey W. Dunn
-
 ## Supplementary Methods {-}
@@
 eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
-Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
+Personal observations on feeding (from SHDH, Anela Choy, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
 The feeding guilds declared in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
@@
 
-Other trees inferred in this work include:
-
 ![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/PNGs/MLunconstrained.png){height=300px}
-
-The constrained tree inferences utilized the following constrain topology:
 
@@
 
-DAPC discriminant analyses:
-
 ![\label{DAPCguilds} DAPC for Feeding guilds.
@@
 
-Ordinary and phylogenetic logistic regression of morphological characters and the presence/absence of prey types:
-
 ![\label{GLMs} Logistic regressions between continuous morphological characters and prey type presences.
@@
 \newpage
-
-Variance-Covariance Matrix analyses of phenotypic intergation and evolutionary modularity:
 
@@
 
-![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
+![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in S21 and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
 
-![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
+![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in S21 and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
 
@@
 
+\FloatBarrier
+
 ## References {-}

### 2020-04-10 Organismal_paper/Organismal_manuscript_and_code.Rmd
started folder and RMD for organismal paper

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
---

```{r setup, include=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)
library(stringr)
library(reshape2)
	## Biological
library(Rphylip)
library(arbutus)
library(vegan)
library(ape)
library(phangorn)
library(phytools)
library(picante)
library(geiger)
library(phylobase)
library(fields)
library(phylosignal)
library(geomorph)
library(phylopath)
library(phylolm)
	## Graphics
library(FactoMineR)
library(factoextra)
library(corrplot)
library(BAMMtools)
library(gridExtra)
library(xtable)
library(colorRamps)

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set(
	  progress=TRUE,
	  verbose=TRUE)
	opts_chunk$set(
	#  include=FALSE,
	  cache=TRUE,
	  echo=FALSE,
	  message=FALSE
	 )
knitr::opts_chunk$set(echo = TRUE)

```

# The Morphological Diversification of Siphonophore Tentilla {-}

Alejandro Damian-Serrano^1^^,‡^, Steven H.D. Haddock^2^, Casey W. Dunn^1^

^1^ Yale University, Department of Ecology and Evolutionary Biology, 165 Prospect St., New Haven, CT 06520, USA

^2^ Monterey Bay Aquarium Research Institute, 7700 Sandholdt Rd., Moss Landing, CA 95039, USA

\‡ Corresponding author: Alejandro Damian-Serrano, email: alejandro.damianserrano@yale.edu

## Abstract {-}

Siphonophore tentilla (tentacle side branches) are unique biological structures for prey capture, composed of a complex arrangement of cnidocytes (stinging cells) bearing different types of nematocysts (stinging capsules) and auxiliary structures. Tentilla present an extreme morphological diversity of form and function across species. While associations between tentilla form and diet have been reported, the evolutionary history giving rise to this morphological diversity is largely unexplored. Here we explore the evolutionary gains and losses of novel tentilla substructures on the most recent siphonophore phylogeny. Tentilla have a precisely coordinated high-speed strike mechanism of synchronous unwinding and nematocysts discharge. Here we characterize the kinematic diversity of this prey capture reaction using high-speed video and find relationships with morphological characters. Since tentillum discharge occurs in synchrony across a broad morphological diversity, we evaluate how phenotypic integration is maintaining character correlations across evolutionary time. Moreover, we analyze the dimensionality of the tentillum morphospace, identify instances of heterochrony and morphological convergence, and generate hypotheses on the diets of understudied siphonophore species. Our findings indicate that siphonophore tentilla are phenotypically integrated structures with a complex evolutionary history leading to a phylogenetically structured diversity of forms which are predictive of kinematic performance and feeding habits.

## Keywords {-}

Siphonophore, tentilla, nematocysts, character evolution

## Introduction {-}

Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration. However, far less attention has been devoted to their unique tentacular structures: the tentilla. Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts. But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by shooting the nematocyst battery to slap around the prey. This maximizes the surface area of contact between the nematocysts and the prey they fire upon. Siphonophore tentilla present an exuberant diversity of morphologies, sizes, and nematocyst complements (Figure 1).

![\label{figure2} Tentillum diversity. The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow). Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species. A - *Erenna laciniata*, 10x. B - *Lychnagalma utricularia*, 10x. C - *Agalma elegans*, 10x. D - *Resomia ornicephala*, 10x. E - *Frillagalma vityazi*, 20x. F - *Bargmannia amoena*, 10x. G - *Cordagalma* sp., reproduced from Carré 1968. H - *Lilyopsis fluoracantha*, 20x. I - *Abylopsis tetragona*, 20x.](~/tentilla_morph/Figures_final/figure2.jpg)

In [@damianserrano2020shaped], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history. The analyses we carried out led to novel insights into the evolution of predatory specialization. However, this work left behind many fascinating discoveries on the evolutionary history of tentilla morphology, including nematocyst novelties, phenotypic integration, convergent evolution, paedomorphosis, and predictions on diet using morphology. Here, we present these findings and shed light on the natural history of siphonophores.

## Methods {-}

We explore the evolutionary history and diversification of tentilla morphologies using phylogenetic comparative methods on the morphological dataset and phylogeny published in [@damianserrano2020shaped].  We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger]. These models include a non-phylogenetic whie-noise model (WN), a neutral divergence Brownian Motion model (BM), an early-burst decreasing rate model (EB), and an Ornstein-Uhlenbeck model with stabilizing selection around a fitted optimum trait value. We then ranked the models in order of increasing parametric complexity (WN, BM, EB, OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support. When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM13). We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM14). We calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM13).

In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools]. Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset. This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters. In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].

## Results {-}

![\label{figure3} Heatmap summarizing the morphological diversity measured in Damian-Serrano *et al.* 2020 for 96 species of siphonophores clustered by similarity (raw data in Dryad repository). Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells. Values scaled by character.](~/tentilla_morph/Figures_final/figure3.jpg)

*Evolutionary history of tentillum morphology* – [@damianserrano2020shaped] produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships. This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*. *Erenna* and *Stephanomia* bear the largest tentilla among all siphonophores, thus their monophyly indicates that there was a single evolutionary transition to giant tentilla. Siphonophore tentilla range in size from ~30 µm in some *Cordagalma* specimens to 2-4 cm in *Erenna* species, and up to 8 cm in *Stephanomia amphytridis* [@pugh2014review]. Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm. The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.

  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis]. The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition. In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.

In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7). Some of these characters include the gain and loss of nematocyst types. Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans. Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora. Haplonemes were likely lost in the tentacles of *Apolemia* but retained as spherical isorhizas in other *Apolemia* tissues [@siebert2013re]. Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.

  The clades defined in [@damianserrano2020shaped] are characterized by unique evolutionary innovations in their tentilla. The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*. Innovations that arose along the stem of this group include spatially segregated heteroneme and haploneme nematocysts, terminal filaments, and elastic strands (Fig. \@ref(figure7)). Pyrostephids evolved a unique bifurcation of the axial gastrovascular canal of the tentillum known as the "saccus" [@totton1965synopsis]. The stem to the clade Tendiculophora (clade containing Euphysonectae and Calycophorae) subsequently acquired further novelties such as the desmoneme and rhopaloneme (acrophore subtype ancestral) nematocysts on the terminal filament (Fig. \@ref(figure7)), which bears no other nematocyst type. These are arranged in sets of 2 parallel rhopalonemes for each single desmoneme [@skaer1988formation;@skaer1991remodelling]. The involucrum is an expansion of the epidermal layer that can cover part or all of the cnidoband (Fig. \@ref(figure2)). This structure, together with differentiated larval tentilla, appeared in the stem branch to Clade A physonects. Calycophorans evolved novelties such as larger desmonemes at the distal end of the cnidoband, pleated pedicles with a “hood” (here considered homologous to the involucrum) at the proximal end of the tentillum, anacrophore rhopalonemes, and microbasic mastigophore-type heteronemes. While calycophorans have diversified into most of the extant described siphonophore species (108 of 186), their tentilla have not undergone any major categorical gains or losses since their most recent common ancestor. Nonetheless, they have evolved a wide variation in nematocyst and cnidoband sizes.

![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped. Some branch lengths were modified from the Bayesian chronogram to improve readability. The main visually distinguishable tentillum types are sketched next to the species that bear them, showing the location and arrangement of the main characters. In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification. The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](~/tentilla_morph/Figures_final/figure7.jpg)

*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damianserrano2020shaped] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)). Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1. Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals. The majority (67%) of characters support BM models, indicating a history of neutral constant divergence. No relationship between phylogenetic signal and BM model support was found. Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time. No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).

![\label{figure8} A. Correlogram showing strength of ordinary (upper triangle) and phylogenetic (lower triangle) correlations between characters. Both size and color of the circles indicate the strength of the correlation (R^2^). B. Scatterplot of phylogenetic correlation against ordinary correlation showing a strong linear relationship (R^2^ = 0.92, 95% confidence between 0.90 and 0.93). Light red and blue boxes indicate congruent negative and positive correlations respectively. Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](~/tentilla_morph/Figures_final/figure8.jpg){height=600px}
*Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae. There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig. \@ref(figure10)). Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this clade, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig. \@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).

![\label{figure10} Phylomorphospace showing haploneme and heteroneme elongation (log scaled). Orange area delimits rod-shaped haplonemes, the blue area covers oval and round-shaped haplonemes. Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM. Species nodes in red lack either haplonemes or heteronemes, and their values projected onto the axis of the nematocyst type they bear. Cystonects have no tentacle heteronemes and are projected onto the haploneme axis. Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis. ](~/tentilla_morph/Figures_final/figure10.jpg)

*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (SM\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (SM\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative. Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5. Similarly, of the across-species correlations, 49.1% were >0.5 and only 1.5% were < -0.5. We found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients. Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length). These disparities can be caused by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered. However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54). Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.

![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters. A. Variance explained by each variable in the PC1-PC2 plane. Axis labels include the phylogenetic signal (K) for each component and p-value. B. Phylogenetic relationships between the species points distributed in that same space.](~/tentilla_morph/Figures_final/figure9.jpg){height=600px}

  In the non-phylogenetic PCA morphospace using only simple characters (SM\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%. In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).

The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes. This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies present. Since most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected. Similarly, correlations between the features of different nematocyst subtypes within a species are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution]. However, we also found correlations between nematocyst and tentillum characters. Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum. These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid). Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation]. Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies. Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.

*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository. While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology. For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002). This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.

  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001). Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012). Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.

*Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published. We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using the linear discriminant analysis of principal components (DAPC) fitted in [@damianserrano2020shaped]. This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
The discriminant analysis in [@damianserrano2020shaped] for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width. We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in the morphological dataset. This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*. When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM\@ref(DAPCsofthard)). The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length. We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans). While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (SM\@ref(DAPCfish),SM\@ref(DAPCcrustacean)), specialization on fish or large crustacean prey can be fully disentangled (SM\@ref(DPACguilds)).

  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC. Cell darkness indicates the posterior probability of belonging to each guild. Training data set transformed so inapplicable states are computed as zeroes. Species ordered and colored according to their predicted feeding guild.](~/tentilla_morph/Figures_final/figure6.jpg)

## Discussion {-}

*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damianserrano2020shaped] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues]. This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures. In addition, these evolutionary modules point to hypothetical functional modules. For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers. obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae. An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major]. The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.

Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny. However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig. \@ref(figure4)). We searched for rate regime shifts in the evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35). BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33). For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig. \@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (SM35). Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids. Most of these taxa have rod-shaped anisorhizas, but *Erenna* have oval ones. No significant regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.

*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, our work reveals the specific morphological changes in the prey capture apparatus associated with these changes. Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans. These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts. Tentilla are expensive single-use structures [@Mackie:1987uy], therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance. *Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*. This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphic heterochrony associated with predatory specialization on smaller prey.

Our work identifies a novel example of convergent evolution. The region of the tentillum morphospace (SM4) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*. Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas. Unlike calycophorans, they lack paired elongate microbasic mastigophores. Instead, they bear exactly three oval stenoteles, and their cnidobands are followed by a branched vesicle, unique to this genus. Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles. Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions]. The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey. The DAPCs in [@damianserrano2020shaped] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.

*Evolution of nematocyst shape* –  A remarkable feature of siphonophore haplonemes is that they are outliers to all other Medusozoa in their surface area to volume relationships, deviating significantly from sphericity [@thomason1988allometry]. This suggests a different mechanism for their discharge that could be more reliant on capsule tension than on osmotic potentials [@carre1980triggering], and strong selection for efficient nematocyst packing in the cnidoband [@thomason1988allometry;@skaer1988formation]. Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state. Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state. Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects. [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora. The two clades that have converged to feed primarily on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) have also converged morphologically toward more compact haplonemes, significantly distinct from their closest relatives. Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst]. *Erenna*’s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers. obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.

  The implications of these results for the evolution of nematocyst function are that an innovation in the discharge mechanism of haplonemes may have occurred during the main shift to elongation. Elongate nematocysts can be tightly packed into cnidobands. We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation]. [@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration. The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey [@purcell1984functions], and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages. Entangling requires less acceleration and power during discharge than penetration, as it does not rely on point pressure. In fish-eating cystonects and *Erenna* species, the haplonemes are much less elongated and very effective at penetration, in congruence with the osmotic discharge hypothesis. Tendiculophora, composed of the clades Euphysonectae and Calycophorae, includes the majority of siphonophore species. Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found. We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade. However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.

*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics. Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone. The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles. While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions. This reveals the need to extensively characterize siphonophore diets and feeding habits. In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species. Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone. In many of the ecological models found in the literature, interactions among the oceanic zooplankton have been treated as a black box [@mitra2009closure]. The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
## Acknowledgements {-}
This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C. Anela Choy). A.D.S. was supported by a Fulbright Spain Graduate Studies Scholarship.

## Supplementary Materials {-}

![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character. Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}

![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character. Cvar = coefficient of variation of the absolute value of the contrasts. Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances. Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node. Shgt = slope of the contrasts against node depth. Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)

## References {-}

```{r code}
# Set paths to input data
setwd("~/tentilla_morph/Organismal_paper/")

#Load raw data
read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_morphology_data.csv") -> numbers
numbers$Species = as.character(numbers$Species)
categorical <- read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_categorical_data.csv")[,-2]
rownames(categorical) = categorical$Species

#Correct species spellings
numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"

#Merge Nanomias
numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"

#Polish fields
castnumbers = numbers
castnumbers[castnumbers=="needDIC"] <- NA
castnumbers[castnumbers=="needConfocal"] <- NA
castnumbers[castnumbers=="needMature"] <- NA
castnumbers[castnumbers=="needReslide"] <- NA
castnumbers[castnumbers==-1] <- NA
castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.character)
castnumbers[,c(-1,-2,-3)] <- sapply(castnumbers[,c(-1,-2,-3)],as.numeric)

#Define functions to deal with NAs and decimals
mean.na <- function(a){mean(a, na.rm = TRUE)}
var.na <- function(a){var(a, na.rm = TRUE)}
round3 <- function(a){round(a, 3)}

#Compute morphometric ratios
coiledness = castnumbers$Cnidoband.free.length..um./castnumbers$Cnidoband.length..um.
heteroneme_elongation = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.width..um.
haploneme_elongation = castnumbers$Haploneme.free.length..um./castnumbers$Haploneme.width..um.
desmoneme_elongation = castnumbers$Desmoneme.length..um./castnumbers$Desmoneme.width..um.
rhopaloneme_elongation = castnumbers$Rhopaloneme.length..um./castnumbers$Rhopaloneme.width..um.
heteroneme_shaft_extension = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.shaft.free.length..um.
Heteroneme_to_CB = castnumbers$Heteroneme.free.length..um./(castnumbers$Cnidoband.free.length..um.+0.001)
total_heteroneme_volume = castnumbers$Heteroneme.volume..um3.*castnumbers$Heteroneme.number
total_haploneme_volume = (castnumbers$Cnidoband.free.length..um./castnumbers$Haploneme.width..um.)*((4*pi/3)*0.5*castnumbers$Haploneme.free.length..um.*((0.5*castnumbers$Haploneme.width..um.)^2))
cnidomic_index = log(total_heteroneme_volume + total_haploneme_volume)
cnidomic_index[which(is.na(cnidomic_index))] <- log(total_haploneme_volume[which(is.na(cnidomic_index))])
cnidomic_index[which(is.na(cnidomic_index))] <- log(castnumbers[which(is.na(cnidomic_index)), "Heteroneme.volume..um3."])
cnidomic_index[cnidomic_index==-Inf]<-NA

#Define surface and volume functions
surface_ellipsoid <- function(L, W){
  a <- L/2
  b <- W/2
  c = b
  S <- 4*pi*((((a*b)^1.6)+((a*c)^1.6)+((c*b)^1.6))/3)^(1/1.6)
  return(S)
}
volume_ellipsoid <- function(L, W){
  a <- L/2
  b <- W/2
  c = b
  V <- (4/3)*pi*a*b*c
  return(V)
}

SAV_haploneme = surface_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)/volume_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)
names(SAV_haploneme) = castnumbers$Species
SAV_heteroneme = surface_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)/volume_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)
names(SAV_heteroneme) = castnumbers$Species

#Combine all morphometric variables
morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index, SAV_haploneme)
names(morphometrics)[1:2] = c("slide_id"," Species")

#Combine morphometrics with regular characters
castnumbers = data.frame(castnumbers,morphometrics[,c(-1,-2)])

#Logtransform variables which are not normal
castlogs = castnumbers
non_normal = apply(castnumbers[,c(-1,-2,-3)], 2, shapiro.test) %>% lapply(function(x){x$p.value}) %>% unlist() 
non_normal = which(as.vector(non_normal) < 0.05)+3
castlogs[,non_normal] <- sapply(castnumbers[,non_normal], log)
castlogs[castlogs==-Inf]<-NA

#Means, varinces, standard errors
castmeans <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], mean.na, na.action = na.pass)
castmean_logs <- aggregate(. ~  Species, data = castlogs[,c(-1,-3)], mean.na, na.action = na.pass)
castvariances <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], FUN = var.na, na.action = na.pass) #[,-2]
castvariance_logs <- aggregate(. ~  Species, data = castlogs[,c(-1,-3)], FUN = var.na, na.action = na.pass)
castvariances[is.na(castvariances)] <- 0
castvariance_logs[is.na(castvariance_logs)] <- 0
castN <- aggregate(. ~  Species, data = castnumbers[,c(-1,-3)], length, na.action = na.pass) 
castN = data.frame(castN$Species, rowMeans(castN[,-1])) #[,-2]
names(castN) = c("Species", "N_specimens")
castSE <- cbind(castvariances$Species, sqrt(castvariances[,-1])/sqrt(castN$N_specimens))
castSE_logs <- cbind(castvariance_logs$Species, sqrt(castvariance_logs[,-1])/sqrt(castN[,-1]))
names(castSE)[1] <- "Species"
names(castSE_logs)[1] <- "Species"

#Make overview of data and heatmap
Ses = castSE[,-1]
Ses[Ses == 0] = NA
morphdata = cbind(castN, castmeans[,-1], Ses)
morphdata = morphdata[,c(1:3,33,4,34,5,35,6,36,7,37,8,38,9,39,10,40,11,41,12,42,13,43,14,44,15,45,16,46,17,47,18,48,19,49,20,50,21,51,22,52,23,53,24,54,25,55,26,56,27,57,28,58,29,59,30,60,31,61,32,62)]
names(morphdata) = str_replace_all(names(morphdata),".1","_SE")
#write.csv(morphdata, "characterdata.csv")

heatdata = as.matrix(castmean_logs[,-1])
rownames(heatdata) = castmean_logs$Species
heatdata[is.nan(heatdata)]<- -1
#hcolors = grDevices::terrain.colors(20)
library(colorspace)
hcolors <- colorRampPalette(c("#e0ecf4","#9ebcda","#8856a7"), bias=1)
hcolors <- colorRampPalette(c("#ffeda0","#feb24c","#f03b20"), bias=1)
hcolors <- colorRampPalette(c("yellow","purple"), bias=1)
#hcolors <- sequential_hcl(17, h = 245, c = c(40, 75, 0), l = c(30, 95), power = 1)
hcolors <- c(rep("#000000FF",10), hcolors(30))
heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)

#Load phylogenetic tree
consensus = read.nexus("~/tentilla_morph/Supplementary_materials/TreeBase/RB_constrained_timetree/TimeTree_siphs_mcmc_MAP.tre") %>% drop.tip(56:61)
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")
#Switch Nanomia bijuga for Nanaomia sp
consensus$tip.label[which(consensus$tip.label == "Nanomia bijuga")] <- "Nanomia sp"

#Prune quant matrix to tree species
matrix = castnumbers[which(!is.na(castnumbers$Species)),]
matrix_logs = castlogs[which(!is.na(castlogs$Species)),]
sharedspp = matrix$Species[which(matrix$Species %in% consensus$tip.label)]
sharedmatrix = matrix[which(matrix$Species %in% sharedspp),]
sharedlogs = matrix_logs[which(matrix$Species %in% sharedspp),]
sharedmeans = castmeans[which(castmeans$Species %in% sharedspp),]
sharedmean_logs = castmean_logs[which(castmean_logs$Species %in% sharedspp),]
sharedvars = castvariances[which(castvariances$Species %in% sharedspp),]
sharedvar_logs = castvariance_logs[which(castvariance_logs$Species %in% sharedspp),]

#Prune categorical matrix to tree species
cat_rowNAs = apply(categorical[,-1], 1, function(x) sum(is.na(x)))
catmatrix = categorical[which(cat_rowNAs<1),] %>% .[,-1]
sharedspp_cat = rownames(catmatrix)[which(rownames(catmatrix) %in% consensus$tip.label)]
sharedcategorical = catmatrix[which(rownames(catmatrix) %in% sharedspp_cat),]

#Prune tree to quant matrix species
nodatatipnames = consensus$tip.label[which(!(consensus$tip.label %in% sharedmatrix$Species))]
nodatatips = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames)]
prunedtree = drop.tip(consensus, nodatatips)
prunedtree$tip.label
plot(prunedtree)
#ultram = chronos(prunedtree)
ultram = prunedtree
plot(ultram)

#Prune tree to categorical matrix species
nodatatipnames_cat = consensus$tip.label[which(!(consensus$tip.label %in% sharedspp_cat))]
nodatatips_cat = c(1:length(consensus$tip.label))[which(consensus$tip.label %in% nodatatipnames_cat)]
cat_tree = drop.tip(consensus, nodatatips_cat)
cat_tree$tip.label
plot(cat_tree)
#ultram_cat = chronos(cat_tree)
ultram_cat = cat_tree
plot(ultram_cat)
sharedcategorical = sharedcategorical[match(ultram_cat$tip.label, rownames(sharedcategorical)),]
cprunedmatrix = sharedcategorical[which(rownames(sharedcategorical)%in%rownames(sharedmatrix)),] %>% .[which(sapply(.,function(x) length(unique(x)))>1)]
sharedbinary = sharedcategorical
sharedbinary$Haploneme.type = as.character(sharedbinary$Haploneme.type)
sharedbinary[sharedbinary=="Isorhizas"] = 0
sharedbinary[sharedbinary=="Anisorhizas"] = 1
sharedbinary$Haploneme.type = as.numeric(sharedbinary$Haploneme.type)
sharedbinary$Heteroneme.type = as.character(sharedbinary$Heteroneme.type)
sharedbinary[sharedbinary=="Stenotele"] = 0
sharedbinary[sharedbinary=="Microbasic mastigophore"] = 1
sharedbinary[sharedbinary=="Eurytele"] = NA
sharedbinary$Heteroneme.type = as.numeric(sharedbinary$Heteroneme.type)

#Purely numerical character sets without slide or species
Q_sharedmatrix = sharedmatrix[,c(-1,-2,-3)]
rownames(sharedmeans) = sharedmeans$Species
Q_sharedmeans = sharedmeans[,-1]
rownames(sharedvars) = sharedvars$Species
Q_sharedvars = sharedvars[,-1]
Q_sharedmean_logs = sharedmean_logs[,-1]
rownames(Q_sharedmean_logs) = sharedmean_logs$Species

### COMPARATIVE ANALYSES ###

phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
#phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmeans[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  #CH_I=as.numeric(sharedmeans[,i])
  names(CH_I) = sharedmean_logs$Species
  #names(CH_I) = sharedmeans$Species
  SE_I = as.numeric(castSE[,i]) %>% log()
  SE_I[which(SE_I==-Inf)] = 0
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  class(treeI) = "phylo"
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
  phylosignals$K = round(phylosignals$K,3)
}
#write.csv(phylosignals, "PhylosignalsWSE_log.csv")

#Model support
AICdf = as.data.frame(matrix(ncol=6,nrow=ncol(Q_sharedmean_logs)))
colnames(AICdf) = c("Variable", "white_noise", "starBM", "BM", "EB", "OU")
for(c in 1:ncol(Q_sharedmean_logs)){
  startree <- rescale(ultram, "lambda", 0)
  C = Q_sharedmean_logs[,c]
  names(C) = rownames(Q_sharedmean_logs)
  C = C[!is.na(C)]
  Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
  startree = drop.tip(startree, which(!(startree$tip.label %in% names(C))))
  Cse = castSE[,c+1] %>% log() %>% abs()
  Cse[which(Cse == Inf)] <- 0
  names(Cse) = castSE$Species
  Cse = Cse[which(names(Cse) %in% names(C))]
  model_matrix = matrix("NA", nrow = 5, ncol = 3)
  colnames(model_matrix) = c("aicc","aicc_best","dAICc")
  row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
  for(j in 1:dim(model_matrix)[1]){
    if(j==2){
      temp_model = fitContinuous(startree, C, model="BM", SE = Cse)$opt
    }
    else{
      temp_model = fitContinuous(Ctree, C, model=row.names(model_matrix)[j], SE = Cse)$opt
    }
    model_matrix = apply(model_matrix,2, as.numeric)
    row.names(model_matrix) = c("white", "starBM", "BM", "EB", "OU")
    model_matrix[j, "aicc"] <- temp_model$aicc
  }
  model_matrix[,"aicc_best"] <- min(model_matrix[,"aicc"])
  model_matrix[,"dAICc"] <- model_matrix[, "aicc"] - model_matrix[j, "aicc_best"]
  print(names(Q_sharedmean_logs)[c])
  string_c <- c(names(Q_sharedmean_logs)[c], model_matrix[,3])
  names(string_c) = colnames(AICdf)
  AICdf[c,] <- string_c
}
AICdf[,2:6] = apply(AICdf[,2:6], 2, as.numeric) %>% apply(2, round3)
#write.csv(AICdf, "log_model_support.csv")

#Model adequacy
worthy_models = AICdf[which(AICdf$white_noise != 0 & AICdf$starBM != 0),]
MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
rownames(MAD) = worthy_models$Variable
for(m in 1:nrow(worthy_models)){
  C = Q_sharedmean_logs[,which(names(Q_sharedmean_logs) == worthy_models$Variable[m])]
  names(C) = rownames(Q_sharedmean_logs)
  C = C[!is.na(C)]
  Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
  C = C[match(Ctree$tip.label, names(C))]
  class(Ctree)="phylo"
  FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
  UTC <- make_unit_tree(FC)
  picstat_data <- calculate_pic_stat(UTC)
  sim <- simulate_char_unit(UTC)
  picstat_sim <- calculate_pic_stat(sim)
  compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
}
phy_models = data.frame(worthy_models,MAD)
phy_models[,7:12] = apply(phy_models[,7:12], 2,round3)
#write.csv(phy_models, "model_adequacy.csv")

#Nematocyst shape evolution - phylomorphospace figure
het_el = sharedmean_logs$heteroneme_elongation
names(het_el) = sharedmean_logs$Species
hap_el = sharedmean_logs$haploneme_elongation
names(hap_el) = sharedmean_logs$Species
het_el = het_el[which(!is.na(het_el))]
hap_el = hap_el[which(!is.na(hap_el))]
hap_el = hap_el[which(names(hap_el) %in% names(het_el))]
het_el = het_el[which(names(het_el) %in% names(hap_el))]
het_el = het_el[match(names(hap_el), names(het_el))]
elon_data = cbind(het_el, hap_el) %>% as.data.frame()
names(elon_data) = c("Heteroneme elongation (log um)", "Haploneme elongation (log um)")
elon_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(hap_el))))
phylomorphospace(elon_tree, elon_data, label="horizontal")

## SIMMAPS used to make categorical evolution figure ##
par(ask=F)
tentilla = sharedcategorical$Tentilla
names(tentilla) = rownames(sharedcategorical)
prox_het = sharedcategorical$Proximal.heteronemes
names(prox_het) = rownames(sharedcategorical)
desmo = sharedcategorical$Desmonemes
names(desmo) = rownames(sharedcategorical)
rhopalo = sharedcategorical$Rhopalonemes
names(rhopalo) = rownames(sharedcategorical)
dyn_cnido = sharedcategorical$Dynamic.cnidoband
names(dyn_cnido) = rownames(sharedcategorical)
elastic = sharedcategorical$Elastic.strand
names(elastic) = rownames(sharedcategorical)
distal_desmo = sharedcategorical$Distal.cnidoband.desmonemes
names(distal_desmo) = rownames(sharedcategorical)
coiled = sharedcategorical$Coiled.tentilla
names(coiled) = rownames(sharedcategorical)
heterotype = sharedcategorical$Heteroneme.type
heterotype=as.character(heterotype)
names(heterotype) = rownames(sharedcategorical)
haplotype = sharedcategorical$Haploneme.type
haplotype=as.character(haplotype)
names(haplotype) = rownames(sharedcategorical)

Simmap_list = list()
###SIMMAP Tentilla:
make.simmap(ultram_cat, tentilla, nsim = 100) -> tentilla_sim
Simmap_list[[1]] <- tentilla_sim
plotTree(ultram_cat, lwd = 4)
tentilla_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Present", "Absent")
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)

###SIMMAP Proximal Heteronemes:
make.simmap(ultram_cat, prox_het, nsim = 100) -> prox_het_sim
Simmap_list[[2]] <- prox_het_sim
plotTree(ultram_cat, lwd = 4)
prox_het_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Present", "Absent")
nodelabels(pie=(describe.simmap(prox_het_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(prox_het_sim)

###SIMMAP Desmonemes:
make.simmap(ultram_cat, desmo, nsim = 100) -> desmo_sim
Simmap_list[[3]] <- desmo_sim
plotTree(ultram_cat, lwd = 4)
desmo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(desmo_sim)

###SIMMAP Rhopalonemes:
make.simmap(ultram_cat, rhopalo, nsim = 100) -> rhopalo_sim
Simmap_list[[4]] <- rhopalo_sim
plotTree(ultram_cat, lwd = 4)
rhopalo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(rhopalo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(rhopalo_sim)

###SIMMAP Dynamic Cnidoband:
make.simmap(ultram_cat, dyn_cnido, nsim = 100) -> dyn_cnido_sim
Simmap_list[[5]] <- dyn_cnido_sim
plotTree(ultram_cat, lwd = 4)
dyn_cnido_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(dyn_cnido_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(dyn_cnido_sim)

###SIMMAP Elastic Strand:
make.simmap(ultram_cat, elastic, nsim = 100) -> elastic_sim
Simmap_list[[6]] <- elastic_sim
plotTree(ultram_cat, lwd = 4)
elastic_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(elastic_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(elastic_sim)

###SIMMAP Distal CB Desmonemes:
make.simmap(ultram_cat, distal_desmo, nsim = 100) -> distal_desmo_sim
Simmap_list[[7]] <- distal_desmo_sim
plotTree(ultram_cat, lwd = 4)
distal_desmo_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(distal_desmo_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(distal_desmo_sim)

###SIMMAP Tentilla Coiledness:
make.simmap(ultram_cat, coiled, nsim = 100) -> coiled_sim
Simmap_list[[8]] <- coiled_sim
plotTree(ultram_cat, lwd = 4)
coiled_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(coiled_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(coiled_sim)

###SIMMAP Heteroneme type:
heterotype = heterotype[heterotype!=""]
HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(heterotype))))
make.simmap(HTtree, heterotype, nsim = 100) -> heterotype_sim
Simmap_list[[9]] <- heterotype_sim
plotTree(HTtree, lwd = 4)
heterotype_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green")
names(colors) = c("Eurytele", "Microbasic mastigophore", "Stenotele")
nodelabels(pie=(describe.simmap(heterotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)

###SIMMAP Haploneme type:
haplotype = haplotype[haplotype!=""]
HTtree = drop.tip(ultram_cat, which(!(ultram_cat$tip.label %in% names(haplotype))))
make.simmap(HTtree, haplotype, nsim = 100) -> haplotype_sim
Simmap_list[[10]] <- haplotype_sim
plotTree(HTtree, lwd = 4)
haplotype_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Isorhizas", "Anisorhizas")
nodelabels(pie=(describe.simmap(haplotype_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(haplotype_sim)

## Character correlations ##
C = sharedmatrix[,c(-1,-3)] %>% .[which(!is.na(rowSums(.[,-1]))),]
Cspecies = C$Species %>% as.character()
C = as.matrix(C[,-1])
rownames(C) = Cspecies
Ctree = drop.tip(ultram,which(!(ultram$tip.label %in% rownames(C))))
class(Ctree) = "phylo"
PICi = Rcontrast(tree=Ctree, X=C, path="phylip-3.695/exe", cleanup=TRUE)

#Correlation visualizations R2
phy_corr = PICi$VarA.Correlations
intra_corr = PICi$VarE.Correlations
phy_corr[upper.tri(phy_corr)] <- NA
combicorr = phy_corr
combicorr[upper.tri(combicorr)] = intra_corr[upper.tri(intra_corr)]
rownames(combicorr) = colnames(C)
colnames(combicorr) = colnames(C)
corrplot(combicorr, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs intraspecific correlations
PICOLS = combicorr
PICOLS[upper.tri(PICOLS)]=cor(C)[upper.tri(cor(C))]
corrplot(PICOLS, diag=F, tl.cex = 0.4, tl.col="black") #phylo correlations vs regular correlations for figure

#Scatterplot phylo vs regular correlations
cbind(as.vector(phy_corr), as.vector(cor(C))) %>% as.data.frame()->phyreg
names(phyreg)<-c("Phylo", "Reg")
ggplot(phyreg, aes(x=Reg, y=Phylo, color=(Phylo+Reg)/2)) + geom_point() + geom_hline(yintercept = 0)  + geom_vline(xintercept = 0) + theme_bw()
abline(h=0)
abline(v=0)

## PCA ##
Q_sharedmean_logs = sharedmean_logs[,-1]
#Q_sharedmean_logs = castmean_logs[,-1]
#rownames(Q_sharedmean_logs) = castmean_logs$Species
rownames(Q_sharedmean_logs) = sharedmean_logs$Species
raw_matrix = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[which(!is.na(rowSums(.))),]
raw_matrix_notf = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[,c(1:7,12:17)] %>% .[which(!is.na(rowSums(.))),]
raw_matrix_NaZeroes = Q_sharedmean_logs[,c(1:2,4:20)]
raw_matrix_NaZeroes[is.na(raw_matrix_NaZeroes)]<-0
compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]

#Using simple characters
PCA(raw_matrix_NaZeroes) -> Pca_raw
PCA(raw_matrix_notf) -> Pca_raw
Pca_raw %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Pca_raw %>% fviz_contrib(choice="var", axes=2, sort.val="desc")
Pca_raw %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE) #For figure A
Pca_raw %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE, axes=c(3,4)) 
raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
phylomorphospace(tree=raw_tree, Pca_raw$ind$coord[,1:2], label = "horizontal", xlab = "PC1", ylab = "PC2") #For figure B
multiPhylosignal(Pca_raw$ind$coord, raw_tree)
physignal(Pca_raw$ind$coord, raw_tree)

#Using Morphometric characters
PCA(compound_matrix) -> Pca_compound
Pca_compound %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Pca_compound %>% fviz_contrib(choice="var", axes=2, sort.val="desc")
Pca_compound %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)
compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))
phylomorphospace(tree=compound_tree, Pca_compound$ind$coord[,1:2], label = "horizontal", xlab = "PC1", ylab = "PC2")
physignal(Pca_compound$ind$coord, compound_tree)
multiPhylosignal(Pca_compound$ind$coord, compound_tree)

#PhyloPCA on simple character
PPCA_raw = phyl.pca(raw_tree, raw_matrix_notf)
PPCA_compound = phyl.pca(compound_tree, compound_matrix)
PPCA_raw %>% biplot(main=paste(signif(summary(PPCA_raw)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_raw)$importance[2,2]*100,3),"%"), cex = .6, expand =1)
PPCA_compound %>% biplot(main=paste(signif(summary(PPCA_compound)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_compound)$importance[2,2]*100,3),"%"), cex = .6, expand =0.4)
phylomorphospace(raw_tree, PPCA_raw$S)

## BAMM ##

traitlist = list()
for(i in 2:ncol(sharedmean_logs)){
  traitlist[[i]] <- sharedmean_logs[,c(1,i)]
  names(traitlist)[i] = names(sharedmean_logs)[i]
}

traitlist <- lapply(traitlist, function(x){x<-x[which(!is.nan(x[,2])),]})

for(i in 2:length(traitlist)){
  treei = drop.tip(ultram, which(!(ultram$tip.label %in% traitlist[[i]]$Species)))
  treei$tip.label = str_replace_all(treei$tip.label, " ", "_")
  write.tree(treei, file = paste("BAMM/",names(traitlist[[i]])[2], "_tree.tre", sep=""))
}

for(i in 2:length(traitlist)){
  traitlist[[i]]$Species = str_replace_all(traitlist[[i]]$Species, " ", "_")
  write.table(traitlist[[i]],file = paste("BAMM/",names(traitlist[[i]])[2], ".txt", sep=""), sep="\t", col.names = F, row.names = F, quote = F)
}

#See BAMM/BAMMsetpriors.R
#See BAMM/BAMMplots.R
#See BAMM/BAMMconfiguration.txt

## Retrieve diet data ##
#Retrieve diet info from literature BINARY
GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5,6)] %>% .[which(grepl("diet",.$character) & .$state==1),]
GC$character = factor(GC$character, levels=unique(GC$character))
GC$species = as.character(GC$species)
#Fix typos#
GC$species[which(GC$species == "Nanomia bijuga")] <- "Nanomia sp"
GC$species[which(GC$species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
GC$species[which(GC$species == "Agalma okeni")] <- "Agalma okenii"
write.csv(GC, "gutcontentliteraturereview.csv")

#Prune to tree species#
GC = GC[which(GC$species %in% ultram$tip.label),]
GC = split(GC,GC$character)
nrowGC = purrr::map(GC,nrow) %>% as.numeric()
GC = GC[which(nrowGC>2)]
GC = purrr::map(GC,unique)
diet= matrix(ncol=length(GC),nrow=length(unique(sharedmeans$Species))) %>% as.data.frame()
names(diet) = names(GC)
rownames(diet) = unique(sharedmeans$Species)
for(E in GC){
  print(E$species)
  for(S in E$species){
    diet[which(rownames(diet) == S),as.character(unique(E$character))] = 1
  }
}
diet[is.na(diet)] <- 0
diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]

#Add personal observations of the authors
cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0),3),nrow=10, ncol = 3) %>% t() %>% as.data.frame()
rownames(cladeB) = c("Erenna richardi", "Erenna sirena", "Stephanomia amphytridis")
krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0),4),nrow=10, ncol = 4) %>% t() %>% as.data.frame()
rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala", "Lychnagalma utricularia", "Bargmannia amoena")
Gelatinous_diet = rep(0,nrow(diet))
diet = cbind(diet, Gelatinous_diet)
names(diet)[ncol(diet)] = "Gelatinous diet"
gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1),1),nrow=10, ncol = 1) %>% t() %>% as.data.frame()
names(gelateaters) = names(diet)
rownames(gelateaters) = c("Apolemia rubriversa")
names(gelateaters)=names(diet)
names(krilleaters)=names(diet)
names(cladeB)=names(diet)
diet = rbind(diet, cladeB, krilleaters, gelateaters)
#Decapod diet column actually encompasses decapods, krill, and mysids (large crustaceans/shrimp like animals)

# Retrive ROV annotation data
VARS <- read.csv("Choy2017.tsv", sep="\t")
VARS_curated = VARS[which(VARS$Pred_lowest_tax %in% ultram$tip.label | VARS$Pred_lowest_tax=="Nanomia bijuga"),]
VARS_cast = acast(VARS_curated, Pred_lowest_tax~Prey_order, fun.aggregate = length)

#Prune morphological matrix to species in diet
dprunedmatrix = sharedmeans[which(sharedmeans$Species%in%rownames(diet)),]
dprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(diet)),]
#Prune tree to diet species
dprunedTree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(diet))))

#Soft bodied vs hard bodied prey
prunediets = softORhard
ldamtrix = baselda
ldamtrix$Species = as.character(ldamtrix$Species)
ldamtrix = cbind(ldamtrix, prunediets[match(baselda$Species, rownames(prunediets)), 1])
names(ldamtrix)[ncol(ldamtrix)]<-"SoftHard"
xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$SoftHard, n.pca.max = 300, training.set = 0.9,
                 result = "groupMean", center = TRUE, scale = TRUE,
                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$SoftHard, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
summary.dapc(DAPClogs)
contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
scatter(DAPClogs, clabel = 0.5)
assignplot(DAPClogs)
compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
predictionset[is.na(predictionset)]<-0
rownames(predictionset)<-predictionset$Species
predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]  #Remove taxa with many unmeasured NAs that create zero-biases
predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
preDIET <- predict(DAPClogs, predictionset[,-1])
cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.9, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)

## SIMPLE ANALYSES OF KINEMATIC DATA ##

kine = read.csv("Kinematics.tsv", sep='\t', header=T) #%>% .[which(apply(., 1, function(x) sum(is.na(x)))<ncol(.)-2),-2]
kineWNA = kine[which(kine$Species %in% ultram$tip.label),]
rownames(kineWNA)=kineWNA$Specimen
rownames(kine)=kine$Specimen
#kineWNA = kineWNA[,-1]
#kine=kine[,-1]
kinetree = drop.tip(ultram, which(!(ultram$tip.label %in% kine$Species)))
kinetree$edge.length = 200*kinetree$edge.length
#kine_clean = kineWNA[,which(colSums(kineWNA)>1)]
#names(kine) = c("ADS", "MDS", "HeDS","HeMDS", "HSDS", "HFL", "HaDS")
kine_byspp = aggregate(. ~ kine$Species, data = kine[,c(-1,-2)], mean.na, na.action = na.pass)
names(kine_byspp)[1] <- "Species"
kinemorph <- castmeans[which(castmeans$Species %in% kine_byspp$Species),] %>% cbind(kine_byspp[which(kine_byspp$Species %in% castmeans$Species),])
plot(kinemorph$Cnidoband.free.length..um., kinemorph$Average.CB.discharge.speed..mm.s.)
calys = kinemorph$Species[c(5,9,12,15,16,17,18)]
euphys = kinemorph$Species[which(!(kinemorph$Species %in% calys))]
relspeed = data.frame(kinemorph$Species, c(kinemorph$Average.CB.discharge.speed..mm.s./kinemorph$Cnidoband.free.length..um.))
names(relspeed) = c("Species", "Speed/Length")
relspeed <- relspeed[which(!(is.na(relspeed$`Speed/Length`))),]
t.test(relspeed[which(relspeed$Species %in% calys),2], relspeed[which(relspeed$Species %in% euphys),2])
t.test(kine$Average.CB.discharge.speed..mm.s.[which(kine$Species %in% calys)], kine$Average.CB.discharge.speed..mm.s.[which(kine$Species %in% euphys)])
t.test(castnumbers$Cnidoband.free.length..um.[which(castnumbers$Species %in% calys)], castnumbers$Cnidoband.free.length..um.[which(castnumbers$Species %in% euphys)])
lm(kinemorph$Average.CB.discharge.speed..mm.s.~ kinemorph$Cnidoband.free.length..um.) %>% summary()
lm(kinemorph$Heteroneme.discharge.speed.MAX..mm.s.~ kinemorph$Heteroneme.volume..um3.) %>% summary()
t.test(kine$Heteroneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% calys)], kine$Heteroneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% euphys)])
t.test(kine$Haploneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% calys)], kine$Haploneme.discharge.speed.AVG..mm.s.[which(kine$Species %in% euphys)])
t.test(kine$Haploneme.discharge.speed.AVG..mm.s., kine$Heteroneme.discharge.speed.AVG..mm.s.)
cor(kinemorph[,c(-1,-32)], use="pairwise.complete.obs") %>% .[c(1:30),c(31:41)] %>% corrplot(diag=F, tl.cex = 0.4, tl.col="black")

```

### 2020-04-27 Organismal_paper/Organismal_manuscript_and_code.Rmd
progress in organismal paper

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, echo=FALSE, eval=FALSE}
 	# Load packages
@@
 library(phylolm)
+library(convevol)
 	## Graphics
@@
 library(colorRamps)
+library(ggfortify)
+library(ggpubr)
 
@@
 
-In [@damianserrano2020shaped], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
+In [@damian2019evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
 The analyses we carried out led to novel insights into the evolution of predatory specialization.
@@
 
-We explore the evolutionary history and diversification of tentilla morphologies using phylogenetic comparative methods on the morphological dataset and phylogeny published in [@damianserrano2020shaped].
+We explore the evolutionary history and diversification of tentilla morphologies using phylogenetic comparative methods on the morphological dataset and phylogeny published in [@damian2019evolution].
 We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
@@
 
-*Evolutionary history of tentillum morphology* – [@damianserrano2020shaped] produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+*Evolutionary history of tentillum morphology* – [@damian2019evolution] produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
 This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
@@
 
-  The clades defined in [@damianserrano2020shaped] are characterized by unique evolutionary innovations in their tentilla.
+  The clades defined in [@damian2019evolution] are characterized by unique evolutionary innovations in their tentilla.
 The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*.
@@
 
-*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damianserrano2020shaped] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)).
+*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)).
 Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1.
@@
 Smaller dots and lines represent phylogenetic relationships and ancestral states of internal nodes under BM.
-Species nodes in red lack either haplonemes or heteronemes, and their values projected onto the axis of the nematocyst type they bear.
+Species nodes in red lack either haplonemes or heteronemes, and their values are projected onto the axis of the nematocyst type they bear.
 Cystonects have no tentacle heteronemes and are projected onto the haploneme axis.
@@
 *Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
-We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using the linear discriminant analysis of principal components (DAPC) fitted in [@damianserrano2020shaped].
+We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using the linear discriminant analysis of principal components (DAPC) fitted in [@damian2019evolution].
 This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
-The discriminant analysis in [@damianserrano2020shaped] for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width.
+The discriminant analysis in [@damian2019evolution] for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width.
 We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in the morphological dataset.
@@
 
-*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damianserrano2020shaped] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
@@
 Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
-However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora (Fig.
-\@ref(figure4)).
+However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora.
 We searched for rate regime shifts in the evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
@@
 The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-The DAPCs in [@damianserrano2020shaped] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
+The DAPCs in [@damian2019evolution] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
 
@@
 
-```{r code}
+```{r prepdata, eval = FALSE, echo = FALSE}
 # Set paths to input data
@@
 
+## Retrieve diet data ##
+GC = read.csv("~/tentilla_morph/Supplementary_materials/Dryad/literature_diet_data.tsv", header = T, sep='\t')
+GC$Prey.type = factor(GC$Prey.type, levels=unique(GC$Prey.type))
+GC$Siphonophore.species = as.character(GC$Siphonophore.species)
+#Fix typos#
+GC$Siphonophore.species[which(GC$Siphonophore.species == "Nanomia bijuga")] <- "Nanomia sp"
+GC$Siphonophore.species[which(GC$Siphonophore.species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
+GC$Siphonophore.species[which(GC$Siphonophore.species == "Agalma okeni")] <- "Agalma okenii"
+GC = GC[,1:2]
+names(GC)<-c("species", "character")
+#write.csv(GC, "gutcontentliteraturereview.csv")
+
+#Prune to tree species#
+GC = GC[which(GC$species %in% ultram$tip.label),]
+GC = split(GC,GC$character)
+nrowGC = purrr::map(GC,nrow) %>% as.numeric()
+GC = GC[which(nrowGC>2)]
+GC = purrr::map(GC,unique)
+diet= matrix(ncol=length(GC),nrow=length(unique(sharedmeans$Species))) %>% as.data.frame()
+names(diet) = names(GC)
+rownames(diet) = unique(sharedmeans$Species)
+for(E in GC){
+  print(E$species)
+  for(S in E$species){
+    diet[which(rownames(diet) == S),as.character(unique(E$character))] = 1
+  }
+}
+diet[is.na(diet)] <- 0
+diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
+
+#Add personal observations of the authors
+cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0),3),nrow=10, ncol = 3) %>% t() %>% as.data.frame()
+rownames(cladeB) = c("Erenna richardi", "Erenna sirena", "Stephanomia amphytridis")
+krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0),4),nrow=10, ncol = 4) %>% t() %>% as.data.frame()
+rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala", "Lychnagalma utricularia", "Bargmannia amoena")
+Gelatinous_diet = rep(0,nrow(diet))
+diet = cbind(diet, Gelatinous_diet)
+names(diet)[ncol(diet)] = "Gelatinous diet"
+gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1),1),nrow=10, ncol = 1) %>% t() %>% as.data.frame()
+names(gelateaters) = names(diet)
+rownames(gelateaters) = c("Apolemia rubriversa")
+names(gelateaters)=names(diet)
+names(krilleaters)=names(diet)
+names(cladeB)=names(diet)
+diet = rbind(diet, cladeB, krilleaters, gelateaters)
+#Decapod diet column actually encompasses decapods, krill, and mysids (large crustaceans/shrimp like animals)
+
+# Retrive ROV annotation data
+VARS <- read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_ROV_data.csv")
+VARS_curated = VARS[which(VARS$Siphonophore.concept %in% ultram$tip.label | VARS$Siphonophore.concept=="Nanomia bijuga"),]
+VARS_cast = acast(VARS_curated, Siphonophore.concept~Prey.taxonomy, fun.aggregate = length)
+
+#Prune morphological matrix to species in diet
+dprunedmatrix = sharedmeans[which(sharedmeans$Species%in%rownames(diet)),]
+dprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(diet)),]
+#Prune tree to diet species
+dprunedTree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(diet))))
+
+hypdiet = c("Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
+names(hypdiet) = dprunedTree$tip.label
+
+#Soft bodied vs hard bodied prey
+soft_hard = cbind((diet$`Copepod diet`+diet$`Crustacean diet` + diet$`Decapod diet`+ diet$`Amphipod diet` + diet$`Ostracod diet`), (diet$`Fish diet`+diet$`Chaetognath diet`+diet$`Gelatinous diet`+diet$`Mollusc diet`+diet$`Polychaete diet`))
+colnames(soft_hard) = c("Hard", "Soft")
+rownames(soft_hard) = rownames(diet)
+soft_hard <- as.data.frame(soft_hard)
+soft_hard[soft_hard>0]<-1
+softORhard = as.data.frame(soft_hard$Hard+soft_hard$Soft)
+rownames(softORhard)=rownames(soft_hard)
+names(softORhard) = "Type"
+softORhard[softORhard==2]<-"Both"
+softORhard[which(soft_hard$Hard==1 & soft_hard$Soft==0),]<-"Hard"
+softORhard[which(soft_hard$Hard==0 & soft_hard$Soft==1),]<-"Soft"
+softORhard
+
+#PCA prep
+Q_sharedmean_logs = sharedmean_logs[,-1]
+#Q_sharedmean_logs = castmean_logs[,-1]
+#rownames(Q_sharedmean_logs) = castmean_logs$Species
+rownames(Q_sharedmean_logs) = sharedmean_logs$Species
+raw_matrix = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[which(!is.na(rowSums(.))),]
+raw_matrix_notf = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[,c(1:7,12:17)] %>% .[which(!is.na(rowSums(.))),]
+raw_matrix_NaZeroes = Q_sharedmean_logs[,c(1:2,4:20)]
+raw_matrix_NaZeroes[is.na(raw_matrix_NaZeroes)]<-0
+compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
+fullraw_nozeroes <- aggregate(. ~ Species, data=castlogs[,c(-1,-3)], FUN = mean)
+rownames(fullraw_nozeroes) <- fullraw_nozeroes$Species
+```
+
+```{r analyses, eval = FALSE, echo = FALSE}
 ### COMPARATIVE ANALYSES ###
@@
 ## PCA ##
-Q_sharedmean_logs = sharedmean_logs[,-1]
-#Q_sharedmean_logs = castmean_logs[,-1]
-#rownames(Q_sharedmean_logs) = castmean_logs$Species
-rownames(Q_sharedmean_logs) = sharedmean_logs$Species
-raw_matrix = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[which(!is.na(rowSums(.))),]
-raw_matrix_notf = Q_sharedmean_logs[,c(1:2,4:20)] %>% .[,c(1:7,12:17)] %>% .[which(!is.na(rowSums(.))),]
-raw_matrix_NaZeroes = Q_sharedmean_logs[,c(1:2,4:20)]
-raw_matrix_NaZeroes[is.na(raw_matrix_NaZeroes)]<-0
-compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
 
 #Using simple characters
-PCA(raw_matrix_NaZeroes) -> Pca_raw
+#PCA(raw_matrix_NaZeroes) -> Pca_raw
 PCA(raw_matrix_notf) -> Pca_raw
@@
 PPCA_compound %>% biplot(main=paste(signif(summary(PPCA_compound)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_compound)$importance[2,2]*100,3),"%"), cex = .6, expand =0.4)
-phylomorphospace(raw_tree, PPCA_raw$S)
+phylomorphospace(raw_tree, PPCA_raw$S, label = "horizontal")
 
@@
 #See BAMM/BAMMconfiguration.txt
-
-## Retrieve diet data ##
-#Retrieve diet info from literature BINARY
-GC = read.csv("Cmerged.csv", header = T, sep=',')[,c(2,4,5,6)] %>% .[which(grepl("diet",.$character) & .$state==1),]
-GC$character = factor(GC$character, levels=unique(GC$character))
-GC$species = as.character(GC$species)
-#Fix typos#
-GC$species[which(GC$species == "Nanomia bijuga")] <- "Nanomia sp"
-GC$species[which(GC$species == "Rhizophysa eyesenhardti")] <- "Rhizophysa eysenhardtii"
-GC$species[which(GC$species == "Agalma okeni")] <- "Agalma okenii"
-write.csv(GC, "gutcontentliteraturereview.csv")
-
-#Prune to tree species#
-GC = GC[which(GC$species %in% ultram$tip.label),]
-GC = split(GC,GC$character)
-nrowGC = purrr::map(GC,nrow) %>% as.numeric()
-GC = GC[which(nrowGC>2)]
-GC = purrr::map(GC,unique)
-diet= matrix(ncol=length(GC),nrow=length(unique(sharedmeans$Species))) %>% as.data.frame()
-names(diet) = names(GC)
-rownames(diet) = unique(sharedmeans$Species)
-for(E in GC){
-  print(E$species)
-  for(S in E$species){
-    diet[which(rownames(diet) == S),as.character(unique(E$character))] = 1
-  }
-}
-diet[is.na(diet)] <- 0
-diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
-
-#Add personal observations of the authors
-cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0),3),nrow=10, ncol = 3) %>% t() %>% as.data.frame()
-rownames(cladeB) = c("Erenna richardi", "Erenna sirena", "Stephanomia amphytridis")
-krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0),4),nrow=10, ncol = 4) %>% t() %>% as.data.frame()
-rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala", "Lychnagalma utricularia", "Bargmannia amoena")
-Gelatinous_diet = rep(0,nrow(diet))
-diet = cbind(diet, Gelatinous_diet)
-names(diet)[ncol(diet)] = "Gelatinous diet"
-gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1),1),nrow=10, ncol = 1) %>% t() %>% as.data.frame()
-names(gelateaters) = names(diet)
-rownames(gelateaters) = c("Apolemia rubriversa")
-names(gelateaters)=names(diet)
-names(krilleaters)=names(diet)
-names(cladeB)=names(diet)
-diet = rbind(diet, cladeB, krilleaters, gelateaters)
-#Decapod diet column actually encompasses decapods, krill, and mysids (large crustaceans/shrimp like animals)
-
-# Retrive ROV annotation data
-VARS <- read.csv("Choy2017.tsv", sep="\t")
-VARS_curated = VARS[which(VARS$Pred_lowest_tax %in% ultram$tip.label | VARS$Pred_lowest_tax=="Nanomia bijuga"),]
-VARS_cast = acast(VARS_curated, Pred_lowest_tax~Prey_order, fun.aggregate = length)
-
-#Prune morphological matrix to species in diet
-dprunedmatrix = sharedmeans[which(sharedmeans$Species%in%rownames(diet)),]
-dprunedmatrix_logs = sharedmean_logs[which(sharedmean_logs$Species%in%rownames(diet)),]
-#Prune tree to diet species
-dprunedTree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(diet))))
-
-#Soft bodied vs hard bodied prey
-prunediets = softORhard
-ldamtrix = baselda
-ldamtrix$Species = as.character(ldamtrix$Species)
-ldamtrix = cbind(ldamtrix, prunediets[match(baselda$Species, rownames(prunediets)), 1])
-names(ldamtrix)[ncol(ldamtrix)]<-"SoftHard"
-xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$SoftHard, n.pca.max = 300, training.set = 0.9,
-                 result = "groupMean", center = TRUE, scale = TRUE,
-                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
-dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$SoftHard, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
-summary.dapc(DAPClogs)
-contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
-scatter(DAPClogs, clabel = 0.5)
-assignplot(DAPClogs)
-compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
-predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
-predictionset[is.na(predictionset)]<-0
-rownames(predictionset)<-predictionset$Species
-predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]  #Remove taxa with many unmeasured NAs that create zero-biases
-predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
-preDIET <- predict(DAPClogs, predictionset[,-1])
-cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
-preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.9, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
+```
+
+```{r newanalyses, echo=F, eval=F}
+### Morphospace analyses ###
+hypfood <- data.frame(hypdiet, hypdiet, stringsAsFactors = F)
+morphood <- raw_matrix_NaZeroes[which(rownames(raw_matrix_NaZeroes) %in% rownames(hypfood)),]
+#morphood <- raw_matrix_notf[which(rownames(raw_matrix_notf) %in% rownames(hypfood)),]
+hypfood <- hypfood[match(rownames(morphood), rownames(hypfood)),]
+morphospace_data <- cbind(morphood, hypfood[,1])
+#morphospace_data = cbind(raw_matrix_NaZeroes, hypfood[match(rownames(raw_matrix_NaZeroes), rownames(hypfood)),1])
+names(morphospace_data)[ncol(morphospace_data)] <- "Diet"
+morphospace_data$Diet <- as.character(morphospace_data$Diet) %>% str_replace_all(" ", "_")
+
+#Test for morphospatial overlap between feeding guilds
+pca_morph <- prcomp(morphospace_data[,-ncol(morphospace_data)])
+autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet", loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = "black")+theme_bw()
+autoplot(ppp, data = morphospace_data, frame = TRUE, label=T, colour="Diet")+theme_bw()
+
+#MANOVA for diet
+LMdata <- cbind(pca_morph$x, morphospace_data$Diet) %>% as.data.frame(stringsAsFactors = F)
+LMdata[,-ncol(LMdata)] <- apply(LMdata[,-ncol(LMdata)], 2, as.numeric)
+names(LMdata)[ncol(LMdata)] <- "Diet"
+MAN1 <- manova(cbind(PC1, PC2) ~ Diet, data = LMdata)
+MAN1 %>% summary.manova() %>% .$SS %>% .$Diet -> MSS1
+var_exp = (MSS1[1,2]+MSS1[2,1])/sum(MSS1)
+library(geiger)
+LMtree <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(LMdata))))
+dat <- LMdata[,1:2]
+D <- LMdata$Diet %>% as.factor()
+names(D) <- rownames(LMdata)
+PMAN <- aov.phylo(dat ~ D, phy = LMtree, nsim=50, test="Wilks")
+PMAN  %>% summary.manova() %>% .$SS %>% .$group -> pMSS
+var_exp_phyl = (pMSS[1,2]+pMSS[2,1])/sum(pMSS)
+
+library(geomorph)
+morphol.disparity(dat ~ 1, groups = D)
+gdf <- geomorph.data.frame(shape = as.matrix(dat), phy = LMtree, grp = D)
+ANOVA <- procD.pgls(shape ~ grp, phy = phy, data = gdf)
+morphol.disparity(f1 = ANOVA, groups = ~grp, data = gdf, iter = 999)
+
+#Fish specialization convergence
+##
+pcanonaphenos = PCA(raw_matrix_NaZeroes)
+phenotree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcanonaphenos$ind$coord))))
+fishtips = c(rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Erenna")], "Physalia physalis", rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Rhizophy")])
+phylomorphospace(phenotree, pcanonaphenos$ind$coord, label = "horizontal")
+convnumsig(phenotree, pcanonaphenos$ind$coord[,1:2], plot=F, convtips = fishtips, nsim=30)
+convnum(phenotree, pcanonaphenos$ind$coord[,1:2], plot=T, convtips = fishtips)
+convrat(phenotree,pcanonaphenos$ind$coord[,1:2], convtips = fishtips)
+convratsig(phenotree,pcanonaphenos$ind$coord[,1:2], convtips = fishtips, nsim=5)
+
+#Frillagalma-Calycophoran convergence
+pcaphenos = PCA(raw_matrix_notf)
+phenotree_2 = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcaphenos$ind$coord))))
+frilltips1 = c("Frillagalma vityazi", extract.clade(phenotree_2, getMRCA(phenotree_2, c("Sphaeronectes koellikeri", "Praya dubia")))$tip.label, "Agalma elegans")
+phylomorphospace(phenotree_2, pcaphenos$ind$coord, label = "horizontal")
+convnumsig(phenotree_2, pcaphenos$ind$coord[,1:2], plot=F,convtips = frilltips1, nsim=30) %>% print()
+convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = frilltips1)
+convrat(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1)
+convratsig(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1, nsim=1)
+
+#Lilyopsis pyrostephids
+convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = c("Bargmannia amoena", "Bargmannia elongata", "Lilyopsis fluoracantha", "Vogtia glabra", "Abylopsis tetragona", "Praya dubia", "Frillagalma vityazi"))
+
+#Heatmap of expected convergence
+coph <- cophenetic(phenotree_2)
+dis <- 1/vegdist(scale(pcaphenos$ind$coord[,1:2]), "euc") %>% as.matrix()
+diag(dis) <- NA
+(dis - mean(dis, na.rm=T))/mean(dis, na.rm=T) -> dis
+dis
+ggplot(melt(dis /coph), aes(Var1, Var2)) + 
+  geom_tile(aes(fill = value), colour = "black") + 
+  scale_fill_distiller(palette = "RdBu", direction=1) + 
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+
+RR = RRphylo(tree=phenotree, y = pcanonaphenos$ind$coord[,1:2])
 
@@
 
-kine = read.csv("Kinematics.tsv", sep='\t', header=T) #%>% .[which(apply(., 1, function(x) sum(is.na(x)))<ncol(.)-2),-2]
+kine = read.csv("~/tentilla_morph/Scrap/RCode_dependencies/Kinematics.tsv", sep='\t', header=T) #%>% .[which(apply(., 1, function(x) sum(is.na(x)))<ncol(.)-2),-2]
 kineWNA = kine[which(kine$Species %in% ultram$tip.label),]

### 2020-04-28 Organismal_paper/Organismal_manuscript_and_code.Rmd
Fixed Forskalia rearrangement

@@
 
+![\label{morphodiet}Phylomorphospace of continuous morphological characters with inapplicable states transformed to zeroes, overlapped with polygons conservatively defining the space occupied by each feeding guild.
+](~/tentilla_morph/Organismal_paper/figures/morphospace_diet.png){height=600px}
+
+In order to examine the occupation structure of the morphospace across all siphonophore species in the dataset, we cast a PCA on the data transforming inapplicable states (due to absence of character) to zeroes.
+This allows us to accommodate species with many missing characters (such as cystonects), and to account for common absences as morphological similarities.
+In this ordination, PC1 explains 49.99% of variation (aligned with characters of the involucrum, terminal filament, and elastic strands) and PC2 explains 25.65% of variation (aligned with heteroneme number and haploneme length).
+When superimposing feeding guilds onto the morphospace (Fig.
+\@ref(morphodiet)), we find that the morphospaces of each feeding guild are barely overlapping in PC1 and PC2.
+A phylogenetic MANOVA showed that feeding guilds explain 22.09% of the variance in those dimensions, an outcome significantly distinct from the expectation under neutral evolution (p-value = 0.0196).
+In addition, a morphological disparity analysis accounting for phylogenetic structure shows that the morphospace of fish specialists is significantly broader than that of generalists and other specialists.
+This is due to the large morphological disparities between cystonects and piscivorous euphysonects.
+The superimposition of feeding guilds on the morphospace predicts the diet of *Erenna laciniata* to be piscivorous, *Lensia conoidea* and *Gymnopraia lapislazula* to be small crustacean eaters, *Lilyopsis fluoracantha* and *Physophora hydrostatica* to be generalists, and *Marrus claudanielis*, *Physophora gilmeri*, and *Halistemma rubrum* to be large crustacean specialists.
+
 *Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
@@
 #write.csv(GC, "gutcontentliteraturereview.csv")
-
-#Prune to tree species#
-GC = GC[which(GC$species %in% ultram$tip.label),]
 GC = split(GC,GC$character)
@@
 GC = purrr::map(GC,unique)
-diet= matrix(ncol=length(GC),nrow=length(unique(sharedmeans$Species))) %>% as.data.frame()
+diet= matrix(ncol=length(GC),nrow=length(unique(castlogs$Species))) %>% as.data.frame()
 names(diet) = names(GC)
-rownames(diet) = unique(sharedmeans$Species)
+rownames(diet) = unique(castlogs$Species)
 for(E in GC){
@@
 #Add personal observations of the authors
-cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0),3),nrow=10, ncol = 3) %>% t() %>% as.data.frame()
+cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0,0),3),nrow=11, ncol = 3) %>% t() %>% as.data.frame()
 rownames(cladeB) = c("Erenna richardi", "Erenna sirena", "Stephanomia amphytridis")
-krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0),4),nrow=10, ncol = 4) %>% t() %>% as.data.frame()
+krilleaters = matrix(rep(c(0,0,0,1,0,0,1,0,0,0,0),4),nrow=11, ncol = 4) %>% t() %>% as.data.frame()
 rownames(krilleaters) = c("Praya dubia", "Resomia ornicephala", "Lychnagalma utricularia", "Bargmannia amoena")
-Gelatinous_diet = rep(0,nrow(diet))
-diet = cbind(diet, Gelatinous_diet)
-names(diet)[ncol(diet)] = "Gelatinous diet"
-gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1),1),nrow=10, ncol = 1) %>% t() %>% as.data.frame()
+gelateaters = matrix(rep(c(0,0,0,0,0,0,0,0,0,1,0),1),nrow=11, ncol = 1) %>% t() %>% as.data.frame()
 names(gelateaters) = names(diet)
@@
 compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
-fullraw_nozeroes <- aggregate(. ~ Species, data=castlogs[,c(-1,-3)], FUN = mean)
+
+temp <- castlogs[,c(-1,-3)]
+temp[is.na(temp)] <- 0
+fullraw_nozeroes <- aggregate(. ~ Species, data=temp, FUN = mean)
 rownames(fullraw_nozeroes) <- fullraw_nozeroes$Species
+
+hypdiet = c("Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
+names(hypdiet) = dprunedTree$tip.label
+
+#hypdiet but for all species not only those in tree
+hypdiet_full = c("Mixed","Mixed","Gelatinous","Gelatinous","Mixed","Large crustacean","Small crustacean","Small crustacean","Small crustacean","Small crustacean","Fish","Fish","Mixed","Small crustacean","Large crustacean","Small crustacean","Large crustacean","Fish","Large crustacean","Large crustacean","Large crustacean","Fish","Fish","Small crustacean","Small crustacean","Fish","Small crustacean","Small crustacean")
+dpruned_full = fullraw_nozeroes[which(fullraw_nozeroes$Species%in%rownames(diet)),]
+dpruned_full <- data.frame(dpruned_full, "Diet" = hypdiet_full)
 ```
@@
 hypfood <- data.frame(hypdiet, hypdiet, stringsAsFactors = F)
-morphood <- raw_matrix_NaZeroes[which(rownames(raw_matrix_NaZeroes) %in% rownames(hypfood)),]
+#morphood <- raw_matrix_NaZeroes[which(rownames(raw_matrix_NaZeroes) %in% rownames(hypfood)),]
 #morphood <- raw_matrix_notf[which(rownames(raw_matrix_notf) %in% rownames(hypfood)),]
-hypfood <- hypfood[match(rownames(morphood), rownames(hypfood)),]
-morphospace_data <- cbind(morphood, hypfood[,1])
-#morphospace_data = cbind(raw_matrix_NaZeroes, hypfood[match(rownames(raw_matrix_NaZeroes), rownames(hypfood)),1])
+#hypfood <- hypfood[match(rownames(morphood), rownames(hypfood)),]
+#morphospace_data <- cbind(morphood, hypfood[,1])
+morphospace_data = cbind(raw_matrix_NaZeroes, hypfood[match(rownames(raw_matrix_NaZeroes), rownames(hypfood)),1])
 names(morphospace_data)[ncol(morphospace_data)] <- "Diet"
@@
 autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet", loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = "black")+theme_bw()
-autoplot(ppp, data = morphospace_data, frame = TRUE, label=T, colour="Diet")+theme_bw()
+autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet")+theme_bw()
+phylomorphospace(drop.tip(ultram, which(!(ultram$tip.label %in% rownames(morphospace_data)))), pca_morph$x[,1:2], label="horizontal")
 

### 2020-04-28 Supplementary_materials/Dryad/R_Code.R

@@ -545,7 +545,7 @@ fitPagel(treeIJ, CH_I, CH_J) %>% .$P
 
 regimetree = dprunedTree
 hypdiet = c("Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
-names(hypdiet) = regimetree$tip.label
+names(hypdiet) = regimetree$tip.label #Important thing here is that Forskalia tholoides was used as a proxy for Forskalia sp. in Purcell 1981b
 DietAnc = ace(hypdiet, regimetree, type = "discrete")$lik.anc
 HypDietAnc = 1:nrow(DietAnc)
 for(row in 1:nrow(DietAnc)){

### 2020-05-15 Organismal_paper/Organismal_manuscript_and_code.Rmd
cleanup writing, add phenotypic integration. Make supplementary materials RMD

@@
 library(convevol)
+library(surface)
 	## Graphics
@@
 Siphonophore tentilla (tentacle side branches) are unique biological structures for prey capture, composed of a complex arrangement of cnidocytes (stinging cells) bearing different types of nematocysts (stinging capsules) and auxiliary structures.
-Tentilla present an extreme morphological diversity of form and function across species.
+Tentilla present an exuberant morphological diversity of form and function across species.
 While associations between tentilla form and diet have been reported, the evolutionary history giving rise to this morphological diversity is largely unexplored.
-Here we explore the evolutionary gains and losses of novel tentilla substructures on the most recent siphonophore phylogeny.
+Here we explore the evolutionary gains and losses of novel tentillum substructures and nematocyst types on the most recent siphonophore phylogeny.
 Tentilla have a precisely coordinated high-speed strike mechanism of synchronous unwinding and nematocysts discharge.
@@
 
-Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-However, far less attention has been devoted to their unique tentacular structures: the tentilla.
+SSiphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
+Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades (cite Phil, Steve, etc), which has been elegantly synthesized in detailed synopsis [@totton1954synopsis, @mapstone2014global].
+In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
+With these assets in hand, we can now begin to study siphonophores from an orthogonal perspective, focusing on the diversity and evolutionary history of specific structures.
+Here we focus on one of such structures: the tentilla.
 Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts.
@@
 This maximizes the surface area of contact between the nematocysts and the prey they fire upon.
-Siphonophore tentilla present an exuberant diversity of morphologies, sizes, and nematocyst complements (Figure 1).
+In addition, siphonophore tentilla present a remarkable diversity of morphologies, sizes, and nematocyst complements (Fig, /@ref(figure2)).
+Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it.
 
@@
 In [@damian2019evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
-The analyses we carried out led to novel insights into the evolution of predatory specialization.
-However, this work left behind many fascinating discoveries on the evolutionary history of tentilla morphology, including nematocyst novelties, phenotypic integration, convergent evolution, paedomorphosis, and predictions on diet using morphology.
-Here, we present these findings and shed light on the natural history of siphonophores.
+The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
+The work we present here is complementary to [@damian2019evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
+
+Nematocysts are unique biological weapons for defense and prey capture exclusive to the phylum Cnidaria.
+Mariscal ([@mariscal1974nematocyst]) reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
+Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles.
+While recent descriptive studies have expanded and confirmed our understanding of this diversity, the evolutionary history of nematocyst type gain and loss in siphonophores remains unexplored.
+Thus, here we reconstruct the evolution of shifts, gains, and losses of nematocyst types, subtypes, and other major categorical traits that led to the extant diversity we see in siphonophore tentilla.
+In [@damian2019evolution], we found strong associations between piscivory and haploneme shape.
+These associations could have been produced by convergent changes in the adaptive optima of these characters.
+Here we set out to test this hypothesis using comparative model fitting methods.
+Analyzing the diversity of morphological states from a phylogenetic perspective allows us to identify the specific evolutionary processes that gave rise to it.
+Here we fit and compare a variety of macroevolutionary models to siphonophore tentilla morphology measurement data to identify instances of neutral divergence, stabilizing selection, changes in the speed of evolution, convergent evolution, and paedomorphosis (larval characters present in mature colonies).
+
+In [@damian2019evolution] we fitted discriminant analyses to identify characters that are predictive of feeding guild.
+These discriminant analyses can be used to generate hypotheses on the diets of ecologically understudied siphonophore species for which we have morphology data.
+Here we present a Bayesian prediction for the feeding guild of 45 species using the morphological dataset in [@damian2019evolution].
+As mentioned above, tentilla are far from being ornamental shapes and are in fact violently reactive weapons for prey capture [@Mackie:1987uy;@damian2019evolution].
+While we now have detailed characterizations of tentilla morphologies across many species, the diversity of dynamic performances and their relationships to the undischarged morphologies have not been examined to date.
+To address this gap, we set out to record high-speed video of the *in vivo* discharge dynamics of several siphonophore species at sea, and compare the kinematic attributes to their morphological characters.
 
@@
 
-We explore the evolutionary history and diversification of tentilla morphologies using phylogenetic comparative methods on the morphological dataset and phylogeny published in [@damian2019evolution].
-We fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
-These models include a non-phylogenetic whie-noise model (WN), a neutral divergence Brownian Motion model (BM), an early-burst decreasing rate model (EB), and an Ornstein-Uhlenbeck model with stabilizing selection around a fitted optimum trait value.
-We then ranked the models in order of increasing parametric complexity (WN, BM, EB, OU), and compared the corrected Akaike Information Criterion (AICc) support scores [@sugiura1978further] to the lowest (best) score, using a cutoff of 2 units to determine significantly better support.
-When the best fitting model was not significantly better than a less complex alternative, we selected the least complex model (SM13).
-We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM14).
-We calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM13).
-
-In order to explore the correlational structure among continuous characters and among their evolutionary histories, we used principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
+All character data and the phylogeny analyzed here were published in [@damian2019evolution].
+We log transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
+When missing data was incorporated as inapplicable states, we removed those species with characters that could not be measured due to technical limitations.
+We used the feeding guild categories detailed in [@damian2019evolution] with one modification: including all *Forskalia* spp.
+as generalists not only a single *Forskalia* species on the tree after a reinterpretation of the data in [@purcell1981dietary].
+In order to characterize the evolutionary history of tentilla morphology, we fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
+These models include a non-phylogenetic white-noise model (WN), a neutral divergence Brownian Motion model (BM), an early-burst decreasing rate model (EB), and an Ornstein-Uhlenbeck (OU) model with stabilizing selection around a fitted optimum trait value.
+In the same way as [@damian2019evolution] we then ordered the models by increasing parametric complexity (WN, BM, EB, OU), and compared their corrected Akaike Information Criterion (AICc) scores [@sugiura1978further].
+We used the lowest (best) score using a delta cutoff of 2 units to determine significance relative to the next simplest model (SM10).
+We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM11).
+We calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM10).
+To reconstruct the ancestral character states of nematocyst types and other categorical traits, we use stochastic character mapping (SIMMAP) using the package *phytools* [@revell2012phytools].
+
+In order to examine the phenotypic integration in the tentillum, we explored the correlational structure among continuous characters and among their evolutionary histories using principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
 Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
-This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters.
-In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package rphylip [@revell2014rphylip].
+This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters (apolemiids and cystonects).
+In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package *rphylip* [@revell2014rphylip].
+We identified four hypothetical modules among the tentillum characters: (1) The tentillum scaffold module -- cnidoband length & width, nematocyst row number, pedicle & elastic strand width, tentacle width; (2) the heteroneme module -- heteroneme length & width, shafts length & width; (3) the haploneme module -- length and width; and (4) the terminal filament module -- desmoneme & rhopaloneme length & width.
+To test an quantify phenotypic integration between these multivariate modules, we used the phylogenetic phenotypic integration test in the package *geomorph* [@adams2016geomorph].
+
+When looking at the morphospace of species in different feeding guilds, we also used PCA on the complete tentacular character dataset transforming inapplicable states of absent characters to zeros to account for similarity based on character presence/absence.
+Using these principal components, we examined the occupation of the morphospace across species in different feeding guilds using a phylogenetic MANOVA with the package *geiger* [@harmon2008geiger] to assess the variation explained, and a morphological disparity test with the package *geomorph* [@adams2016geomorph] to assess differences in the extent occupied by each guild.
+
+In order to detect and evaluate instances of convergent evolution, we used the package SURFACE [@ingram2013surface].
+This tool identifies OU regimes and their optima given a tree and character data, and then evaluates where the same regime has appeared independently in different lineages.
+We applied these analyses to the haploneme nematocyst length and width characters as well as to the most complete dataset without inapplicable character states.
+
+In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) trained in [@damian2019evolution] using the package *adegenet* [@jombart2008adegenet] to predict the feeding guilds of species in the dataset for which there are no published feeding observations.
+
+In order to observe the discharge behavior of different tentilla, we recorded high speed footage (1000-3000 fps) of tentillum and nematocyst discharge by live siphonophore specimens (26 species) using a Phantom Miro 320S camera mounted on a stereoscopic microscope.
+We mechanically elicited tentillum and nematocyst discharge using a fine metallic pin.
+We used the Phantom PCC software to analyze the footage.
+For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (μm), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data available in the Dryad repository).
 
@@
 
-![\label{figure3} Heatmap summarizing the morphological diversity measured in Damian-Serrano *et al.* 2020 for 96 species of siphonophores clustered by similarity (raw data in Dryad repository).
+![\label{figure3} Heatmap summarizing the morphological diversity measured in Damian-Serrano *et al.* 2020 for 96 species of siphonophores clustered by similarity (raw data published in Damian-Serrano 2020).
 Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.](~/tentilla_morph/Figures_final/figure3.jpg)
-
-*Evolutionary history of tentillum morphology* – [@damian2019evolution] produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+Values scaled by character.
+](~/tentilla_morph/Figures_final/figure3.jpg)
+
+*Evolutionary history of tentillum morphology* – In [@damian2019evolution], we produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
 This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
@@
 Most siphonophore tentilla measure between 175 and 1007 µm (1st and 3rd quartiles), with a median of 373 µm.
-The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes.
+The extreme gain of tentillum size in this newly found clade may have important implications for access to large prey size classes such as adult deep-sea fishes.
 
@@
 The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved]) that tentilla are likely ancestral to all siphonophores, and secondarily lost in *Apolemia* and *Bathyphysa conifera*.
-
-In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM22-30) and summarized in \@ref(figure7).
+In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2019evolution]) that tentilla are likely ancestral to all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.
+
+  In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
+\@ref(figure7)).
 Some of these characters include the gain and loss of nematocyst types.
-Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans.
+Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans [@mariscal1974nematocysts].
 Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
@@
 Nonetheless, they have evolved a wide variation in nematocyst and cnidoband sizes.
+Ancestrally (and retained in most prayomorphs and hippopodids), the calycophoran tentillum is recurved where the proximal and distal ends of the cnidoband are close together.
+Diphyomorph tentilla are slightly different in shape, with straighter cnidobands.
 
@@
 In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](~/tentilla_morph/Figures_final/figure7.jpg)
-
-*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM\@ref(ModelSupport)).
+The hypothesized phylogenetic placement of the rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](~/tentilla_morph/Figures_final/figure7.jpg)
+
+*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM10).
 Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1.
@@
 The majority (67%) of characters support BM models, indicating a history of neutral constant divergence.
-No relationship between phylogenetic signal and BM model support was found.
-Haploneme nematocyst length is the only character with support for an EB model of decreasing rate of evolution with time.
-No character had support for a single-optimum OU model (when uninformed by feeding guild regime priors).
+We did not find any relationship between phylogenetic signal and BM model support.
+Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
+No character had support for a single-optimum OU model (when notinformed by feeding guild regime priors).
 
@@
 Darker red and blue boxes indicate strong (<-0.5 or >0.5) negative and positive correlation coefficients respectively.](~/tentilla_morph/Figures_final/figure8.jpg){height=600px}
+
 *Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
@@
 \@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
+Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
+However, much of this correlation is due to the sharp contrast between Pyrostephidae and their sister group Tendiculophora.
+We searched for regime shifts in the evolution of haploneme nematocyst shape characters using a SURFACE [@ingram2013surface].
+SURFACE identified seven distinct OU regimes in the evolutionary history of haploneme length and width (Fig.
+\@ref(surface)A).
+The different regimes are located (1) in cystonects, (2) in pyrostephids, (7) in apolemiids, (9) in *Erenna*, (6) in *Stephanomia*, (3) in most of Tendiculophora, (5) in *Cordagalma ordinatum*, (4) in most diphyomorphs, and (8) in *Abylopsis tetragona* and *Diphyes dispar*.
 
@@
 Apolemiids have no tentacle haplonemes and are projected onto the heteroneme axis.
-](~/tentilla_morph/Figures_final/figure10.jpg)
-
-*Phenotypic integration of the tentillum* – Of the phylogenetic correlations (SM\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (SM\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
+](~/tentilla_morph/Figures_final/figure10-01-01.jpg)
+
+*Phenotypic integration of the tentillum* – Phenotypically integrated structures maintain evolutionary correlations between its constituent characters.
+Of the phylogenetic correlations (Fig.
+\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
+\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
 Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
-Similarly, of the across-species correlations, 49.1% were >0.5 and only 1.5% were < -0.5.
-We found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
+Similarly, among the correlations across extant species, 49.1% were >0.5 and only 1.5% were < -0.5.
+In addition, we found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
 Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
-These disparities can be caused by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
+These disparities could be explained by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
 However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of  -0.54).
 Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
+The phenotypic integration test showed significant integration signal between all modules, tentillum and haploneme modules sharing the greatest regression coefficient (SM12).
 
@@
 
-  In the non-phylogenetic PCA morphospace using only simple characters (SM\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
+  In the non-phylogenetic PCA morphospace using only simple characters (Fig.
+\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
 In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
+
+![\label{morphodiet}Phylomorphospace showing PC1 and PC2 from a PCA of continuous morphological characters with inapplicable states transformed to zeroes, overlapped with polygons conservatively defining the space occupied by each feeding guild.
+Lines between species coordinates show the phylogenetic relationships between them.
+](~/tentilla_morph/Organismal_paper/figures/morphospace_diets_full.png){height=600px}
+
+*Morphospace occupation* – In order to examine the occupation structure of the morphospace across all siphonophore species in the dataset, we cast a PCA on the data after transforming inapplicable states (due to absence of character) to zeroes.
+This allows us to accommodate species with many missing characters (such as cystonects or apolemiids), and to account for common absences as morphological similarities.
+In this ordination, PC1 explains 47.45% of variation (aligned with cnidoband size) and PC2 explains 16.73% of variation (aligned with heteroneme volume and involucrum).
+When superimposing feeding guilds onto the morphospace (Fig.
+\@ref(morphodiet)), we find that the morphospaces of each feeding guild are only slightly overlapping in PC1 and PC2.
+A phylogenetic MANOVA showed that feeding guilds explain 27.63% of variance across extant species (p value < 0.000001), and 20.97% of the variance in the tree species accounting for phylogeny, an outcome significantly distinct from the expectation under neutral evolution (p-value = 0.0196).
+In addition, a morphological disparity analysis accounting for phylogenetic structure shows that the morphospace of fish specialists is significantly broader than that of generalists and other specialists.
+This is due to the large morphological disparities between cystonects and piscivorous euphysonects.
+There are no significant differences among the morphospace disparities of the other feeding guilds.
+
+![\label{surface} SURFACE plots showing convergent evolutionary regimes modelled under OU for (A) haploneme nematocyst length & width, and (B) for PC1 & 2 of all continuous characters with the exception of terminal filament nematocysts, and removing taxa with inapplicable character states.
+Node numbers on the tree label different regimes, regimes of the same color are identified as convergent.
+Small circles on the scatterplots indicate species values, large circles indicate the average position of the OU optima (*theta*) for a given combination of convergent regimes.](~/tentilla_morph/Organismal_paper/figures/SURFACE-01.jpg){height=700px}
+
+*Convergent evolution* – Convergence is a widespread evolutionary phenomenon where distantly related clades independently evolve similar phenotypes.
+Using the package SURFACE [@ingram2013surface], we identified convergence in haploneme nematocyst shape and in morphospace position.
+In [@damian2019evolution], we identified haploneme nematocyst shape as one of the traits associated with the convergent evolution of piscivory.
+Here we find that indeed wider haploneme nematocysts have convergently evolved in the piscivore cytonects and *Erenna* spp.
+(Fig.
+\@ref(surface)A).
+Extremely narrow haplonemes have also evolved convergently in *Cordagalma ordinatum* and copepod specialist calycophorans such as *Sphaeronectes koellikeri*.
+When integrating many traits into a couple principal components, we find two distinct convergences between euphysonects and calycophorans with a reduced prey capture apparatus.
+Those convergences are between *Frillagalma vityazi* and calycophorans, and once again between *Cordagalma ordinatum* and *Spaheronectes koellikeri* (Fig.
+\@ref(surface)B).
+
+*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
+While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
+For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
+This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
+In addition, we observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
+Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
+Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
+
+*Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
+To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology using one the linear discriminant analyses of principal components (DAPC) fitted in [@damian2019evolution].
+This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
+The discriminant analysis for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width.
+We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in the morphological dataset.
+This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*.
+When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM13).
+The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
+
+  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
+Cell darkness indicates the posterior probability of belonging to each guild.
+Training data set transformed so inapplicable states are computed as zeroes.
+Species ordered and colored according to their predicted feeding guild.](~/tentilla_morph/Figures_final/figure6.jpg)
+
+## Discussion {-}
+
+*On the evolution of tentilla morphology* -- *On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
+The rate covariance results are congruent with the evolutionary correlations we found (Fig.
+/ref(figure8)).
+In addition, these evolutionary modules point to hypothetical functional modules.
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers.
+obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
+The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
+An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
+The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
+A specific instance of this may have been the access to the abundant small crustacean prey such as copepods.
+The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands.
 
@@
 
-![\label{morphodiet}Phylomorphospace of continuous morphological characters with inapplicable states transformed to zeroes, overlapped with polygons conservatively defining the space occupied by each feeding guild.
-](~/tentilla_morph/Organismal_paper/figures/morphospace_diet.png){height=600px}
-
-In order to examine the occupation structure of the morphospace across all siphonophore species in the dataset, we cast a PCA on the data transforming inapplicable states (due to absence of character) to zeroes.
-This allows us to accommodate species with many missing characters (such as cystonects), and to account for common absences as morphological similarities.
-In this ordination, PC1 explains 49.99% of variation (aligned with characters of the involucrum, terminal filament, and elastic strands) and PC2 explains 25.65% of variation (aligned with heteroneme number and haploneme length).
-When superimposing feeding guilds onto the morphospace (Fig.
-\@ref(morphodiet)), we find that the morphospaces of each feeding guild are barely overlapping in PC1 and PC2.
-A phylogenetic MANOVA showed that feeding guilds explain 22.09% of the variance in those dimensions, an outcome significantly distinct from the expectation under neutral evolution (p-value = 0.0196).
-In addition, a morphological disparity analysis accounting for phylogenetic structure shows that the morphospace of fish specialists is significantly broader than that of generalists and other specialists.
-This is due to the large morphological disparities between cystonects and piscivorous euphysonects.
-The superimposition of feeding guilds on the morphospace predicts the diet of *Erenna laciniata* to be piscivorous, *Lensia conoidea* and *Gymnopraia lapislazula* to be small crustacean eaters, *Lilyopsis fluoracantha* and *Physophora hydrostatica* to be generalists, and *Marrus claudanielis*, *Physophora gilmeri*, and *Halistemma rubrum* to be large crustacean specialists.
-
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
-While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
-For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
-
-  We also observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
-Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
-Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
-
-*Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
-We generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology and the associations between morphology and diet reported here for other species using the linear discriminant analysis of principal components (DAPC) fitted in [@damian2019evolution].
-This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
-The discriminant analysis in [@damian2019evolution] for feeding guild (7 principal components, 4 discriminants) produced 100% discrimination, and the highest loading contributions were found for the characters (ordered from highest to lowest): Involucrum length, heteroneme volume, heteroneme number, total heteroneme volume, tentacle width, heteroneme length, total nematocyst volume, and heteroneme width.
-We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in the morphological dataset.
-This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*.
-When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM\@ref(DAPCsofthard)).
-The main characters driving this discrimination are involucrum length, heteroneme number, heteroneme volume, tentacle width, total nematocyst volume, total haploneme volume, elastic strand width, and heteroneme length.
-We only selected prey types with sufficient variation in the data to carry out these analyses (copepods, fish, and large crustaceans).
-While the presence of fish or large crustaceans in the diet cannot be unambiguously discriminated using tentillum morphology (SM\@ref(DAPCfish),SM\@ref(DAPCcrustacean)), specialization on fish or large crustacean prey can be fully disentangled (SM\@ref(DPACguilds)).
-
-  ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
-Cell darkness indicates the posterior probability of belonging to each guild.
-Training data set transformed so inapplicable states are computed as zeroes.
-Species ordered and colored according to their predicted feeding guild.](~/tentilla_morph/Figures_final/figure6.jpg)
-
-## Discussion {-}
-
-*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
-This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers.
-obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
-The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-
-Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
-However, much of this correlation is due to the contrast between Pyrostephidae and their sister group Tendiculophora.
-We searched for rate regime shifts in the evolution of nematocyst shape characters using a Bayesian Analysis of Macroevolutionary Mixtures (BAMM) [@rabosky2014bamm] (SM32-35).
-BAMM located a regime shift in heteroneme shape evolution on the branches leading to *Agalma* and *Athorybia* (SM33).
-For the rates of haploneme shape evolution, BAMM identified two main independent regime shifts (Fig.
-\@ref(figure10)): one in the branch leading to Codonophora (anisorhizas diverging from cystonects’ spherical isorhizas), and one in the branch leading to Clade B physonects (SM35).
-Clade B includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids.
-Most of these taxa have rod-shaped anisorhizas, but *Erenna* have oval ones.
-No significant regime shift patterns were identified in the evolution of desmoneme and rhopaloneme shape.
-
-*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, our work reveals the specific morphological changes in the prey capture apparatus associated with these changes.
-Copepod-specialized diets have evolved convergently in *Cordagalma* and some calycophorans.
-These evolutionary transitions happened together with transitions to smaller tentilla with fewer cnidoband nematocysts.
+*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2019evolution]revealed the specific morphological changes in the prey capture apparatus associated with these changes.
+Copepod-specialized diets have evolved independently in *Cordagalma* and some calycophorans.
+These evolutionary transitions happened together with transitions to smaller tentilla with fewer and smaller cnidoband nematocysts.
+We found that these morphological transitions evolved convergently in these taxa.
 Tentilla are expensive single-use structures [@Mackie:1987uy], therefore we would expect that specialization in small prey would beget reductions in the size of the prey capture apparatus to the minimum required for the ecological performance.
-*Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*.
+Such a reduction in size would require extremely fast rates of trait evolution in an ordinary scenario.
+However, *Cordagalma*’s tentilla strongly resemble the larval tentilla (only found in the first-budded feeding body of the colony) of their sister genus *Forskalia*.
 This indicates that the evolution of *Cordagalma* tentilla could be a case of paedomorphic heterochrony associated with predatory specialization on smaller prey.
-
-Our work identifies a novel example of convergent evolution.
-The region of the tentillum morphospace (SM4) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+This developmental shift may have provided a shortcut for the evolution of a smaller prey capture apparatus.
+
+Our work identifies yet another novel example of convergent evolution.
+The region of the tentillum morphospace (Fig.
+/@ref(figure9) & Fig.
+/ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 Their tentillum morphology is very different from that of other related physonects, which tend to have long, coiled, cnidobands with many paired oval stenoteles.
+Our SURFACE analysis clearly indicates a regime convergence in the cnidoband morphospace between *Frillagalma* and calycophorans (Fig.
+/@ref(surface)B).
 Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
@@
 Our results show that Codonophora underwent a shift towards elongation and Cystonectae towards sphericity, assuming the common ancestor had an intermediate state.
-Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects retain this ancestral state.
+Since we know that the haplonemes of other hydrozoan outgroups are generally spheroid, it is more parsimonious to assume that cystonects are simply retaining this ancestral state.
 Later, we observe a return to more rounded (ancestral) haplonemes in *Erenna*, concurrent with a secondary gain of a piscivorous trophic niche, like that exhibited by cystonects.
-[@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
-The two clades that have converged to feed primarily on fish (Cystonectae and Clade B, which includes *Erenna*, *Stephanomia*, *Marrus*, and rhodaliids) have also converged morphologically toward more compact haplonemes, significantly distinct from their closest relatives.
+Our SURFACE analysis shows that this transition to roundness is convergent with the regime occupied by cystonects (Fig.
+/@ref(surface)A).
+Purcell [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
+It is no coincidence that the two clades that have converged to feed primarily on fish have also converged morphologically toward more compact haplonemes.
 Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
@@
 We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-[@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
+Thomason [@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
 The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey [@purcell1984functions], and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
@@
 Within these clades are the most abundant siphonophore species, and a greater morphological and ecological diversity is found.
-We hypothesize that this packing-efficient haploneme morphology may have been a key innovation leading to the diversification of this clade.
-However, other characters that shifted concurrently in the stem of this clade may have been responsible for their extant diversity.
-
-*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research was to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
+We hypothesize that this packing-efficient haploneme morphology may have also been a key innovation leading to the diversification of this clade.
+However, other characters that shifted concurrently in the stem of this clade could have been equally responsible for their extant diversity.
+
+*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research is to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
 Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
@@
 This reveals the need to extensively characterize siphonophore diets and feeding habits.
-In future work, we can test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
+In future work, we will test these ecological hypotheses and validate these models by directly characterizing the diets of some of those siphonophore species.
 Predicting diet using morphology is a powerful tool to reconstruct food web topologies from community composition alone.
@@
 The ability to predict such interactions, including those of siphonophores and their prey, will enhance the taxonomic resolution of nutrient-flow models constructed from plankton community composition data.
+
 ## Acknowledgements {-}
@@
 was supported by a Fulbright Spain Graduate Studies Scholarship.
-
-## Supplementary Materials {-}
-
-![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character.
-Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}
-
-![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character.
-Cvar = coefficient of variation of the absolute value of the contrasts.
-Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances.
-Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node.
-Shgt = slope of the contrasts against node depth.
-Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.
-](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
 
@@
 #hypdiet but for all species not only those in tree
-hypdiet_full = c("Mixed","Mixed","Gelatinous","Gelatinous","Mixed","Large crustacean","Small crustacean","Small crustacean","Small crustacean","Small crustacean","Fish","Fish","Mixed","Small crustacean","Large crustacean","Small crustacean","Large crustacean","Fish","Large crustacean","Large crustacean","Large crustacean","Fish","Fish","Small crustacean","Small crustacean","Fish","Small crustacean","Small crustacean")
-dpruned_full = fullraw_nozeroes[which(fullraw_nozeroes$Species%in%rownames(diet)),]
-dpruned_full <- data.frame(dpruned_full, "Diet" = hypdiet_full)
+## ALSO reconsidering Forskalia interpretation as small crustacean specialist, and assigning all Forskalia species
+hypdiet_full = c("Mixed","Mixed","Gelatinous","Gelatinous","Mixed","Large crustacean","Small crustacean","Small crustacean","Small crustacean","Small crustacean","Fish","Fish","Mixed","Small crustacean","Large crustacean","Small crustacean","Large crustacean","Fish","Large crustacean","Large crustacean","Large crustacean","Fish","Fish","Small crustacean","Small crustacean","Fish","Small crustacean","Small crustacean","Mixed", "Mixed", "Mixed")
+names(hypdiet_full) = c("Agalma elegans", "Agalma okenii", "Apolemia rubriversa", "Apolemia uvaria", "Athorybia rosacea", "Bargmannia amoena", "Bassia bassensis", "Chelophyes appendiculata", "Cordagalma ordinatum", "Diphyes dispar", "Erenna richardi", "Erenna sirena", "Forskalia tholoides", "Hippopodius hippopus", "Lychnagalma utricularia", "Marrus orthocanna", "Nanomia sp", "Physalia physalis", "Praya dubia", "Resomia ornicephala", "Resomia persica", "Rhizophysa eysenhardtii", "Rhizophysa filiformis", "Rosacea cymbiformis", "Sphaeronectes koellikeri", "Stephanomia amphytridis", "Stephanophyes superba", "Sulculeolaria quadrivalvis", "Forskalia formosa", "Forskalia asymmetrica", "Forskalia edwardsii")
+#dpruned_full = fullraw_nozeroes[which(fullraw_nozeroes$Species%in%names(hypdiet_full)),]
+#dpruned_full <- data.frame(dpruned_full, "Diet" = hypdiet_full)
+dpruned_full = data.frame(fullraw_nozeroes, "Diet" = hypdiet_full[match(rownames(fullraw_nozeroes), names(hypdiet_full))], stringsAsFactors = F)
 ```
@@
 phylomorphospace(raw_tree, PPCA_raw$S, label = "horizontal")
-
-## BAMM ##
-
-traitlist = list()
-for(i in 2:ncol(sharedmean_logs)){
-  traitlist[[i]] <- sharedmean_logs[,c(1,i)]
-  names(traitlist)[i] = names(sharedmean_logs)[i]
-}
-
-traitlist <- lapply(traitlist, function(x){x<-x[which(!is.nan(x[,2])),]})
-
-for(i in 2:length(traitlist)){
-  treei = drop.tip(ultram, which(!(ultram$tip.label %in% traitlist[[i]]$Species)))
-  treei$tip.label = str_replace_all(treei$tip.label, " ", "_")
-  write.tree(treei, file = paste("BAMM/",names(traitlist[[i]])[2], "_tree.tre", sep=""))
-}
-
-for(i in 2:length(traitlist)){
-  traitlist[[i]]$Species = str_replace_all(traitlist[[i]]$Species, " ", "_")
-  write.table(traitlist[[i]],file = paste("BAMM/",names(traitlist[[i]])[2], ".txt", sep=""), sep="\t", col.names = F, row.names = F, quote = F)
-}
-
-#See BAMM/BAMMsetpriors.R
-#See BAMM/BAMMplots.R
-#See BAMM/BAMMconfiguration.txt
-```
-
-```{r newanalyses, echo=F, eval=F}
-### Morphospace analyses ###
-hypfood <- data.frame(hypdiet, hypdiet, stringsAsFactors = F)
-#morphood <- raw_matrix_NaZeroes[which(rownames(raw_matrix_NaZeroes) %in% rownames(hypfood)),]
-#morphood <- raw_matrix_notf[which(rownames(raw_matrix_notf) %in% rownames(hypfood)),]
-#hypfood <- hypfood[match(rownames(morphood), rownames(hypfood)),]
-#morphospace_data <- cbind(morphood, hypfood[,1])
-morphospace_data = cbind(raw_matrix_NaZeroes, hypfood[match(rownames(raw_matrix_NaZeroes), rownames(hypfood)),1])
-names(morphospace_data)[ncol(morphospace_data)] <- "Diet"
-morphospace_data$Diet <- as.character(morphospace_data$Diet) %>% str_replace_all(" ", "_")
-
-#Test for morphospatial overlap between feeding guilds
-pca_morph <- prcomp(morphospace_data[,-ncol(morphospace_data)])
-autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet", loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = "black")+theme_bw()
-autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet")+theme_bw()
-phylomorphospace(drop.tip(ultram, which(!(ultram$tip.label %in% rownames(morphospace_data)))), pca_morph$x[,1:2], label="horizontal")
-
-#MANOVA for diet
-LMdata <- cbind(pca_morph$x, morphospace_data$Diet) %>% as.data.frame(stringsAsFactors = F)
-LMdata[,-ncol(LMdata)] <- apply(LMdata[,-ncol(LMdata)], 2, as.numeric)
-names(LMdata)[ncol(LMdata)] <- "Diet"
-MAN1 <- manova(cbind(PC1, PC2) ~ Diet, data = LMdata)
-MAN1 %>% summary.manova() %>% .$SS %>% .$Diet -> MSS1
-var_exp = (MSS1[1,2]+MSS1[2,1])/sum(MSS1)
-library(geiger)
-LMtree <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(LMdata))))
-dat <- LMdata[,1:2]
-D <- LMdata$Diet %>% as.factor()
-names(D) <- rownames(LMdata)
-PMAN <- aov.phylo(dat ~ D, phy = LMtree, nsim=50, test="Wilks")
-PMAN  %>% summary.manova() %>% .$SS %>% .$group -> pMSS
-var_exp_phyl = (pMSS[1,2]+pMSS[2,1])/sum(pMSS)
-
-library(geomorph)
-morphol.disparity(dat ~ 1, groups = D)
-gdf <- geomorph.data.frame(shape = as.matrix(dat), phy = LMtree, grp = D)
-ANOVA <- procD.pgls(shape ~ grp, phy = phy, data = gdf)
-morphol.disparity(f1 = ANOVA, groups = ~grp, data = gdf, iter = 999)
-
-#Fish specialization convergence
-##
-pcanonaphenos = PCA(raw_matrix_NaZeroes)
-phenotree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcanonaphenos$ind$coord))))
-fishtips = c(rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Erenna")], "Physalia physalis", rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Rhizophy")])
-phylomorphospace(phenotree, pcanonaphenos$ind$coord, label = "horizontal")
-convnumsig(phenotree, pcanonaphenos$ind$coord[,1:2], plot=F, convtips = fishtips, nsim=30)
-convnum(phenotree, pcanonaphenos$ind$coord[,1:2], plot=T, convtips = fishtips)
-convrat(phenotree,pcanonaphenos$ind$coord[,1:2], convtips = fishtips)
-convratsig(phenotree,pcanonaphenos$ind$coord[,1:2], convtips = fishtips, nsim=5)
-
-#Frillagalma-Calycophoran convergence
-pcaphenos = PCA(raw_matrix_notf)
-phenotree_2 = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcaphenos$ind$coord))))
-frilltips1 = c("Frillagalma vityazi", extract.clade(phenotree_2, getMRCA(phenotree_2, c("Sphaeronectes koellikeri", "Praya dubia")))$tip.label, "Agalma elegans")
-phylomorphospace(phenotree_2, pcaphenos$ind$coord, label = "horizontal")
-convnumsig(phenotree_2, pcaphenos$ind$coord[,1:2], plot=F,convtips = frilltips1, nsim=30) %>% print()
-convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = frilltips1)
-convrat(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1)
-convratsig(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1, nsim=1)
-
-#Lilyopsis pyrostephids
-convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = c("Bargmannia amoena", "Bargmannia elongata", "Lilyopsis fluoracantha", "Vogtia glabra", "Abylopsis tetragona", "Praya dubia", "Frillagalma vityazi"))
-
-#Heatmap of expected convergence
-coph <- cophenetic(phenotree_2)
-dis <- 1/vegdist(scale(pcaphenos$ind$coord[,1:2]), "euc") %>% as.matrix()
-diag(dis) <- NA
-(dis - mean(dis, na.rm=T))/mean(dis, na.rm=T) -> dis
-dis
-ggplot(melt(dis /coph), aes(Var1, Var2)) + 
-  geom_tile(aes(fill = value), colour = "black") + 
-  scale_fill_distiller(palette = "RdBu", direction=1) + 
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1))
-
-RR = RRphylo(tree=phenotree, y = pcanonaphenos$ind$coord[,1:2])
 
@@
 cor(kinemorph[,c(-1,-32)], use="pairwise.complete.obs") %>% .[c(1:30),c(31:41)] %>% corrplot(diag=F, tl.cex = 0.4, tl.col="black")
-
 ```
+
+```{r newanalyses, echo=F, eval=F}
+### Morphospace analyses ###
+hypfood <- data.frame(hypdiet, hypdiet, stringsAsFactors = F)
+hypfood_full <- data.frame(hypdiet_full, hypdiet_full, stringsAsFactors = F)
+#morphood <- raw_matrix_NaZeroes[which(rownames(raw_matrix_NaZeroes) %in% rownames(hypfood)),]
+#morphood <- raw_matrix_notf[which(rownames(raw_matrix_notf) %in% rownames(hypfood)),]
+#hypfood <- hypfood[match(rownames(morphood), rownames(hypfood)),]
+#morphospace_data <- cbind(morphood, hypfood[,1])
+morphospace_data = cbind(raw_matrix_NaZeroes, hypfood_full[match(rownames(raw_matrix_NaZeroes), rownames(hypfood_full)),1])
+names(morphospace_data)[ncol(morphospace_data)] <- "Diet"
+morphospace_data$Diet <- as.character(morphospace_data$Diet) %>% str_replace_all(" ", "_")
+
+#Test for morphospatial overlap between feeding guilds
+pca_morph <- prcomp(morphospace_data[,-ncol(morphospace_data)])
+autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet", loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = "black")+theme_bw()
+autoplot(pca_morph, data = morphospace_data, frame = TRUE, label=T, colour="Diet")+theme_bw()
+phylomorphospace(drop.tip(ultram, which(!(ultram$tip.label %in% rownames(morphospace_data)))), pca_morph$x[,1:2], label="horizontal")
+
+#MANOVA for diet
+LMdata <- cbind(pca_morph$x, morphospace_data$Diet) %>% as.data.frame(stringsAsFactors = F)
+LMdata[,-ncol(LMdata)] <- apply(LMdata[,-ncol(LMdata)], 2, as.numeric)
+names(LMdata)[ncol(LMdata)] <- "Diet"
+MAN1 <- manova(cbind(PC1, PC2) ~ Diet, data = LMdata)
+MAN1 %>% summary.manova() %>% .$SS %>% .$Diet -> MSS1
+var_exp = (MSS1[1,2]+MSS1[2,1])/sum(MSS1)
+
+#phyl.MANOVA
+LMtree <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(LMdata))))
+dat <- LMdata[,1:2]
+D <- LMdata$Diet %>% as.factor()
+names(D) <- rownames(LMdata)
+PMAN <- aov.phylo(dat ~ D, phy = LMtree, nsim=50, test="Wilks")
+PMAN  %>% summary.manova() %>% .$SS %>% .$group -> pMSS
+var_exp_phyl = (pMSS[1,2]+pMSS[2,1])/sum(pMSS)
+
+#geomorph disparity
+Di <- D[!is.na(D)]
+dati <- dat[which(rownames(dat) %in% names(Di)),]
+tree_i <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(dati))))
+morphol.disparity(dati ~ 1, groups = Di)
+gdf <- geomorph.data.frame(shape = as.matrix(dati), phy = tree_i, grp = Di)
+ANOVA <- procD.pgls(shape ~ grp, phy = phy, data = gdf)
+morphol.disparity(f1 = ANOVA, groups = ~grp, data = gdf, iter = 999)
+
+###FULL PCA DIET ###
+dpruned_full <- dpruned_full[which(!(dpruned_full$Species %in% c("Nectadamas richardi", "Thermopalia taraxaca", "Halistemma foliacea", "Halistemma transliratum", "Halistemma cupulifera", "Resomia dunni", "Resomia persica", "Cardianecta parchelion", "Forskalia tholoides"))),]
+dpruned_full_raw <- dpruned_full[,c(1:21,33)]
+pca_fullmorph <- prcomp(dpruned_full_raw[,c(-1,-ncol(dpruned_full_raw))])
+autoplot(pca_fullmorph, data = dpruned_full_raw, frame = TRUE, label=T, colour="Diet", loadings = TRUE, loadings.colour = 'black', loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = "black")+theme_bw()
+
+autoplot(pca_fullmorph, data = dpruned_full_raw, frame = TRUE, label=T, colour="Diet")+theme_bw()
+
+phylomorphospace(drop.tip(ultram, which(!(ultram$tip.label %in% rownames(dpruned_full_raw)))), pca_fullmorph$x[which(rownames(pca_fullmorph$x) %in% ultram$tip.label),1:2], label="horizontal")
+
+#full MANOVA
+full_LMdata <- cbind(pca_fullmorph$x, dpruned_full$Diet) %>% as.data.frame(stringsAsFactors = F)
+full_LMdata[,-ncol(full_LMdata)] <- apply(full_LMdata[,-ncol(full_LMdata)], 2, as.numeric)
+names(full_LMdata)[ncol(full_LMdata)] <- "Diet"
+full_MAN1 <- manova(cbind(PC1, PC2) ~ Diet, data = full_LMdata)
+full_MAN1 %>% summary.manova() %>% .$SS %>% .$Diet -> full_MSS1
+full_var_exp = (full_MSS1[1,2]+full_MSS1[2,1])/sum(full_MSS1)
+
+#phyl.MANOVA full
+full_LMtree <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(full_LMdata))))
+full_dat <- full_LMdata[,1:2]
+full_D <- full_LMdata$Diet %>% as.factor()
+names(full_D) <- rownames(full_LMdata)
+full_PMAN <- aov.phylo(full_dat ~ full_D, phy = full_LMtree, nsim=50, test="Wilks")
+full_PMAN  %>% summary.manova() %>% .$SS %>% .$group -> full_pMSS
+full_var_exp_phyl = (full_pMSS[1,2]+full_pMSS[2,1])/sum(full_pMSS)
+
+#geomorph disparity
+full_Di <- full_D[!is.na(full_D)]
+full_Di <- full_Di[which(names(full_Di) %in% rownames(full_dat) & names(full_Di) %in% ultram$tip.label)]
+full_dati <- full_dat[which(rownames(full_dat) %in% names(full_Di) & rownames(full_dat) %in% ultram$tip.label),]
+full_tree_i <- drop.tip(ultram, which(!(ultram$tip.label %in% rownames(full_dati))))
+morphol.disparity(full_dati ~ 1, groups = full_Di)
+full_gdf <- geomorph.data.frame(shape = as.matrix(full_dati), phy = full_tree_i, grp = full_Di)
+full_ANOVA <- procD.pgls(shape ~ grp, phy = phy, data = full_gdf)
+morphol.disparity(f1 = full_ANOVA, groups = ~grp, data = full_gdf, iter = 999)
+
+#### CONVERGENCE ###
+pcanonaphenos = PCA(raw_matrix_NaZeroes)
+phenotree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcanonaphenos$ind$coord))))
+phylomorphospace(phenotree, pcanonaphenos$ind$coord[which(rownames(pcanonaphenos$ind$coord) %in% ultram$tip.label),], label = "horizontal")
+
+#Fish specialization convergence
+fishtips = c(rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Erenna")], "Physalia physalis", rownames(pcanonaphenos$ind$coord)[startsWith(rownames(pcanonaphenos$ind$coord), "Rhizophy")])
+
+phenotypes <- raw_matrix_NaZeroes[,6:7]
+convnumsig(phenotree, phenotypes, plot=F, convtips = fishtips, nsim=30) %>% print()
+convnum(phenotree, phenotypes, plot=T, convtips = fishtips)
+convrat(phenotree,phenotypes, convtips = fishtips)
+convratsig(phenotree,phenotypes, convtips = fishtips, nsim=5)
+
+#Frillagalma-Calycophoran convergence
+pcaphenos = PCA(raw_matrix_notf)
+phenotree_2 = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(pcaphenos$ind$coord))))
+frilltips1 = c("Frillagalma vityazi", extract.clade(phenotree_2, getMRCA(phenotree_2, c("Sphaeronectes koellikeri", "Praya dubia")))$tip.label, "Agalma elegans")
+phylomorphospace(phenotree_2, pcaphenos$ind$coord, label = "horizontal")
+convnumsig(phenotree_2, pcaphenos$ind$coord[,1:2], plot=F,convtips = frilltips1, nsim=30) %>% print()
+convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = frilltips1)
+convrat(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1)
+convratsig(phenotree_2,pcaphenos$ind$coord, convtips = frilltips1, nsim=1)
+
+#Lilyopsis pyrostephids
+convnum(phenotree_2, pcaphenos$ind$coord[,1:2], plot=T,convtips = c("Bargmannia amoena", "Bargmannia elongata", "Lilyopsis fluoracantha", "Vogtia glabra", "Abylopsis tetragona", "Praya dubia", "Frillagalma vityazi"))
+
+##SURFACE##
+
+surfaceALL <- function(data){
+  Tree <- nameNodes(drop.tip(ultram, which(!(ultram$tip.label %in% rownames(data)))))
+  olist <- convertTreeData(Tree, data)
+  otree<-olist[[1]]
+  odata<-olist[[2]]
+  fwd<-surfaceForward(otree, odata, aic_threshold = 0, exclude = 0, verbose = FALSE, plotaic = FALSE)
+  k<-length(fwd)
+  fsum<-surfaceSummary(fwd)
+  bwd<-surfaceBackward(otree, odata, starting_model = fwd[[k]], aic_threshold = 0, only_best = TRUE, verbose = FALSE, plotaic = FALSE)
+  bsum<-surfaceSummary(bwd)
+  kk<-length(bwd)
+  print("N regimes BWD")
+  bsum$n_regimes %>% return()
+  par(mfrow=c(1,2))
+  surfaceTreePlot(Tree, bwd[[kk]], labelshifts = T) %>% return()
+  surfaceTraitPlot(data, bwd[[kk]], whattraits = c(1,2)) %>% return()
+  newsim<-surfaceSimulate(Tree, type="hansen-fit", hansenfit=fwd[[k]]$fit, shifts=fwd[[k]]$savedshifts, sample_optima=TRUE)
+  newout<-runSurface(Tree, newsim$dat, only_best = TRUE)
+  newsum<-surfaceSummary(newout$bwd)
+  newkk<-length(newout$bwd)
+  print("N regimes SIM")
+  newsum$n_regimes %>% return()
+}
+
+raw_matrix_NaZeroes[,6:7]
+pcaphenos$ind$coord[,1:2] %>% as.data.frame()
+PCA(raw_matrix_NaZeroes)$ind$coord[,1:2] %>% as.data.frame()
+
+surfaceALL(raw_matrix_NaZeroes[,6:7]) #haploneme shape
+surfaceALL(pcaphenos$ind$coord[,1:3] %>% as.data.frame()) #trait values PCA 1 2 without TF, excluding some species
+surfaceALL(PCA(raw_matrix_NaZeroes)$ind$coord[,1:2] %>% as.data.frame()) #ALL TRAITS PC1 and 2, all SPP in tree, NA to zeroes ALL TRAITS PC1 and 2, all SPP in MORPH dataset, NA to zeroes
+surfaceALL(raw_matrix_NaZeroes[,8:11]) #desmonemes rhopalonemes?
+
+#Phenotypic integration test
+
+M1_het <- sharedmean_logs[c(2:6)]
+rownames(M1_het) <- sharedmean_logs$Species
+M1_het <- M1_het[which(!is.na(rowSums(M1_het))),]
+
+M2_hap <- sharedmean_logs[c(8:9)]
+rownames(M2_hap) <- sharedmean_logs$Species
+M2_hap <- M2_hap[which(!is.na(rowSums(M2_hap))),]
+
+M3_tf <- sharedmean_logs[c(10:13)]
+rownames(M3_tf) <- sharedmean_logs$Species
+M3_tf <- M3_tf[which(!is.na(rowSums(M3_tf))),]
+
+M4_tent <- sharedmean_logs[c(14:21)]
+rownames(M4_tent) <- sharedmean_logs$Species
+M4_tent <- M4_tent[which(!is.na(rowSums(M4_tent))),]
+
+phint <- function(MA,MB,Tr){
+  a <- MA[which(rownames(MA) %in% rownames(MB)),]
+  b <- MB[which(rownames(MB) %in% rownames(a)),]
+  t <- drop.tip(Tr, which(!(Tr$tip.label %in% rownames(a) & Tr$tip.label %in% rownames(b))))
+  phylo.integration(A = as.matrix(a), A2 = as.matrix(b), phy = t) %>% return()
+  }
+
+table.phint <- function(modules, tree){
+  I <- length(modules)
+  R <- data.frame(matrix(ncol=I, nrow=I))
+  rownames(R) = names(modules)
+  names(R) = names(modules)
+  P <- data.frame(matrix(ncol=I, nrow=I))
+  rownames(P) = names(modules)
+  names(P) = names(modules)
+  for(i in 1:I){
+    for(j in 1:I){
+      if(i != j){
+        ph_ij <- phint(modules[[i]], modules[[j]], Tr = tree)
+        R[i,j] <- ph_ij$r.pls
+        P[i,j] <- ph_ij$P.value
+      }
+      print(R);print(P)
+    }
+    print(R); print(P)
+  }
+  Rm <- melt(cbind(names(modules),R))
+  names(Rm) <- c("M1", "M2", "rPLS")
+  Pm <- melt(cbind(names(modules),P))
+  names(Pm) <- c("M1", "M2", "P.value")
+  return(full_join(Rm,Pm))
+}
+
+MODS <- list(M1_het, M2_hap, M3_tf, M4_tent)
+names(MODS) <- c("Heteronemes", "Haplonemes", "Terminal filament", "Tentillum")
+MODSphint <- table.phint(MODS, tree = ultram)
+
+ordering <- c("Tentillum","Heteronemes","Haplonemes", "Terminal filament")
+ggplot(MODSphint, aes(factor(M1, levels = ordering), factor(M2, levels = ordering))) + 
+  geom_tile(aes(fill = rPLS), colour = "black") + 
+  scale_fill_distiller(palette = "Blues", direction=1) + 
+  geom_text(aes(label = P.value %>% round(3))) +
+  labs(y= "", x = "") +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+
+```

### 2020-05-15 Organismal_paper/Organismal_supplement.Rmd
cleanup writing, add phenotypic integration. Make supplementary materials RMD

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
---

```{r setup, include=FALSE, echo=FALSE, eval=FALSE}
	# Load packages
	## General
library(knitr)
library(tidyverse)

	# Configure knitr, see http://yihui.name/knitr/options
	opts_knit$set(
	  progress=TRUE,
	  verbose=TRUE)
	opts_chunk$set(
	#  include=FALSE,
	  cache=TRUE,
	  echo=FALSE,
	  message=FALSE
	 )
knitr::opts_chunk$set(echo = TRUE)

```

#Supplementary Materials## Supplementary Materials {-}

![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/tentillaPresenceSIM.png)

![\label{SIMMAPproxhet} SIMMAP Cnidoband proximal heteroneme presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/proxhet_presence.png)

![\label{SIMMAPdesmorhopalo} SIMMAP Desmoneme+Rhopaloneme presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/desmorhopalo_SIM.png)

![\label{SIMMAPdischarge} SIMMAP Actively discharging cnidobands presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/discharge_SIM.png)

![\label{SIMMAP_ES} SIMMAP Elastic strands presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Elasticstrands_SIM.png)

![\label{SIMMAP_distalDesmo} SIMMAP Cnidoband distal desmonemes presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/distalDesmo_SIM.png)

![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoaband phenotype presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)

![\label{SIMMAP_HetType} SIMMAP Heteroneme type.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/hettype_SIM.png)

![\label{SIMMAP_HapType} SIMMAP Haploneme type.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/haptype_SIM.png)

![\label{ModelSupport} Model support (delta AICc), phylogenetic signal (Blomberg’s K), and phylogenetic signal permutation test p-value for each continuous character. Ntaxa = Number of taxa used in the analyses after removing those where the character sate is inapplicable or the data is missing.](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelSupport.png){height=600px}

![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character. Cvar = coefficient of variation of the absolute value of the contrasts. Svar = Slope of a linear model fitted to the absolute value of the contrasts against their expected variances. Sasr = slope of the contrasts against the ancestral state inferred at each corresponding node. Shgt = slope of the contrasts against node depth. Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)

![\label{ph.int} Heatmap showing the phenotypic integration between character modules accounting for phylogeny. Text in cells shows p-values. Color indicates the partial least squares (PLS) multivariate correlation coefficients. ](~/tentilla_morph/Figures_final/phint.png)

![\label{DAPCsofthard} DAPC for soft-bodied vs. hard bodied prey specialization. Six PCs retained after a-score optimization (100 iterations). Two LDA functions used. Discriminant power on training set: 90.9%. Grayscale heat map shows the posterior probability distribution of the predictions. Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_softhard.png)

### 2020-05-15 Organismal_paper/Organismal_supplement.Rmd
knitted supplements

@@
 
-#Supplementary Materials## Supplementary Materials {-}
+# Supplementary Materials {-}
+\FloatBarrier
 

### 2020-05-15 Organismal_paper/Organismal_manuscript_and_code.Rmd
knitted modified MS text

@@
 ---
-bibliography: manuscript.bib
+bibliography: org_manuscript.bib
 csl: pnas.csl
@@
 SSiphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades (cite Phil, Steve, etc), which has been elegantly synthesized in detailed synopsis [@totton1954synopsis, @mapstone2014global].
+Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades (cite Phil, Steve, etc), which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
 In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
@@
 Nematocysts are unique biological weapons for defense and prey capture exclusive to the phylum Cnidaria.
-Mariscal ([@mariscal1974nematocyst]) reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
+Mariscal ([@mariscal1974nematocysts]) reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
 Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles.
@@
 When looking at the morphospace of species in different feeding guilds, we also used PCA on the complete tentacular character dataset transforming inapplicable states of absent characters to zeros to account for similarity based on character presence/absence.
-Using these principal components, we examined the occupation of the morphospace across species in different feeding guilds using a phylogenetic MANOVA with the package *geiger* [@harmon2008geiger] to assess the variation explained, and a morphological disparity test with the package *geomorph* [@adams2016geomorph] to assess differences in the extent occupied by each guild.
+Using these principal components, we examined the occupation of the morphospace across species in different feeding guilds using a phylogenetic MANOVA with the package *geiger* [@harmon2007geiger] to assess the variation explained, and a morphological disparity test with the package *geomorph* [@adams2016geomorph] to assess differences in the extent occupied by each guild.
 
@@
 We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length (μm), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data available in the Dryad repository).
+For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length ($\mu$m), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data available in the Dryad repository).
 

### 2020-05-22 Organismal_paper/Organismal_manuscript_and_code.Rmd
model adequacy chunk

@@
 
-SSiphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades (cite Phil, Steve, etc), which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
+Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
+Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
 In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
@@
 This maximizes the surface area of contact between the nematocysts and the prey they fire upon.
-In addition, siphonophore tentilla present a remarkable diversity of morphologies, sizes, and nematocyst complements (Fig, /@ref(figure2)).
+In addition, siphonophore tentilla present a remarkable diversity of morphologies, sizes, and nematocyst complements (Fig.
+\@ref(figure2)).
 Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it.
@@
 
-In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) trained in [@damian2019evolution] using the package *adegenet* [@jombart2008adegenet] to predict the feeding guilds of species in the dataset for which there are no published feeding observations.
+In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2019evolution] to predict the feeding guilds of species in the dataset for which there are no published feeding observations.
 
@@
 ## Results {-}
-
-![\label{figure3} Heatmap summarizing the morphological diversity measured in Damian-Serrano *et al.* 2020 for 96 species of siphonophores clustered by similarity (raw data published in Damian-Serrano 2020).
-Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
-Values scaled by character.
-](~/tentilla_morph/Figures_final/figure3.jpg)
 
@@
 Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
-No character had support for a single-optimum OU model (when notinformed by feeding guild regime priors).
+No character had support for a single-optimum OU model (when not informed by feeding guild regime priors).
+The model adequacy tests (SM11) indicate that many characters may have a relationship between the states and the rates of evolution (Sasr) not captured in the basic models compared here, accompanied by a signal of unaccounted rate heterogeneity (Cvar).
+No characters show significant deviations in the overall rate of evolution estimated (Msig).
+Some characters show a perfect fit (no significant deviations across all metrics) under BM evolution, such as heteroneme shape, length, width & volume, haploneme width & SA/V, tentacle width and pedicle width.
+Haploneme row number and rhopaloneme shape have significant deviations across four metrics, indicating that BM (best model) is a poor fit.
+These characters likely evolved under complex models which would require many more data points than we have available to fit with accuracy.
 
@@
 The rate covariance results are congruent with the evolutionary correlations we found (Fig.
-/ref(figure8)).
+\ref(figure8)).
 In addition, these evolutionary modules point to hypothetical functional modules.
@@
 The region of the tentillum morphospace (Fig.
-/@ref(figure9) & Fig.
-/ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+\@ref(figure9) & Fig.
+\ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 Our SURFACE analysis clearly indicates a regime convergence in the cnidoband morphospace between *Frillagalma* and calycophorans (Fig.
-/@ref(surface)B).
+\@ref(surface)B).
 Most studies on calycophoran diets have reported their prey to be primarily composed of small crustaceans, such as copepods or ostracods [@purcell1981dietary;@purcell1984functions].
@@
 Our SURFACE analysis shows that this transition to roundness is convergent with the regime occupied by cystonects (Fig.
-/@ref(surface)A).
+\@ref(surface)A).
 Purcell [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.

### 2020-05-22 Organismal_paper/Organismal_supplement.Rmd
model adequacy chunk

@@
 
-![\label{ModelAdequacy} Model adequacy scores for the best model supported for each morphological character.
+![\label{ModelAdequacy} P-values of the model adequacy score tests for the best model supported for each morphological character.
 Cvar = coefficient of variation of the absolute value of the contrasts.
@@
 Dcfd = Kolmolgorov-Smirnov D-statistic comparing contrasts to a normal distribution with SD equal to the root of the mean of squared contrasts.
+P-values < 0.05 were highlighted in grey, indicating significant deviations between the model and the observed data.
 ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/modelAdequacy.png)
@@
 Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/DAPC_softhard.png)
+
+![\label{figure3} Heatmap summarizing the morphological diversity measured in Damian-Serrano *et al.* 2020 for 96 species of siphonophores clustered by similarity (raw data published in Damian-Serrano 2020).
+Missing values from absent characters presented as dark grey cells, missing values produced from technical difficulties presented as white cells.
+Values scaled by character.](~/tentilla_morph/Figures_final/figure3.jpg)

### 2020-07-08 Organismal_paper/Organismal_manuscript_and_code.Rmd
first round of corrections after CWD partial pass - starting new intro figure for organismal paper

@@
 
+Siphonophores are free-living predatory colonial hydrozoan cnidarians found in every ocean of the world.
 Siphonophore tentilla (tentacle side branches) are unique biological structures for prey capture, composed of a complex arrangement of cnidocytes (stinging cells) bearing different types of nematocysts (stinging capsules) and auxiliary structures.
-Tentilla present an exuberant morphological diversity of form and function across species.
+Tentilla present an extensive morphological and functional diversity across species.
 While associations between tentilla form and diet have been reported, the evolutionary history giving rise to this morphological diversity is largely unexplored.
-Here we explore the evolutionary gains and losses of novel tentillum substructures and nematocyst types on the most recent siphonophore phylogeny.
+Here we examine the evolutionary gains and losses of novel tentillum substructures and nematocyst types on the most recent siphonophore phylogeny.
 Tentilla have a precisely coordinated high-speed strike mechanism of synchronous unwinding and nematocysts discharge.
@@
 Since tentillum discharge occurs in synchrony across a broad morphological diversity, we evaluate how phenotypic integration is maintaining character correlations across evolutionary time.
-Moreover, we analyze the dimensionality of the tentillum morphospace, identify instances of heterochrony and morphological convergence, and generate hypotheses on the diets of understudied siphonophore species.
+We found that the the tentillum morphospace has low dimensionality, we identified instances of heterochrony and morphological convergence, and generated hypotheses on the diets of understudied siphonophore species.
 Our findings indicate that siphonophore tentilla are phenotypically integrated structures with a complex evolutionary history leading to a phylogenetically structured diversity of forms which are predictive of kinematic performance and feeding habits.
@@
 Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-Today we hold more knowledge than ever on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
+Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
 In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
@@
 Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts.
-But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by shooting the nematocyst battery to slap around the prey.
+But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by rapidly unfolding the nematocyst battery to slap around the prey.
 This maximizes the surface area of contact between the nematocysts and the prey they fire upon.
@@
 \@ref(figure2)).
-Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it.
+Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it
 
@@
 The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
+The primary findings of that work were that generalists evolved from crustacean-specialist ancestors, and that feeding specializations were associated with distinct modes of evolution and character integration patterns.
 The work we present here is complementary to [@damian2019evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
@@
 Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles.
+Werner [@werner1965nesselkapseln] noted that there are nine types of nematocyst found in siphonophores, of which four, anacrophore rhopalonemes, acrophore rhopalonemes, homotrichous anisorhizas, and birhopaloids, are unique to them.
+Heteroneme and haploneme nematocysts serve penetrant and entangling functions, while rhopalonemes and desmonemes work by adhering to the surface of the prey.
 While recent descriptive studies have expanded and confirmed our understanding of this diversity, the evolutionary history of nematocyst type gain and loss in siphonophores remains unexplored.
 Thus, here we reconstruct the evolution of shifts, gains, and losses of nematocyst types, subtypes, and other major categorical traits that led to the extant diversity we see in siphonophore tentilla.
-In [@damian2019evolution], we found strong associations between piscivory and haploneme shape.
-These associations could have been produced by convergent changes in the adaptive optima of these characters.
-Here we set out to test this hypothesis using comparative model fitting methods.
-Analyzing the diversity of morphological states from a phylogenetic perspective allows us to identify the specific evolutionary processes that gave rise to it.
-Here we fit and compare a variety of macroevolutionary models to siphonophore tentilla morphology measurement data to identify instances of neutral divergence, stabilizing selection, changes in the speed of evolution, convergent evolution, and paedomorphosis (larval characters present in mature colonies).
-
-In [@damian2019evolution] we fitted discriminant analyses to identify characters that are predictive of feeding guild.
+
+In [@damian2019evolution] we fit discriminant analyses to identify characters that are predictive of feeding guild.
 These discriminant analyses can be used to generate hypotheses on the diets of ecologically understudied siphonophore species for which we have morphology data.
@@
 
-  Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle gastrovascular lumen with epidermal nematocysts [@totton1965synopsis].
+Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle (including its gastrovascular lumen), armed with epidermal nematocysts [@totton1965synopsis].
 The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2019evolution]) that tentilla are likely ancestral to all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.
-
-  In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
+In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2019evolution]) that tentilla were present in the most recent common ancestor of all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
 \@ref(figure7)).
 Some of these characters include the gain and loss of nematocyst types.
-Based on external information, we assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans [@mariscal1974nematocysts].
-Haplonemes first diverged into spherical isorhizas of 2 size classes in Cystonectae, and elongated anisorhizas of one size class in Codonophora.
+
+We assume that haploneme nematocysts are ancestrally present in siphonophore tentacles since they are present in the tentacles of many other hydrozoans [@mariscal1974nematocysts].
+Haplonemes are toxin-bearing open-ended nematocysts characterized by the lack of a shaft preceding the tubule.
+Two subtypes are found in siphonophores: the isorhizas of homogeneous tubule width, and the anisorhizas with a slight bulking of the tubule near the base.
+In Cystonectae, haplonemes diverged into spherical isorhizas of two size classes.
+There is one size of haplonemes in Codonophora, which consist of elongated anisorhizas.
 Haplonemes were likely lost in the tentacles of *Apolemia* but retained as spherical isorhizas in other *Apolemia* tissues [@siebert2013re].
-Similarly, while heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
+While heteronemes exist in other tissues of cystonects, they appear in the tentacles of codonophorans exclusively, as birhopaloids in *Apolemia*, stenoteles in eucladophoran physonects, and microbasic mastigophores in calycophorans.
+The four nematocyst types unique to siphonophores appear in two events in the phylogeny (Fig.
+\@ref(figure7)): birhopaloids arose in the stem to *Apolemia*, while rhopalonemes (acrophore and anacrophore) and homotrichous anisorhizas arose in the stem to Tendiculophora.
+
+  Nematocyst type gain and loss is also associated with prey capture functions.
+For example, the loss of desmonemes and rhopalonemes in piscivorous *Erenna*, retaining solely the penetrant (and venom injecting) anisothizas and stenoteles (two size classes) is reminiscent of the two size classes of penetrant isorhizas in the fish-specialist cystonects.
+Moreover, with the gain of anisorhizas, desmonemes, and rhopalonemes, the Tendiculophora gained versatility in entangling and adhesive functions of the cnidoband and terminal filament, which may have allowed their  feeding niches to diversify.
+Part of the effectiveness of calycophoran cnidobands at entangling crustaceans may be attributed to the subspecialization of their heteronemes.
+These shifted from the ancestral penetrating stenotele to the microbasic mastigophore (or eurytele in some species) with a long barmed shaft with many long spines.
+This heteroneme subtype could be better at interlocking with the setae of crustacean legs and antennae.
+
+  In those species that have a functional terminal filament, the desmonemes and rhopalonemes play a fundamental role in the first stages of adhesion of the prey.
+In many species, the tugs of the struggling prey on the terminal filament trigger the cnidoband discharge [@Mackie:1987uy and pers.
+obs.].The adhesive terminal filament has been lost several times in the Euphysonectae (*Frillagalma*, *Lychnagalma*-*Physophora*, *Erenna*, and some species of *Cordagalma*).
+In these species, we hypothesize that a different trigger mechanism is at play, possibly involving the prey actively biting or grasping the tentillum or lure.
 
@@
 In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The hypothesized phylogenetic placement of the rhizophysid *Bathyphysa conifera* branch was appended manually as a polytomy (dashed line).](~/tentilla_morph/Figures_final/figure7.jpg)
-
-*Evolution of tentillum and nematocyst characters* – One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM10).
-Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1.
+The hypothesized phylogenetic placement of the rhizophysid *Bathyphysa conifera*, for which no molecular data are yet available, was added manually (dashed line).](Figures_final/figure7.jpg)
+
+*Evolution of tentillum and nematocyst characters* – Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1.
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
-The majority (67%) of characters support BM models, indicating a history of neutral constant divergence.
+The majority (67%) of characters were best fitted by BM models, indicating a history of neutral constant divergence.
 We did not find any relationship between phylogenetic signal and BM model support.
+One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM10).
 Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
@@
 However, much of this correlation is due to the sharp contrast between Pyrostephidae and their sister group Tendiculophora.
-We searched for regime shifts in the evolution of haploneme nematocyst shape characters using a SURFACE [@ingram2013surface].
-SURFACE identified seven distinct OU regimes in the evolutionary history of haploneme length and width (Fig.
+We searched for regime shifts in the evolution of haploneme nematocyst shape characters using SURFACE [@ingram2013surface].
+SURFACE identified eight distinct OU regimes in the evolutionary history of haploneme length and width (Fig.
 \@ref(surface)A).
-The different regimes are located (1) in cystonects, (2) in pyrostephids, (7) in apolemiids, (9) in *Erenna*, (6) in *Stephanomia*, (3) in most of Tendiculophora, (5) in *Cordagalma ordinatum*, (4) in most diphyomorphs, and (8) in *Abylopsis tetragona* and *Diphyes dispar*.
+The different regimes are located (1) in cystonects, (2) in most of Tendiculophora, (3) in most diphyomorphs, (4) in *Cordagalma ordinatum*, (5) in *Stephanomia amphytridis*, (6) in pyrostephids, (7) in *Diphyes dispar* + *Abylopsis tetragona*, and (8) in *Erenna* spp.
 
@@
 
-![\label{figure9} Phylomorphospace of the simple continuous characters principal components, excluding ratios and composite characters.
+![\label{figure9} Phylomorphospace of the simple-measurement continuous characters principal components, excluding ratios and composite characters.
 A.
@@
 
-  In the non-phylogenetic PCA morphospace using only simple characters (Fig.
+  In the non-phylogenetic PCA morphospace using only characters derived from simple measurements (Fig.
 \@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
@@
 *Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
-To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology using one the linear discriminant analyses of principal components (DAPC) fitted in [@damian2019evolution].
+To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology using one of the linear discriminant analyses of principal components (DAPC) fitted in [@damian2019evolution].
 This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
@@
 We used the predictions from this discriminant function to generate hypotheses about the feeding guild of 45 species in the morphological dataset.
-This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata*is a fish specialist like *Erenna richardi*.
+This extrapolation predicts that two other *Apolemia* species are gelatinous prey specialists like *Apolemia rubriversa*, and predicts that *Erenna laciniata* is a fish specialist like *Erenna richardi*.
 When predicting soft- and hard-bodied prey specialization, the DAPC achieved 90.9% discrimination success, only marginally confounding hard-bodied specialists with generalists (SM13).
@@
 
-*On the evolution of tentilla morphology* -- *On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
 The rate covariance results are congruent with the evolutionary correlations we found (Fig.
-\ref(figure8)).
+\@ref(figure8)).
 In addition, these evolutionary modules point to hypothetical functional modules.
@@
 
-*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2019evolution]revealed the specific morphological changes in the prey capture apparatus associated with these changes.
+*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2019evolution] revealed the specific morphological changes in the prey capture apparatus associated with these changes.
 Copepod-specialized diets have evolved independently in *Cordagalma* and some calycophorans.
@@
 \@ref(figure9) & Fig.
-\ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+\@ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 
-*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research is to understand the links between predator capture tools and their diets so we can generate hypotheses about the diets of siphonophores based on morphological characteristics.
+*Generating hypotheses on siphonophore feeding ecology* – One motivation for our research is to understand the links between prey-capture tools and diets so we can generate hypotheses about the diets of predators based on morphological characteristics.
 Indeed, our discriminant analyses were able to distinguish between different siphonophore diets based on morphological characters alone.
@@
 
-surfaceALL(raw_matrix_NaZeroes[,6:7]) #haploneme shape
+surfaceALL(raw_matrix_NaZeroes[-which(rownames(raw_matrix_NaZeroes) %in% c("Apolemia lanosa", "Apolemia rubriversa")),6:7]) #haploneme shape
 surfaceALL(pcaphenos$ind$coord[,1:3] %>% as.data.frame()) #trait values PCA 1 2 without TF, excluding some species

### 2020-07-16 Organismal_paper/Organismal_manuscript_and_code.Rmd
changes after CWD comments

@@
 Since tentillum discharge occurs in synchrony across a broad morphological diversity, we evaluate how phenotypic integration is maintaining character correlations across evolutionary time.
-We found that the the tentillum morphospace has low dimensionality, we identified instances of heterochrony and morphological convergence, and generated hypotheses on the diets of understudied siphonophore species.
+We found that the tentillum morphospace has low dimensionality, we identified instances of heterochrony and morphological convergence, and generated hypotheses on the diets of understudied siphonophore species.
 Our findings indicate that siphonophore tentilla are phenotypically integrated structures with a complex evolutionary history leading to a phylogenetically structured diversity of forms which are predictive of kinematic performance and feeding habits.
@@
 Here we focus on one of such structures: the tentilla.
-Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts.
+Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts (Fig.
+\@ref(anatomy)).
 But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by rapidly unfolding the nematocyst battery to slap around the prey.
 This maximizes the surface area of contact between the nematocysts and the prey they fire upon.
-In addition, siphonophore tentilla present a remarkable diversity of morphologies, sizes, and nematocyst complements (Fig.
-\@ref(figure2)).
-Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it
+In addition, siphonophore tentilla present a remarkable diversity of morphologies (Fig.
+\@ref(figure2)), sizes, and nematocyst complements (Fig.
+\@ref(nematocysts)).
+Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it.
+
+![\label{anatomy} Siphonophore anatomy.
+A - Nanomia sp.
+siphonophore colony (photo by Catriona Munro).
+B, C - Illustration of a Nanomia colony, gastrozooid, and tentacle closeup (by Freya Goetz).
+D - Nanomia sp.
+Tentillum illustration and main parts.
+E - Differential interference contrast micrograph of the tentillum illustrated in D.
+Figure reproduced from Damian-Serrano et al.
+2020 with permission.](~/tentilla_morph/Organismal_paper/figures/anatomy.png)
+
+In [@damian2019evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
+The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
+The primary findings of that work were that generalists evolved from crustacean-specialist ancestors, and that feeding specializations were associated with distinct modes of evolution and character integration patterns.
+The work we present here is complementary to [@damian2019evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
 
 ![\label{figure2} Tentillum diversity.
-The illustrations delineate the pedicle (green), involucrum (blue), cnidoband (orange), elastic strands (pink), terminal structures (yellow).
-Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are depicted in red for some species.
+The illustrations delineate the pedicle, involucrum, cnidoband, elastic strands, terminal structures.
+Heteroneme nematocysts (stenoteles in C,E,F,G and mastigophores in H,I) are only depicted for some species.
 A - *Erenna laciniata*, 10x.
@@
 H - *Lilyopsis fluoracantha*, 20x.
-I - *Abylopsis tetragona*, 20x.](~/tentilla_morph/Figures_final/figure2.jpg)
-
-In [@damian2019evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
-The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
-The primary findings of that work were that generalists evolved from crustacean-specialist ancestors, and that feeding specializations were associated with distinct modes of evolution and character integration patterns.
-The work we present here is complementary to [@damian2019evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
+I - *Abylopsis tetragona*, 20x.](~/tentilla_morph/Organismal_paper/figures/diversity.png)
 
@@
 Mariscal ([@mariscal1974nematocysts]) reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
-Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles.
+Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles (Fig.
+\@ref(nematocysts)).
 Werner [@werner1965nesselkapseln] noted that there are nine types of nematocyst found in siphonophores, of which four, anacrophore rhopalonemes, acrophore rhopalonemes, homotrichous anisorhizas, and birhopaloids, are unique to them.
@@
 Thus, here we reconstruct the evolution of shifts, gains, and losses of nematocyst types, subtypes, and other major categorical traits that led to the extant diversity we see in siphonophore tentilla.
+
+![\label{nematocysts} Phylogenetic distribution of nematocyst types, subtypes, functions, and locations in the zooid across the major siphonophore clades.
+Illustrations reproduced with permission from Mapstone 2014.
+Undischarged capsules to the left, discharged to the right.
+Agalmatidae* here refers only to the genera *Agalma*, *Athorybia*, *Halistemma*, and *Nanomia*.
+](~/tentilla_morph/Organismal_paper/figures/nematocysts.png)
+
+Distantly related organisms that evolved to feed on similar resources often evolve similar adaptations [@winemiller2015functional].
+In [@damian2019evolution], we found strong associations between piscivory and haploneme shape across distantly related siphonophore lineages.
+These associations could have been produced by convergent changes in the adaptive optima of these characters.
+Here we set out to test this hypothesis using comparative model fitting methods.
+Analyzing the diversity of morphological states from a phylogenetic perspective allows us to identify the specific evolutionary processes that gave rise to it.
+Here we fit and compare a variety of macroevolutionary models to siphonophore tentilla morphology measurement data to identify instances of neutral divergence, stabilizing selection, changes in the speed of evolution, convergent evolution, and paedomorphosis (larval characters present in mature colonies).
 
@@
 In large, complex-shaped euphysonect tentilla, haplonemes were omitted for simplification.
-The hypothesized phylogenetic placement of the rhizophysid *Bathyphysa conifera*, for which no molecular data are yet available, was added manually (dashed line).](Figures_final/figure7.jpg)
+The hypothesized phylogenetic placement of the rhizophysid *Bathyphysa conifera*, for which no molecular data are yet available, was added manually (dashed line).](~/tentilla_morph/Figures_final/figure7.jpg)
 
@@
 The majority (67%) of characters were best fitted by BM models, indicating a history of neutral constant divergence.
-We did not find any relationship between phylogenetic signal and BM model support.
-One-third of the characters measured in [@damian2019evolution] support a non-phylogenetic generative model, indicating they are not phylogenetically conserved (SM10).
+We did not find any relationship between phylogenetic signal and specific model support, where characters with high and low phylogenetic signal were broadly distributed among the best fitted for each model.
+One-third of the characters measured in [@damian2019evolution] did not recover significant support for any of the phylogenetic models tested, indicating they are either not phylogenetically conserved, or they evolved under a complex evolutionary process not represented among the models tested (SM10).
 Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
@@
 
-*Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species other than Cystonects, *Apolemia*, and Pyrostephidae.
+*Evolution of nematocyst shape* – The greatest evolutionary change in haploneme nematocyst shape occurred in a single shift towards elongation in the stem of Tendiculophora, which contains the majority of described siphonophore species, *i.e.* all siphonophores other than Cystonects, *Apolemia*, and Pyrostephidae.
 There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig.
 \@ref(figure10)).
-Heteroneme evolution presents a less discrete evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal.
+Heteroneme evolution presents a less discrete evolutionary history.
+Tendiculophora evolved more elongate heteronemes along the stem, but the difference between theirs and other siphonophores’ is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal within this clade.
 In this clade, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape (Fig.
 \@ref(figure10)), which has remained fairly constant (elongation between 1.5 and 2.5).
+
 Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
@@
 This allows us to accommodate species with many missing characters (such as cystonects or apolemiids), and to account for common absences as morphological similarities.
-In this ordination, PC1 explains 47.45% of variation (aligned with cnidoband size) and PC2 explains 16.73% of variation (aligned with heteroneme volume and involucrum).
+In this ordination, PC1 (aligned with cnidoband size) explains 47.45% of variation and PC2 (aligned with heteroneme volume and involucrum length) explains 16.73% of variation .
 When superimposing feeding guilds onto the morphospace (Fig.
@@
 *Convergent evolution* – Convergence is a widespread evolutionary phenomenon where distantly related clades independently evolve similar phenotypes.
+When the dimensionality of the state space is small as it is in tentilla morphology, convergence is more likely given the same amount of evolutionary change.
 Using the package SURFACE [@ingram2013surface], we identified convergence in haploneme nematocyst shape and in morphospace position.
@@
 
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed measurements are available in the Dryad repository.
+*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed videos and measurements are available in the Dryad repository.
 While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
 For example, cnidoband length is strongly correlated with discharge speed (p value = 0.0002).
-This is probably the sole driver of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
-In addition, we observed that calycophoran haploneme tubules fire faster than those of euphysonects (T-test p value = 0.001).
-Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (T-test p value = 0.0012).
+This explains much  of the considerable difference between euphysonect and calycophoran tentilla discharge speeds (average discharge speeds: 225.0mm/s and 41.8mm/s respectively; t-test p value = 0.011), since the euphysonects have larger tentilla than the calycophorans among the species recorded.
+In addition, we observed that calycophoran haploneme tubules fire faster than those of euphysonects (t-test p value = 0.001).
+Haploneme nematocysts discharge 2.8x faster than heteroneme nematocysts (t-test p value = 0.0012).
 Finally, we observed that the stenoteles of the Euphysonectae discharge a helical filament that “drills” itself through the medium it penetrates as it everts.
@@
 
+\FloatBarrier
+
 ![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
@@
 
+\FloatBarrier
+
 ## Discussion {-}
 
-*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
@@
 In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos (pers.
-obs.) show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
 The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
@@
 
-The siphonophore tentillum morphospace has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
-This is consistent with strong phenotypic integration where genetic and developmental correlations are maintained by natural selection to preserve a complex function across the wide variety of morphologies present.
-Since most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle), structural correlations are expected.
-Similarly, correlations between the features of different nematocyst subtypes within a species are also expected given their common evolutionary and developmental origin [@bode1988control;@david2008evolution].
+Siphonophore tentilla are beautifully complex and highly diverse.
+Our analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
+This can be due to many causes including structural constraints, shared developmental programs (by homology or proximity), or natural selection on separate developmental programs to preserve an adaptive function.
+A familiar example of functionally-maintained correlations between distinct structures can be found in maple trees, where leaf size, twig width, and branch spacing evolve in correlation to ensure that hydraulic supply and demand are balanced (Corner’s rules) [@ackerly1998leaf].
+We believe some of the correlations we found are also maintained by natural selection to preserve a complex function across a wide variety of shapes and sizes.
+Most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle),  and different nematocyst subtypes share a common evolutionary and developmental origin [@bode1988control;@david2008evolution].
+In this sense, correlations within these modules are expected for reasons other than adaptive natural selection.
 However, we also found correlations between nematocyst and tentillum characters.
@@
 Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
-Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies.
+Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies, and they originate from evolutionarily distinct cell lineages.
 Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
+In order to adequately test these hypotheses, future work would need to study the genetic mechanisms underlying the development of tentilla from a comparative, evolutionary approach.
+Fortunately, the unique biology of siphonophore tentacles displays the full developmental sequence of tentilla along each tentacle, making siphonophores an ideal system for the comparative study of development.
 

### 2020-08-05 Organismal_paper/Organismal_manuscript_and_code.Rmd
changes to discussion early paragraphs

@@
 
-*On the evolution of tentilla morphology* -- The evolutionary rate covariance results in [@damian2019evolution] indicate that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
-This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-The rate covariance results are congruent with the evolutionary correlations we found (Fig.
-\@ref(figure8)).
-In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
-The clade Tendiculophora contains far more species than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-An increase in clade richness and ecological diversification can be triggered by a ‘key innovation’ [@simpson1955major].
-The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-A specific instance of this may have been the access to the abundant small crustacean prey such as copepods.
-The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands.
-
-Siphonophore tentilla are beautifully complex and highly diverse.
-Our analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
+*On the evolution of tentilla morphology* -- Siphonophore tentilla are beautifully complex and highly diverse.
+Our new analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
 This can be due to many causes including structural constraints, shared developmental programs (by homology or proximity), or natural selection on separate developmental programs to preserve an adaptive function.
-A familiar example of functionally-maintained correlations between distinct structures can be found in maple trees, where leaf size, twig width, and branch spacing evolve in correlation to ensure that hydraulic supply and demand are balanced (Corner’s rules) [@ackerly1998leaf].
-We believe some of the correlations we found are also maintained by natural selection to preserve a complex function across a wide variety of shapes and sizes.
 Most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle),  and different nematocyst subtypes share a common evolutionary and developmental origin [@bode1988control;@david2008evolution].
@@
 Fortunately, the unique biology of siphonophore tentacles displays the full developmental sequence of tentilla along each tentacle, making siphonophores an ideal system for the comparative study of development.
+
+The evolutionary rate covariance results in [@damian2019evolution] indicated that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
+The rate covariance results are congruent with the evolutionary correlations we found (Fig.
+\@ref(figure8)).
+In addition, these evolutionary modules point to hypothetical functional modules.
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
+The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
+A specific instance of this may have been the access to the abundant small crustacean prey such as copepods.
+The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands.
+Dietary diversification may be related to the far greater number of species in Tendicilophora than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
 

### 2020-08-07 Organismal_paper/Organismal_manuscript_and_code.Rmd
created post-review files for PNAs

@@
 Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopsis [@totton1965synopsis, @mapstone2014global].
+Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopses [@totton1965synopsis, @mapstone2014global].
 In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
@@
 
-*On the evolution of tentilla morphology* -- Siphonophore tentilla are beautifully complex and highly diverse.
+*On the evolution of tentilla morphology* -- The evolutionary history of siphonophore tentilla shows three major transition points which have structured the morphological diversity we see today.
+First, the earliest split between codonophorans and cystonects divides lineages with penetrating isorhizas from those which utilize heteronemes for prey capture.
+Second, the split between apolemiids and eucladophorans divided the simple-tentacled *Apolemia* from the lineage that evolved composite tentilla with heteronemes and haplonemes.
+Finally, the branch leading to tendiculophorans fostered innovations such as the elastic strands and the terminal filament nematocysts which produced the most complex tentilla structures and greatest morphological diversity we observe among siphonophores.
+
+ Siphonophore tentilla are beautifully complex and highly diverse.
 Our new analyses show, however, that the siphonophore tentillum morphospace actually has a fairly low extant dimensionality due to having an evolutionary history with many synchronous, correlated changes.
-This can be due to many causes including structural constraints, shared developmental programs (by homology or proximity), or natural selection on separate developmental programs to preserve an adaptive function.
-Most tentillum characters develop from a common bud (budding tentilla near the base of the tentacle),  and different nematocyst subtypes share a common evolutionary and developmental origin [@bode1988control;@david2008evolution].
-In this sense, correlations within these modules are expected for reasons other than adaptive natural selection.
-However, we also found correlations between nematocyst and tentillum characters.
-Siphonophore tentacle nematocysts (in their cnidocytes) are not produced nor matured in the developing tentillum.
-These cnidocytes are produced by dividing cnidoblasts in the basigaster (basal swelling of the gastrozooid).
-Once the cnidocytes have assembled the nematocyst, they migrate outward along the tentacle [@carre1972study] and position themselves in the tentillum according to their type and size [@skaer1988formation].
-Thus, the developmental programs that produce the observed nematocyst morphologies are spatially separated from those producing the tentillum morphologies, and they originate from evolutionarily distinct cell lineages.
+This can be due to many causes including structural constraints, developmental constraints, or selection that reduces the viable state space.
+Though siphonophore development has not been extensively studied, what is known suggests that developmental constraints alone could not explain the highly correlated evolutionary changes we observe.
+The nematocysts that arm the tentillum are developed in a completely separate region of the gastrozooid [@carre1972study] and then migrate and assemble within the tentillum later on [@skaer1988formation].
+This lack of proximity and physical independence of development between traits makes developmental constraints unlikely.
+Surprisingly, many of the strong correlations we find are between nematocyst and structural tentillum characters.
 Therefore, we hypothesize the genetic correlations and phenotypic integration between tentillum and nematocyst characters are maintained through natural selection on separate regulatory networks, out of the necessity to work together and meet the spatial, mechanical, and functional constraints of their prey capture behavior.
@@
 
-The evolutionary rate covariance results in [@damian2019evolution] indicated that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
+In [@damian2019evolution] we examined the covariance terms in the multivariate rate matrix for the evolution of tentillum and nematocyst characters.
+Building on this work, here we examine the correlations among the trait values while accounting for phylogenetic structure.
+The results for both analyses indicate that tentilla are not only phenotypically integrated (with widespread evolutionary correlations across structures) but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters [@wagner1996homologues].
 This may be indicative of the underlying genetic and developmental dependencies among closely homologous nematocyst types (such as desmonemes and rhopalonemes) and structures.
-The rate covariance results are congruent with the evolutionary correlations we found (Fig.
-\@ref(figure8)).
 In addition, these evolutionary modules point to hypothetical functional modules.
@@
 The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
+For example, the unique tentilla morphology of *Frillagalma* is predicted to render a generalist diet, or one of the undescribed deep-sea physonect species examined is predicted to be a fish specialist, which if true would show a third instance of independently evolved piscivory.
 While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.

### 2020-09-03 PNAS_PostReview/Manuscript_PostReview.Rmd
PNAS post review manuscript addressing ADS

--- 2020-04-07 Manuscript_supershort.Rmd
@@
 
-*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@bardi2007taxonomic;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
+*Feeding ecology* – We extracted categorical diet data for different siphonophore species from published sources, including seminal papers [@biggs1977field;@purcell1981dietary;@purcell1984functions;@Mackie:1987uy;@pugh1988two;@purcell1984predation;@andersen1981redescription], and ROV observation data [@choy2017deep;@hissmann2005situ] with the assistance of Elizabeth Hetherington and C.
 Anela Choy (data available in Dryad repository).

### 2020-09-30 PNAS_PostReview/Manuscript_PostReview.Rmd
PNAS post-review resubmission formatting and packaging

@@
 output:
-  bookdown::pdf_document2:
+  bookdown::word_document2:
     toc: FALSE
@@
 header-includes:
-  - \usepackage[left]{lineno}
-  - \linenumbers
   - \usepackage{setspace}
@@
 Instead of a dead-end, we found that siphonophore specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey types are linked to shifts in the morphology, mode of evolution, and genetic correlations of tentilla and their nematocysts.
+Our results show that siphonophore tentillum morphology has strong evolutionary associations with prey type, and suggest that shifts between prey types are linked to shifts in the morphology, mode of evolution, and evolutionary correlations of tentilla and their nematocysts.
 The evolutionary history of siphonophore specialization helps build a broader perspective on predatory niche diversification via morphological innovation and evolution.
@@
 However, in predators like siphonophores, armed with modular structures used exclusively for prey capture, this assumption is challenged.
-Our results show that siphonophores can evolve generalism and new prey-type specializations by modifying the morphological states, modes of evolution, and genetic correlations between the parts of their prey capture apparatus.
+Our results show that siphonophores can evolve generalism and new prey-type specializations by modifying the morphological states, modes of evolution, and evolutionary correlations between the parts of their prey capture apparatus.
 These findings demonstrate how studying open-ocean non-bilaterian predators can reveal novel patterns and mechanisms in the evolution of specialization.
@@
   Siphonophores (Cnidaria: Hydrozoa) are a clade of gelatinous, colonial organisms that swim in the open ocean, feeding on a wide diversity of prey (often fish, crustaceans, and jellyfish).
-Siphonophores carry modular structures that are exclusively used for prey capture: the tentilla (Fig.
+Siphonophore colonies have a modular body plan with different zooids specialized for different tasks.
+This modularity extends also within the feeding gastrozooids, which carry modular structures on the tentacle that are exclusively used for prey capture: the tentilla (Fig.
 \@ref(figure1)).
@@
 When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy].
-In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
+In addition, some species have elaborate fluorescent or bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].
 
@@
 F - Nematocyst types (illustration reproduced with permission from Mapstone 2014), hypothesized homologies, and locations in the tentillum.
-Undischarged to the left, discharged to the right.](Figures_final/figure1.jpg)
+Undischarged to the left, discharged to the right.](~/tentilla_morph/Figures_final/figure1.jpg)
 
@@
 
-  Specialization has been thought to be an evolutionary ‘dead-end’, meaning that specialized lineages are unlikely to evolve into generalists or to shift the resource for which they are specialized [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization].
-However, recent studies have found that interspecific competition can favor the evolution of generalists from specialists [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and specialist resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
+  Specialization in resource acquisition and use has often been presented as an evolutionary ‘dead-end’ [@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization; summarized by @futuyma1988evolution].
+The concept of a ‘dead-end’ can be problematic because it conflates very different macroevolutionary patterns.
+These patterns can pertain to the clade, such as higher extinction rates or lower diversification rates, or to the evolutionary lock-in of lineages to particular attributes.
+Here we exclusively focus on this last sense, in which feeding specialization can be considered a ‘dead-end’ if lineages that are feeding specialists do not give rise to feeding generalists or specialists on other prey.
+However, recent studies have found that ecological mechanisms such as interspecific competition can favor the evolution of generalists from specialists [@stireman2005evolution;@johnson2009competition;@nosil2002transition] and specialist resource switching [@hoberg2008macroevolutionary;@hardy2014specialization].
 In addition to studying relationships with morphology, we seek to identify what evolutionary transitions in trophic niche breadth are prevalent in these open-ocean tactile predators.
@@
   In this study, we present an extensive morphological characterization of tentilla and their nematocysts across a broad variety of shallow and deep-sea siphonophore species using modern imaging technologies, summarize the literature on siphonophore diets, expand the phylogenetic tree of siphonophores by combining ribosomal gene sequences from a broad range of taxa with a transcriptome-based backbone tree, and explore the evolutionary histories and correlations between diet, tentillum, and nematocyst characters.
-Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and genetic correlations in their prey capture apparatus.
+Our results suggest that siphonophores can evolve new specializations and generalism by modifying the phenotypes and evolutionary correlations in their prey capture apparatus.
 These findings show how studying elusive non-bilaterian predators can challenge traditional views on the evolution of predatory specialization.
@@
 Tips with purple squares indicate genus-level correspondence to taxa included in Munro *et al.* (2018).
-The main clades are labeled: with black bars for described taxonomic units, and grey bars for operational phylogenetic designations.](Figures_final/figure4.png){height=600px}
+The main clades are labeled: with black bars for described taxonomic units, and grey bars for operational phylogenetic designations.](~/tentilla_morph/Figures_final/figure4.png){height=600px}
 
@@
 Right - Grid showing the prey items consumed from which the feeding guild categories were derived.
-Diet data were obtained from the literature review, available in the Dryad repository.](Figures_final/figure5.jpg)
+Diet data were obtained from the literature review, available in the Dryad repository.](~/tentilla_morph/Figures_final/figure5.jpg)
 
@@
 ```{r tab1, echo=FALSE, out.width='100%'}
-knitr::include_graphics('Final_tables/table1.png')
+knitr::include_graphics('~/tentilla_morph/Final_tables/table1.png')
 ```
@@
 ```{r tab2, echo=FALSE, out.width='60%'}
-knitr::include_graphics('Final_tables/table2.png')
+knitr::include_graphics('~/tentilla_morph/Final_tables/table2.png')
 ```
@@
 
-Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization can be an irreversible dead-end due to the constraints posed by extreme phenotypic specialization.
+Several studies [@futuyma1988evolution;@siddall1993phylogeny;@hougen1994interactions; @robinson1996trade;@kelley1998specialization] have suggested that resource specialization can be an irreversible state due to the constraints posed by extreme phenotypic specialization.
 Our results show that this is not the case for siphonophores, where the prey type on which they specialize has shifted at least 5 times.
@@
 Our results are also consistent with analyses of lepidopterans [@hardy2014specialization], where specialized resource switching is the primary transition type while niche breadth remains fairly constant.
+These results show how an ancestor specialized for feeding on a particular prey can still give rise to multiple lineages and to novel feeding guilds, including generalists.
+For example, we find that, Eucladophora, a large clade of siphonophores that contains the majority of extant species and diverse feeding strategies, arose from a most recent common ancestor that was a specialist on large crustacean prey.
+Though ‘evolutionary dead-end’ is a problematic term that could apply to several evolutionary patterns, this result is inconsistent with multiple specific uses of this term.
+
 The evolutionary history of tentilla shows that siphonophores are an example of trophic niche diversification via morphological innovation and evolution, which allowed transitions between specialized trophic niches.
@@
 Additional dietary data could reveal transitions from generalists to specialists we were unable to detect for two reasons: some of the taxa in our dataset have a very limited number of feeding observations, which could lead to apparent specialization; and some of the taxa not included in our dataset could be undiscovered generalists.
-When interpreting these results, it is also important to remember that diet is also dependent on environmental prey availability.
+When interpreting these results, it is important to remember that diet is also dependent on environmental prey availability, which was not available in most of the sources we used (except Purcell 1981 & Purcell 1984).
+We integrated published dietary data collected using different methods bearing different inherent biases.
+Gut content inspections (used in the majority of our literature sources) are very effective at detecting small hard-bodied prey, but can fail to detect rapidly-digested soft-bodied prey.
+ROV observations can be biased towards large (often gelatinous) prey, and can easily oversee smaller prey items.
 In addition, selectivity differences across siphonophore species could be also driven by other phenotypes not accounted for in this study.
 Finally, further observations on behavior, digestion biochemistry, and toxin composition are necessary to assess their relative importance in determining diet.
+
+We hypothesize that siphonophores are able to evolve from specialization for one prey type to other states due to their prey-capture apparatus being extremely independent from the rest of the bodies in terms of location and function.
+We also hypothesize that the homogeneous midwater environment they live in favors the evolution of extreme morphological adaptations for prey capture.
+Testing these hypotheses will be interesting in its own right, and also give a better sense of how generalizable our results are beyond siphonophores.
+It is important to note that our hypotheses only apply to organisms with access to a broad-enough diversity of resources (such as prey, or hosts) on which to specialize, and only when said resources pose distinct challenges that require anatomical modifications.
+Otherwise, there would not be enough variation to detect these patterns in the first place.
 
@@
 While much of the feeding ecology literature focuses on how predatory generalists evolve into predatory specialists, in siphonophores we find predatory specialists can evolve into generalists, and that specialists on one prey type have directly evolved into specialists on other prey types.
-We find that the character states, evolutionary optima, and genetic correlations of many morphological characters have evolved following these ecological shifts.
+We find that the character states, evolutionary optima, and evolutionary correlations of many morphological characters have evolved following these ecological shifts.
 We find that the relationships between form and ecology hold across a large set of siphonophore taxa and characters.
@@
 We reconstructed ancestral states using ML (R phytools::anc.ML [@revell2012phytools]), and stochastic character mapping (R phytools::make.simmap) for categorical characters.
+When reconstructing the evolutionary history of feeding guilds, we fitted our SIMMAP model under the agnostic assumption that a generalist diet poses morphological challenges that are as distinct as each specialization is from each other.
+Thus, we do not impose any *a priori* constraints or weighting in the model for what state transition rates are permissible, letting the data determine the parameters.
 For more details on the data wrangling prior to these analyses, please see the Supplementary Methods.
@@
 
-Data will be available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.NNNN](http://dx.doi.org/10.5061/dryad.[NNNN])
+Data are available from the Dryad Digital Repository: [http://dx.doi.org/10.5061/dryad.p2ngf1vp2](http://dx.doi.org/10.5061/dryad.p2ngf1vp2)
 Supplementary Materials (Supplementary Methods and figures) are appended following this manuscript text, data available in [https://github.com/dunnlab/tentilla_morph/tree/master/Supplementary_materials](https://github.com/dunnlab/tentilla_morph/tree/master/Supplementary_materials)
@@
 
-This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.
+This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., OCE-1829805 to S.H.D.H., and OCE-1829812 to C.
 Anela Choy).

### 2020-12-03 Organismal_paper/Organismal_manuscript_and_code.Rmd
PNAS post review manuscript addressing ADS
quick pass for minor edits on the organismal manuscript

@@
 Figure reproduced from Damian-Serrano et al.
-2020 with permission.](~/tentilla_morph/Organismal_paper/figures/anatomy.png)
+2020 with permission.
+F.
+Action strip showing the behavior of tentilla during prey capture, illustrated by Riley Thompson.
+](~/tentilla_morph/Organismal_paper/figures/anatomy.png)
 
@@
 ![\label{nematocysts} Phylogenetic distribution of nematocyst types, subtypes, functions, and locations in the zooid across the major siphonophore clades.
-Illustrations reproduced with permission from Mapstone 2014.
+Illustrations reproduced with permission from Mapstone (2014).
 Undischarged capsules to the left, discharged to the right.
@@
 Analyzing the diversity of morphological states from a phylogenetic perspective allows us to identify the specific evolutionary processes that gave rise to it.
-Here we fit and compare a variety of macroevolutionary models to siphonophore tentilla morphology measurement data to identify instances of neutral divergence, stabilizing selection, changes in the speed of evolution, convergent evolution, and paedomorphosis (larval characters present in mature colonies).
+Here we fit and compare a variety of macroevolutionary models to siphonophore tentilla morphology measurement data to identify instances of neutral divergence, stabilizing selection, changes in the speed of evolution, and convergent evolution.
 
@@
 These discriminant analyses can be used to generate hypotheses on the diets of ecologically understudied siphonophore species for which we have morphology data.
-Here we present a Bayesian prediction for the feeding guild of 45 species using the morphological dataset in [@damian2019evolution].
+Here we present a Bayesian prediction for the feeding guild of 45 species uusing the discriminant functions and morphological dataset in [@damian2019evolution].
 As mentioned above, tentilla are far from being ornamental shapes and are in fact violently reactive weapons for prey capture [@Mackie:1987uy;@damian2019evolution].
@@
 We log transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
-When missing data was incorporated as inapplicable states, we removed those species with characters that could not be measured due to technical limitations.
+Inapplicable characters were recorded as NA states, and species with states that could not be measured due to technical limitations were removed before the analyses.
 We used the feeding guild categories detailed in [@damian2019evolution] with one modification: including all *Forskalia* spp.
-as generalists not only a single *Forskalia* species on the tree after a reinterpretation of the data in [@purcell1981dietary].
+as generalists instead of as a single *Forskalia* species on the tree after a reinterpretation of the data in [@purcell1981dietary].
 In order to characterize the evolutionary history of tentilla morphology, we fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
@@
 We used the lowest (best) score using a delta cutoff of 2 units to determine significance relative to the next simplest model (SM10).
-We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM11).
-We calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM10).
-To reconstruct the ancestral character states of nematocyst types and other categorical traits, we use stochastic character mapping (SIMMAP) using the package *phytools* [@revell2012phytools].
+We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM11), and calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM10).
+To reconstruct the ancestral character states of nematocyst types and other categorical traits, we used stochastic character mapping (SIMMAP) using the package *phytools* [@revell2012phytools].
 
 In order to examine the phenotypic integration in the tentillum, we explored the correlational structure among continuous characters and among their evolutionary histories using principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character dataset contains many gaps due to missing characters and inapplicable states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
+Since the character dataset contains gaps due to missing data and inapplicable character states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
 This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters (apolemiids and cystonects).
-In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package *rphylip* [@revell2014rphylip].
-We identified four hypothetical modules among the tentillum characters: (1) The tentillum scaffold module -- cnidoband length & width, nematocyst row number, pedicle & elastic strand width, tentacle width; (2) the heteroneme module -- heteroneme length & width, shafts length & width; (3) the haploneme module -- length and width; and (4) the terminal filament module -- desmoneme & rhopaloneme length & width.
-To test an quantify phenotypic integration between these multivariate modules, we used the phylogenetic phenotypic integration test in the package *geomorph* [@adams2016geomorph].
-
-When looking at the morphospace of species in different feeding guilds, we also used PCA on the complete tentacular character dataset transforming inapplicable states of absent characters to zeros to account for similarity based on character presence/absence.
+In addition, we obtained the correlations between the phylogenetic independent contrasts [@felsenstein1985phylogenies] using the package *rphylip* [@revell2014rphylip] accounting for intraspecific variation.
+Using these contrasts, we identified multivariate correlational modules among characters.
+To test and quantify phenotypic integration between these multivariate modules, we used the phylogenetic phenotypic integration test in the package *geomorph* [@adams2016geomorph].
+
+When comparing the morphospaces of species in different feeding guilds, we carried out a PCA on the complete character dataset while transforming inapplicable states of absent characters to zeros (i.e.
+cnidoband length = 0 when no cnidoband is present) to account for similarity based on character presence/absence.
 Using these principal components, we examined the occupation of the morphospace across species in different feeding guilds using a phylogenetic MANOVA with the package *geiger* [@harmon2007geiger] to assess the variation explained, and a morphological disparity test with the package *geomorph* [@adams2016geomorph] to assess differences in the extent occupied by each guild.
@@
 
-In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2019evolution] to predict the feeding guilds of species in the dataset for which there are no published feeding observations.
+In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2019evolution].
+We predict the feeding guilds of species in the dataset for which there are no published feeding observations using their morphological data as inputs, and presenting the predictive output in the form of posterior probabilities for each guild category.
 
@@
 Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
+We identified four hypothetical modules among the tentillum characters: (1) The tentillum scaffold module including cnidoband length & width, nematocyst row number, pedicle & elastic strand width, tentacle width; (2) the heteroneme module including heteroneme length & width, shafts length & width; (3) the haploneme module including length and width; and (4) the terminal filament module including desmoneme & rhopaloneme length & width.
 The phenotypic integration test showed significant integration signal between all modules, tentillum and haploneme modules sharing the greatest regression coefficient (SM12).
@@
 B.
-Phylogenetic relationships between the species points distributed in that same space.](~/tentilla_morph/Figures_final/figure9.jpg){height=600px}
+Phylogenetic relationships between the species points and reconstructed ancestors distributed in that same space.](~/tentilla_morph/Figures_final/figure9.jpg){height=600px}
 
@@
 This allows us to accommodate species with many missing characters (such as cystonects or apolemiids), and to account for common absences as morphological similarities.
-In this ordination, PC1 (aligned with cnidoband size) explains 47.45% of variation and PC2 (aligned with heteroneme volume and involucrum length) explains 16.73% of variation .
+In this ordination, PC1 (aligned with cnidoband size) explains 47.45% of variation and PC2 (aligned with heteroneme volume and involucrum length) explains 16.73% of variation.
 When superimposing feeding guilds onto the morphospace (Fig.
 \@ref(morphodiet)), we find that the morphospaces of each feeding guild are only slightly overlapping in PC1 and PC2.
-A phylogenetic MANOVA showed that feeding guilds explain 27.63% of variance across extant species (p value < 0.000001), and 20.97% of the variance in the tree species accounting for phylogeny, an outcome significantly distinct from the expectation under neutral evolution (p-value = 0.0196).
+A phylogenetic MANOVA showed that feeding guilds explain 27.63% of variance across extant species (p value < 0.000001), and 20.97% of the variance when accounting for phylogeny, an outcome significantly distinct from the expectation under neutral evolution (p-value = 0.0196).
 In addition, a morphological disparity analysis accounting for phylogenetic structure shows that the morphospace of fish specialists is significantly broader than that of generalists and other specialists.
@@
 Cell darkness indicates the posterior probability of belonging to each guild.
-Training data set transformed so inapplicable states are computed as zeroes.
-Species ordered and colored according to their predicted feeding guild.](~/tentilla_morph/Figures_final/figure6.jpg)
+The training dataset was transformed so inapplicable states are computed as zeroes.
+Species are sorted and colored according to their predicted feeding guild.](~/tentilla_morph/Figures_final/figure6.jpg)
 
@@
 In addition, these evolutionary modules point to hypothetical functional modules.
-For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high-speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband distally (towards the prey).
+For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while the involucrum may help direct the whiplash of the uncoiling cnidoband distally (towards the prey).
 The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
@@
 ## Acknowledgements {-}
-This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., and NSF-OCE 1829835 to C.W.D., S.H.D.H., and C.
+This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., NSF-OCE 1829835 to C.W.D., OCE-1829805 to S.H.D.H., and OCE-1829812 to C.
 Anela Choy).

### 2020-12-07 Organismal_paper/Organismal_manuscript_and_code.Rmd
cover letter

@@
 bibliography: org_manuscript.bib
-csl: pnas.csl
+csl: zoologica-scripta.csl
 site: "bookdown::bookdown_site"
@@
 
+## Keywords {-}
+
+Siphonophora, tentilla, nematocysts, character evolution
+
+\newpage
+
 ## Abstract {-}
@@
 
-## Keywords {-}
-
-Siphonophore, tentilla, nematocysts, character evolution
+\newpage
 
@@
 All character data and the phylogeny analyzed here were published in [@damian2019evolution].
+Details on the specimen collection, microscopy, and measurements can be found in the aforementioned publication.
+However, we included here the character definitions (SM14) and specimen list (SM15) in the Supporting Information.
 We log transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
@@
 was supported by a Fulbright Spain Graduate Studies Scholarship.
+
+\newpage
 

### 2020-12-07 Organismal_paper/Organismal_supplement.Rmd
cover letter

@@
 Values scaled by character.](~/tentilla_morph/Figures_final/figure3.jpg)
+
+![\label{appendix2} Character definitions. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/character_def.png){height=500px}
+
+![\label{specimens} Specimen catalog. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/slide_catalog_numbers.png){height=2000px}

### 2020-12-15 Organismal_paper/Organismal_manuscript_and_code.Rmd
preparing to submit to ZOoScripta - getting word docs for dissertation

@@
 Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopses [@totton1965synopsis, @mapstone2014global].
-In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2019evolution] have provided a macroevolutionary context to interpret this diversity.
+In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2020evolution] have provided a macroevolutionary context to interpret this diversity.
 With these assets in hand, we can now begin to study siphonophores from an orthogonal perspective, focusing on the diversity and evolutionary history of specific structures.
@@
 
-In [@damian2019evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
+In [@damian2020evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
 The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
 The primary findings of that work were that generalists evolved from crustacean-specialist ancestors, and that feeding specializations were associated with distinct modes of evolution and character integration patterns.
-The work we present here is complementary to [@damian2019evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
+The work we present here is complementary to [@damian2020evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
 
@@
 Distantly related organisms that evolved to feed on similar resources often evolve similar adaptations [@winemiller2015functional].
-In [@damian2019evolution], we found strong associations between piscivory and haploneme shape across distantly related siphonophore lineages.
+In [@damian2020evolution], we found strong associations between piscivory and haploneme shape across distantly related siphonophore lineages.
 These associations could have been produced by convergent changes in the adaptive optima of these characters.
@@
 
-In [@damian2019evolution] we fit discriminant analyses to identify characters that are predictive of feeding guild.
+In [@damian2020evolution] we fit discriminant analyses to identify characters that are predictive of feeding guild.
 These discriminant analyses can be used to generate hypotheses on the diets of ecologically understudied siphonophore species for which we have morphology data.
-Here we present a Bayesian prediction for the feeding guild of 45 species uusing the discriminant functions and morphological dataset in [@damian2019evolution].
-As mentioned above, tentilla are far from being ornamental shapes and are in fact violently reactive weapons for prey capture [@Mackie:1987uy;@damian2019evolution].
+Here we present a Bayesian prediction for the feeding guild of 45 species using the discriminant functions and morphological dataset in [@damian2020evolution].
+As mentioned above, tentilla are far from being ornamental shapes and are in fact violently reactive weapons for prey capture [@Mackie:1987uy;@damian2020evolution].
 While we now have detailed characterizations of tentilla morphologies across many species, the diversity of dynamic performances and their relationships to the undischarged morphologies have not been examined to date.
@@
 
-All character data and the phylogeny analyzed here were published in [@damian2019evolution].
+All character data and the phylogeny analyzed here were published in [@damian2020evolution].
 Details on the specimen collection, microscopy, and measurements can be found in the aforementioned publication.
-However, we included here the character definitions (SM14) and specimen list (SM15) in the Supporting Information.
-We log transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
+However, we included here the character definitions (SM15) and specimen list (SM16) in the Supporting Information.
+We log-transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
 Inapplicable characters were recorded as NA states, and species with states that could not be measured due to technical limitations were removed before the analyses.
-We used the feeding guild categories detailed in [@damian2019evolution] with one modification: including all *Forskalia* spp.
+We used the feeding guild categories detailed in [@damian2020evolution] with one modification: including all *Forskalia* spp.
 as generalists instead of as a single *Forskalia* species on the tree after a reinterpretation of the data in [@purcell1981dietary].
@@
 These models include a non-phylogenetic white-noise model (WN), a neutral divergence Brownian Motion model (BM), an early-burst decreasing rate model (EB), and an Ornstein-Uhlenbeck (OU) model with stabilizing selection around a fitted optimum trait value.
-In the same way as [@damian2019evolution] we then ordered the models by increasing parametric complexity (WN, BM, EB, OU), and compared their corrected Akaike Information Criterion (AICc) scores [@sugiura1978further].
+In the same way as [@damian2020evolution] we then ordered the models by increasing parametric complexity (WN, BM, EB, OU), and compared their corrected Akaike Information Criterion (AICc) scores [@sugiura1978further].
 We used the lowest (best) score using a delta cutoff of 2 units to determine significance relative to the next simplest model (SM10).
 We calculated model adequacy scores using the R package *arbutus* [@pennell2015model] (SM11), and calculated phylogenetic signals in each of the measured characters using Blomberg’s K [@blomberg2003testing] (SM10).
-To reconstruct the ancestral character states of nematocyst types and other categorical traits, we used stochastic character mapping (SIMMAP) using the package *phytools* [@revell2012phytools].
+To reconstruct the ancestral character states of nematocyst types and other categorical traits  (character matrix available in Supplementary Information), we used stochastic character mapping (SIMMAP) using the package *phytools* [@revell2012phytools].
 
 In order to examine the phenotypic integration in the tentillum, we explored the correlational structure among continuous characters and among their evolutionary histories using principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
-Since the character dataset contains gaps due to missing data and inapplicable character states, we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
+Since the character dataset contains gaps due to missing data and inapplicable character states (SM14), we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
 This was done by removing the terminal filament characters (which are only shared by a small subset of species), and then removing species which had inapplicable states for the remaining characters (apolemiids and cystonects).
@@
 
-In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2019evolution].
+In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2020evolution].
 We predict the feeding guilds of species in the dataset for which there are no published feeding observations using their morphological data as inputs, and presenting the predictive output in the form of posterior probabilities for each guild category.
@@
 We used the Phantom PCC software to analyze the footage.
-For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length ($\mu$m), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data available in the Dryad repository).
+For the 10 species recorded, we measured total cnidoband discharge time (ms), heteroneme filament length ($\mu$m), and discharge speeds (mm/s) for cnidoband, heteronemes, haplonemes, and heteroneme shafts when possible (data available in the Supplementary Information).
 
@@
 
-*Evolutionary history of tentillum morphology* – In [@damian2019evolution], we produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+*Evolutionary history of tentillum morphology* – In [@damian2020evolution], we produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
 This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
@@
 The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2019evolution]) that tentilla were present in the most recent common ancestor of all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
+In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2020evolution]) that tentilla were present in the most recent common ancestor of all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
 \@ref(figure7)).
@@
 
-  The clades defined in [@damian2019evolution] are characterized by unique evolutionary innovations in their tentilla.
+  The clades defined in [@damian2020evolution] are characterized by unique evolutionary innovations in their tentilla.
 The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*.
@@
 
-*Evolution of tentillum and nematocyst characters* – Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1.
+*Evolution of tentillum and nematocyst characters* – Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1 (SM10).
 Total nematocyst volume and cnidoband-to-heteroneme length ratio showed strongly conserved phylogenetic signals.
@@
 We did not find any relationship between phylogenetic signal and specific model support, where characters with high and low phylogenetic signal were broadly distributed among the best fitted for each model.
-One-third of the characters measured in [@damian2019evolution] did not recover significant support for any of the phylogenetic models tested, indicating they are either not phylogenetically conserved, or they evolved under a complex evolutionary process not represented among the models tested (SM10).
+One-third of the characters measured in [@damian2020evolution] did not recover significant support for any of the phylogenetic models tested, indicating they are either not phylogenetically conserved, or they evolved under a complex evolutionary process not represented among the models tested (SM10).
 Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
@@
 Similarly, among the correlations across extant species, 49.1% were >0.5 and only 1.5% were < -0.5.
-In addition, we found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients.
+In addition, we found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients (Fig.
+\@ref(surface)B).
 Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
@@
 
-![\label{figure9} Phylomorphospace of the simple-measurement continuous characters principal components, excluding ratios and composite characters.
+![\label{figure9} PCA of the simple-measurement continuous characters principal components, excluding ratios and composite characters.
 A.
@@
 Using the package SURFACE [@ingram2013surface], we identified convergence in haploneme nematocyst shape and in morphospace position.
-In [@damian2019evolution], we identified haploneme nematocyst shape as one of the traits associated with the convergent evolution of piscivory.
+In [@damian2020evolution], we identified haploneme nematocyst shape as one of the traits associated with the convergent evolution of piscivory.
 Here we find that indeed wider haploneme nematocysts have convergently evolved in the piscivore cytonects and *Erenna* spp.
@@
 
-*Functional morphology of tentillum and nematocyst discharge* –  Tentillum and nematocyst discharge high speed videos and measurements are available in the Dryad repository.
+*Functional morphology of tentillum and nematocyst discharge* – Tentillum and nematocyst discharge high speed videos and measurements are available in the Suplemmentary Information.
 While the sample sizes of these measurements were insufficient to draw reliable statistical results at a phylogenetic level, we did observe patterns that may be relevant to their functional morphology.
@@
 *Generating dietary hypotheses using tentillum morphology* – For many siphonophore species, no feeding observations have yet been published.
-To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores based on their known tentacle morphology using one of the linear discriminant analyses of principal components (DAPC) fitted in [@damian2019evolution].
+To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores (Fig.
+\@ref{figure6}) based on their known tentacle morphology using one of the linear discriminant analyses of principal components (DAPC) fitted in [@damian2020evolution].
 This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
@@
 
-In [@damian2019evolution] we examined the covariance terms in the multivariate rate matrix for the evolution of tentillum and nematocyst characters.
+In [@damian2020evolution] we examined the covariance terms in the multivariate rate matrix for the evolution of tentillum and nematocyst characters.
 Building on this work, here we examine the correlations among the trait values while accounting for phylogenetic structure.
@@
 
-*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2019evolution] revealed the specific morphological changes in the prey capture apparatus associated with these changes.
+*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2020evolution] revealed the specific morphological changes in the prey capture apparatus associated with these changes.
 Copepod-specialized diets have evolved independently in *Cordagalma* and some calycophorans.
@@
 The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-The DAPCs in [@damian2019evolution] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
+The DAPCs in [@damian2020evolution] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
 
@@
 ## Acknowledgements {-}
-This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., NSF-OCE 1829835 to C.W.D., OCE-1829805 to S.H.D.H., and OCE-1829812 to C.
+This work was supported by the Society of Systematic Biologists (Graduate Student Award to A.D.S.); the Yale Institute of Biospheric Studies (Doctoral Pilot Grant to A.D.S.); and the National Science Foundation (Waterman Award to C.W.D., OCE-1829835 to C.W.D., OCE-1829805 to S.H.D.H., and OCE-1829812 to C.
 Anela Choy).

### 2020-12-15 Supplement_forThesis.Rmd
preparing to submit to ZOoScripta - getting word docs for dissertation

--- 2020-04-07 Supplement_forPNAS.Rmd
@@
 These were selected to minimize the number of categories while keeping the most different types of prey separate.
+The gut content observations on *Forskalia* sp.
+were synonymized to an arbitrary *Forskalia* species on the tree (*F.
+tholoides*) for comparative analyses.
 
@@
 
-![\label{appendix2} Character definitions. ](Supplementary_materials/Online_appendices/PNGs/Appendix2.png){height=500px}
+![\label{appendix2} Character definitions. ](Supplementary_materials/Online_appendices/PNGs/character_def.png){height=500px}
 

### 2020-12-23 Organismal_paper/Organismal_manuscript_and_code.Rmd
repo uptodate

@@
 We found that the tentillum morphospace has low dimensionality, we identified instances of heterochrony and morphological convergence, and generated hypotheses on the diets of understudied siphonophore species.
-Our findings indicate that siphonophore tentilla are phenotypically integrated structures with a complex evolutionary history leading to a phylogenetically structured diversity of forms which are predictive of kinematic performance and feeding habits.
+Our findings indicate that siphonophore tentilla are phenotypically integrated structures with a complex evolutionary history leading to a phylogenetically-structured diversity of forms which are predictive of kinematic performance and feeding habits.
 
@@
 Siphonophores have fascinated zoologists for centuries for their extremely subspecialized colonial organization and integration.
-Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopses [@totton1965synopsis, @mapstone2014global].
+Today we have a comprehensive taxonomic coverage on the morphological diversity of this group due to the extensive work of siphonophore taxonomists in the past few decades  [@pugh1983benthic;@pugh1986new;@pugh1988two;@pugh2001review;@hissmann2005situ;@haddock2005re;@dunn2005marrus;@bardi2007taxonomic;@pugh2010three;@pugh2014review], which has been elegantly synthesized in detailed synopses [@totton1965synopsis;@mapstone2014global].
 In addition, recent advances in phylogenetic analyses of siphonophores [@munro2018improved;@damian2020evolution] have provided a macroevolutionary context to interpret this diversity.
@@
 Like many cnidarians, siphonophore tentacles bear side branches (tentilla) with nematocysts (Fig.
-\@ref(anatomy)).
-But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by rapidly unfolding the nematocyst battery to slap around the prey.
+\@ref(anatomy)C-E).
+But unlike other cnidarians, most siphonophore tentilla are dynamic structures that react to prey encounters by rapidly unfolding the nematocyst battery to slap around the prey (Fig.
+\@ref(anatomy)F).
 This maximizes the surface area of contact between the nematocysts and the prey they fire upon.
@@
 Our overarching aim is to organize all this phenotypic diversity in a phylogenetic context, and identify the evolutionary processes that generated it.
+
+\FloatBarrier
 
@@
 Action strip showing the behavior of tentilla during prey capture, illustrated by Riley Thompson.
-](~/tentilla_morph/Organismal_paper/figures/anatomy.png)
-
-In [@damian2020evolution], we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
+](~/tentilla_morph/Organismal_paper/figures/anatomy-01.png)
+
+\FloatBarrier
+
+In @damian2020evolution, we collected the most extensive morphological dataset on siphonophore tentilla and nematocysts using state-of-the-art microscopy techniques, and expanded the taxon sampling of the phylogeny to disentangle the evolutionary history.
 The analyses we carried out led to novel, generalizable insights into the evolution of predatory specialization.
 The primary findings of that work were that generalists evolved from crustacean-specialist ancestors, and that feeding specializations were associated with distinct modes of evolution and character integration patterns.
-The work we present here is complementary to [@damian2020evolution], showcasing a far more detailed account on the evolutionary history of tentilla morphology.
+The work we present here is complementary to @damian2020evolution, showcasing a far more detailed account on the evolutionary history of tentilla morphology.
+
+\FloatBarrier
 
@@
 
+\FloatBarrier
+
 Nematocysts are unique biological weapons for defense and prey capture exclusive to the phylum Cnidaria.
-Mariscal ([@mariscal1974nematocysts]) reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
+@mariscal1974nematocysts reported that hydrozoans have the largest diversity of nematocyst types among cnidarians.
 Among them, siphonophores present the greatest variety of types [@mapstone2014global], and vary widely across taxa in which and how many types they carry on their tentacles (Fig.
 \@ref(nematocysts)).
-Werner [@werner1965nesselkapseln] noted that there are nine types of nematocyst found in siphonophores, of which four, anacrophore rhopalonemes, acrophore rhopalonemes, homotrichous anisorhizas, and birhopaloids, are unique to them.
+@werner1965nesselkapseln noted that there are nine types of nematocyst found in siphonophores, of which four, anacrophore rhopalonemes, acrophore rhopalonemes, homotrichous anisorhizas, and birhopaloids, are unique to them.
 Heteroneme and haploneme nematocysts serve penetrant and entangling functions, while rhopalonemes and desmonemes work by adhering to the surface of the prey.
@@
 Thus, here we reconstruct the evolution of shifts, gains, and losses of nematocyst types, subtypes, and other major categorical traits that led to the extant diversity we see in siphonophore tentilla.
+
+\FloatBarrier
 
@@
 
+\FloatBarrier
+
 Distantly related organisms that evolved to feed on similar resources often evolve similar adaptations [@winemiller2015functional].
-In [@damian2020evolution], we found strong associations between piscivory and haploneme shape across distantly related siphonophore lineages.
+In @damian2020evolution, we found strong associations between piscivory and haploneme shape across distantly related siphonophore lineages.
 These associations could have been produced by convergent changes in the adaptive optima of these characters.
@@
 
-In [@damian2020evolution] we fit discriminant analyses to identify characters that are predictive of feeding guild.
+In @damian2020evolution we fit discriminant analyses to identify characters that are predictive of feeding guild.
 These discriminant analyses can be used to generate hypotheses on the diets of ecologically understudied siphonophore species for which we have morphology data.
-Here we present a Bayesian prediction for the feeding guild of 45 species using the discriminant functions and morphological dataset in [@damian2020evolution].
+Here we present a Bayesian prediction for the feeding guild of 45 species using the discriminant functions and morphological dataset in @damian2020evolution.
 As mentioned above, tentilla are far from being ornamental shapes and are in fact violently reactive weapons for prey capture [@Mackie:1987uy;@damian2020evolution].
@@
 
-All character data and the phylogeny analyzed here were published in [@damian2020evolution].
+All character data and the phylogeny analyzed here were published in @damian2020evolution.
 Details on the specimen collection, microscopy, and measurements can be found in the aforementioned publication.
-However, we included here the character definitions (SM15) and specimen list (SM16) in the Supporting Information.
+To facilitate access, we re-included here the character definitions (SM15) and specimen list (SM16) in the Supporting Information.
 We log-transformed all the continuous characters that did not pass Shapiro-Wilks normality tests, and used the ultrametric constrained Bayesian time tree in all comparative analyses.
 Inapplicable characters were recorded as NA states, and species with states that could not be measured due to technical limitations were removed before the analyses.
-We used the feeding guild categories detailed in [@damian2020evolution] with one modification: including all *Forskalia* spp.
-as generalists instead of as a single *Forskalia* species on the tree after a reinterpretation of the data in [@purcell1981dietary].
+We used the feeding guild categories detailed in @damian2020evolution with one modification: including all *Forskalia* spp.
+as generalists instead of as a single *Forskalia* species on the tree after a reinterpretation of the data in @purcell1981dietary.
 In order to characterize the evolutionary history of tentilla morphology, we fitted different models generating the observed data distribution given the phylogeny for each continuous character using the function fitContinuous in the R package *geiger* [@harmon2007geiger].
 These models include a non-phylogenetic white-noise model (WN), a neutral divergence Brownian Motion model (BM), an early-burst decreasing rate model (EB), and an Ornstein-Uhlenbeck (OU) model with stabilizing selection around a fitted optimum trait value.
-In the same way as [@damian2020evolution] we then ordered the models by increasing parametric complexity (WN, BM, EB, OU), and compared their corrected Akaike Information Criterion (AICc) scores [@sugiura1978further].
+In the same way as @damian2020evolution, we then ordered the models by increasing parametric complexity (WN, BM, EB, OU), and compared their corrected Akaike Information Criterion (AICc) scores [@sugiura1978further].
 We used the lowest (best) score using a delta cutoff of 2 units to determine significance relative to the next simplest model (SM10).
@@
 
-In order to examine the phenotypic integration in the tentillum, we explored the correlational structure among continuous characters and among their evolutionary histories using principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
+In order to examine the degree of phenotypic integration within the tentillum, we explored the correlational structure among continuous characters and among their evolutionary histories using principal component analysis (PCA) and phylogenetic PCA [@revell2012phytools].
 Since the character dataset contains gaps due to missing data and inapplicable character states (SM14), we carried out these analyses on a subset of species and characters that allowed for the most complete dataset.
@@
 
-In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in [@damian2020evolution].
+In order to generate hypotheses on the diets of siphonophores using tentilla morphology, we used the discriminant analyses of principal components (DAPC) [@jombart2010discriminant] trained in @damian2020evolution.
 We predict the feeding guilds of species in the dataset for which there are no published feeding observations using their morphological data as inputs, and presenting the predictive output in the form of posterior probabilities for each guild category.
@@
 
-*Evolutionary history of tentillum morphology* – In [@damian2020evolution], we produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
+*Evolutionary history of tentillum morphology* – In @damian2020evolution, we produced the most speciose siphonophore molecular phylogeny to date, while incorporating the most recent findings in siphonophore deep node relationships.
 This phylogeny revealed for the first time that the genus *Erenna* is the sister to *Stephanomia amphytridis*.
@@
 Siphonophore tentilla are defined as lateral, monostichous evaginations of the tentacle (including its gastrovascular lumen), armed with epidermal nematocysts [@totton1965synopsis].
-The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but [@bardi2007taxonomic] and our observations [@munro2018improved], confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
-In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with [@munro2018improved] and [@damian2020evolution]) that tentilla were present in the most recent common ancestor of all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts using stochastic character mapping (SM1-9) and summarized in (Fig.
+The buttons on *Physalia* tentacles were not traditionally regarded as tentilla, but @bardi2007taxonomic, @munro2018improved, and our own observations confirm that the buttons contain evaginations of the gastrovascular lumen, thus satisfying all the criteria for the definition.
+In this light, and given that most Cystonectae bear conspicuous tentilla, we conclude (in agreement with @munro2018improved and @damian2020evolution) that tentilla were present in the most recent common ancestor of all siphonophores, and secondarily lost twice, once in *Apolemia* and again in *Bathyphysa conifera*.
+In order to gain a broad perspective on the evolutionary history of tentilla, we reconstructed the phylogenetic positions of the main categorical character shifts (such as gains and losses of nematocyst types) using stochastic character mapping (SM1-9) and manual reconstructions.
+This phylogenetic roadmap of evolutionary novelties is summarized in (Fig.
 \@ref(figure7)).
-Some of these characters include the gain and loss of nematocyst types.
 
@@
 Part of the effectiveness of calycophoran cnidobands at entangling crustaceans may be attributed to the subspecialization of their heteronemes.
-These shifted from the ancestral penetrating stenotele to the microbasic mastigophore (or eurytele in some species) with a long barmed shaft with many long spines.
+These shifted from the ancestral penetrating stenotele to the microbasic mastigophore (or eurytele in some species) with a long barbed shaft armed with many long spines.
 This heteroneme subtype could be better at interlocking with the setae of crustacean legs and antennae.
@@
 In many species, the tugs of the struggling prey on the terminal filament trigger the cnidoband discharge [@Mackie:1987uy and pers.
-obs.].The adhesive terminal filament has been lost several times in the Euphysonectae (*Frillagalma*, *Lychnagalma*-*Physophora*, *Erenna*, and some species of *Cordagalma*).
+obs.].
+The adhesive terminal filament has been lost several times in the Euphysonectae (*Frillagalma*, *Lychnagalma*-*Physophora*, *Erenna*, and some species of *Cordagalma*).
 In these species, we hypothesize that a different trigger mechanism is at play, possibly involving the prey actively biting or grasping the tentillum or lure.
 
-  The clades defined in [@damian2020evolution] are characterized by unique evolutionary innovations in their tentilla.
+\FloatBarrier
+
+  The clades defined in @damian2020evolution are characterized by unique evolutionary innovations in their tentilla.
 The clade Eucladophora (containing Pyrostephidae, Euphysonectae, and Calycophorae) encompasses all of the extant Siphonophore species (178 of 186) except Cystonects and *Apolemia*.
@@
 
+\FloatBarrier
+
 ![\label{figure7} Siphonophore cladogram with the main categorical character gains (green) and losses (red) mapped.
@@
 
+\FloatBarrier
+
 *Evolution of tentillum and nematocyst characters* – Most (74%) characters present a significant phylogenetic signal, yet only total nematocyst volume, haploneme length, and heteroneme-to-cnidoband length ratio had a phylogenetic signal with K larger than 1 (SM10).
@@
 We did not find any relationship between phylogenetic signal and specific model support, where characters with high and low phylogenetic signal were broadly distributed among the best fitted for each model.
-One-third of the characters measured in [@damian2020evolution] did not recover significant support for any of the phylogenetic models tested, indicating they are either not phylogenetically conserved, or they evolved under a complex evolutionary process not represented among the models tested (SM10).
+One-third of the characters measured in @damian2020evolution did not recover significant support for any of the phylogenetic models tested, indicating they are either not phylogenetically conserved, or they evolved under a complex evolutionary process not represented among the models tested (SM10).
 Haploneme nematocyst length was the only character with support for an EB model of decreasing rate of evolution with time.
@@
 
+*Phenotypic integration of the tentillum* – Phenotypically integrated structures maintain evolutionary correlations between its constituent characters.
+Of the phylogenetic correlations among tentillum and nematocyst characters examined here (Fig.
+\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
+\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
+Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
+Similarly, among the correlations across extant species, 49.1% were >0.5 and only 1.5% were < -0.5.
+In addition, we found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients (Fig.
+\@ref(figure8)B).
+Just 4% of character pairs have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
+These disparities could be explained by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology, as suggested by @uyeda2018rethinking) is considered.
+However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of -0.54).
+Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
+We identified four hypothetical modules among the tentillum characters: (1) The tentillum scaffold module including cnidoband length & width, nematocyst row number, pedicle & elastic strand width, tentacle width; (2) the heteroneme module including heteroneme length & width, shafts length & width; (3) the haploneme module including length and width; and (4) the terminal filament module including desmoneme & rhopaloneme length & width.
+The phenotypic integration test showed significant integration signal between all modules, tentillum and haploneme modules sharing the greatest regression coefficient (SM12).
+
+\FloatBarrier
+
 ![\label{figure8} A.
@@
 
-Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
-However, much of this correlation is due to the sharp contrast between Pyrostephidae and their sister group Tendiculophora.
-We searched for regime shifts in the evolution of haploneme nematocyst shape characters using SURFACE [@ingram2013surface].
-SURFACE identified eight distinct OU regimes in the evolutionary history of haploneme length and width (Fig.
-\@ref(surface)A).
-The different regimes are located (1) in cystonects, (2) in most of Tendiculophora, (3) in most diphyomorphs, (4) in *Cordagalma ordinatum*, (5) in *Stephanomia amphytridis*, (6) in pyrostephids, (7) in *Diphyes dispar* + *Abylopsis tetragona*, and (8) in *Erenna* spp.
+\FloatBarrier
 
@@
 
-*Phenotypic integration of the tentillum* – Phenotypically integrated structures maintain evolutionary correlations between its constituent characters.
-Of the phylogenetic correlations (Fig.
-\@ref(figure8)a, lower triangle), 81.3% were positive and 18.7% were negative, while of the ordinary correlations (Fig.
-\@ref(figure8)a, upper triangle) 74.6% were positive and 25.4% were negative.
-Half (49.9%) of phylogenetic correlations were >0.5, while only 3.6% are < -0.5.
-Similarly, among the correlations across extant species, 49.1% were >0.5 and only 1.5% were < -0.5.
-In addition, we found that 13.9% of character pairs had opposing phylogenetic and ordinary correlation coefficients (Fig.
-\@ref(surface)B).
-Just 4% have negative phylogenetic and positive ordinary correlations (such as rhopaloneme elongation ~ heteroneme-to-cnidoband length ratio and haploneme elongation, or haploneme elongation ~ heteroneme number), and only 9.9% of character pairs had positive phylogenetic correlation yet negative ordinary correlation (such as heteroneme elongation ~ cnidoband convolution and involucrum length, or rhopaloneme elongation with cnidoband length).
-These disparities could be explained by Simpson’s paradox [@blyth1972simpson]: the reversal of the sign of a relationship when a third variable (or a phylogenetic topology [@uyeda2018rethinking]) is considered.
-However, no character pair had correlation coefficient differences larger than 0.64 between ordinary and phylogenetic correlations (heteroneme shaft extension ~ rhopaloneme elongation has a Pearson’s correlation of 0.10 and a phylogenetic correlation of -0.54).
-Rhopaloneme elongation shows the most incongruencies between phylogenetic and ordinary correlations with other characters.
-We identified four hypothetical modules among the tentillum characters: (1) The tentillum scaffold module including cnidoband length & width, nematocyst row number, pedicle & elastic strand width, tentacle width; (2) the heteroneme module including heteroneme length & width, shafts length & width; (3) the haploneme module including length and width; and (4) the terminal filament module including desmoneme & rhopaloneme length & width.
-The phenotypic integration test showed significant integration signal between all modules, tentillum and haploneme modules sharing the greatest regression coefficient (SM12).
+\FloatBarrier
+
+Haploneme and heteroneme shape share 21% of their variance across extant values, and 53% of the variance in their shifts along the branches of the phylogeny.
+However, much of this correlation is due to the sharp contrast between Pyrostephidae and their sister group Tendiculophora.
+We searched for regime shifts in the evolution of haploneme nematocyst shape characters using SURFACE [@ingram2013surface].
+SURFACE identified eight distinct OU regimes in the evolutionary history of haploneme length and width (Fig.
+\@ref(surface)A).
+The different regimes are located (1) in cystonects, (2) in most of Tendiculophora, (3) in most diphyomorphs, (4) in *Cordagalma ordinatum*, (5) in *Stephanomia amphytridis*, (6) in pyrostephids, (7) in *Diphyes dispar* + *Abylopsis tetragona*, and (8) in *Erenna* spp.
+
+\FloatBarrier
+
+![\label{surface} SURFACE plots showing convergent evolutionary regimes modelled under OU for (A) haploneme nematocyst length & width, and (B) for PC1 & PC2 of all continuous characters with the exception of terminal filament nematocysts, and removing taxa with inapplicable character states.
+Node numbers on the tree label different regimes, regimes of the same color are identified as convergent.
+Small circles on the scatterplots indicate species values, large circles indicate the average position of the OU optima (*theta*) for a given combination of convergent regimes.](~/tentilla_morph/Organismal_paper/figures/SURFACE-01.jpg){height=700px}
+
+\FloatBarrier
+
+  In the non-phylogenetic PCA morphospace using only characters derived from simple measurements (Fig.
+\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
+In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
 
@@
 
-  In the non-phylogenetic PCA morphospace using only characters derived from simple measurements (Fig.
-\@ref(figure9)), PC1 (aligned with tentillum and tentacle size) explained 69.3% of the variation in the tentillum morphospace, whereas PC2 (aligned with heteroneme length, heteroneme number, and haploneme arrangement) explained 13.5%.
-In a phylogenetic PCA, 63% of the evolutionary variation in the morphospace is explained by PC1 (aligned with shifts in tentillum size), while 18% is explained by PC2 (aligned with shifts in heteroneme number and involucrum length).
-
-![\label{morphodiet}Phylomorphospace showing PC1 and PC2 from a PCA of continuous morphological characters with inapplicable states transformed to zeroes, overlapped with polygons conservatively defining the space occupied by each feeding guild.
-Lines between species coordinates show the phylogenetic relationships between them.
-](~/tentilla_morph/Organismal_paper/figures/morphospace_diets_full.png){height=600px}
+\FloatBarrier
 
@@
 
-![\label{surface} SURFACE plots showing convergent evolutionary regimes modelled under OU for (A) haploneme nematocyst length & width, and (B) for PC1 & 2 of all continuous characters with the exception of terminal filament nematocysts, and removing taxa with inapplicable character states.
-Node numbers on the tree label different regimes, regimes of the same color are identified as convergent.
-Small circles on the scatterplots indicate species values, large circles indicate the average position of the OU optima (*theta*) for a given combination of convergent regimes.](~/tentilla_morph/Organismal_paper/figures/SURFACE-01.jpg){height=700px}
+\FloatBarrier
+
+![\label{morphodiet}Phylomorphospace showing PC1 and PC2 from a PCA of continuous morphological characters with inapplicable states transformed to zeroes, overlapped with polygons conservatively defining the space occupied by each feeding guild.
+Lines between species coordinates show the phylogenetic relationships between them.
+](~/tentilla_morph/Organismal_paper/figures/morphospace_diets_full.png){height=600px}
+
+\FloatBarrier
 
@@
 Using the package SURFACE [@ingram2013surface], we identified convergence in haploneme nematocyst shape and in morphospace position.
-In [@damian2020evolution], we identified haploneme nematocyst shape as one of the traits associated with the convergent evolution of piscivory.
+In @damian2020evolution, we identified haploneme nematocyst shape as one of the traits associated with the convergent evolution of piscivory.
 Here we find that indeed wider haploneme nematocysts have convergently evolved in the piscivore cytonects and *Erenna* spp.
@@
 To help bridge this gap of knowledge, we generated hypotheses about the diets of these understudied siphonophores (Fig.
-\@ref{figure6}) based on their known tentacle morphology using one of the linear discriminant analyses of principal components (DAPC) fitted in [@damian2020evolution].
+\@ref(figure6)) based on their known tentacle morphology using one of the linear discriminant analyses of principal components (DAPC) fitted in @damian2020evolution.
 This provides concrete predictions to be tested in future work and helps extrapolate our findings to many poorly known species that are extremely difficult to collect and observe.
@@
 
-![\label{figure6} Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
+![\label{figure6}Hypothetical feeding guilds for siphonophore species predicted by a 6 PCA DAPC.
 Cell darkness indicates the posterior probability of belonging to each guild.
@@
 
-In [@damian2020evolution] we examined the covariance terms in the multivariate rate matrix for the evolution of tentillum and nematocyst characters.
+In @damian2020evolution we examined the covariance terms in the multivariate rate matrix for the evolution of tentillum and nematocyst characters.
 Building on this work, here we examine the correlations among the trait values while accounting for phylogenetic structure.
@@
 The evolutionary innovation of the Tendiculophora tentilla with shooting cnidobands and modular regions may have facilitated further dietary diversification.
-A specific instance of this may have been the access to the abundant small crustacean prey such as copepods.
+A specific instance of this dietary diversification may have been the access to the abundant small crustacean prey such as copepods.
 The rapid darting escape response of copepods may preclude their capture in siphonophores without shooting cnidobands.
-Dietary diversification may be related to the far greater number of species in Tendicilophora than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
-
-*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, [@damian2020evolution] revealed the specific morphological changes in the prey capture apparatus associated with these changes.
+The trophic opportunities unlocked by these morphological novelties may be responsible for the far greater number of species in Tendicilophora than its relatives Cystonectae, Apolemiidae, and Pyrostephidae.
+
+*Heterochrony and convergence in the evolution of tentilla with diet* - In addition to identifying shifts in prey type, @damian2020evolution revealed the specific morphological changes in the prey capture apparatus associated with these shifts.
 Copepod-specialized diets have evolved independently in *Cordagalma* and some calycophorans.
@@
 Our work identifies yet another novel example of convergent evolution.
-The region of the tentillum morphospace (Fig.
-\@ref(figure9) & Fig.
-\@ref(surface)B) occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi*.
+The region of the tentillum morphospace occupied by calycophorans was independently (and more recently) occupied by the physonect *Frillagalma vityazi* (Fig.
+\@ref(surface)B).
 Like calycophorans, *Frillagalma* tentilla have small C-shaped cnidobands with a few rows of anisorhizas.
@@
 The diet of *Frillagalma vityazi* is unknown, but this morphological convergence suggests that they evolved to capture similar kinds of prey.
-The DAPCs in [@damian2020evolution] predict that *Frillagalma* has a generalist niche with both soft and hard-bodied prey, including copepods.
+However, our DAPCs predict that *Frillagalma* has a generalist niche (Fig.
+\@ref(figure6)) with both soft and hard-bodied prey (SM13).
 
@@
 \@ref(surface)A).
-Purcell [@purcell1984functions] showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
+@purcell1984functions showed that haplonemes have a penetrating function as isorhizas in cystonects and an adhesive function as anisorhizas in Tendiculophora.
 It is no coincidence that the two clades that have converged to feed primarily on fish have also converged morphologically toward more compact haplonemes.
 Isorhizas in cystonects are known to penetrate the skin of fish during prey capture, and to deliver the toxins that aid in paralysis and digestion [@hessinger1988nematocyst].
-*Erenna*’s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review] (and pers.
-obs.), a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
+*Erenna*’s anisorhizas are also able to penetrate human skin and deliver a painful sting [@pugh2001review], a common feature of piscivorous cnidarians like the Portuguese man-o-war or box jellies.
 
@@
 We hypothesize this may be a Tendiculophora lineage-specific adaptation to packing more nematocysts into a limited tentillum space, as suggested by [@skaer1988formation].
-Thomason [@thomason1988allometry] hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
+@thomason1988allometry hypothesized that smaller, more spherical nematocysts, with a lower surface area to volume ratio, are more efficient in osmotic-driven discharge and thus have more power for skin penetration.
 The elongated haplonemes of crustacean-eating Tendiculophora have never been observed penetrating their crustacean prey [@purcell1984functions], and are hypothesized to entangle the prey through adhesion of the abundant spines to the exoskeletal surfaces and appendages.
@@
 The models produced by these analyses generated testable predictions about the diets of many species for which we only have morphological data of their tentacles.
-For example, the unique tentilla morphology of *Frillagalma* is predicted to render a generalist diet, or one of the undescribed deep-sea physonect species examined is predicted to be a fish specialist, which if true would show a third instance of independently evolved piscivory.
+For example, the unique tentilla morphology of *Frillagalma* is predicted to render a generalist diet, or one of the undescribed deep-sea physonect species examined is predicted to be a fish specialist, which is congruent with its close phylogenetic relationship to other piscivorous physonects.
 While the limited dataset used here is informative for generating tentative hypotheses, the empirical dietary data are still scarce and insufficient to cast robust predictions.

### 2020-12-23 Organismal_paper/Other_Supplementary_Information/Rcode_ZooScripta.R

@@ -1,0 +1,825 @@
+#R code used for the analyses and figures in Damian-Serrano et al. Zoologica Scripta
+library(tidyverse)
+library(stringr)
+library(reshape2)
+## Biological
+library(Rphylip)
+library(arbutus)
+library(vegan)
+library(ape)
+library(phangorn)
+library(phytools)
+library(picante)
+library(geiger)
+library(phylobase)
+library(fields)
+library(phylosignal)
+library(geomorph)
+library(phylopath)
+library(phylolm)
+library(convevol)
+library(surface)
+## Graphics
+library(FactoMineR)
+library(factoextra)
+library(corrplot)
+library(BAMMtools)
+library(gridExtra)
+library(xtable)
+library(colorRamps)
+library(ggfortify)
+library(ggpubr)
+
+# Set paths to input data
+setwd("~/tentilla_morph/Organismal_paper/")
+
+#Load raw data
+read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_morphology_data.csv") -> numbers
+numbers$Species = as.character(numbers$Species)
+categorical <- read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_categorical_data.csv")[,-2]
+rownames(categorical) = categorical$Species
+
+#Correct species spellings
+numbers$Species[which(numbers$Species == "Agalma okeni")] <- "Agalma okenii"
+numbers$Species[which(numbers$Species == "Forskalia edwardsi")] <- "Forskalia edwardsii"
+numbers$Species[which(numbers$Species == "Rhizophysa eysenhardti")] <- "Rhizophysa eysenhardtii"
+
+#Merge Nanomias
+numbers$Species[which(numbers$Species == "Nanomia cara")] <- "Nanomia sp"
+numbers$Species[which(numbers$Species == "Nanomia bijuga")] <- "Nanomia sp"
+
+#Polish fields
+castnumbers = numbers
+castnumbers[castnumbers=="needDIC"] <- NA
+castnumbers[castnumbers=="needConfocal"] <- NA
+castnumbers[castnumbers=="needMature"] <- NA
+castnumbers[castnumbers=="needReslide"] <- NA
+castnumbers[castnumbers==-1] <- NA
[…]

### 2021-01-04 PNAS_PostReview/Manuscript_PostReview.Rmd
preparing final files for PNAS

@@
 ```{r tab1, echo=FALSE, out.width='100%'}
-knitr::include_graphics('~/tentilla_morph/Final_tables/table1.png')
+knitr::include_graphics('~/tentilla_morph/Final_tables/table1-PNAS.png')
 ```
@@
 ```{r tab2, echo=FALSE, out.width='60%'}
-knitr::include_graphics('~/tentilla_morph/Final_tables/table2.png')
+knitr::include_graphics('~/tentilla_morph/Final_tables/table2-PNAS.png')
 ```

### 2021-01-04 Supplement_forPNAS.Rmd
ADS final edits for submission
Fixed Forskalia rearrangement
preparing final files for PNAS

@@
 eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores.
-Personal observations on feeding (from SHDH, Anela Choy, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*.
+Other published observations on feeding were also included for *Resomia ornicephala* [@pugh2010three], *Erenna richardi*, *Erenna laciniata*, *Erenna sirena* [@pugh2016description], *Lychnagalma utricularia*, *Bargmannia amoena*, and *Apolemia rubriversa* [@choy2017deep].
 The feeding guilds declared in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group).
 These were selected to minimize the number of categories while keeping the most different types of prey separate.
+The gut content observations on *Forskalia* sp.
+were synonymized to an arbitrary *Forskalia* species on the tree (*F.
+tholoides*) for comparative analyses.
 

### 2021-01-04 Supplement_forPNASproofs.Rmd
preparing final files for PNAS

--- 2021-01-04 Supplement_forPNAS.Rmd
@@
 
-![\label{appendix2} Character definitions. ](Supplementary_materials/Online_appendices/PNGs/character_def.png){height=500px}
+![\label{appendix2} Character definitions. ](Supplementary_materials/Online_appendices/HD_Supplements/character_definitions-01.jpg){height=500px}
 
-![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/PNGs/MLunconstrained.png){height=300px}
+![\label{MLIqtree} Maximum likelihood IQTree inference, unconstrained.
+Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/HD_Supplements/MLunconstrained.jpg){height=300px}
 
@@
 (2018).
-](Supplementary_materials/Online_appendices/PNGs/constrain.png){height=400px}
+](Supplementary_materials/Online_appendices/HD_Supplements/constrain.jpg){height=400px}
 
-![\label{ML_constrained} Constrained IQTree ML inference. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/PNGs/MLconstrained.png){height=300px}
+![\label{ML_constrained} Constrained IQTree ML inference. Node labels are bootstrap support values.](Supplementary_materials/Online_appendices/HD_Supplements/MLconstrained.jpg){height=300px}
 
-![\label{Bayes_unconstrained} Unconstrained Bayesian topology inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/PNGs/BAYESunconstrained.png){height=300px}
+![\label{Bayes_unconstrained} Unconstrained Bayesian topology inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/HD_Supplements/BAYESunconstrained.jpg){height=300px}
 
-![\label{Bayes_constrained} Clade constrained Bayesian inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/PNGs/BayesConstrained.png){height=300px}
+![\label{Bayes_constrained} Clade constrained Bayesian inference in RevBayes (node labels are Bayesian posteriors).](Supplementary_materials/Online_appendices/HD_Supplements/BAYESconstrained.jpg){height=300px}
 
 ![\label{unconstrained_timetree} Unconstrained ultrametric Bayesian time tree branch length and topology inference in RevBayes (node labels are Bayesian posteriors).
-Arbitrary rooting.).](Supplementary_materials/Online_appendices/PNGs/Unconstrained timetree.png){height=400px}
+Arbitrary rooting.).](Supplementary_materials/Online_appendices/HD_Supplements/Unconstrained_timetree.jpg){height=400px}
 
@@
 Topology clamped to the Bayesian constrained topology inference in \@ref{Bayes_constrained}.
-Tree rooted using outgroup constraint.](Supplementary_materials/Online_appendices/PNGs/constrainedTimetree.png){height=500px}
+Tree rooted using outgroup constraint.](Supplementary_materials/Online_appendices/HD_Supplements/Constrained_timetree.jpg){height=500px}
 
@@
 Prediction posterior distribution heat map in main text Figure 6.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_guilds.png){height=500px}
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/HD_Supplements/DAPC_guilds.jpg){height=500px}
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_copepod.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/HD_Supplements/DAPC_copepods-01.jpg)
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_fish.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/HD_Supplements/DAPC_fish-01.jpg)
 
@@
 Grayscale heat map shows the posterior probability distribution of the predictions.
-Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/PNGs/DAPC_crustacean.png)
+Variable contribution (top quartile) calculated by the sum of the LDA variable loadings weighted by the eigenvalue of each LDA.](Supplementary_materials/Online_appendices/HD_Supplements/DAPC_crustacean-01.jpg)
 
@@
 Not all regimes are represented in all contrasts.
-Question marks represent computationally singular contrasts.](Supplementary_materials/Online_appendices/PNGs/VCV_regimes.png){height=600px}
+Question marks represent computationally singular contrasts.](PNAS_PostReview/NewVCVs/SimpleVCVs-01.jpg){height=600px}
 
-![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in S21 and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}
+![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in S21 and the whole tree covariance matrix (S21A).](PNAS_PostReview/NewVCVs/SubtractWholeVCVs-01.jpg){height=600px}
 
-![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in S21 and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)
+![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in S21 and the covariance matrices in their preceding regime, the large-crustacean specialist regime (S21C).](PNAS_PostReview/NewVCVs/SubtractLC_VCVs-01.jpg)
 

### 2021-01-04 Supplementary_materials/Dryad/R_Code.R

@@ -924,7 +924,6 @@ VCVshortlist <- VCVlist[which(lapply(VCVlist, class)=="evolvcv.lite")]
 bestmodel_number = lapply(VCVshortlist, function(y){lapply(y,function(x){x$AIC}) %>% unlist() %>% .[which(. == min(.))] %>% names()})
 bestmodel_number <- bestmodel_number %>% unlist() %>% as.vector() %>% str_extract("[0-9]") %>% as.numeric()
 bestmodel_descriptors <- list()
-names(bestmodel_descriptors)=names(VCVshortlist)
 for(i in 1:length(bestmodel_number)){
   VCVshortlist[[i]][bestmodel_number[i]][[1]] -> bestmodel_descriptors[[i]]
 }
@@ -932,7 +931,6 @@ names(bestmodel_descriptors)=names(VCVshortlist)
 
 ##R.simple VCV##
 generalmodel_descriptors <- list()
-names(generalmodel_descriptors)=names(VCVshortlist)
 for(i in 1:length(VCVshortlist)){
   VCVshortlist[[i]][1][[1]] -> generalmodel_descriptors[[i]]
 }
@@ -950,6 +948,25 @@ Simplejoin <- Simplejoin[,-1]
 Simplejoin = Simplejoin[match(sort(rownames(Simplejoin)), rownames(Simplejoin)), match(sort(names(Simplejoin)), names(Simplejoin))]
 #Simplejoin[is.na(Simplejoin)] <- 0
 corrplot(Simplejoin %>% as.matrix())
+
+##LARGE CRUSTACEAN SPECIFIC VCV##
+bestmodel_LargeCrustacean <- bestmodel_descriptors %>% lapply(function(x){x$R["Large crustacean"] %>% unlist() %>% matrix(nrow=2,ncol=2) %>% cov2cor() %>% as.data.frame()})
+for(i in 1:length(bestmodel_LargeCrustacean)){
+  rownames(bestmodel_LargeCrustacean[[i]])<- names(bestmodel_LargeCrustacean)[i] %>% str_split(" ") %>% unlist()
+  names(bestmodel_LargeCrustacean[[i]])<- names(bestmodel_LargeCrustacean)[i] %>% str_split(" ") %>% unlist()
+  bestmodel_LargeCrustacean[[i]] %<>% mutate(parameter=rownames(.))
+}
[…]

### 2021-03-10 Organismal_paper/Organismal_supplement.Rmd
repo uptodate
started post review process at IOB

@@
 
-![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/tentillaPresenceSIM.png)
+![\label{SIMMAPtentilla} SIMMAP Tentilla presence/absence.](~/tentilla_morph/Organismal_paper/IOB-PostReview/raw_figures/SM1_SIMMAPtentilla-01.png)
 
@@
 
-![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoaband phenotype presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)
+![\label{SIMMAP_Coiled} SIMMAP Coiled cnidoband phenotype presence/absence.](~/tentilla_morph/SysBio_Submission/Post-submission modifications/Supplementary_materials/Online_appendices/PNGs/Coiled_Sim.png)
 
@@
 ![\label{appendix2} Character definitions. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/character_def.png){height=500px}
-
-![\label{specimens} Specimen catalog. ](~/tentilla_morph/Supplementary_materials/Online_appendices/PNGs/slide_catalog_numbers.png){height=2000px}

### 2021-03-10 Organismal_paper/Other_Supplementary_Information/Rcode_ZooScripta.R

@@ -36,7 +36,7 @@ setwd("~/tentilla_morph/Organismal_paper/")
 #Load raw data
 read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_morphology_data.csv") -> numbers
 numbers$Species = as.character(numbers$Species)
-categorical <- read.csv("~/tentilla_morph/Supplementary_materials/Dryad/raw_categorical_data.csv")[,-2]
+categorical <- read.csv("~/tentilla_morph/Organismal_paper/IOB-PostReview/raw_figures/CategoricalCharacters.csv")[,-2]
 rownames(categorical) = categorical$Species
 
 #Correct species spellings
@@ -225,7 +225,7 @@ names(GC)<-c("species", "character")
 #write.csv(GC, "gutcontentliteraturereview.csv")
 GC = split(GC,GC$character)
 nrowGC = purrr::map(GC,nrow) %>% as.numeric()
-GC = GC[which(nrowGC>2)]
+GC = GC[which(nrowGC>0)]
 GC = purrr::map(GC,unique)
 diet= matrix(ncol=length(GC),nrow=length(unique(castlogs$Species))) %>% as.data.frame()
 names(diet) = names(GC)
@@ -238,6 +238,7 @@ for(E in GC){
 }
 diet[is.na(diet)] <- 0
 diet = diet[which(rowSums(diet)>0),which(colSums(diet)<nrow(diet))]
+diet=diet[,-c(3,7,14:17)]
 
 #Add personal observations of the authors
 cladeB <- matrix(rep(c(0,1,0,0,0,0,0,0,0,0,0),3),nrow=11, ncol = 3) %>% t() %>% as.data.frame()
@@ -297,10 +298,6 @@ temp[is.na(temp)] <- 0
 fullraw_nozeroes <- aggregate(. ~ Species, data=temp, FUN = mean)
 rownames(fullraw_nozeroes) <- fullraw_nozeroes$Species
 
-
-hypdiet = c("Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Small crustacean", "Large crustacean", "Mixed", "Mixed", "Mixed", "Large crustacean", "Large crustacean", "Mixed", "Small crustacean", "Large crustacean", "Fish", "Fish", "Fish", "Large crustacean", "Gelatinous", "Fish", "Fish", "Fish")
-names(hypdiet) = dprunedTree$tip.label
-
 #hypdiet but for all species not only those in tree
[…]
